% Flavor catalog per-process template.
% process_id: E002
% family: edm_neutrino
% owner_agent_id: PKA-E002
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: E002.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{E002: Muon electric dipole moment}

\subsection*{Process}
\textbf{Standard notation:} \(d_\mu\).  This entry covers the flavor-diagonal
CP-odd electric dipole moment of the muon, cataloged in the
\texttt{edm\_neutrino} family.  It is an EDM-adjacent lepton-sector process,
not a charged-lepton-flavor-violating decay and not a quark \(\Delta F=2\)
observable.

\subsection*{PDG / equivalent value(s)}
PDG Live 2026 (\texttt{PDG2026:MuonEDM}) lists the canonical direct
experimental bound as
\[
  |d_\mu| < 1.8\times10^{-19}\ e\,\mathrm{cm}
  \qquad (95\%~\mathrm{CL}),
\]
from the Bennett et al. BNL E821 storage-ring analysis; see
\texttt{flavor\_catalog/references/E002/pdg2026\_muon\_edm\_datablock.txt}.
The same PDG datablock records the combined result as
\((0.0\pm0.9)\times10^{-19}\ e\,\mathrm{cm}\).  The primary arXiv abstract
(\texttt{Bennett:MuonEDM2009}) reports
\(d_\mu=-0.1(0.9)\times10^{-19}\ e\,\mathrm{cm}\) and quotes
\(|d_\mu|<1.9\times10^{-19}\ e\,\mathrm{cm}\) at \(95\%\) CL.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
A nonzero \(d_\mu\) probes the imaginary part of the flavor-diagonal muon
dipole operator, schematically
\(\bar\mu\sigma_{\alpha\beta}\gamma_5\mu F^{\alpha\beta}\).  In warped
lepton extensions, anarchic charged-lepton and neutrino Yukawa structures can
generate such dipoles through loop matching involving KK leptons, Higgs
dynamics, or gauge-sector phases.  The process therefore diagnoses CP
alignment in the muon sector, complementary to \(\mu\to e\gamma\), but it does
not directly constrain the existing quark-only scan.

\subsection*{Post-2008 developments}
Relative to the 2008 CFW warped-flavor reference point
(\texttt{CsakiFalkowskiWeiler:RSFlavor2008}), the key direct experimental
development is the BNL E821 publication in 2009.  That analysis used muon
\(g-2\) storage-ring spin-precession data and remains the basis of the PDG
direct limit.  The major post-2008 prospective change is the dedicated PSI
muEDM program.  The 2021 PSI letter of intent
(\texttt{Adelmann:MuonEDMPSI2021}) proposes a frozen-spin search with
\(p=125~\mathrm{MeV}/c\), \(|B|=3~\mathrm{T}\), a rest-frame electric field
of \(1~\mathrm{GV/m}\), and an expected sensitivity
\(\sigma(d_\mu)\leq6\times10^{-23}\ e\,\mathrm{cm}\).  A 2024 muEDM status
proceeding (\texttt{Renga:MuonEDMStatus2024}) describes a first phase aimed
at demonstrating feasibility by 2026, with an ultimate goal of improving the
sensitivity by a factor of \(100\) by the early 2030s.

\subsection*{Constraint validity and model dependence}
The PDG number is a robust direct storage-ring bound on a static muon EDM.
Its interpretation in RS is model-dependent: a live constraint requires the
lepton-sector CP phases, the dipole matching scale, and the treatment of
SMEFT/low-energy running to be fixed.  The PSI entries are projections and
should be treated as roadmap information, not current exclusions.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Focused greps for \texttt{muEDM}, \texttt{muon.?EDM},
\texttt{muon electric dipole}, \texttt{d\_mu}, and \texttt{dmu} over
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/} found no muon-EDM
implementation.  The nearby dipole code is the off-diagonal
\(\mu\to e\gamma\) helper in \texttt{flavorConstraints/muToEGamma.py:3},
\texttt{:21}, and \texttt{:81}, with the MEG II branching-fraction default at
\texttt{scanParams/scan.py:33}; that is a different observable.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production implementation needs a new flavor-diagonal
CP-odd lepton dipole observable, loop matching from the lepton/KK sector, and
likely SMEFT-to-low-energy running.  The existing \(\Delta F=2\) basis and the
\(\mu\to e\gamma\) NDA helper do not calculate \(d_\mu\).

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026:MuonEDM}, \texttt{Bennett:MuonEDM2009},
\texttt{Adelmann:MuonEDMPSI2021}, \texttt{Renga:MuonEDMStatus2024}, and
\texttt{CsakiFalkowskiWeiler:RSFlavor2008}.
