% Flavor catalog per-process template.
% process_id: E006
% family: edm_neutrino
% owner_agent_id: PKA-E006
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: E006.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{E006: Mercury-199 electric dipole moment}

\subsection*{Process}
\textbf{Standard notation:} \(d_{\mathrm{Hg}}\), for neutral
\(^{199}\mathrm{Hg}\).  This entry covers the permanent EDM of the
diamagnetic \(^{199}\mathrm{Hg}\) atom, cataloged in the
\texttt{edm\_neutrino} family as a hadronic/nuclear CP probe.  It is a
flavor-diagonal observable, but its interpretation constrains CP-odd quark,
gluon, semileptonic, and nuclear Schiff-moment sources.

\subsection*{PDG / equivalent value(s)}
The canonical direct experimental limit is the Graner et al. 2016
\(^{199}\mathrm{Hg}\) result (\texttt{Graner:HgEDM2016}):
\[
  |d_{\mathrm{Hg}}| < 7.4\times 10^{-30}\ e\,\mathrm{cm}
  \qquad (95\%~\mathrm{C.L.}).
\]
The local snapshot
\texttt{flavor\_catalog/references/E006/graner2016\_arxiv1601\_04339.txt}
also records the arXiv-v4 central measurement and uncertainties; because the
PKA flagged the erratum cross-check for the signed central value, the direct
limit is the catalog value.  PDG Live 2026 does not expose a standalone
Hg-atom datablock here, but the neutron and proton EDM datablocks cite the
same Hg measurement for theory-derived nucleon limits.  In the neutron
datablock, PDG lists Graner 2016 as a \(^{199}\mathrm{Hg}\)-plus-theory row,
\(<0.16\) in units of \(10^{-25}\ e\,\mathrm{cm}\) at \(95\%\) CL, and
Sahoo 2017 as \(<0.22\) in the same units and confidence level
(\texttt{PDG2026:NeutronEDMHgCrossref}); see
\texttt{flavor\_catalog/references/E006/pdg2026\_neutron\_edm\_hg\_crossref.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Warped or composite anarchic flavor models generically contain new CP phases.
Loop matching can generate quark EDMs, quark chromo-EDMs, the Weinberg
three-gluon operator, and semileptonic CP-odd operators.  In a diamagnetic
closed-shell atom such as \(^{199}\mathrm{Hg}\), the dominant hadronic
sensitivity is usually phrased through the nuclear Schiff moment and
CP-odd pion-nucleon interactions, rather than through a simple elementary
fermion EDM.  The observable is therefore complementary to the neutron EDM:
it probes a different linear combination of CP-odd low-energy operators and
nuclear matrix elements.

\subsection*{Post-2008 developments}
Relative to the 2008 CFW warped-flavor baseline
(\texttt{CsakiFalkowskiWeiler:RSFlavor2008}), the main experimental update is
the 2016 Washington \(^{199}\mathrm{Hg}\) measurement
(\texttt{Graner:HgEDM2016}), which improved the previous Hg bound by a factor
of \(4\) and remains the standard diamagnetic-atom benchmark.  The post-2008
theory update represented here by Sahoo 2017
(\texttt{Sahoo:HgEDMTheory2017}) combines the Hg atom limit with relativistic
atomic calculations and quotes derived limits including
\(d_n<2.2\times10^{-26}\ |e|\,\mathrm{cm}\),
\(d_p<2.1\times10^{-25}\ |e|\,\mathrm{cm}\),
\(|\bar\theta|<1.1\times10^{-10}\), and
\(|\tilde d_u-\tilde d_d|<5.5\times10^{-27}\ |e|\,\mathrm{cm}\)
(\texttt{Sahoo:HgEDMTheory2017}).

\subsection*{Constraint validity and model dependence}
The experimental atom-EDM bound is robust as a null search for a
\(P\)- and \(T\)-violating energy shift.  Translating it into RS parameters is
model-dependent: the result depends on the chosen CP-odd operator basis,
QCD running and thresholds, atomic many-body coefficients, nuclear Schiff
moments, hadronic matrix elements, and possible cancellations among sources.
It should be treated as an EDM-adjacent loop/nuclear-translation constraint,
not as a direct \(\Delta F=2\) bound in the current quark scan.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps and a focused search for
\texttt{Hg}, \texttt{mercury}, \texttt{199Hg}, \texttt{d\_Hg},
\texttt{Schiff}, \texttt{diamagnetic}, \texttt{chromo-EDM},
\texttt{Weinberg}, and generic \texttt{EDM}/\texttt{dipole} terms over
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/} found no
\(^{199}\mathrm{Hg}\) EDM implementation.  The only nearby dipole code is the
off-diagonal \(\mu\to e\gamma\) helper in
\texttt{flavorConstraints/muToEGamma.py:3}, \texttt{:21}, and \texttt{:81}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A live constraint would require new CP-odd quark/gluon and
semileptonic operator matching, RG running to hadronic scales, and an
atomic/nuclear translation layer for \(^{199}\mathrm{Hg}\).  The existing
SLL/SLR/VLL/VRR/LR \(\Delta F=2\) basis and the \(\mu\to e\gamma\) NDA helper
do not cover this observable.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{Graner:HgEDM2016}, \texttt{PDG2026:NeutronEDMHgCrossref},
\texttt{Sahoo:HgEDMTheory2017}, and
\texttt{CsakiFalkowskiWeiler:RSFlavor2008}.
