\documentclass[11pt]{article}

% ============================================================
%  Physics + status summary for external collaborators.
%  Self-contained: assumes general BSM/flavour background,
%  zero knowledge of any specific implementation.
% ============================================================

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{mathtools}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

% lightweight "callout" box
\colorlet{shadecolor}{gray!12}
\newenvironment{callout}[1]{%
  \par\medskip\begin{shaded}\noindent\textbf{#1}\par\smallskip}{\end{shaded}\medskip}

\newcommand{\MKK}{M_{\mathrm{KK}}}
\newcommand{\LIR}{\Lambda_{\mathrm{IR}}}
\newcommand{\epsK}{\varepsilon_K}
\newcommand{\dmd}{\Delta m_d}
\newcommand{\dms}{\Delta m_s}
\newcommand{\phis}{\phi_s}
\newcommand{\eps}{\varepsilon}
\newcommand{\vev}{v}
\newcommand{\cwsq}{c_W^2}

\setlist{nosep}

\title{\bf A Warped Extra Dimension for Flavour and Electroweak Physics\\[3pt]
\large Physics logic and project status --- a summary for external collaborators}
\author{Project summary note}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
We summarise, for an external reader with a general BSM/flavour background, the
physics of a Randall--Sundrum (RS) warped-extra-dimension model of fermion masses
and mixings, the observables we require it to reproduce, and the precision
constraints we impose. The central claim of the framework is that the observed
hierarchies in charged-fermion masses and CKM/PMNS mixing arise from
\emph{geometry} --- the localisation of bulk fermions in the warped fifth
dimension --- rather than from hierarchical five-dimensional couplings, which are
taken anarchic and $\mathcal{O}(1)$. We then give an honest, item-by-item account
of how each constraint is treated, distinguishing the observables we compute
with full in-repo matching paths (the main $\Delta F=2$ meson-mixing set and the
$Z\to b\bar b$ vertex) from those handled as approximate or framework-dependent
predictions (the lepton-flavour-violating dipole, the oblique parameters $S,T,U$,
and the direct collider bounds), and close with the project status and open items.
\end{abstract}

% ====================================================================
\section{The model in one section}
% ====================================================================

The spacetime is a slice of five-dimensional anti-de~Sitter space (AdS$_5$)
bounded by two branes,
\begin{equation}
ds^2 = e^{-2k|y|}\,\eta_{\mu\nu}\,dx^\mu dx^\nu - dy^2,
\qquad 0 \le y \le \pi r_c,
\end{equation}
with a UV (Planck-scale) brane at $y=0$ and an IR (TeV-scale) brane at
$y=\pi r_c$. The exponential warp factor $\eps = e^{-k\pi r_c}\sim 10^{-15}$
generates the Planck/electroweak hierarchy from an $\mathcal{O}(1)$ radius. A
single large dimensionless number,
\begin{equation}
L \equiv k\pi r_c = \ln(1/\eps) = \ln(M_{\rm Pl}/\mathrm{TeV}) \approx 35,
\end{equation}
controls almost everything below.

\paragraph{Geometric flavour.} The Higgs is localised near the IR brane, and each
Standard-Model (SM) fermion is the zero mode of a bulk field whose profile is set
by a single dimensionless bulk-mass parameter $c$ (in units of $k$). For $c>1/2$
the zero mode is repelled from the IR brane and its value there is exponentially
small; for $c<1/2$ it is $\mathcal{O}(1)$.
The 4D Yukawa coupling of a given fermion is the product of the IR-brane
overlaps (``$f$-factors'') of the two chiralities times the anarchic
five-dimensional Yukawa,
\begin{equation}
y^{\rm 4D}_{ij} \;\sim\; f_{Q_i}\, Y^{\rm 5D}_{ij}\, f_{u_j},
\qquad
f^2(c) = \frac{\tfrac12 - c}{1 - \eps^{\,1-2c}},
\end{equation}
with all $Y^{\rm 5D}_{ij}=\mathcal{O}(1)$ and generic in phase. Because the
$f$-factors span many orders of magnitude as $c$ is dialled across $1/2$, the
\emph{products} $f_{Q_i}f_{u_j}$ are strongly hierarchical even though every
fundamental coupling is of order unity. This reproduces the charged-fermion mass
hierarchy and, through the same hierarchical left-handed $f$-factors, the small
CKM mixing angles --- mixing among generation $i$ and $j$ scales as
$f_{Q_i}/f_{Q_j}$. The complex anarchic Yukawas supply the CKM CP phase with no
extra ingredient.

\paragraph{RS-GIM alignment.} The same localisation that explains the masses
automatically suppresses flavour-changing neutral currents. Kaluza--Klein (KK)
gauge bosons couple to a fermion in proportion to its IR overlap, so their
flavour-violating couplings are controlled by the \emph{same} small $f$-factors
that already suppress the light-quark masses. This built-in alignment --- the
``RS-GIM'' mechanism --- means new-physics flavour amplitudes are not generic at
the $1/\MKK^2$ scale but carry an extra mass-weighted suppression. It is partial,
not complete: a small, generically complex misalignment survives, and that
residue is what the meson-mixing constraints of Section~\ref{sec:constraints}
probe.

\paragraph{Neutrinos.} Light neutrino masses are generated by a UV-localised
Majorana mass for right-handed singlet neutrinos, giving a Type-I seesaw. In the
charged-lepton mass basis the PMNS matrix is carried by the neutrino Yukawa,
$Y_N \to V_{\rm PMNS}\,\mathrm{diag}(Y_{N_1},Y_{N_2},Y_{N_3})$, and the seesaw
fixes the overall neutrino-mass scale through the right-handed bulk-mass profile
and the UV Majorana scale.

% ====================================================================
\section{What we require the model to reproduce}
% ====================================================================

The target observables, treated as data the model must accommodate, are:
\begin{itemize}[leftmargin=1.4em]
\item the three charged-lepton masses and the six quark masses (PDG central
values, run to a common scale);
\item the CKM matrix --- all four parameters, including the CP-violating phase
(equivalently the Jarlskog invariant);
\item in the lepton sector, the PMNS mixing angles and the two measured neutrino
mass-squared splittings $\Delta m^2_{21}$ and $\Delta m^2_{31}$, with the sum of
neutrino masses kept below the cosmological bound $\sum m_\nu \lesssim 0.082$~eV.
\end{itemize}
A viable parameter point is one whose anarchic $\mathcal{O}(1)$ five-dimensional
couplings, after geometric localisation, reproduce these to within their
uncertainties while keeping all couplings perturbative.

% ====================================================================
\section{The constraints we impose}
\label{sec:constraints}
% ====================================================================

Each subsection states the physics and our treatment status
(\emph{rigorous} vs.\ \emph{proxy}).

\subsection{$\Delta F=2$ meson mixing: the RS flavour/CP problem}

\emph{Status: rigorous for the implemented short-distance $K$, $B$, and
$D$-mixing amplitude paths; the $D$ CP-violation companion is a flagged proxy.}

A heavy KK gluon couples to both quark chiralities, so integrating it out at
tree level generates the relevant vector and left--right $\Delta F=2$ operators
for this benchmark --- not only the vector left--left operator that the SM box
already produces, but also chirality-flipping left--right operators. The
left--right operators are
\emph{doubly enhanced}: by a large chiral factor in the hadronic matrix element
(for the kaon, $(m_K/(m_s+m_d))^2 \approx 26$; this number is scale- and
scheme-dependent, and is sometimes quoted as a smaller matrix-element ratio
times a separate RG factor) and by QCD renormalisation-group
running between the multi-TeV matching scale and the few-GeV hadronic scale.
Our pipeline builds the genuine Wilson coefficients from the localisation
profiles, runs them, contracts with lattice or documented in-repo matrix
elements, and vetoes any point exceeding an uncertainty-aware budget. The set
comprises:
\begin{itemize}[leftmargin=1.4em]
\item \textbf{$\epsK$} (the CP-violating, imaginary part of $K^0$--$\bar K^0$
mixing): the single sharpest constraint. Because it probes the imaginary part of
the chirally- and RG-enhanced left--right operator, carrying a generic
$\mathcal{O}(1)$ phase with no extra GIM protection, it is roughly an order of
magnitude tighter than the real part. In an anarchic warped model it historically
forces the lightest KK gluon above $\sim 20$~TeV. This is ``the RS flavour/CP
problem.''
\item \textbf{$D^0$--$\bar D^0$ mixing} (up-sector magnitude), \textbf{$\dmd$}
and \textbf{$\dms$} ($B_d$ and $B_s$ mass splittings), and the \textbf{$B_s$
mixing CP phase $\phis$}. The $B_{d,s}$ channels are live rigorous constraints;
the $D$-mixing magnitude veto is rigorous but deliberately conservative because
the SM long-distance charm amplitude is not subtracted. The separate $D$
CP-violation entry uses a one-dimensional CP-odd proxy until the full HFLAV
$(|q/p|,\phi_D)$ likelihood, $\Gamma_{12}$, and the SM long-distance phase are
implemented.
\end{itemize}

\subsection{$\mu\to e\gamma$: the lepton-flavour-violating dipole}

\emph{Status: live HARD constraint with a rigorous experimental limit, but an
NDA lepton-MFV prediction rather than a finite KK-loop calculation.}

With leptons and the photon in the bulk and a brane Higgs, KK exchange generates
a chirality-flipping magnetic-dipole operator
$\bar e\,\sigma^{\mu\nu}\mu\,F_{\mu\nu}$ mediating $\mu\to e\gamma$. The
prediction is sharply model-dependent on the lepton-flavour structure, so we
adopt a lepton minimal-flavour-violation framework in which the dipole's flavour
violation is tied to the neutrino Yukawa and the seesaw. The implemented
constraint is a validated NDA formula,
$\mathrm{BR}\propto |(\bar Y_N\bar Y_N^\dagger)_{e\mu}|^2(3~\mathrm{TeV}/\MKK)^4$;
a fully rigorous upgrade would replace that prefactor with the finite bulk-Higgs
KK-loop calculation. We veto against the latest experimental limit,
$\mathrm{BR}(\mu\to e\gamma) < 1.5\times10^{-13}$.
Because this constraint lives entirely in the lepton sector, it does not enter
the quark-sector scans.

\subsection{$Z\to b\bar b$: the non-universal bottom coupling}

\emph{Status: rigorous for the minimal-RS tree path; custodial protection is a
documented proxy relaxation.}

RS is not a universal theory: the IR-localised third-generation doublet
$(t_L,b_L)$ couples most strongly to the KK gauge tower, so its $Z$ coupling is
distorted the most. This shows up as a shift in the left-handed bottom coupling
$g_L^b$, probed by the $Z$-pole pseudo-observables $R_b$ (the $b\bar b$ branching
fraction, mostly $g_L^b$) and $A_b$ (the asymmetry, sensitive to
$g_L^b - g_R^b$). This is a genuine vertex correction, not an oblique effect, and
cannot be folded into $S,T,U$. In the minimal model it is the \emph{dominant
electroweak constraint}, setting a rigorous floor of $\sim 25$--$30$~TeV in
physical first-KK-gauge mass.

\subsection{Oblique parameters $S$, $T$, $U$}

\emph{Status: leading-order parametric PROXY --- not a spectral computation.}

The Peskin--Takeuchi parameters package the universal new-physics shifts to the
$W$/$Z$ self-energies. $T$ measures custodial-isospin breaking; $S$ measures the
overall size of the new electroweak sector. In RS, the IR-brane Higgs mixes the
flat gauge zero modes with the IR-localised KK tower, giving
$\{S,T\}\sim \vev^2/\MKK^2$. The danger is the coefficient of $T$: with the
minimal (SM) bulk gauge group there is no custodial symmetry, and the gauge
normalisation over the warped volume produces a factor of $L\approx 35$,
\begin{equation}
\Delta T_{\rm minimal} \simeq \frac{\pi L}{2\,\cwsq}\,\frac{\vev^2}{\MKK^2}
\;\approx\; 71.5\,\frac{\vev^2}{\MKK^2},
\qquad \vev = 246~\text{GeV},
\end{equation}
where here $\vev = 246$~GeV is the full Higgs-doublet vacuum expectation value
(the convention of the literature this estimate is drawn from; the coefficient
would be $\approx 143$ in the $\vev = 174 = 246/\sqrt2$~GeV normalisation). With
$\vev = 246$~GeV, even at $\MKK = 3$~TeV one finds $\Delta T \approx 0.5$, a
$\sim 7\sigma$ excursion.
\textbf{Our treatment is honest about being a proxy:} we use the
closed-form parametric scalings above (with $\Delta S = c_S\,\vev^2/\MKK^2$,
$c_S=\mathcal{O}(\text{tens})$, $U\equiv 0$) and test against the PDG global
$(S,T)$ ellipse. The \emph{experimental} side is rigorous; the \emph{prediction}
is leading-order and omits the higher-derivative oblique parameters ($W,Y$) that
are not negligible for light KK modes. A rigorous treatment would replace the
parametric coefficients with a per-point spectral/loop computation.

\subsection{Direct collider bounds on KK masses}

\emph{Status: PROXY recasts (near-flat mass floor).}

LHC resonance searches (a colour-octet KK gluon decaying to $t\bar t$, a KK
graviton in diboson/diphoton, KK electroweak vectors, and pair-produced
vector-like quark partners in the custodial version) each report a mass-exclusion
edge; together they form a near-flat direct-search floor of a few TeV. We do not
run full collider recasts: each bound is interpreted as a mass-exclusion proxy
that asks whether the scan's KK scale clears the catalogued benchmark edge.
Because the indirect flavour bounds already push $\MKK$ well above these edges,
the direct floors essentially never bind once the indirect constraints are on.

% ====================================================================
\section{Minimal vs.\ custodial: where the KK scale floor sits}
% ====================================================================

In the \textbf{minimal} model (SM bulk gauge group), the volume-enhanced oblique
$T$ and the $Z\to b\bar b$ vertex are the killers: together they force the
lightest KK gauge scale to $\sim 25$--$30$~TeV in physical mass (equivalently
$\sim 10$--$12$~TeV in IR-scale $\LIR$ units, the two differing by the first KK
gauge root $x_1\approx 2.45$, close to the first zero of the Bessel function
$J_0$ at $2.405$).

Enlarging the bulk gauge group to the standard \textbf{custodial} structure,
$SU(2)_L\times SU(2)_R\times U(1)_X$ with a discrete left--right parity
$P_{LR}$, cures these. The continuous $SU(2)_R$ removes the volume enhancement of
$T$ (the coefficient $\pi L/2\cwsq$ flips to $-\pi/4\cwsq L$, a suppression by
$\sim 1/(2L^2)\sim 4\times10^{-4}$), and the discrete $P_{LR}$ separately
protects the $Z\bar b_L b_L$ vertex. In the paired quark-sector scans, with their
particular flavour-structure choices, neutralising $T$ and $Z b_L$ moves the
rigorous floor onto the $\Delta F=2$ flavour set at $\sim 2$--$3$~TeV. When the
proxy oblique-$S$ (now the binding oblique number, unprotected) and the proxy
collider edges are folded in, the \emph{inclusive} floor rises to $\sim 7$~TeV.

\begin{callout}{The crucial honest point.}
Custodial protection helps the \emph{electroweak} bounds only. It does
\emph{nothing} for the flavour/CP problem: the KK-gluon $\Delta F=2$ amplitudes,
and $\epsK$ in particular, are untouched by $SU(2)_R$ or $P_{LR}$. The
$\sim 20$~TeV anarchic $\epsK$ bound therefore remains the separate, hardest
constraint, addressable only by flavour alignment, larger bulk masses, or an
imposed flavour symmetry --- not by the custodial cure.
\end{callout}

\begin{table}[t]
\centering
\small
\begin{tabular}{@{}p{4.0cm} p{4.4cm} c p{2.9cm}@{}}
\toprule
\textbf{Constraint} & \textbf{Physics target} & \textbf{Treatment} & \textbf{Role} \\
\midrule
$\epsK$ (kaon CP) & Im part of $K$--$\bar K$ mixing & rigorous & generic anarchic floor ($\sim 20$~TeV) \\
$\dmd,\ \dms,\ \phis$ & $B_{d,s}$ mixing + CP phase & rigorous & scan flavour floor (few TeV) \\
$D^0$--$\bar D^0$ & up-sector magnitude; CP proxy separate & rigorous / partial & alignment complement \\
$\mu\to e\gamma$ & LFV magnetic dipole & NDA LMFV & lepton sector; seesaw-tied \\
$Z\to b\bar b$ ($R_b,A_b$) & non-universal $g_{L,R}^b$ & rigorous & dominant EW (minimal) \\
$S,T,U$ (oblique) & $W$/$Z$ self-energies & \textbf{proxy} & $T$ kills minimal model \\
Direct KK searches & on-shell LHC resonances & \textbf{proxy} & near-flat floor (few TeV) \\
\bottomrule
\end{tabular}
\caption{Constraint catalogue: physics target, treatment status, and role.}
\end{table}

% ====================================================================
\section{Where we are: project status}
% ====================================================================

\begin{itemize}[leftmargin=1.4em]
\item \textbf{Quark-sector scans completed.} Parameter scans over the quark
sector are done for both the minimal and custodial models, run as a paired
comparison. These reproduce the quark masses and the CKM matrix (including its
CP phase) and apply the $\Delta F=2$ set, $Z\to b\bar b$, and the oblique and
collider proxies. The quoted few-TeV custodial scan floor is the result after the
scan's flavour-structure choices; it should not be read as erasing the separate
generic anarchic $\epsK$ estimate of order $20$~TeV.
\item \textbf{Lepton-sector LFV implemented, not yet in production scans.} The
$\mu\to e\gamma$ constraint is built and validated against the experimental
limit, but is not yet wired into the production parameter scans; the lepton-sector
fit (PMNS, neutrino splittings) is follow-up scope.
\item \textbf{Oblique and collider bounds are leading-order proxies.} The
$S,T,U$ prediction is the closed-form parametric scaling described above, and the
collider bounds are mass-exclusion recasts. Both are flagged as approximate and
await a full spectral/loop (oblique) and proper recast (collider) treatment.
\item \textbf{Custodial one-loop top-partner contributions computed, not switched
on.} The finite, calculable one-loop corrections from the light top-partner KK
fermions (a positive $\Delta T$ from the top-singlet partner, correlated with a
$\delta g_L^b$ shift of opposite sign) are derived and available, but the
custodial scans currently run at tree level with the loop deferred.
\end{itemize}

\paragraph{Rigorous vs.\ approximate, in one line.} The main $K/B/D$ mixing
amplitude paths and the minimal-RS $Z\to b\bar b$ tree path are rigorous in the
repo's current matching conventions; $D$-mixing CP violation is partial,
$\mu\to e\gamma$ is an NDA LMFV estimate, custodial $Zb_L$ protection is a proxy
relaxation, and the oblique $S,T,U$ and collider bounds are leading-order
proxies. The bottom line is robust to this split: generic anarchic flavour,
especially $\epsK$, is the hardest physics problem, while the paired custodial
scan shows how much the floor moves once a particular flavour structure is
chosen.

\paragraph{Open items / caveats.}
\begin{itemize}[leftmargin=1.4em]
\item Replace the oblique $S,T,U$ proxy with a per-point spectral computation,
including the higher-derivative ($W,Y$) parameters relevant for light KK modes.
\item Replace the collider mass-exclusion proxies with genuine cross-section
recasts.
\item Switch on the custodial one-loop top-partner contributions in the scans;
re-derive the custodial floors with the loop included.
\item Bring the lepton-sector LFV and the PMNS/neutrino-splitting fit into the
production scans.
\item Note the two distinct conventions for ``KK mass'' (physical first KK mass
vs.\ the IR scale $\LIR$), which differ by the first KK gauge root
$x_1\approx 2.45$ (near the first $J_0$ zero, $2.405$); all quoted floors
state which is meant.
\end{itemize}

% ====================================================================
\section*{Reading pointers}
\addcontentsline{toc}{section}{Reading pointers}
% ====================================================================

Warped flavour and RS-GIM: Gherghetta--Pomarol (hep-ph/0003129),
Grossman--Neubert (hep-ph/9912408), Agashe--Contino--Pomarol (hep-ph/0412089).
Anarchic $\Delta F=2$ and the $\epsK$ bound: Csaki--Falkowski--Weiler
(arXiv:0804.1954), Blanke et al.\ (arXiv:0809.1073). Charged-lepton flavour
violation: Agashe--Blechman--Petriello (hep-ph/0606021). Custodial cure of $T$:
Agashe--Delgado--May--Sundrum (hep-ph/0308036); $P_{LR}$ protection of
$Z\bar b_L b_L$: Agashe--Contino--Da~Rold--Pomarol (hep-ph/0605341); one-loop
top-partner analysis: Carena--Ponton--Santiago--Wagner (hep-ph/0701055). An
alternative geometry lowering the floor without custodial symmetry:
Cabrer--von~Gersdorff--Quir\'os (arXiv:1103.1388).

\end{document}
