% Flavor catalog per-process template.
% process_id: K002
% family: kaon
% owner_agent_id: PKA-K002
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K002.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(\Delta m_K\): \(K_L-K_S\) mass difference}{Delta m K: KL-KS mass difference}}

\subsection*{Process}
\textbf{Standard notation:} \(\Delta m_K \equiv m_{K_L}-m_{K_S}\).
This kaon-family entry covers the CP-even magnitude of neutral-kaon mixing,
separate from the CP-violating \(\varepsilon_K\) entry.  The process id is
\(K002\).

\subsection*{PDG / equivalent value(s)}
The canonical PDG-sidecar value is the 2026 pdgLive fit assuming CPT,
\[
  \Delta m_K = (0.5293\pm0.0009)\times 10^{10}\,\hbar\,{\rm s}^{-1},
\]
with the quoted PDG uncertainty including a scale factor of \(1.3\).  The same
snapshot gives the companion fit not assuming CPT,
\((0.5289\pm0.0010)\times 10^{10}\,\hbar\,{\rm s}^{-1}\).  Both values trace to
\texttt{flavor\_catalog/references/K002/pdg\_live\_S013D\_20260516.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic warped flavor models, tree-level exchange of KK gluons generates
\(\Delta S=2\) four-quark operators after rotating to the quark-mass basis.
\(\Delta m_K\) constrains the real part of the new \(K^0-\bar K^0\) mixing
amplitude, while \(\varepsilon_K\) constrains its imaginary part.  The same
VLL, VRR, SLL/SLR, and LR operator structures used for the repo's neutral-meson
mixing lane apply here, and the LR matrix elements remain chirally enhanced.
The important physics caveat is that the measured mass splitting contains a
large long-distance Standard Model component, so the catalog should treat
\(\Delta m_K\) as a conservative magnitude bound unless a controlled SM
subtraction is supplied.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 baseline, the experimental side was updated by
KTeV's final neutral-kaon analysis, which the PDG fit still uses.  The more
important post-2008 shift is theoretical: lattice calculations began attacking
the long-distance contribution directly.  Christ, Izubuchi, Sachrajda, Soni,
and Yu developed the long-distance method in 2013; Bai et al. then reported a
first complete lattice calculation in 2014, obtaining
\(\Delta M_K=3.19(41)(96)\times10^{-12}\,{\rm MeV}\) at heavier-than-physical
masses.  Later physical-quark-mass studies reported a statistical uncertainty
approaching \(9\%\) but highlighted remaining systematics.  For BSM
interpretation, FLAG Review 2024 and the 2024 physical-mass BSM kaon-mixing
matrix-element calculation update the \(B_K\) and additional four BSM bag-input
landscape used to translate Wilson coefficients into matrix elements.

\subsection*{Constraint validity and model dependence}
The experimental number is precise, but \(\Delta m_K\) is long-distance
limited as a new-physics constraint.  A conservative RS scan can require the
absolute new-physics contribution not to exceed the measured splitting, or use
only a fraction of it by policy.  A sharper bound would require specifying the
short-distance charm-loop treatment, the long-distance lattice input, and the
CPT-fit convention.  This entry is therefore robust as a conservative
\(\Delta F=2\) magnitude check, but not as a clean SM-subtracted exclusion.

\subsection*{Code coverage in this repo}
\textbf{PARTIAL.}  The methodology note lists \(\Delta m_K\) among the five
\(\Delta F=2\) scan observables at
\texttt{docs/quark\_scan\_methodology\_note.tex:118}.  The legacy kaon helper
sets the PDG mass splitting at \texttt{quarkConstraints/deltaf2.py:615} and
implements \texttt{evaluate\_delta\_mk} at
\texttt{quarkConstraints/deltaf2.py:755}.  The modern lane also has a
\texttt{K} input displayed as \(\Delta m_K\) at
\texttt{quarkConstraints/modern/inputs.py:958} and a bridge evaluator at
\texttt{quarkConstraints/modern/phenomenology.py:493}.  I keep the status
partial because the legacy default kaon input is still the \(\varepsilon_K\)
entry at \texttt{quarkConstraints/deltaf2.py:209}, and the catalog has not
audited a standalone long-distance policy.

\subsection*{Implementation difficulty}
\textbf{LOW.}  No new operator basis is needed for a conservative catalog or
scan-side magnitude bound: the existing \(\Delta F=2\) VLL/VRR/LR machinery
covers the required Wilson coefficients.  A future precision SM-subtracted
\(\Delta m_K\) likelihood would be a separate high-theory-effort project.

\subsection*{Key references}
Local source keys: \texttt{pdg\_live\_S013D\_20260516},
\texttt{ktev\_2011}, \texttt{christ\_2013\_ld\_delta\_mk},
\texttt{bai\_2014\_delta\_mk}, \texttt{wang\_2020\_physical\_delta\_mk},
\texttt{wang\_2023\_delta\_mk}, \texttt{boyle\_2024\_bsm\_kaon\_mixing},
\texttt{flag2024}, and \texttt{cfw\_2008}.
