% Flavor catalog per-process template.
% process_id: K003
% family: kaon
% owner_agent_id: PKA-K003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(\varepsilon'/\varepsilon\) in \(K\to\pi\pi\)}{epsilon prime over epsilon in K to pi pi}}

\subsection*{Process}
\textbf{Standard notation:} \(\mathrm{Re}(\varepsilon'/\varepsilon)\).
This entry covers direct CP violation in the two-pion decay amplitudes of
neutral kaons, commonly written through
\(\mathrm{Re}(\varepsilon'/\varepsilon)=(1-|\eta_{00}/\eta_{+-}|)/3\).
The process id is \(K003\), matching the kaon-sector row for
``epsilon'/epsilon'' in plan v1.

\subsection*{PDG / equivalent value(s)}
The canonical numerical value is taken from the sidecar
\texttt{pdg\_or\_equivalent} block:
\[
  \mathrm{Re}(\varepsilon'/\varepsilon)=0.00166\pm0.00023
  = (16.6\pm2.3)\times 10^{-4}.
\]
The local PDG snapshot is
\texttt{flavor\_catalog/references/K003/pdg\_live\_S013\_20260516.txt}.
The companion PDG DataBlock snapshot records the measurement table and the
two dominant modern inputs: KTeV reports
\((19.2\pm2.1)\times10^{-4}\), while NA48 reports
\((14.7\pm2.2)\times10^{-4}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Unlike \(\varepsilon_K\), this is a \(\Delta S=1\) nonleptonic observable.
It tests CP-odd short-distance contributions to the \(K\to\pi\pi\) amplitudes
after they are filtered through long-distance QCD.  In warped or composite
flavor models with anarchic Yukawas, the dangerous effects are not the
repo's current neutral-meson-mixing operators but new penguin, scalar/tensor,
and dipole structures.  BSM master-formula work identifies strong sensitivity
to electroweak left-right penguin \(Q_8\), QCD penguin \(Q_6\), and
chromo-magnetic \(O_{8g}\)-type operators, making the channel a natural
stress test for UV completions with non-minimal chirality structure.

\subsection*{Post-2008 developments}
The experimental average has not been replaced by a new kaon experiment, but
KTeV's final \(K\to\pi\pi\) result was published after the CFW-era reference
point.  The major post-2008 changes are theoretical.  RBC/UKQCD produced a
physical-kinematics lattice calculation of \(A_0\) and \(\varepsilon'\),
finding \(\mathrm{Re}(\varepsilon'/\varepsilon)=
21.7(2.6)(6.2)(5.0)\times10^{-4}\).  Aebischer, Bobeth, and Buras then
reanalysed the same ratio with NNLO electroweak-penguin corrections and
ChPT isospin-breaking inputs, obtaining
\((17.4\pm6.1)\times10^{-4}\) in the octet treatment and
\((13.9\pm5.2)\times10^{-4}\) in the nonet treatment.  In parallel, 2019
BSM master-formula papers organized the \(\Delta S=1\) operator dependence
in WET/SMEFT language rather than treating \(\varepsilon'/\varepsilon\) as a
single phenomenological number.

\subsection*{Constraint validity and model dependence}
As a catalog constraint, \(K003\) is highly informative but not plug-and-play.
The experimental number is cleanly established, while the SM subtraction and
BSM interpretation depend on hadronic matrix elements, isospin breaking,
operator matching, and RG evolution.  It should be classified as a
theory-limited, model-dependent \(\Delta S=1\) amplitude constraint rather
than a robust tree-level exclusion like the current \(\Delta F=2\) kaon lane.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no direct implementation of
\(\varepsilon'/\varepsilon\), \(K\to\pi\pi\), \(\Delta S=1\), \(Q_6\),
\(Q_8\), or \(O_{8g}\).  The nearby kaon code is explicitly a
\(\Delta F=2\) benchmark slice in \texttt{quarkConstraints/deltaf2.py:1},
with default inputs for \(\varepsilon_K\) at
\texttt{quarkConstraints/deltaf2.py:209} and an
\(\varepsilon_K\) evaluator at \texttt{quarkConstraints/deltaf2.py:729}.
The modern policy surface likewise enumerates only
\(\varepsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) systems at
\texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint would require a new \(\Delta S=1\)
operator basis, matching from the warped/composite UV model to WET/SMEFT
coefficients, RG running to hadronic scales, and lattice/ChPT inputs for
\(K\to\pi\pi\) matrix elements.  The current \(\Delta F=2\) VLL/VRR/LR
machinery cannot be reused as a direct evaluator.

\subsection*{Key references}
Local source keys: \texttt{pdg\_live\_S013\_20260516},
\texttt{pdg\_live\_S013EPS\_datablock\_20260516}, \texttt{ktev\_2011},
\texttt{na48\_2002}, \texttt{rbc\_ukqcd\_2020},
\texttt{aebischer\_buras\_2020}, \texttt{bsm\_master\_2019},
\texttt{bsm\_anatomy\_2019}, and \texttt{cfw\_2008}.

