% Flavor catalog process: K004
% family: kaon
% owner_agent_id: PKA-K004
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K004.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K004: \(K^+ \to \pi^+ \nu\bar{\nu}\)}

\subsection*{Process}
Standard notation: \(K^+ \to \pi^+ \nu\bar{\nu}\).  This entry covers the
charged ``golden'' kaon decay governed by the short-distance
\(s\to d\nu\bar{\nu}\) flavor-changing neutral current, with emphasis on the
real-part sensitivity that complements \(K_L\to\pi^0\nu\bar{\nu}\).

\subsection*{PDG / equivalent value(s)}
For this draft the canonical experimental-equivalent value is the latest NA62
combination, rather than an older PDG average:
\[
  \BRof{K^+ \to \pi^+ \nu\bar{\nu}}
  = \left(9.6^{+1.9}_{-1.8}\right)\times 10^{-11},
\]
from NA62 data collected in 2016--2024.  The local snapshot is
\url{flavor_catalog/references/K004/na62_2026_arxiv2604_12649.txt}.  The
published 2016--2022 observation anchor is
\(\left(13.0^{+3.3}_{-3.0}\right)\times 10^{-11}\), with 51 signal candidates
and an expected background of \(18^{+3}_{-2}\) events; see
\url{flavor_catalog/references/K004/na62_2025_arxiv2412_12015.txt}.  For the
SM comparison, the sidecar records the Buras--Venturini benchmark
\(\BR_{\rm SM}=\left(8.60\pm0.42\right)\times10^{-11}\) and the
Brod--Gorbahn--Stamou update
\(\BR_{\rm SM}=7.73(61)\times10^{-11}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models can generate misaligned \(s\)-\(d\) neutral currents
through KK gauge exchange, \(Z\)-coupling shifts, or related electroweak
matching effects.  Unlike the current quark lane's \(\DeltaFtwo\) kaon
observables, this is a \(\Delta F=1\) semileptonic process.  It therefore
tests whether the model has controlled short-distance neutral currents beyond
the four-quark \(K\)-mixing sector.  The charged mode is especially useful
because it is theoretically clean, uses a hadronic matrix element tied to
semileptonic kaon data, and can interfere with the SM amplitude rather than
only setting an incoherent upper bound.

\subsection*{Post-2008 developments}
The CFW-era RS discussion used \(\DeltaFtwo\) flavor bounds as the central
pressure point, quoting a generic RS KK-gluon mass scale of about \(21\) TeV
and a composite pseudo-Goldstone scenario scale of about \(33\) TeV.  Since
that era, the charged rare-kaon channel has become experimentally active:
NA62 reported the published observation in 2025 and a newer 2026 preliminary
combination with sub-20-percent precision.  On the theory side, post-2008 SM
updates have sharpened the short-distance prediction and exposed the role of
CKM-input choices: Brod--Gorbahn--Stamou quote \(7.73(61)\times10^{-11}\),
while Buras--Venturini quote \((8.60\pm0.42)\times10^{-11}\) using a strategy
designed to avoid the direct \(|V_{cb}|\) and \(|V_{ub}|\) tensions.

\subsection*{Constraint validity and model dependence}
As an experimental branching-ratio constraint this mode is clean, but its use
inside an RS scan is model-dependent.  A production constraint needs Wilson
coefficients for
\((\bar{s}\gamma_\mu P_{L,R}d)(\bar{\nu}\gamma^\mu(1-\gamma_5)\nu)\), a
choice of neutrino-flavor treatment, and a convention for SM--NP interference.
The Buras--Venturini SM number also assumes no new-physics infection in the
\(\DeltaFtwo\) inputs used to remove CKM ambiguities, so a checker should keep
that assumption visible if the catalog later turns this process into a hard
bound.

\subsection*{Code coverage in this repo}
Coverage status: NO.  The required grep sweep finds kaon mixing, generic
neutrino-mass utilities, and the catalog planning row, but no implementation
of \(K^+\to\pi^+\nu\bar{\nu}\), no \(\Delta F=1\) \(s\to d\nu\bar{\nu}\)
operator, and no branching-ratio acceptance gate.  The closest quark-code
surfaces are the \(\DeltaFtwo\) entries in
\texttt{quarkConstraints/deltaf2.py} and the modern policy list
\texttt{MODERN\_PHENOMENOLOGY\_SYSTEM\_IDS = (epsilon\_K, K, B\_d, B\_s, D0)}.

\subsection*{Implementation difficulty}
Implementation difficulty: MEDIUM.  The observable needs a new \(\Delta F=1\)
semileptonic operator basis and a branching-ratio formula with SM--NP
interference, but the hadronic input is standard and this channel does not
require the angular likelihood machinery needed for many \(b\to s\ell\ell\)
observables.  The difficulty would become HIGH only if the catalog requires a
full RS tower and neutrino-sector matching rather than an EFT Wilson input.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
NA62:KpPipNunu2026, NA62:KpPipNunu2025,
BurasVenturini:KpPipNunu2022, BrodGorbahnStamou:KpPipNunu2021, and
CsakiFalkowskiWeiler:RSFlavor2008.
