% Flavor catalog per-process draft.
% process_id: K005
% family: kaon
% owner_agent_id: PKA-K005
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K005.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\(K_L \to \pi^0\nu\bar\nu\)}

\subsection*{Process}
Standard notation: \(K_L \to \pi^0\nu\bar\nu\).  This entry covers the
CP-violating neutral-kaon golden mode, a \(\Delta S=1\) flavor-changing
neutral-current decay with an invisible neutrino pair.  The process id is
K005 from the kaon table in plan v1.

\subsection*{PDG / equivalent value(s)}
The sidecar value is
\[
  {\cal B}(K_L^0 \to \pi^0\nu\bar\nu) < 2.2\times 10^{-9}
  \quad (90\%~{\rm CL}),
\]
from the 2026 PDG pdgLive S013R40 table, snapshot
\texttt{flavor\_catalog/references/K005/pdg2026\_pdgLive\_S013R40.txt}.
The same sidecar records the direct KOTO 2025 input behind the PDG value:
the 2021 KOTO data set had expected background
\(0.252\pm0.055_{\rm stat}{}^{+0.052}_{-0.067}{}_{\rm syst}\), single-event
sensitivity \((9.33\pm0.06_{\rm stat}\pm0.84_{\rm syst})\times10^{-10}\),
and no signal-region events, yielding the same \(2.2\times10^{-9}\) limit.

For SM comparison the sidecar gives two current theory benchmarks:
Brod--Gorbahn--Stamou quote
\({\cal B}_{\rm SM}=2.59(29)\times10^{-11}\), while the
Buras--Venturini \(|V_{cb}|\)- and \(|V_{ub}|\)-independent determination
quotes \((2.94\pm0.15)\times10^{-11}\) under its no-new-physics assumptions
in \(|\varepsilon_K|\) and \(S_{\psi K_S}\).  The related charged golden mode
has the 2026 NA62 value
\({\cal B}(K^+\to\pi^+\nu\bar\nu)=(9.6^{+1.9}_{-1.8})\times10^{-11}\),
included only as program context and not as a direct K005 measurement.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This mode is one of the cleanest probes of short-distance flavor violation:
the hadronic matrix element is tied to semileptonic kaon data, and the neutral
mode isolates the imaginary part of the \(s\to d\nu\bar\nu\) amplitude.  In
RS/anarchic-flavor language it tests flavor-changing \(Z\), \(Z'\), or other
neutral-current couplings induced by fermion localization and KK mixing, plus
loop-level contributions if the ultraviolet completion generates them.  It is
therefore complementary to \(\varepsilon_K\): both are CP-sensitive kaon
observables, but K005 is a \(\Delta S=1\) rare decay rather than a
\(\Delta F=2\) mixing constraint.

\subsection*{Post-2008 developments}
Since the Csaki--Falkowski--Weiler era, the experimental frontier moved from
older E391a/KOTO pilot limits to the KOTO direct search now mirrored by PDG.
KOTO's 2025 PRL result improves the previous KOTO direct bound and reports a
background expectation below one event for the 2021 analysis.  On the charged
side, NA62 has moved \(K^+\to\pi^+\nu\bar\nu\) from evidence/observation to a
combined 2016--2024 value with sub-\(20\%\) precision, sharpening the
cross-check between the charged and neutral golden modes.  Theory updates also
matter: Brod--Gorbahn--Stamou updated the SM \(K\to\pi\nu\bar\nu\) prediction,
and Buras--Venturini recast the prediction in ratios designed to reduce
\(|V_{cb}|\) and \(|V_{ub}|\) dependence.

\subsection*{Constraint validity and model dependence}
The SM channel is short-distance dominated and unusually clean, but the
present catalog value is still an upper limit.  The interpretation is robust
for high-scale new physics that modifies semileptonic \(s\to d\nu\bar\nu\)
operators.  It becomes model-dependent if the missing energy is a light
non-neutrino particle, if neutrino flavor structure is non-universal, or if a
global kaon fit is used to correlate K005 with the charged mode.

\subsection*{Code coverage in this repo}
Coverage status: NO.  I searched the requested code areas, excluding
notebooks, for \(K_L\to\pi^0\nu\bar\nu\), KOTO, NA62, \(s\to d\), penguin,
and generic rare-kaon strings.  No rare-decay implementation was found.  The
only relevant \(K_L\) hit was the mixing input
\texttt{quarkConstraints/deltaf2.py:615} for \(\Delta m_K\), and the broader
kaon code is \(\Delta F=2\) mixing machinery rather than a \(\Delta S=1\)
semileptonic decay calculation.

\subsection*{Implementation difficulty}
HIGH.  A production implementation would need a new \(s\to d\nu\bar\nu\)
Wilson/operator path, the CP-odd \(K_L\) projection, SM normalization and
interference handling, neutrino-flavor bookkeeping, and a mode-level likelihood
or limit treatment.  The existing audited code can supply kaon-mixing context,
but not the rare-decay observable itself.

\subsection*{Key references}
Process-local keys deposited in \texttt{flavor\_catalog/references/K005/}:
\texttt{PDG2026:K005}, \texttt{KOTO2025:KLPi0NuNu},
\texttt{BrodGorbahnStamou2021:KPiNuNu},
\texttt{BurasVenturini2022:RareK}, \texttt{NA622026:KPlusPiNuNu}, and
\texttt{BuchallaBuras1996:KPiNuNu}.
