% Flavor catalog process: K006
% Canonical metadata sidecar: K006.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\(K_L \to \mu^+\mu^-\)}

\subsection*{Process}
The process is the long-lived neutral-kaon rare decay
\(K_L\to\mu^+\mu^-\), catalog id K006 in the kaon family.  It is a
strangeness-changing weak-neutral-current mode.  The observed rate is dominated by
the two-photon long-distance amplitude, but the dispersive component leaves a
short-distance window for \(s\to d\) \(Z\)-penguin and electroweak-box effects.

\subsection*{PDG / equivalent value(s)}
The YAML sidecar source of truth lists the current PDG value as
\[
  \mathcal{B}(K_L\to\mu^+\mu^-)
  = (6.84 \pm 0.11)\times 10^{-9},
\]
from the PDG \(K_L^0\) listing, \(\Gamma_{24}\), in the 2024 Review of
Particle Physics.  The local snapshot is
\texttt{flavor\_catalog/references/K006/pdg2024\_kl\_decay\_modes.txt}
with sha256
\texttt{7b8d82405b9c4bf76bf9efb6c3db59a5bd21ae2d77339e6ef0dce389ef50c585},
accessed 2026-05-16.  The primary E871 measurement snapshot records
\(\mathcal{B}=(7.18\pm0.17)\times10^{-9}\), used here only as experimental
provenance rather than as the catalog average.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped or anarchic-flavor models this channel is relevant through the same
flavor-changing \(s\to d\) neutral-current structures that appear in rare kaon
phenomenology: modified \(Z\) couplings, heavy gauge-boson penguins, and box
topologies.  It is less clean than \(K\to\pi\nu\bar\nu\), because the measured
branching fraction is almost saturated by long-distance two-photon physics, but
it is still a useful diagnostic for large semileptonic short-distance effects.
The Isidori-Unterdorfer dispersive analysis quoted in the sidecar gives a
conservative bound
\(\mathcal{B}(K_L\to\mu^+\mu^-)_{\rm short}<2.5\times10^{-9}\), which is the
right order-of-magnitude target for any future catalog-to-code translation.

\subsection*{Post-2008 developments}
No newer high-precision \(K_L\to\mu^+\mu^-\) branching-fraction measurement was
found beyond the PDG average used above.  The main post-2008 movement is
theoretical: D'Ambrosio-Kitahara identified direct-CP and \(K_L\)-\(K_S\)
interference handles for \(K\to\mu^+\mu^-\); Dery-Ghosh-Grossman-Schacht
showed that time-dependent information can isolate a clean short-distance
\(K_S\) observable with hadronic uncertainty below \(1\%\); and Chao-Christ
developed a lattice-QCD framework for the long-distance two-photon amplitude,
with a quoted \(10\%\) target accuracy.  These papers do not replace the PDG
branching fraction, but they sharpen how this family of modes could become a
cleaner short-distance probe after the CFW-era treatment.

\subsection*{Constraint validity and model dependence}
As a direct rate constraint this is long-distance-limited.  New physics with
large scalar or pseudoscalar lepton operators would require separate treatment;
the short-distance interpretation above is aimed at vector/axial semileptonic
operators generated by \(Z\)-penguins and electroweak boxes.  A production
constraint should therefore use either a conservative dispersive allowance or a
future lattice-assisted SM subtraction, not the total PDG branching fraction as
a clean short-distance observable.

\subsection*{Code coverage in this repo}
NO.  A targeted grep across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/}, excluding notebooks and binary-like assets, found no
\(K_L\to\mu^+\mu^-\), dimuon, or \(s\to d\ell^+\ell^-\) implementation.  The
nearest kaon hit is \texttt{quarkConstraints/deltaf2.py:615}, which defines the
\(K_L-K_S\) mass difference for \(\Delta F=2\) mixing, not this decay.

\subsection*{Implementation difficulty}
HIGH.  Implementing K006 would need a new rare-kaon semileptonic observable,
short-distance \(s\to d\mu^+\mu^-\) matching, and an explicit treatment of the
long-distance two-photon dispersive amplitude or a conservative external bound.
Those ingredients are not present in the audited \(\Delta F=2\) code path.

\subsection*{Key references}
\begin{itemize}
\item \texttt{PDG2024:K006}: PDG \(K_L^0\) listing, \(\Gamma_{24}\).
\item \texttt{Ambrose2000:E871KLMuMu}: primary branching-ratio measurement.
\item \texttt{IsidoriUnterdorfer2004:KLMuMuSD}: short-distance bound.
\item \texttt{DAmbrosioKitahara2017:KMuMuCP}: post-2008 interference/CP handle.
\item \texttt{DeryGhoshGrossmanSchacht2021:KMuMuClean}: time-dependent clean probe proposal.
\item \texttt{ChaoChrist2024:KLMuMuLattice}: lattice two-photon framework.
\end{itemize}
