% Flavor catalog per-process entry.
% process_id: K008
% family: kaon
% owner_agent_id: PKA-K008
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{K008: \(K_L \to \pi^0 e^+e^-\)}{K008: KL -> pi0 e+e-}}

\subsection*{Process}
\textbf{Standard notation:} \(K_L \to \pi^0 e^+e^-\).  This rare
semileptonic neutral-kaon mode is a \(\Delta S=1\) weak-neutral-current
channel.  Its Standard-Model rate is conventionally decomposed into indirect
CP violation, direct CP violation, their interference, and a small
CP-conserving two-photon piece
(\texttt{isidori\_smith\_unterdorfer2004\_kl\_pi0ll\_arxiv.txt}).

\subsection*{PDG / equivalent value(s)}
The canonical PDG/API limit is
\[
  {\cal B}(K_L \to \pi^0 e^+e^-) < 2.8\times 10^{-10}\quad(90\%\ {\rm CL}),
\]
from the 2026 PDG pdgLive entry \(S013.20\), accessed 2026-05-16
(\texttt{pdg2026\_kl\_pi0ee\_pdgLive.txt}).  PDG traces the value to the KTeV
combined result in PRL 93, 021805.  The KTeV 1999--2000 sample observed one
candidate with \(0.99\pm0.35\) expected background events and set a standalone
\(3.5\times10^{-10}\) limit at 90\% CL; the combination with the 1997 data
gives the PDG value
(\texttt{ktev2004\_kl\_pi0ee\_arxiv.txt},
\texttt{pdg2026\_kl\_pi0ee\_pdgLive.txt}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This decay probes \(s\to d e^+e^-\) electroweak-penguin and semileptonic
contact structures rather than the \(\Delta F=2\) KK-gluon lane already present
in the repository.  In anarchic or warped models it is a diagnostic for
flavor-changing \(Z\) couplings, heavy neutral gauge exchange, and dipole or
photon-penguin effects.  The KTeV theory summary quotes a Standard-Model rate
of order \(3\times10^{-11}\), a CP-violating range of
\(8\)--\(45\times10^{-12}\), a direct-CP estimate of
\(3\)--\(6\times10^{-12}\), and a 40\% direct-CP interference contribution
(\texttt{ktev2004\_kl\_pi0ee\_arxiv.txt}).  The present experimental limit is
therefore above, but near, the scale where short-distance effects become
interesting.

\subsection*{Post-2008 developments}
No post-2008 experiment in the PKA snapshot supersedes the KTeV/PDG
\(K_L\to\pi^0 e^+e^-\) limit.  The important developments are interpretive.
The PDG 2026 listing records the CP-conserving contribution inferred from
\(K_L\to\pi^0\gamma\gamma\) as
\((0.0047^{+0.0022}_{-0.0018})\times10^{-10}\)
(\texttt{pdg2026\_kl\_pi0ee\_pdgLive.txt}), supporting the standard view that
the electron mode is CPV dominated.  The supporting \(K_S\to\pi^0e^+e^-\)
input for the indirect-CP amplitude remains the NA48 value
\((3.0^{+1.5}_{-1.2}\pm0.2)\times10^{-9}\) for \(m_{ee}>0.165\,{\rm GeV}\),
with an extrapolated full-region value
\(5.8^{+2.9}_{-2.4}\times10^{-9}\)
(\texttt{na48\_ks\_pi0ee\_pdgLive.txt}).  Since 2008, lattice work has begun
addressing long-distance \(K\to\pi\ell^+\ell^-\) amplitudes
(\texttt{ChristEtAl2016:KPiLLLattice}), and the Snowmass rare-kaon white paper
keeps \(K_{L,S}\to\pi^0\ell^+\ell^-\) branching ratios and \(q^2\) spectra in
the short-distance rare-kaon program
(\texttt{AebischerBurasKumar2022:RareKaons}).

\subsection*{Constraint validity and model dependence}
Class: long-distance-limited, CP-decomposition-dependent, and not yet a clean
single-Wilson-coefficient bound.  A useful implementation must keep the
indirect CPV piece tied to \(K_S\to\pi^0e^+e^-\), the direct CPV short-distance
piece, their sign-dependent interference, and the small two-photon CPC
component separate.  The Isidori--Smith--Unterdorfer decomposition gives
\(C_{\rm mix}^e=(15.7\pm0.3)|a_S|^2\), \(C_{\rm int}^e=(6.2\pm0.3)|a_S|\),
\(C_{\rm dir}^e=2.4\pm0.2\), \(C_{\rm CPC}^e\simeq0\),
\(|a_S|=1.2\pm0.2\), and
\(({\rm Im}\lambda_t/10^{-4})_{\rm SM}=1.36\pm0.12\), entering the rate in
units of \(10^{-12}\)
(\texttt{isidori\_smith\_unterdorfer2004\_kl\_pi0ll\_arxiv.txt}).

\subsection*{Code coverage in this repo}
\textbf{NO.}  Targeted PKA greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(K_L\to\pi^0 e^+e^-\), \(K_S\to\pi^0e^+e^-\),
\(a_S\), or \(s\to d e^+e^-\) implementation.  Existing kaon coverage is
\(\Delta F=2\) only, e.g. \texttt{quarkConstraints/deltaf2.py:209} and
\texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  K008 requires a new \(\Delta S=1\) semileptonic observable,
short-distance matching to \(s\to d e^+e^-\), treatment of indirect/direct CP
separation and interference, and long-distance inputs from \(K_S\) and
\(K_L\to\pi^0\gamma\gamma\).  The existing \(\Delta F=2\) operator basis is not
sufficient.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026:K008}, \texttt{KTeV2004:KLPi0EE},
\texttt{NA482003:KSPi0EE}, \texttt{IsidoriSmithUnterdorfer2004:KLPi0LL},
\texttt{CFW2008:RSFlavor}, \texttt{ChristEtAl2016:KPiLLLattice}, and
\texttt{AebischerBurasKumar2022:RareKaons}.  Numeric claims above are tied to
the sidecar-listed local snapshots.
