% Flavor catalog per-process entry.
% process_id: K009
% family: kaon
% owner_agent_id: PKA-K009
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K009.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K009: \(K_L \to \pi^0\mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_L \to \pi^0\mu^+\mu^-\).  This entry covers the
long-lived neutral-kaon rare semileptonic muon channel, a \(\Delta S=1\)
weak-neutral-current process receiving indirect-CP, direct-CP, interference,
and CP-conserving two-photon contributions.

\subsection*{PDG or equivalent value}
The canonical measured limit is
\[
  {\cal B}(K_L \to \pi^0\mu^+\mu^-) < 3.8\times10^{-10}
  \quad(90\%\ {\rm CL}),
\]
from the 2026 PDG pdgLive entry \(S013.16/S013R30\), accessed 2026-05-16
(\texttt{pdg2026\_kl\_pi0mumu\_pdgLive.txt}).  PDG traces the active limit to
the KTeV search in PRL 84, 5279.  The KTeV snapshot records two observed
events, \(0.87\pm0.15\) expected background events, and the same
\(3.8\times10^{-10}\) upper limit
(\texttt{ktev2000\_kl\_pi0mumu\_arxiv.txt}).

\subsection*{Relevance to RS / anarchic flavor}
This mode probes \(s\to d\mu^+\mu^-\) semileptonic and electroweak-penguin
structures, not the \(\Delta F=2\) KK-gluon mixing lane currently implemented.
In RS or anarchic-flavor variants it is sensitive to flavor-changing \(Z\)
couplings, heavy neutral gauge exchange, and short-distance vector/axial
operators.  The muon mode's CP-conserving two-photon contribution is
numerically important in the PKA theory decomposition, so a future signal would
require separating CPV short-distance information from long-distance hadronic
input.

\subsection*{Post-2008 developments}
No post-2008 experimental result was found that supersedes the KTeV/PDG
\(K_L\to\pi^0\mu^+\mu^-\) limit.  The supporting short-lived mode remains the
NA48/PDG \(K_S\to\pi^0\mu^+\mu^-\) value
\((2.9^{+1.5}_{-1.2}\pm0.2)\times10^{-9}\), based on six observed events and
\(0.22^{+0.18}_{-0.11}\) expected background events
(\texttt{na48\_ks\_pi0mumu\_pdgLive.txt},
\texttt{na48\_ks\_pi0mumu\_arxiv.txt}).  Since arXiv:0804.1954, the main
developments are interpretive: exploratory lattice work has started on
long-distance \(K\to\pi\ell^+\ell^-\) amplitudes
(\texttt{christ\_feng\_juettner\_lawson\_portelli\_sachrajda2016\_lattice\_arxiv.txt}),
and the Snowmass rare-kaon white paper keeps
\(K_{L,S}\to\pi^0\ell^+\ell^-\) branching ratios and spectra in the
short-distance rare-kaon program
(\texttt{aebischer\_buras\_kumar2022\_rare\_kaon\_arxiv.txt}).

\subsection*{Constraint validity / model dependence}
Class: long-distance-limited and CP-decomposition-dependent.  The
Isidori--Smith--Unterdorfer decomposition writes the rate as mixing,
interference, direct, and CP-conserving pieces multiplying \(10^{-12}\).  For
the muon mode the coefficients are
\[
 C_{\rm mix}^{\mu}=(3.7\pm0.1)|a_S|^2,\quad
 C_{\rm int}^{\mu}=(1.6\pm0.1)|a_S|,\quad
 C_{\rm dir}^{\mu}=1.0\pm0.1,\quad
 C_{\rm CPC}^{\mu}=5.2\pm1.6,
\]
with \(|a_S|=1.2\pm0.2\).  The same paper quotes the constructive-interference
SM expectation as \((1.5\pm0.3)\times10^{-11}\), well below the current
experimental limit.  These numerical theory inputs are recorded in the YAML
\texttt{theory\_decomposition} block and trace to
\texttt{isidori\_smith\_unterdorfer2004\_kl\_pi0mumu\_arxiv.txt}.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Targeted greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(K_L\to\pi^0\mu^+\mu^-\), \(K_S\to\pi^0\mu^+\mu^-\),
\(a_S\), or \(s\to d\mu^+\mu^-\) implementation.  Existing nearby kaon coverage
is \(\Delta F=2\), e.g. \texttt{quarkConstraints/deltaf2.py:209} and the modern
policy list at \texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint needs a new \(\Delta S=1\) semileptonic
observable, short-distance \(s\to d\mu^+\mu^-\) matching, CPV/interference
bookkeeping tied to \(K_S\to\pi^0\mu^+\mu^-\), and a long-distance
two-photon/CPC treatment.  The existing \(\Delta F=2\) SLL/SLR/VLL/VRR/LR
basis is not sufficient.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026:K009}, \texttt{KTeV2000:KLPi0MuMu},
\texttt{NA482004:KSPi0MuMu},
\texttt{IsidoriSmithUnterdorfer2004:KLPi0MuMu},
\texttt{CFW2008:RSFlavor}, \texttt{ChristEtAl2016:KPiLLLattice}, and
\texttt{AebischerBurasKumar2022:RareKaons}.
