% Flavor catalog per-process entry.
% process_id: K010
% family: kaon
% owner_agent_id: PKA-K010
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K010.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K010: \(K_S \to \pi^0 e^+e^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(K_S\to\pi^0 e^+e^-)\).
This entry covers the short-lived neutral-kaon rare semileptonic mode
\(K_S\to\pi^0 e^+e^-\), a CP-conserving/CP-allowed \(\Delta S=1\)
weak-neutral-current decay.  It is the electron-mode \(K_S\) companion to
\(K008\) because it fixes the indirect-CP input used in \(K_L\to\pi^0 e^+e^-\)
phenomenology.

\subsection*{PDG / equivalent value(s)}
The canonical PDG 2026 pdgLive listing \(S012.10\), accessed 2026-05-16, gives
the NA48/1 measurement
\[
  \mathcal{B}(K_S\to\pi^0 e^+e^-;\,m_{ee}>0.165~{\rm GeV})
  = \left(3.0^{+1.5}_{-1.2}\,{\rm stat}\pm0.2\,{\rm syst}\right)
    \times10^{-9}.
\]
The same listing records the NA48/1 full-kinematic extrapolation, using a
constant form factor and vector matrix element,
\[
  \mathcal{B}(K_S\to\pi^0 e^+e^-)
  = \left(5.8^{+2.9}_{-2.4}\right)\times10^{-9}.
\]
The local PDG snapshot is
\texttt{flavor\_catalog/references/K010/pdg2026\_ks\_pi0ee\_pdgLive.txt}; the
NA48/1 arXiv abstract-page snapshot is
\texttt{flavor\_catalog/references/K010/na48\_2003\_ks\_pi0ee\_arxiv.txt}.
NA48/1 reports 7 observed events with an expected background of 0.15 events in
the high-intensity \(K_S\) data set.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This mode probes \(s\to d e^+e^-\) semileptonic neutral-current structure,
not the \(\Delta F=2\) kaon-mixing lane already implemented in the repository.
In warped or anarchic-flavor models it is sensitive, through a hadronic
long-distance amplitude, to flavor-changing \(Z\), photon-penguin, and heavy
neutral-gauge effects.  Its most immediate catalog role is as an experimental
normalization for the indirect-CP part of \(K_L\to\pi^0 e^+e^-\), so it should
be kept distinct from short-distance theory prefactors or NDA normalizations.

\subsection*{Post-2008 developments}
No post-2008 measurement was found that supersedes the NA48/1 value used by
PDG.  The important developments are interpretive: the rare-kaon Snowmass
white paper emphasizes \(K_{L,S}\to\pi^0\ell^+\ell^-\) branching ratios and
\(q^2\) distributions as new-physics probes, with correlations to
\(\varepsilon'/\varepsilon\), \(\varepsilon_K\), and \(\Delta M_K\).  The
modern literature also treats this \(K_S\) input as part of the indirect-CP
normalization for the \(K_L\) modes rather than as a standalone clean Wilson
coefficient bound.

\subsection*{Constraint validity and model dependence}
Class: long-distance-limited rare kaon decay.  The measured partial branching
fraction is robust, but the full-kinematic number is model-dependent because
it assumes a vector matrix element and a unit form factor.  A model constraint
must specify whether it uses the directly measured \(m_{ee}>0.165\) GeV region
or the extrapolated total rate, and whether it predicts the chiral
long-distance amplitude or only a short-distance \(s\to d e^+e^-\) Wilson
coefficient.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Focused greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(K_S\to\pi^0 e^+e^-\), \(S012.10\),
\(a_S\), or \(s\to d e^+e^-\) implementation.  The nearest kaon coverage is
\(\Delta F=2\): \texttt{quarkConstraints/deltaf2.py:209} starts the default
neutral-meson-mixing inputs, \texttt{quarkConstraints/deltaf2.py:755}
evaluates \(\Delta m_K\), and
\texttt{quarkConstraints/modern/phenomenology.py:23} lists only
\(\varepsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D0\) policy systems.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production integration would need a new \(\Delta S=1\)
semileptonic rare-kaon observable, Wilson normalization for \(s\to d e^+e^-\),
and a documented treatment of the \(K_S\) form factor or a conservative
experimental-input-only interpretation.  The existing SLL/SLR/VLL/VRR/LR
\(\Delta F=2\) basis does not cover this decay.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026:K010}, \texttt{NA482003:KSPi0EE},
\texttt{IsidoriSmithUnterdorfer2004:KPi0LL},
\texttt{AebischerBurasKumar2022:RareKaons}, and
\texttt{CFW2008:RSFlavor}.
