% Flavor catalog process: K012
% Canonical metadata sidecar: K012.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\(K_S \to \mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_S^0\to\mu^+\mu^-\).  This kaon entry covers the
short-lived neutral-kaon dimuon decay, the \(K_S\) companion of
\(K_L\to\mu^+\mu^-\).  It is a rare \(\Delta S=1\)
weak-neutral-current mode, not a neutral-kaon mixing observable.

\subsection*{PDG / equivalent value(s)}
The sidecar \texttt{pdg\_or\_equivalent} block, backed by the local
\texttt{pdg2025\_ks\_decay\_modes.txt} snapshot, records the 2025 PDG limit
\[
  \mathcal{B}(K_S^0\to\mu^+\mu^-) < 2.1\times 10^{-10}
  \quad (90\%~{\rm CL}),
\]
from the \(K_S^0\) particle listing, accessed 2026-05-16.  Additional
sidecar \texttt{pdg\_or\_equivalent} entries from
\texttt{lhcb\_2020\_ksmumu\_arxiv.txt} show the LHCb
standalone 2016--2018 bound,
\(\mathcal{B}<2.2\times10^{-10}\) at \(90\%\) CL, and the combined
\(\mathcal{B}<2.1\times10^{-10}\) at \(90\%\) CL.  The Run-1 predecessor,
stored in \texttt{lhcb\_2017\_ksmumu\_arxiv.txt}, was
\(\mathcal{B}<0.8~(1.0)\times10^{-9}\) at \(90\%~(95\%)\) CL.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped or anarchic-flavor scenarios this mode probes \(s\to d\mu^+\mu^-\)
neutral currents rather than the \(\Delta F=2\) kaon-mixing surface already
implemented in the repo.  Modified \(Z\) couplings, heavy neutral-gauge
exchange, electroweak penguins, and scalar or pseudoscalar lepton operators can
feed the dimuon final state.  The sidecar \texttt{pdg\_or\_equivalent} entry
from \texttt{chobanova\_2018\_ksmumu\_susy\_arxiv.txt} gives the Standard
Model scale as approximately \(5\times10^{-12}\), so the present limit mainly
bounds large new-physics enhancements rather than precision SM-sized effects.

\subsection*{Post-2008 developments}
The post-2008 change is mostly experimental: LHCb moved the bound from the
Run-1 \(0.8\times10^{-9}\) result to the combined \(2.1\times10^{-10}\)
limit, with both values recorded in the sidecar.  On the theory side,
Chobanova et al. supplied the SM-scale and Higgs-penguin context, while Dery,
Ghosh, Grossman, and Schacht showed that time-dependent
\(K\to\mu^+\mu^-\) interference can isolate the \(\ell=0\) \(K_S\) component
with hadronic uncertainty below \(1\%\); the latter number is stored in the
sidecar entry for \texttt{dery\_ghosh\_grossman\_schacht\_2021\_kmumu\_arxiv.txt}.

\subsection*{Constraint validity and model dependence}
The experimental upper limit is robust, but a model interpretation is
operator-dependent.  The total \(K_S\to\mu^+\mu^-\) branching fraction includes
long-distance physics and is not the same object as a clean short-distance
\(\ell=0\) extraction.  A catalog-to-code constraint should therefore distinguish
vector/axial \(s\to d\mu\mu\) contributions from scalar or pseudoscalar
operators and should not treat the PDG limit as a pure \(\Delta F=2\) bound.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Targeted greps across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(K_S\to\mu^+\mu^-\), dimuon rare-kaon, or
\(s\to d\ell^+\ell^-\) implementation.  The nearest kaon hit is
\texttt{quarkConstraints/deltaf2.py:615}, the \(K_L-K_S\) mass difference used
for \(\Delta F=2\) mixing, not this decay.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  K012 needs a new rare-kaon \(\Delta S=1\) semileptonic
calculation, Wilson/operator mapping for \(s\to d\mu^+\mu^-\), and a documented
treatment of long-distance and \(K_S/K_L\) interference effects.  The existing
SLL/SLR/VLL/VRR/LR \(\Delta F=2\) basis is not sufficient for this observable.

\subsection*{Key references}
\begin{itemize}
\item \texttt{PDG2025:K012}: PDG \(K_S^0\) particle listing, \(\Gamma_{12}\), and headline limit.
\item \texttt{LHCb2020:KSmumu}: standalone and combined LHCb upper limits.
\item \texttt{LHCb2017:KSmumu}: Run-1 predecessor limit.
\item \texttt{Chobanova2018:KSmumuSUSY}: SM scale and BSM Higgs-penguin context.
\item \texttt{DeryGhoshGrossmanSchacht2021:KMuMuClean}: time-dependent clean-probe proposal.
\end{itemize}
