% Flavor catalog per-process entry.
% process_id: K013
% family: kaon
% owner_agent_id: PKA-K013
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K013.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K013: \(K_L \to \pi^0\gamma\gamma\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_L \to \pi^0\gamma\gamma\).  This entry covers
the long-lived neutral-kaon radiative decay listed by PDG as
\(\Gamma(\pi^0 2\gamma)/\Gamma_{\rm total}\), process \(K013\) in the kaon
family.  The orchestrator decision maps the PI's ambiguous
\(K1\to\pi\gamma\) seed to this channel; the neighboring
\(K_S\to\pi^0\gamma\gamma\) entry remains separate.

\subsection*{PDG / equivalent value(s)}
The canonical sidecar value is
\[
  {\cal B}(K_L\to\pi^0\gamma\gamma)=(1.273\pm0.033)\times10^{-6},
\]
from the PDG \(K_L^0\) listing, 2025 update, accessed 2026-05-16; see
\texttt{flavor\_catalog/references/K013/pdg2025\_kl\_pi0gammagamma.txt}.
PDG forms this average from the KTeV final result and the NA48 measurement
after rescaling both to the current \(K_L\to\pi^0\pi^0\) normalization.  The
sidecar records the PDG-rescaled inputs, \(1.28\pm0.06\pm0.01\) from KTeV and
\(1.27\pm0.04\pm0.01\) from NA48, both in units of \(10^{-6}\), plus the
originally reported branching fractions and vector-exchange parameters \(a_V\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is not a clean tree-level KK-gluon constraint like \(\varepsilon_K\) or
\(\Delta m_K\).  It is a \(\Delta S=1\) radiative rare decay dominated by
long-distance chiral dynamics and vector-meson-exchange effects.  Its practical
catalog role is diagnostic: it fixes the size and shape of the two-photon
amplitude that feeds the CP-conserving part of
\(K_L\to\pi^0\ell^+\ell^-\), and it checks whether an RS extension with
enhanced \(s\to d\gamma\gamma\), dipole, or electroweak-penguin structure is
already in tension with radiative kaon data.

\subsection*{Post-2008 developments}
Relative to the Csaki--Falkowski--Weiler era, the KTeV full-sample analysis is
the decisive update: it superseded the earlier KTeV value and is one of the two
inputs in the current PDG average.  The PKA did not find a newer neutral-mode
branching-ratio measurement in the PDG 2025 listing.  The main later
experimental development is adjacent rather than identical: NA48/2 measured the
charged analogue \(K^\pm\to\pi^\pm\gamma\gamma\), with the sidecar recording
the model-independent \(z>0.2\) and ChPT-extrapolated branching fractions.
Cappiello, Cata, and D'Ambrosio 2018 show that radiative-kaon data constrain
weak chiral counterterms, which is the right language for this mode rather than
a short-distance Wilson-only bound.

\subsection*{Constraint validity and model dependence}
Class: long-distance-limited and model-dependent.  The measured branching
fraction should not be imposed as a hard RS exclusion without a dedicated
\(\Delta S=1\) radiative calculation and a prescription for the SM
long-distance amplitude.  It is safer as a consistency target and as an
auxiliary input to \(K_L\to\pi^0\ell^+\ell^-\) estimates.  A new-physics
interpretation must avoid double counting two-photon contributions already
absorbed into chiral counterterms.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The PKA reran the plan-required greps and a K013-specific search
across \texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The repository
contains kaon \(\Delta F=2\) machinery and unrelated generic \(\gamma\)-symbol
occurrences, but no implementation of \(K_L\to\pi^0\gamma\gamma\), no \(a_V\)
parameter, and no radiative-kaon likelihood.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint would need new \(\Delta S=1\)
radiative matching, chiral-amplitude inputs, long-distance SM treatment, and
possibly differential-shape information.  The existing \(\Delta F=2\) operator
basis and running code are not enough.

\subsection*{Key references}
Process-local source keys before bibliography consolidation: \texttt{PDG2025\_KL\_pi0gammagamma}, \texttt{KTeV2008\_KL\_pi0gammagamma}, \texttt{NA482002\_KL\_pi0gammagamma}, \texttt{NA482014\_Kpm\_pigammagamma}, \texttt{CappielloCataDAmbrosio2018\_radiative\_chiral}, and \texttt{GabbianiValencia2001\_KL\_pi0gammagamma}.
