% Flavor catalog process: K017
% family: kaon
% owner_agent_id: PKA-K017
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K017.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K017: \(K^+ \to \ell^+ \nu\) and \(R_K\)}

\subsection*{Process}
\textbf{Standard notation:} \(R_K =
\Gamma(K^+\to e^+\nu_e(\gamma))/\Gamma(K^+\to\mu^+\nu_\mu(\gamma))\).
This entry covers the charged-kaon leptonic lepton-flavor-universality ratio
using the PDG/NA62 convention that includes internal bremsstrahlung and
separates direct-emission radiation.

\subsection*{PDG / equivalent value(s)}
The PDG API average is
\[
  R_K = (2.488\pm0.009)\times10^{-5},
\]
from PDG API node \texttt{S010R28}, accessed on 2026-05-16 and snapshotted at
\texttt{flavor\_catalog/references/K017/pdg2025\_rk\_api\_20260516.txt}
(\texttt{PDG2025:K017RK}).  The same snapshot records the main inputs: NA62
finds
\((2.488\pm0.007_{\rm stat}\pm0.007_{\rm syst})\times10^{-5}\)
(\texttt{NA62:RK2013}), and KLOE finds
\((2.493\pm0.025_{\rm stat}\pm0.019_{\rm syst})\times10^{-5}\)
(\texttt{KLOE:RK2009}).  For the SM comparison, Cirigliano--Rosell give
\[
  R_K^{\rm SM}=(2.477\pm0.001)\times10^{-5},
\]
in the local snapshot
\texttt{flavor\_catalog/references/K017/cirigliano\_rosell\_2007\_arxiv0707\_4464.txt}
(\texttt{CiriglianoRosell:RKSM2007}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is not a neutral-meson \(\Delta F=2\) observable and does not probe the
existing quark scan's KK-gluon mixing lane directly.  Its value is that the
ratio cancels the common \(V_{us}\), \(f_K\), and much of the kaon-rate
normalization, leaving a helicity-suppressed charged-current LFU test
(\texttt{FlaviaNet:Kaon2010}).
Nonminimal warped models with lepton localization, heavy neutral leptons,
nonunitary charged currents, charged scalars, or nonuniversal \(W\)-coupling
shifts can modify \(K_{e2}\) relative to \(K_{\mu2}\).  In a quark-only RS
interpretation it should therefore be cataloged as a lepton-extension or
charged-current diagnostic, not as a hard bound on the current anarchic
quark fit.

\subsection*{Post-2008 developments}
The 2008 CFW baseline predates the precision \(R_K\) consolidation and did
not make this charged-current LFU ratio a central RS constraint
(\texttt{CsakiFalkowskiWeiler:RSFlavor2008}).  Since then, KLOE published a
precise inclusive measurement in 2009 (\texttt{KLOE:RK2009}), the FlaviaNet
kaon working group consolidated post-2008 kaon-decay inputs in 2010
(\texttt{FlaviaNet:Kaon2010}), and NA62 superseded earlier charged-kaon data
with its 2007--2008 data set in 2013 (\texttt{NA62:RK2013}).  The modern PDG
average is driven by those post-2008 measurements.  The theory reference value
was already clean before 2008, but the experimental precision now makes
\(R_K\) a useful null test for scalar or right-handed charged-current effects
that evade many hadronic uncertainties.

\subsection*{Constraint validity and model dependence}
As a measured ratio, \(R_K\) is robust and experimentally clean, provided the
radiative convention is kept fixed: the PDG/NA62 ratio includes internal
bremsstrahlung, while direct-emission radiation is separated.  Its mapping
onto this repository's default model is model-dependent.  A minimal quark
flavor scan with no nonstandard charged-current lepton sector has no direct
parameter controlling this observable, whereas a 5D lepton extension or
charged-scalar completion could generate visible effects through chirality-
enhanced scalar amplitudes or lepton-nonuniversal \(W\) couplings.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required coverage greps across \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} find no \(K^+\to e^+\nu\),
\(K^+\to\mu^+\nu\), \(K_{\ell2}\), or \(R_K\) implementation.  The nearest
surfaces are the \(\Delta F=2\) default inputs in
\texttt{quarkConstraints/deltaf2.py:209} and the modern policy fence
\texttt{quarkConstraints/modern/phenomenology.py:23}, which enumerates only
\(\varepsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D0\).

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A catalog-to-code implementation would need a new
charged-current leptonic-decay observable, including the SM amplitude,
radiative-convention bookkeeping, and whatever BSM operator basis the PI wants
to expose.  The ratio avoids new lattice matrix elements, but it is not covered
by the existing \(\Delta F=2\) SLL/SLR/VLL/VRR/LR machinery.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
PDG2025:K017RK, NA62:RK2013, KLOE:RK2009, CiriglianoRosell:RKSM2007,
FlaviaNet:Kaon2010, and CsakiFalkowskiWeiler:RSFlavor2008.
