% Flavor catalog process: K018
% family: kaon
% owner_agent_id: PKA-K018
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K018.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K018: \(K_{\ell3}\) and semileptonic \(V_{us}\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_{\ell3}\), with \(K\to\pi e\nu\) and
\(K\to\pi\mu\nu\).  This entry records the kaon semileptonic source input
\(|V_{us}|f_+(0)\) and its mode-by-mode consistency tests.  The first-row CKM
unitarity combination is cataloged separately in EW002.

\subsection*{PDG / equivalent value(s)}
The sidecar \texttt{pdg\_or\_equivalent} entry
\texttt{PDG2025:K018:average\_fplus\_vus}, backed by
\texttt{pdg2025\_vud\_vus\_kl3.txt}, records
\[
  |V_{us}|f_+(0)=0.21656(35),
\]
from the 2025 PDG update, accessed 2026-05-16.  The same sidecar block records
the PDG Table 67.1 products: \(0.2169(6)\) for \(K^\pm e3\),
\(0.2168(10)\) for \(K^\pm\mu3\), \(0.2162(5)\) for \(K_L e3\),
\(0.2165(6)\) for \(K_L\mu3\), \(0.2169(8)\) for \(K_S e3\), and
\(0.2125(47)\) for \(K_S\mu3\).  Additional \texttt{pdg\_or\_equivalent}
entries record the FLAG \(N_f=2+1+1\) normalization \(f_+(0)=0.9698(17)\)
and the PDG-derived \(|V_{us}|=0.22330(53)\); these are normalization inputs,
not separate measured \(K_{\ell3}\) rates.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is a tree-level charged-current process, not a neutral-meson
\(\Delta F=2\) observable.  In the current quark scan it is relevant mainly
as the semileptonic source behind the fitted \(|V_{us}|\) target and the
EW002 first-row unitarity test.  Nonminimal warped models with modified
\(W\)-quark couplings, vector-like fermion mixing, lepton nonuniversality, or
right-handed charged currents could shift the extracted \(V_{us}\) or the
\(K_{\mu3}/K_{e3}\) consistency test, but a minimal KK-gluon flavor analysis
does not map this measurement into the existing operator basis.

\subsection*{Post-2008 developments}
The 2008 RS-flavor baseline \texttt{CsakiFalkowskiWeiler:RSFlavor2008}
centered on flavor-changing neutral constraints, so the post-2008 K018 story
is precision charged-current consolidation.  The sidecar entries
\texttt{FlaviaNet2010:K018:average\_fplus\_vus} and
\texttt{FlaviaNet2010:K018:r\_mue} record the 2010 FlaviaNet average
\(|V_{us}|f_+(0)=0.2163(5)\) and \(K_{\mu3}/K_{e3}\) universality ratio
\(r_{\mu e}=1.002(5)\).  The 2025 PDG update keeps the same source-level
convention while tightening the average to \(0.21656(35)\).  FLAG 2024 supplies
the auxiliary lattice normalization, \(f_+(0)=0.9698(17)\), and the derived
\(|V_{us}|=0.22328(58)\), which feed the CKM-unitarity entry rather than
replacing the measured K018 product.

\subsection*{Constraint validity and model dependence}
The measured \(|V_{us}|f_+(0)\) product is experimentally robust but depends
on consistent radiative, isospin, and phase-space conventions.  The derived
\(|V_{us}|\) additionally depends on the lattice \(f_+(0)\) average.  As an
RS constraint, K018 is model-dependent: it is a charged-current CKM and
lepton-universality diagnostic, not a standalone FCNC bound unless the model
specifies nonstandard \(W\), scalar, tensor, or right-handed-current effects.

\subsection*{Code coverage in this repo}
\textbf{PARTIAL.}  The repo has a generic CKM target containing \(|V_{us}|\):
\texttt{quarkConstraints/scan.py:43} documents the PDG-derived CKM averages,
\texttt{quarkConstraints/scan.py:247} labels the reduced CKM observable as
\texttt{Vus}, and \texttt{tests/test\_quark\_fit.py:587} anchors the target
against PDG 2024.  The coverage grep found no \(K_{\ell3}\) decay-rate,
\(|V_{us}|f_+(0)\), \(f_+(0)\), \(K_{e3}\), or \(K_{\mu3}\) implementation.
The modern flavor surface is still limited to \(\varepsilon_K\), \(K\),
\(B_d\), \(B_s\), and \(D0\) systems at
\texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A live K018 constraint would need a charged-current
semileptonic likelihood or EFT wrapper, radiative/isospin convention
bookkeeping, lattice \(f_+(0)\) provenance, and a decision about whether it is
implemented as a direct \(V_{us}\) target, an EW002 sub-input, or a BSM
charged-current operator constraint.  The existing \(\Delta F=2\)
SLL/SLR/VLL/VRR/LR machinery does not cover it.

\subsection*{Key references}
\begin{itemize}
\item \texttt{PDG2025:K018Kl3}: PDG 2025 \(K_{\ell3}\) product average and mode values.
\item \texttt{FLAG2024:K018KaonSemileptonic}: lattice \(f_+(0)\) normalization and derived \(|V_{us}|\).
\item \texttt{FlaviaNet:K018Kaon2010}: post-2008 \(K_{\ell3}\) consolidation and \(r_{\mu e}\).
\item \texttt{CsakiFalkowskiWeiler:RSFlavor2008}: 2008 warped-flavor context.
\end{itemize}
