% Flavor catalog process: C001
% family: charm
% owner_agent_id: PKA-C001
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C001.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{C001: \(D^0-\bar D^0\) Mixing}

\subsection*{Process}
\textbf{Standard notation:} neutral-charm mixing, parameterized by
\(x_D=\Delta m_D/\Gamma_D\), \(y_D=\Delta\Gamma_D/(2\Gamma_D)\), and
\(\Delta m_D=|m_1-m_2|\).  This entry covers the CP-even mixing magnitudes
used for RS-flavor constraints; the dedicated CP-violation observables
\(|q/p|\) and \(\phi_D\) belong to C002.

\subsection*{PDG / equivalent value(s)}
The headline values are the HFLAV CKM25 all-CPV global-fit results, version
through 14 September 2025:
\[
  x_D=(0.405\pm0.043)\%,\qquad
  y_D=(0.636\pm0.024)\%.
\]
The 95\% C.L. intervals are \(x_D\in[0.320,0.489]\%\) and
\(y_D\in[0.590,0.682]\%\).  These values are traced to
\texttt{flavor\_catalog/references/C001/hflav\_ckm25\_dmixing\_global\_fit.txt}
and to the PDG 2025 Table 70.7 excerpt.  PDG Live separately gives
\[
  \Delta m_D=(0.997\pm0.116)\times10^{10}\hbar\,{\rm s}^{-1}
             =(6.56\pm0.76)\times10^{-15}\,{\rm GeV},
\]
from \texttt{flavor\_catalog/references/C001/pdg2025\_deltam\_d\_pdgLive.txt}.
For the orchestrator-requested \(\delta y\) block, the sidecar records the
latest HFLAV/LHCb CPV-sensitive input
\(\Delta y=(0.031\pm0.035\pm0.013)\%\); it also records the derived
\(\Delta\Gamma_D/\Gamma_D=2y_D=(1.272\pm0.048)\%\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic warped models, KK-gluon and other heavy neutral exchanges generate
\(\Delta C=2\) four-quark operators connecting \(u\) and \(c\).  The same
operator-basis logic used for \(K\), \(B_d\), and \(B_s\) mixing applies, but
the charm system is up-sector and long-distance dominated.  It is therefore a
useful complementary test of whether the scan's flavor alignment suppresses
both down- and up-sector neutral currents.

\subsection*{Post-2008 developments}
The CFW 2008 baseline already treated warped anarchic flavor as strongly
constrained, with generic RS KK-gluon scales around \(21\) TeV and composite
pseudo-Goldstone scenarios around \(33\) TeV.  Since then, the charm-mixing
experimental picture has become much sharper.  LHCb's 2021
\(D^0\to K_S^0\pi^+\pi^-\) analysis observed a nonzero neutral-charm
mass difference with significance above seven standard deviations, and the
current HFLAV/PDG global fits now exclude the no-mixing point at more than
\(11.5\sigma\).  The same HFLAV fit still finds indirect CP violation
consistent with zero, so the CP-even magnitudes remain the clean C001 inputs.

\subsection*{Constraint validity and model dependence}
As a new-physics constraint this is robust in the sense that any short-distance
\(\Delta C=2\) amplitude contributes to \(M_{12}^D\).  It is also
SM-theory-limited: the observed mixing is believed to be dominated by
long-distance Standard Model amplitudes that are hard to compute.  The safe
catalog interpretation is therefore conservative, bounding the magnitude of a
new-physics contribution rather than subtracting a precise SM prediction.

\subsection*{Code coverage in this repo}
\textbf{YES.}  The legacy lane has a default D-mixing input at
\texttt{quarkConstraints/deltaf2.py:252}, with reject reason
\texttt{d\_mix} at \texttt{quarkConstraints/deltaf2.py:256}, D0 hadronic inputs
starting at \texttt{quarkConstraints/deltaf2.py:655}, and
\texttt{DELTA\_M\_D\_EXP} at \texttt{quarkConstraints/deltaf2.py:665}.  The
numeric evaluator is \texttt{evaluate\_d0\_mixing} at
\texttt{quarkConstraints/deltaf2.py:941}.  The scan writes
\texttt{d\_mix\_ratio} at \texttt{quarkConstraints/scan.py:103} and
\texttt{quarkConstraints/scan.py:439}.  The modern policy surface also lists
\(D^0\) at \texttt{quarkConstraints/modern/phenomenology.py:23} and evaluates
the bridge result at \texttt{quarkConstraints/modern/phenomenology.py:1356}.

\subsection*{Implementation difficulty}
\textbf{LOW.}  The existing \(\Delta F=2\) machinery already contains the
D0 evaluator and the required VLL/VRR/LR operator structure.  A future
production update would mainly refresh the experimental value and document the
conservative long-distance treatment, not add a new operator basis.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{hflav\_ckm25\_dmixing\_global\_fit},
\texttt{pdg2025\_deltam\_d\_pdgLive},
\texttt{pdg2025\_dmixing\_review\_table70\_7},
\texttt{lhcb2021\_arxiv2106\_03744}, and
\texttt{cfw2008\_arxiv0804\_1954}.
