% Flavor catalog process: C003
% family: charm
% owner_agent_id: PKA-C003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{C003: \(\Delta A_{CP}(D^0\to K^+K^-,\pi^+\pi^-)\)}{C003: Delta ACP in D0 -> KK, pi pi}}

\subsection*{Process}
\textbf{Standard notation:} \(\Delta A_{CP}\equiv
A_{CP}(D^0\to K^+K^-)-A_{CP}(D^0\to\pi^+\pi^-)\).  This entry covers
time-integrated direct CP violation in singly Cabibbo-suppressed neutral-charm
decays; indirect CP violation in charm mixing is cataloged separately.

\subsection*{PDG / equivalent value(s)}
The canonical equivalent source is HFLAV.  The direct-vs-indirect CPV
combination updated in 2025 gives
\[
  \Delta a_{CP}^{\rm dir}=(-0.159\pm0.029)\% ,
\]
with \(a_{CP}^{\rm ind}=(-0.010\pm0.012)\%\) and a no-CPV discrepancy quoted
as \(5.3\sigma\).  The local snapshot is
\texttt{flavor\_catalog/references/C003/hflav2025\_direct\_indirect\_cpv.txt}.
The LHCb 2019 discovery anchor gives
\[
  \Delta A_{CP}=(-15.4\pm2.9)\times10^{-4}=(-0.154\pm0.029)\% ,
\]
as recorded in \texttt{lhcb2019\_arxiv1903\_08726.txt}.  HFLAV CKM25 also
lists the same measured input \(A_{CP}^K-A_{CP}^{\pi}=(-0.154\pm0.029)\%\)
and the all-CPV fit parameters \(A_{\pi}=(0.225\pm0.057)\%\) and
\(A_K=(0.068\pm0.051)\%\), traced to
\texttt{hflav\_ckm25\_dcpv\_inputs.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped flavor generically carries new CP phases in both up- and
down-sector flavor transitions.  Unlike neutral-charm mixing, this is not a \(\Delta C=2\)
mixing constraint: it probes \(\Delta C=1\) nonleptonic amplitudes, including
possible chromomagnetic dipoles and four-quark penguin structures.  It is
therefore a diagnostic for BSM CP phases in \(c\to u\) transitions that can be
hidden by a neutral-meson-mixing-only scan.

\subsection*{Post-2008 developments}
The CFW 2008 RS-flavor baseline predates the charm direct-CP observation.
The important post-2008 change is experimental: LHCb reported the first
observation of CP violation in charm decays in 2019, and HFLAV now provides a
compact direct-vs-indirect CPV combination with percent-level fit parameters.
The 2025 CKM25 charm fit additionally folds the \(\Delta A_{CP}\) input into a
global all-CPV fit together with \(A_K\) and \(A_{\pi}\).

\subsection*{Constraint validity and model dependence}
The experimental observable is robust because the difference cancels many
production and detection asymmetries.  Interpreting it as a bound on a specific
new-physics Wilson coefficient is much less clean: Standard Model long-distance
charm amplitudes are difficult to compute, and the HFLAV extraction separates
direct and indirect CPV using small mixing corrections.  Treat this as a
model-dependent \(\Delta C=1\) CP-phase constraint, not as a clean
short-distance subtraction.

In down-aligned or kaon-protected RS variants, up-sector observables become
leading rather than secondary diagnostics.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required grep finds neutral \(D^0\)-mixing support but no
direct charm CP-asymmetry implementation.  The current implemented charm
surface is \texttt{evaluate\_d0\_mixing} at
\texttt{quarkConstraints/deltaf2.py:941}; the modern policy labels \(D^0\) as
conservative non-CP mixing at \texttt{quarkConstraints/modern/phenomenology.py:46}.
Focused searches for \texttt{DeltaA\_CP}, \texttt{A\_CP}, direct CP, and
\(D^0\to K^+K^-,\pi^+\pi^-\) across the required implementation directories
found no C003 observable.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production integration would require a new \(\Delta C=1\)
operator/matching layer, RG treatment for the relevant four-quark and dipole
operators, and a hadronic-amplitude or likelihood prescription for the
nonleptonic charm modes.  The existing \(\Delta F=2\) basis does not cover it.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{hflav2025\_direct\_indirect\_cpv},
\texttt{hflav\_ckm25\_dcpv\_inputs},
\texttt{lhcb2019\_arxiv1903\_08726}, and
\texttt{cfw2008\_arxiv0804\_1954}.
