% Flavor catalog process: C004
% family: charm
% owner_agent_id: PKA-C004
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C004.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{C004: \(D^0\to\mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(D^0\to\mu^+\mu^-)\).
This entry covers the rare neutral-charm leptonic decay
\(D^0\to\mu^+\mu^-\), a \(\Delta C=1\), \(c\to u\ell^+\ell^-\)
flavor-changing neutral-current test.  It is distinct from C001/C002
neutral-charm mixing and from semileptonic rare-charm modes because the final
state is purely leptonic and directly probes axial-vector, scalar, and
pseudoscalar short-distance operators.

\subsection*{PDG / equivalent value(s)}
The current PDG Live/API entry S032.28, accessed on 2026-05-16, gives the
headline limit
\[
  \mathcal{B}(D^0\to\mu^+\mu^-) < 2.1\times10^{-9}
  \qquad (90\%~{\rm C.L.}).
\]
The same PDG entry notes that the underlying CMS 2025 analysis reports the
95\% C.L. limit
\[
  \mathcal{B}(D^0\to\mu^+\mu^-) < 2.4\times10^{-9}.
\]
These values are traced to
\texttt{flavor\_catalog/references/C004/pdg2026\_d0\_mumu\_pdgLive.txt}
and \texttt{cms2025\_d0\_mumu\_public.txt}.  The requested LHCb predecessor
used \(9\,{\rm fb}^{-1}\) at 7, 8, and 13 TeV and set
\(\mathcal{B}(D^0\to\mu^+\mu^-)<3.1\times10^{-9}\) at 90\% C.L.,
with a 95\% C.L. companion limit of \(3.5\times10^{-9}\)
(\texttt{lhcb2023\_arxiv2212\_11203}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models can generate flavor-changing \(c\to u\) neutral-current
couplings through KK gauge exchange, electroweak \(Z\)-like effects, Higgs or
radion scalar exchange, or lepton-sector extensions.  This channel is therefore
a useful up-sector \(\Delta C=1\) complement to the implemented \(\Delta F=2\)
D-mixing constraint.  For the present quark-only scan it is best treated as a
catalog and roadmap entry; a live constraint would require lepton-current
normalization in addition to the quark flavor spurions.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 warped-flavor baseline, the experimental bound has
moved by orders of magnitude.  LHCb's full Run 1+2 search improved the rare
charm dimuon limit to \(3.1\times10^{-9}\) at 90\% C.L.  CMS then used the
Run 3 inclusive dimuon-trigger program, \(64.5\,{\rm fb}^{-1}\) from
2022--2023, to set the stronger 95\% C.L. limit of \(2.4\times10^{-9}\).
On the theory side, the 2024 rare-charm EFT analysis incorporated recent
\(\Delta C=1\) data, including \(D^0\to\mu^+\mu^-\), into constraints on
\(C_{7,9,10}^{(\prime)}\) while emphasizing that null-test observables still
leave room for new physics.

\subsection*{Constraint validity and model dependence}
The experimental limit is robust, but the Standard Model prediction is not a
clean short-distance number.  The classic rare-charm calculation estimates the
long-distance two-photon contribution as
\(\mathcal{B}(D^0\to\mu^+\mu^-)_{\gamma\gamma}
\simeq 2.7\times10^{-5}\mathcal{B}(D^0\to\gamma\gamma)\), implying a
long-distance floor of at least \(3\times10^{-13}\) for the assumptions quoted
there.  The safe catalog use is therefore an upper bound on extra
short-distance contributions, not a precision SM subtraction.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps and a focused search for
\texttt{D0.*mu}, \texttt{c.?->.?u}, \texttt{rare.?charm},
\texttt{C10}, \texttt{C\_S}, \texttt{C\_P}, and scalar/pseudoscalar rare-decay
terms found no live \(D^0\to\mu^+\mu^-\) implementation in
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, or \texttt{tests/}.  Nearby hits are
unrelated: \(D^0\) mixing appears at \texttt{quarkConstraints/deltaf2.py:256}
and \texttt{quarkConstraints/deltaf2.py:941}, while
\(\mu\to e\gamma\) is handled separately at
\texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  \(D^0\to\mu^+\mu^-\) is a new \(c\to u\) dilepton mode
requiring a new \(\Delta C=1\) Wilson-coefficient normalization and a documented
long-distance subtraction; it is not covered by the existing \(\Delta F=2\)
backend.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{PDG2026:D0MuMu}, \texttt{CMS2025:D0MuMu},
\texttt{LHCb2023:D0MuMu},
\texttt{BurdmanGolowichHewettPakvasa2002:RareCharm},
\texttt{GisbertHillerSuelmann2024:RareCharmEFT}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
