% Flavor catalog process: C005
% family: charm
% owner_agent_id: PKA-C005
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C005.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{C005: \(D^0\to e^+e^-\)}{C005: D0 -> e+e-}}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(D^0\to e^+e^-)\).  This entry
covers the rare neutral-charm leptonic decay \(D^0\to e^+e^-\), a
\(\Delta C=1\), \(c\to u e^+e^-\) flavor-changing neutral-current probe.
Charge-conjugate modes are implicit in the experimental listings.  It is the
electron-mode counterpart to C004, \(D^0\to\mu^+\mu^-\), but has a separate
experimental record.

\subsection*{PDG / equivalent value(s)}
The current PDG Live/API entry \(S032.39\), accessed on 2026-05-16, gives
\[
  \mathcal{B}(D^0\to e^+e^-) < 7.9\times10^{-8}
  \qquad (90\%~{\rm C.L.}).
\]
The sidecar source key is \texttt{PDG2026:D0Ee}, with local snapshot
\texttt{pdg2026\_d0\_ee\_pdgLive.txt}.  The PDG-used input is the Belle 2010
search with \(660\,{\rm fb}^{-1}\) at KEKB.  Belle reports the same
\(7.9\times10^{-8}\) upper limit and no signal evidence
(\texttt{Belle2010:D0Ee};
\texttt{belle2010\_arxiv1003\_2345.txt}).  The independent BaBar 2012 search
used \(468\,{\rm fb}^{-1}\) and set the weaker \(1.7\times10^{-7}\) upper
limit at 90\% CL
(\texttt{BaBar2012:D0EeMuMuEMu};
\texttt{babar2012\_arxiv1206\_5419.txt}).  The dispatch note called this an
LHCb upper limit, but the accessed PDG/API measurement list contains no LHCb
\(D^0\to e^+e^-\) entry
(\texttt{pdg2026\_d0\_ee\_pdgLive.txt}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models can induce up-sector flavor-changing neutral currents
through nonuniversal KK gauge couplings, flavor-violating \(Z\)-like effects,
Higgs/radion scalar exchange, or lepton-sector extensions
(\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}).  C005 therefore tests a
pure \(c\to u\) dilepton amplitude rather than the four-quark \(\Delta F=2\)
operator basis used for neutral \(D\)-mixing.  For the current quark-only scan
it is a catalog and roadmap process; a live veto would need both the
\(c\to u\) current and electron-current normalization.

\subsection*{Post-2008 developments}
The 2008 RS-flavor baseline predates the Belle and BaBar leptonic \(D^0\)
searches (\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}).  The main
post-2008 experimental development is Belle's 2010 improvement to the current
PDG limit, followed by BaBar's 2012 cross-check in a separate
\(e^+e^-\to c\bar c\) sample
(\texttt{Belle2010:D0Ee}, \texttt{BaBar2012:D0EeMuMuEMu}).  Unlike C004,
which has newer hadron-collider dimuon searches, the accessed C005 PDG record
still uses the Belle result as the headline input.  Rare-charm theory work
emphasizes that purely leptonic \(D^0\) limits are clean null tests
experimentally but require care when separating short-distance new physics from
long-distance charm dynamics
(\texttt{BurdmanGolowichHewettPakvasa2002:RareCharm}).

\subsection*{Constraint validity and model dependence}
The upper limit itself is experimentally robust.  Its interpretation as an RS
constraint is model dependent because the electron mode is helicity sensitive,
bremsstrahlung and electron identification enter the experimental acceptance,
and the Standard Model rare-charm amplitude is not a precision short-distance
prediction.  A conservative use is an upper bound on additional short-distance
\(c\to u e^+e^-\) amplitudes in a specified operator basis, not a direct
subtraction against a sharply predicted Standard Model rate
(\texttt{BurdmanGolowichHewettPakvasa2002:RareCharm}).

\subsection*{Code coverage in this repo}
\textbf{NO.}  The PKA greps and a focused search for
\texttt{D0.*e+e-}, \texttt{D0.*ee}, \texttt{c.?->.?u.*e}, and
\texttt{rare.?charm} found no \(D^0\to e^+e^-\) implementation in
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, or \texttt{tests/}.  Nearby hits are
not C005: \(D^0\) mixing is configured at
\texttt{quarkConstraints/deltaf2.py:252} and evaluated at
\texttt{quarkConstraints/deltaf2.py:941}; the modern policy likewise lists
only \(D^0\) mixing at \texttt{quarkConstraints/modern/phenomenology.py:23}
and \texttt{quarkConstraints/modern/phenomenology.py:668}.  The
\(\mu\to e\gamma\) dipole check at
\texttt{flavorConstraints/muToEGamma.py:75} is a separate LFV observable.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use would require a new \(\Delta C=1\) rare
leptonic module with vector, axial-vector, scalar, and pseudoscalar
normalizations, electron-mode acceptance conventions, and a documented
long-distance treatment.  The existing \(\Delta F=2\) SLL/SLR/VLL/VRR/LR
basis is not enough.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{PDG2026:D0Ee}, \texttt{Belle2010:D0Ee},
\texttt{BaBar2012:D0EeMuMuEMu},
\texttt{BurdmanGolowichHewettPakvasa2002:RareCharm}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.  Numeric claims above are
tied to these sidecar source keys and local snapshots.
