% Flavor catalog process: C007
% family: charm
% owner_agent_id: PKA-C007
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C007.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{C007: \(D^+\to\pi^+\mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:}
\(\mathcal{B}(D^+\to\pi^+\mu^+\mu^-)\).
This entry covers the rare charged-charm semileptonic decay
\(D^+\to\pi^+\mu^+\mu^-\), a \(\Delta C=1\), \(c\to u\mu^+\mu^-\)
flavor-changing neutral-current probe.  Charge-conjugate modes are implied by
the experimental sources.

\subsection*{PDG / equivalent value(s)}
The current PDG Live/API entry S031.42, accessed on 2026-05-16, lists
\[
  \mathcal{B}(D^+\to\pi^+\mu^+\mu^-) < 6.7\times 10^{-8}
  \qquad (90\%~{\rm C.L.})
\]
from the LHCb 2021 search in \(1.6\,{\rm fb}^{-1}\) of 2016 \(pp\) data.
The LHCb source table gives the companion 95\% C.L. limit
\(7.4\times10^{-8}\).  The predecessor LHCb 2013 nonresonant search, using
\(1.0\,{\rm fb}^{-1}\) at \(\sqrt{s}=7\,{\rm TeV}\), reported
\(7.3(8.3)\times10^{-8}\) at 90\% (95\%) C.L.  These numbers are traced to
\texttt{flavor\_catalog/references/C007/pdg2026\_dplus\_piplus\_mumu\_pdgLive.txt},
\texttt{lhcb2021\_arxiv2011\_00217.txt}, and
\texttt{lhcb2013\_arxiv1304\_6365.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models can induce up-sector flavor-changing neutral currents
through nonuniversal KK gauge couplings, \(Z\)-like flavor violation, Higgs or
radion scalar effects, and lepton-current extensions.  This process is the
charged semileptonic \(\Delta C=1\) analogue of the implemented neutral
\(D^0\)-mixing lane: it probes \(c\to u\) vector, axial-vector, and possible
scalar semileptonic operators rather than four-quark \(\Delta F=2\) operators.
It is therefore a roadmap constraint for a broader flavor backend, not a
constraint currently applied by the quark scan.

\subsection*{Post-2008 developments}
The arXiv:0804.1954 RS-flavor baseline predates the modern LHCb rare-charm
program.  Since then, LHCb first set nonresonant \(D^+\to\pi^+\mu^+\mu^-\)
limits at the \(10^{-8}\) level in 2013 and then folded the channel into a
2021 search for 25 rare or forbidden \(D^+\) and \(D_s^+\) decays.  The 2021
analysis found no evidence in any of the investigated modes and tightened the
PDG-listed C007 limit to \(6.7\times10^{-8}\) at 90\% C.L.  On the theory side,
post-2008 rare-charm EFT work, especially de Boer and Hiller 2015, clarified
that \(D_{(s)}\to P\ell^+\ell^-\) branching-ratio recasts must separate
short-distance Wilson coefficients from resonance-dominated long-distance
physics; the LHCb 2021 introduction quotes short-distance SM branching
fractions of order \(10^{-12}\), with dilepton resonances dominating the
physical spectrum.

\subsection*{Constraint validity and model dependence}
The experimental upper limit is robust as a counting result, but its use as an
RS short-distance bound is model dependent.  Long-distance hadronic resonances,
weak-annihilation effects, and the exact phase-space definition of the
``nonresonant'' signal matter.  A conservative catalog use is an upper bound on
additional short-distance \(c\to u\mu^+\mu^-\) contributions in the same
experimental region, with an explicit recast needed before treating it as a
hard scan veto.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps and a focused search for
\texttt{D+.*pi+.*mu}, \texttt{c.?->.?u}, \texttt{rare.?charm},
\texttt{semileptonic.*charm}, \texttt{C9}, and \texttt{C10} found no
\(D^+\to\pi^+\mu^+\mu^-\) implementation in \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, or \texttt{tests/}.  Nearby hits are unrelated:
\(D^0\) mixing appears at \texttt{quarkConstraints/deltaf2.py:252} and
\texttt{quarkConstraints/deltaf2.py:941}, the modern policy lists only
\(D^0\) mixing at \texttt{quarkConstraints/modern/phenomenology.py:23} and
\texttt{quarkConstraints/modern/phenomenology.py:668}, and
\(\mu\to e\gamma\) is separate at
\texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production implementation needs a new \(\Delta C=1\)
semileptonic operator basis and matching for \(C_{9,10}^{(\prime)}\) and
possible scalar/tensor terms, plus a \(D\to\pi\mu^+\mu^-\) mode calculation
with form factors, phase-space cuts, and a documented treatment of resonant
long-distance contributions.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{PDG2026:DPlusPiMuMu}, \texttt{LHCb2021:DPlusPiMuMu},
\texttt{LHCb2013:DPlusPiMuMu},
\texttt{DeBoerHiller2015:RareCharmLeptons}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
