% Flavor catalog process: C008
% family: charm
% owner_agent_id: PKA-C008
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: C008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{C008: \texorpdfstring{\(D^+\to\pi^+e^\pm\mu^\mp\)}{D+ -> pi+ e mu}}

\subsection*{Process}
\textbf{Standard notation:}
\(\mathcal{B}(D^+\to\pi^+e^+\mu^-)\) and
\(\mathcal{B}(D^+\to\pi^+e^-\mu^+)\).  This entry covers the two
opposite-sign charged-lepton-flavor-violating semileptonic charm decays
usually summarized as \(D^+\to\pi^+e^\pm\mu^\mp\).  Charge-conjugate
decays are implied by the experimental sources.

\subsection*{PDG / equivalent value(s)}
The sidecar sources \texttt{PDG2026:DPlusPiEMuPlus} and
\texttt{PDG2026:DPlusPiEMuMinus}, PDG Live/API entries S031.110 and
S031.111 accessed on 2026-05-16, list separate 90\% C.L. upper limits:
\[
  \mathcal{B}(D^+\to\pi^+e^+\mu^-) < 2.1\times10^{-7},
  \qquad
  \mathcal{B}(D^+\to\pi^+e^-\mu^+) < 2.2\times10^{-7}.
\]
Both current limits come from \texttt{LHCb2021:DPlusPiEMu}, a search in
\(1.6\,{\rm fb}^{-1}\) of 2016 \(pp\) data.  The LHCb table gives companion
95\% C.L. limits of \(2.3\times10^{-7}\) and \(2.2\times10^{-7}\),
respectively.  The predecessor search \texttt{BaBar2011:RareForbiddenCharm},
using \(384\,{\rm fb}^{-1}\), reported 90\% C.L. limits of
\(2.9\times10^{-6}\) and \(3.6\times10^{-6}\).  These values are traced to
\texttt{flavor\_catalog/references/C008/pdg2026\_dplus\_piplus\_ep\_mum\_pdgLive.txt},
\texttt{pdg2026\_dplus\_piplus\_em\_mup\_pdgLive.txt},
\texttt{lhcb2021\_arxiv2011\_00217.txt}, and
\texttt{babar2011\_arxiv1107\_4465.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This process tests a product of up-sector flavor violation and charged-lepton
flavor violation: schematically, short-distance operators such as
\((\bar u\,\Gamma c)(\bar e\,\Gamma'\mu)\).  Minimal quark-only RS scans do
not generate a live constraint for this mode, but lepton-sector extensions
with nonuniversal KK gauge couplings, scalar exchange, or flavor-violating
brane terms can generate it.  It is therefore a useful catalog marker for a
future combined quark-plus-lepton flavor backend rather than a current veto.

\subsection*{Post-2008 developments}
The arXiv:0804.1954 RS-flavor baseline
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor} predates the modern
rare/forbidden semileptonic charm searches.  BaBar
\texttt{BaBar2011:RareForbiddenCharm} subsequently set or improved limits for
charged-charm LFV modes in \(384\,{\rm fb}^{-1}\).  LHCb
\texttt{LHCb2021:DPlusPiEMu} searched for 25 rare and forbidden \(D^+\) and
\(D_s^+\) modes in 2016 data, found no significant deviation from background,
and tightened the two C008 charge channels to the present
\(2\times10^{-7}\)-level limits.

\subsection*{Constraint validity and model dependence}
The experimental limits are robust upper bounds on the listed exclusive
branching fractions.  Their interpretation as RS constraints is model
dependent because the mapping requires a \(\Delta C=1\), LFV semileptonic
operator basis, \(D\to\pi\) form factors, lepton-chirality assumptions, and a
phase-space treatment matching the LHCb analysis.  The Standard Model
background for charged-LFV final states is negligible for catalog purposes.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The sidecar \texttt{code\_coverage} block records the required
coverage greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/}, plus a focused search for
\texttt{D+.*pi+.*e.*mu}, \texttt{pi+.*e.*mu}, rare-charm, and
\texttt{c->u} LFV patterns, found no \(D^+\to\pi^+e^\pm\mu^\mp\)
implementation.  Nearby hits are unrelated: \(D^0\) mixing appears at
\texttt{quarkConstraints/deltaf2.py:252} and
\texttt{quarkConstraints/deltaf2.py:941}, the modern policy lists only
\(D^0\) mixing at \texttt{quarkConstraints/modern/phenomenology.py:23} and
\texttt{quarkConstraints/modern/phenomenology.py:668}, and the implemented
LFV observable is \(\mu\to e\gamma\) at
\texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production implementation needs a new \(\Delta C=1\)
LFV semileptonic operator basis and a \(D^+\to\pi^+e\mu\) branching-fraction
calculation with form factors, phase-space acceptance, and chirality
conventions.  This is beyond adding an input to the existing \(\Delta F=2\)
or \(\mu\to e\gamma\) paths.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{PDG2026:DPlusPiEMuPlus}, \texttt{PDG2026:DPlusPiEMuMinus},
\texttt{LHCb2021:DPlusPiEMu}, \texttt{BaBar2011:RareForbiddenCharm}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
