% Flavor catalog per-process template.
% process_id: EW003
% family: top_higgs_ew
% owner_agent_id: PKA-EW003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: EW003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(|V_{cb}|\) and \(|V_{ub}|\) Inclusive--Exclusive Tensions}{Vcb and Vub Inclusive--Exclusive Tensions}}

\subsection*{Process}
This entry covers the inclusive versus exclusive determinations of
\(|V_{cb}|\) and \(|V_{ub}|\) from semileptonic \(b\)-hadron decays.
Although the underlying modes are beauty charged currents, the NIT-1 process
id places the entry in \texttt{top\_higgs\_ew}; it is an electroweak CKM-input
diagnostic with direct ties to \(b\to c\tau\nu\) and \(b\to u\tau\nu\) BSM
fits.

\subsection*{PDG / equivalent value(s)}
The canonical PDG 2024 snapshot is
\texttt{flavor\_catalog/references/EW003/pdg\_2024\_vcb\_vub.txt}.  PDG quotes
\(|V_{cb}|_{\rm incl}=(42.2\pm0.5)\times10^{-3}\) and
\(|V_{cb}|_{\rm excl}=(39.8\pm0.6)\times10^{-3}\), with the scaled average
\((41.1\pm1.2)\times10^{-3}\) to be treated with caution because the two inputs
are only marginally consistent, about \(3.0\sigma\).  For \(|V_{ub}|\), PDG
quotes \((4.13\pm0.12_{\rm exp}{}^{+0.13}_{-0.14}{}_{\rm theo}
\pm0.18_{\Delta{\rm model}})\times10^{-3}\) inclusive and
\((3.70\pm0.10\pm0.12)\times10^{-3}\) exclusive, giving
\((3.82\pm0.20)\times10^{-3}\) after error scaling.  HFLAV's 2023
semileptonic report refines the split: the preferred inclusive
\(|V_{cb}|\) input is \((41.97\pm0.48)\times10^{-3}\), while the combined
exclusive fit gives \((|V_{ub}|,|V_{cb}|)=
(3.43\pm0.12,39.77\pm0.46)\times10^{-3}\).  FLAG 2024 gives lattice-anchored
exclusive values \(|V_{cb}|=39.23(65)\times10^{-3}\) for
\(B\to D^*\ell\nu\) with \(N_f=2+1\), and
\(|V_{ub}|=(3.61\pm0.16)\times10^{-3}\) for \(B\to\pi\ell\nu\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
The present scan fits CKM observables as output of anarchic quark masses, so
the inclusive--exclusive split is a diagnostic for how much CKM target choice
can move flavor predictions.  In an RS extension with non-SM charged-current
operators, the same observables also set the normalization for \(b\to c\) and
\(b\to u\) semitauonic Wilson-coefficient fits.

\subsection*{Post-2008 developments}
Relative to arXiv:0804.1954, the main change is not a new RS formula but a
new input ecosystem.  Belle, Belle II, BaBar, and LHCb now feed HFLAV averages;
inclusive \(|V_{cb}|\) uses mature kinetic and \(q^2\)-moment heavy-quark
expansion fits; and FLAG 2024 provides full-recoil lattice-plus-experiment
fits for \(B\to D^{(*)}\ell\nu\) and \(B\to\pi\ell\nu\).  The same period also
turned \(R(D^{(*)})\), \(B_c\to\tau\nu\), and \(B\to(\pi,\rho,\omega)\tau\nu\)
into standard charged-current EFT interpretation channels.

\subsection*{Constraint validity and model dependence}
For \(e,\mu\) final states these are CKM extraction inputs, not clean
standalone BSM exclusions.  Inclusive values depend on heavy-quark expansion
schemes and shape-function/model choices, while exclusive values depend on
lattice form factors, parameterization choices, and experimental correlations.
Tau-mode translations are more model dependent because vector, scalar, and
tensor operators can change both rates and templates.

\subsection*{Code coverage in this repo}
\textbf{PARTIAL}.  CKM target handling exists, including \(|V_{cb}|\) and
\(|V_{ub}|\) tolerances at \texttt{quarkConstraints/scan.py:42},
\texttt{quarkConstraints/scan.py:46}, \texttt{quarkConstraints/scan.py:47},
\texttt{quarkConstraints/scan.py:52}, and the regression check at
\texttt{tests/test\_quark\_fit.py:575}.  No grep hit implements inclusive or
exclusive semileptonic \(B\) rates, \(B\to D^{(*)}\ell\nu\),
\(B\to\pi\ell\nu\), or \(b\to c/u\,\tau\nu\) WET operators in
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, or \texttt{tests/}.

\subsection*{Implementation difficulty}
\textbf{HIGH}.  A production constraint would need a new charged-current
semileptonic likelihood, scheme handling for inclusive extractions, lattice
form-factor inputs for exclusive modes, and optional \(b\to c/u\,\tau\nu\)
Wilson operators.  This is outside the existing \(\Delta F=2\) basis.

\subsection*{Key references}
\texttt{pdg\_2024\_vcb\_vub};
\texttt{hflav\_2023\_semileptonic\_report};
\texttt{flag\_2024\_b\_semileptonic\_lattice};
\texttt{iguro\_2024\_bc\_tau\_global\_fit};
\texttt{bhatta\_2021\_bu\_tau\_np};
\texttt{cfw\_2008\_rs\_flavor\_baseline}.
