% Flavor catalog per-process draft.
% process_id: T001
% family: top_higgs_ew
% owner_agent_id: PKA-T001
% Canonical metadata sidecar: T001.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to c Z\)}{t -> c Z} FCNC Top Decay}

\subsection*{Process}
The observable is the flavor-changing neutral-current branching fraction
\(\mathcal{B}(t\to cZ)\), catalog id T001 in the top/Higgs/electroweak
family.  It covers direct LHC searches for a top quark coupled to a charm
quark and a \(Z\) boson, including analyses that combine \(t\bar t\) events
with one FCNC top decay and single-top production in association with a
\(Z\) boson.

\subsection*{PDG-or-equivalent value}
The source-of-truth numerical entries are the \texttt{pdg\_or\_equivalent}
block in \texttt{T001.yaml}.  The PDG 2025 top-quark listing quotes the ATLAS
Run-2 limits in units of \(10^{-3}\) (\texttt{PDG2025TopFCNCTZQ}):
\[
  \mathcal{B}(t\to Zc) < 1.3\times 10^{-4}
\]
for the left-handed \(tcZ\) benchmark
(\texttt{PDG2025:T001:tZc\_left}) and
\[
  \mathcal{B}(t\to Zc) < 1.2\times 10^{-4}
\]
for the right-handed benchmark (\texttt{PDG2025:T001:tZc\_right}), both at
95\% CL.  The same PDG table records the CMS comparison limit
\(\mathcal{B}(t\to Zc)<0.049\%\), also at 95\% CL
(\texttt{CMS2017:T001:tZc}).  The local PDG snapshot is
\texttt{flavor\_catalog/references/T001/pdg\_2025\_top\_fcnc\_tzq.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped or partially composite flavor models, non-universal fermion profiles
and mass-basis rotations can produce flavor off-diagonal neutral-current
couplings.  The \(t\to cZ\) channel is especially diagnostic of the top sector:
it probes the \(t\)-\(c\) rotation and the degree of right-handed top
compositeness more directly than light-meson \(\Delta F=2\) observables.  A
direct top FCNC limit is therefore complementary to the existing kaon, \(B\),
and \(D\)-mixing lane rather than a substitute for it.

\subsection*{Post-2008 developments}
The CFW-era reference point is arXiv:0804.1954, which framed warped flavor
constraints before the full LHC top-FCNC program.  Since then, the key
experimental change is the move from Tevatron and early-LHC inclusive \(t\to
Zq\) limits to flavor-separated LHC constraints.  CMS used
\(19.7~\mathrm{fb}^{-1}\) at \(\sqrt{s}=8~\mathrm{TeV}\)
(\texttt{CMS2017:T001:dataset}) and found
\(\mathcal{B}(t\to Zc)<0.049\%\) (\texttt{CMS2017:T001:tZc}).  ATLAS later used
\(139~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\)
(\texttt{ATLAS2023:T001:dataset}), combining single-top \(tZ\) production and
\(t\bar t\) FCNC-decay topologies, and improved the \(t\to Zc\) reach to the
\(10^{-4}\) level (\texttt{ATLAS2023:T001:tZc\_left},
\texttt{ATLAS2023:T001:tZc\_right}).  A 2026 RS-specific study,
arXiv:2601.14966, recasts post-LHC constraints on \(Ztc\) and notes that
HL-LHC direct searches may reach an equivalent \(\mathcal{B}(t\to cZ)\) level
of about \(10^{-6}\) (\texttt{AirenFranceschini2026:T001:HL\_LHC\_projection}).

\subsection*{Constraint validity and model dependence}
Experimentally this is a clean upper limit; there is no SM-sized background
from true \(t\to cZ\) decays.  The SM branching estimate is about \(10^{-14}\),
so any observed signal would be unambiguous new physics
(\texttt{AguilarSaavedra2004:T001:SM}; \texttt{PDG2025:T001:SM}).  The
interpretation is not fully model independent: ATLAS quotes separate left- and
right-handed tensor-SMEFT benchmarks, while an RS model may generate vector-like
\(Ztc\) couplings, heavy-vector exchange, or correlated contact interactions.
A scan backend would need to map the RS parameters into a chosen operator
convention before applying the PDG-number as a hard cut.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The PKA reran the required plan greps and a targeted
search for \(t\to cZ\), \(tZc\), \(tcZ\), and generic FCNC text across
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/}.  The only non-doc hits were generic
FCNC prose/comments, not an observable, likelihood, or branching-ratio check.

\subsection*{Implementation difficulty}
The cataloging difficulty is medium, but production integration is \textbf{HIGH}.
The repo has no electroweak top-FCNC operator basis, no \(tcZ\) width or
single-production reinterpretation, and no top-sector flavor-rotation interface.
Implementing it honestly would require a new RS-to-SMEFT or direct \(Ztc\)
matching convention before this limit can be compared to scan points.

\subsection*{Key references}
\texttt{PDG2025TopFCNCTZQ}; \texttt{ATLAS2023TopFCNCTZQ};
\texttt{CMS2017TZQFCNC}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor};
\texttt{AirenFranceschini2026RSTopFCNC}.
