% Flavor catalog per-process draft.
% process_id: T002
% family: top_higgs_ew
% owner_agent_id: PKA-T002
% Canonical metadata sidecar: T002.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to u Z\)}{t -> u Z} FCNC Top Decay}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(t\to uZ)\).
This entry catalogs the flavor-changing neutral-current top decay \(t\to uZ\)
in the top/Higgs/electroweak family.  It covers direct LHC searches for a top
quark coupled to an up quark and a \(Z\) boson, including interpretations that
combine \(t\bar t\) events with one FCNC top decay and single-top production in
association with a \(Z\) boson.

\subsection*{PDG-or-equivalent value}
The source-of-truth numerical entries are the
\texttt{pdg\_or\_equivalent} block in \texttt{T002.yaml}.  The current PDG
2025 top-quark listing quotes the ATLAS AAD 23AS limits in units of
\(10^{-3}\) (\texttt{PDG2025TopFCNCTZQ}):
\[
  \mathcal{B}(t\to Zu) < 6.2\times 10^{-5}
\]
for the left-handed \(tuZ\) benchmark
(\texttt{PDG2025:T002:tZu\_left}) and
\[
  \mathcal{B}(t\to Zu) < 6.6\times 10^{-5}
\]
for the right-handed benchmark (\texttt{PDG2025:T002:tZu\_right}), both at
95\% CL.  The same PDG table records the CMS SIRUNYAN 17E comparison limit
\(\mathcal{B}(t\to Zu)<0.022\%\), also at 95\% CL
(\texttt{CMS2017:T002:tZu}).  The local PDG snapshot is
\texttt{flavor\_catalog/references/T002/pdg\_2025\_top\_fcnc\_tzq.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped models with bulk fermions, non-universal zero-mode profiles and
mass-basis rotations can induce flavor off-diagonal neutral-current \(Z\)
couplings.  The \(t\to uZ\) channel probes the first--third generation
up-sector rotation and is therefore complementary to charm and neutral-meson
constraints.  In anarchic RS language it is sensitive to the same profile and
Yukawa structures that control \(u\)-\(c\)-\(t\) mixing, while remaining a
direct top observable rather than a low-energy hadronic matrix-element
constraint.

\subsection*{Post-2008 developments}
The CFW reference point is arXiv:0804.1954, which framed generic
warped-flavor bounds before the full LHC top-FCNC program
(\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}).  Shortly after it, the
RS-specific Casagrande--Goertz--Haisch--Neubert--Pfoh analysis included
\(t\to c(u)Z\), noting that \(t\to uZ\) is typically about two orders of
magnitude below \(t\to cZ\) in the minimal RS model
(\texttt{Casagrande2008:T002:RS\_suppression}).  Since then the key
experimental development is flavor-separated LHC sensitivity.  CMS used
\(19.7~\mathrm{fb}^{-1}\) at \(\sqrt{s}=8~\mathrm{TeV}\)
(\texttt{CMS2017:T002:dataset}) and found
\(\mathcal{B}(t\to Zu)<0.022\%\) (\texttt{CMS2017:T002:tZu}).  ATLAS later
used \(139~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\)
(\texttt{ATLAS2023:T002:dataset}), combining single-top \(tZ\) production and
\(t\bar t\) FCNC-decay topologies, and improved the \(t\to Zu\) reach to the
\(6\times10^{-5}\) level (\texttt{ATLAS2023:T002:tZu\_left},
\texttt{ATLAS2023:T002:tZu\_right}).

\subsection*{Constraint validity and model dependence}
Experimentally this is a clean 95\% CL upper limit; there is no Standard Model
signal at the observable level.  Aguilar-Saavedra's benchmark SM estimate is
\(\mathcal{B}(t\to uZ)\simeq 8\times10^{-17}\)
(\texttt{AguilarSaavedra2004:T002:SM}).  The interpretation is
operator-dependent: ATLAS quotes left- and right-handed tensor-SMEFT
benchmarks, while an RS model can generate vector-like \(Ztu\) couplings,
KK-mediated contact effects, or correlated shifts in other electroweak
vertices.  A live constraint therefore needs a matching convention before the
branching-ratio limit can be used as a hard scan cut.

In down-aligned or kaon-protected RS variants, top FCNCs become leading rather
than secondary diagnostics.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The PKA reran the required plan greps and a targeted
search for \(t\to uZ\), \(tZu\), \(tuZ\), \(tZq\), and generic FCNC text across
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The only
targeted code-directory hits were generic FCNC prose/comments, not an
observable implementation, likelihood, or branching-ratio check.

\subsection*{Implementation difficulty}
The cataloging difficulty is medium, but production integration is \textbf{HIGH}.
The repo has no electroweak top-FCNC operator basis, no \(tuZ\) decay-width or
single-production reinterpretation, and no top-sector flavor-rotation
interface.  Implementing it honestly would require new RS-to-SMEFT or direct
\(Ztu\) matching before comparing this limit to scan points.

\subsection*{Key references}
\texttt{PDG2025TopFCNCTZQ}; \texttt{ATLAS2023TopFCNCTZQ};
\texttt{CMS2017TZQFCNC}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor};
\texttt{CasagrandeGoertzHaischNeubertPfoh2008RSFlavor}.
