% Flavor catalog per-process draft.
% process_id: T003
% family: top_higgs_ew
% owner_agent_id: PKA-T003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: T003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to c\gamma\)}{t -> c gamma} FCNC Top-Photon Decay}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(t\to c\gamma)\).
This entry catalogs the flavor-changing neutral-current top decay
\(t\to c\gamma\), process id T003 in the top/Higgs/electroweak family.  It
covers LHC searches for a top quark coupled to a charm quark and a photon,
including single-top-plus-photon production and \(t\bar t\) events with one
FCNC top decay.

\subsection*{PDG value}
The sidecar headline uses the CMS-TOP-21-013 Run-2 charm-specific result,
based on \(138~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\)
(\texttt{CMS2024:T003:dataset}):
\[
  \mathcal{B}(t\to c\gamma)<1.51\times10^{-5}
\]
at 95\% CL, with an expected limit of \(1.54\times10^{-5}\)
(\texttt{CMS2024:T003:tcgamma}).  The ATLAS full-Run-2 comparison result used
\(139~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\)
(\texttt{ATLAS2023:T003:dataset}) and gave
\[
  \mathcal{B}(t\to c\gamma)<4.2\times10^{-5}
\]
for a left-handed \(tq\gamma\) coupling and \(<4.5\times10^{-5}\) for a
right-handed coupling (\texttt{ATLAS2023:T003:tcgamma\_left},
\texttt{ATLAS2023:T003:tcgamma\_right}).  The PDG live top summary separately
lists a generic \(t\to\gamma q\), \(q=u,c\), row
\(<9.5\times10^{-6}\) at 95\% CL, defined as
\(\Gamma(t\to\gamma q)/\Gamma(t\to Wb)\); that row is not charm separated
(\texttt{PDG2026:T003:gammaq\_summary}).

\subsection*{Relevance to RS / anarchic flavor}
In anarchic warped flavor, the IR-localized top and non-universal fermion
profiles can generate mass-basis flavor violation in the up sector.  The
top-photon channel probes an electromagnetic dipole or heavy-vector matching
direction that is absent from the existing neutral-meson \(\Delta F=2\) lane.
It is therefore complementary to T001 (\(t\to cZ\)) and T005 (\(t\to cg\)):
the same top-charm rotations can appear with different gauge quantum numbers.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 RS-flavor baseline
(\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}), the main change is
experimental.  The LHC program moved this channel from indirect expectations to
direct full-Run-2 searches with separate \(tu\gamma\) and \(tc\gamma\)
hypotheses.  ATLAS reached the \(4.2\times10^{-5}\) left-handed charm benchmark
in its 2023 result (\texttt{ATLAS2023:T003:tcgamma\_left}).  CMS then used
\(138~\mathrm{fb}^{-1}\) and improved the charm-specific observed limit to
\(1.51\times10^{-5}\) (\texttt{CMS2024:T003:dataset};
\texttt{CMS2024:T003:tcgamma}).  The Standard Model expectation remains tiny:
Aguilar-Saavedra quotes
\(\mathcal{B}(t\to c\gamma)=4.6\times10^{-14}\)
(\texttt{AguilarSaavedra2004:T003:SM}), so present bounds are new-physics
searches rather than SM precision tests.

\subsection*{Constraint validity / model dependence}
The upper limit is experimentally clean because the SM decay rate is
negligible.  Its interpretation is model dependent: CMS quotes a single
nonzero anomalous coupling at a time, while ATLAS separates left- and
right-handed \(tq\gamma\) benchmarks.  A warped-model scan would need to map
its top-sector rotations and electromagnetic dipoles into the same operator
normalization before using the number as a hard exclusion.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required greps across \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(t\to c\gamma\),
\(tc\gamma\), \(tq\gamma\), or top-photon FCNC implementation.  Existing
coverage is limited to neutral-meson \(\Delta F=2\) inputs at
\texttt{quarkConstraints/deltaf2.py:209}, the modern policy list
\(\epsilon_K,K,B_d,B_s,D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}, and a lepton-sector
\(\mu\to e\gamma\) dipole check at \texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Cataloging the external upper limit is straightforward, but a
live RS constraint would require a top electromagnetic FCNC operator
convention, RS-to-SMEFT or direct dipole matching, a \(t\to c\gamma\) width
normalization, and a choice about how to reinterpret production-plus-decay LHC
limits when more than one chirality or flavor coupling is present.

\subsection*{Key references}
\texttt{CMS2024TopFCNCTQGamma}; \texttt{ATLAS2023TopFCNCTQGamma};
\texttt{PDG2026TopGammaQSummary}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}.
