% Flavor catalog per-process draft.
% process_id: T005
% family: top_higgs_ew
% owner_agent_id: PKA-T005
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: T005.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to c g\)}{t -> c g} Top-Gluon FCNC}

\subsection*{Process}
The observable is the flavor-changing neutral-current top decay
\(\mathcal{B}(t\to c g)\), catalog id T005 in the top/Higgs/electroweak
family.  Experimentally it is constrained mainly through anomalous single-top
production, \(c g\to t\), then translated into an equivalent top-decay
branching fraction under a specified chromomagnetic-operator convention.

\subsection*{PDG / equivalent value(s)}
The canonical experimental source is the PDG/pdgLive Q007TUG top-FCNC gluon
datablock, accessed on 2026-05-16
(\texttt{references/T005/pdg\_2025\_top\_tug\_tcg.txt}).  Its current ATLAS
entry, AAD 2022T, uses \(139~\mathrm{fb}^{-1}\) of \(13~\mathrm{TeV}\) \(pp\)
data.  For the charm-gluon production mode it gives
\[
  \sigma(cg\to t)\,{\cal B}(t\to bW)\,{\cal B}(W\to \ell\nu)<4.7~\mathrm{pb}
\]
at 95\% CL, interpreted in the EFT basis as
\[
  |C^{ct}_{uG}|/\Lambda^2 < 0.14~\mathrm{TeV}^{-2},
  \qquad
  {\cal B}(t\to c g)<3.7\times10^{-4}.
\]
The same PDG block records the CMS 7 and 8 TeV comparison result based on
\(5.0~\mathrm{fb}^{-1}\) and \(19.7~\mathrm{fb}^{-1}\):
\(|\kappa_{tcg}|/\Lambda<1.8\times10^{-2}~\mathrm{TeV}^{-1}\), corresponding to
\({\cal B}(t\to c g)<4.1\times10^{-4}\).  For SM context, not as a measured
PDG value, Aguilar-Saavedra gives
\({\cal B}(t\to c g)=4.6\times10^{-12}\) as the central SM benchmark.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This channel probes color-carrying top-charm flavor violation rather than the
neutral-meson \(\Delta F=2\) four-quark operators already audited in the quark
scan.  In anarchic warped flavor, the heavy color sector and the IR-localized
top can generate non-universal mass-basis couplings and loop-level
chromomagnetic dipoles.  A \(t\to c g\) limit is therefore a direct up-sector
top-flavor diagnostic, complementary to \(D^0\) mixing and to electroweak
channels such as \(t\to cZ\) or \(t\to cH\).

\subsection*{Post-2008 developments}
The 2008 CFW reference point emphasized KK-gluon exchange and generic
anarchic-flavor bounds near \(21~\mathrm{TeV}\) for ordinary RS and
\(33~\mathrm{TeV}\) in the composite pseudo-Goldstone Higgs setup, but it did
not provide a direct \(t\to c g\) catalog limit.  Since then the important
change is experimental: LHC searches now constrain the top-gluon FCNC operator
directly.  CMS used 7 and 8 TeV t-channel single-top data, while ATLAS later
used the full Run-2 \(139~\mathrm{fb}^{-1}\) dataset at 13 TeV with a neural
network separation of \(ug\to t\), \(cg\to t\), and backgrounds.  The resulting
limits remain many orders of magnitude above the SM prediction, so they are
new-physics limits rather than SM precision tests.

\subsection*{Constraint validity and model dependence}
The experimental upper bound is clean in the sense that the SM rate is
negligible.  Its use as an RS scan cut is model dependent: ATLAS quotes a
left-handed SMEFT \(C_{uG}^{ct}\) interpretation, while CMS uses an older
\(\kappa_{tcg}\) convention.  The conversion from single-top production to
\({\cal B}(t\to c g)\) assumes one FCNC operator at a time, standard top
decays, and a specific normalization of the chromomagnetic interaction.  A
model producing both chiralities, contact terms, or correlated heavy-gluon
resonance effects needs a dedicated reinterpretation.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required plan greps were rerun on 2026-05-16, followed by a
targeted search for \(t\to c g\), \(tcg\), \(tqg\), \(C_{uG}\), and
\(cg\to t\) across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/}.  The only implementation-directory hits were generic FCNC
prose/comments at \texttt{quarkConstraints/PAPER\_0710\_1869.md:35} and
\texttt{tests/test\_paper\_couplings.py:258}.  The modern phenomenology surface
enumerates only \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}, and states that it is
policy-only at \texttt{quarkConstraints/modern/phenomenology.py:165}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Cataloging the external limit is straightforward, but live
integration would need a top chromomagnetic FCNC operator convention,
RS-to-SMEFT matching, decay-width and \(cg\to t\) production normalization,
PDF/collider acceptance assumptions or a validated recast, and QCD-running
choices not present in the existing \(\Delta F=2\) code.

\subsection*{Key references}
\texttt{PDG2025TopFCNCTUG}; \texttt{ATLAS2022TopFCNCTUG};
\texttt{CMS2017TopFCNCTUG}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}.
