% Flavor catalog per-process draft.
% process_id: T006
% family: top_higgs_ew
% owner_agent_id: PKA-T006
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: T006.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to u g\)}{t -> u g} Top-Gluon FCNC}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(t\to u g)\).
This entry covers the flavor-changing neutral-current top decay \(t\to u g\),
catalog id T006 in the top/Higgs/electroweak family.  Experimentally it is
constrained mainly through anomalous single-top production, \(u g\to t\), then
translated into an equivalent top-decay branching fraction under a specified
chromomagnetic-operator convention.

\subsection*{PDG / equivalent value(s)}
The canonical experimental source is the PDG/pdgLive Q007TUG top-FCNC gluon
datablock, accessed on 2026-05-16
(\texttt{PDG2025:T006:ATLAS2022:t\_ug};
\texttt{references/T006/pdg\_2025\_top\_tug.txt}).  Its current ATLAS entry,
AAD 2022T, uses \(139~\mathrm{fb}^{-1}\) of \(13~\mathrm{TeV}\) \(pp\) data
(\texttt{PDG2025:T006:ATLAS2022:dataset}).  For the up-gluon production mode
it gives
\[
  \sigma(ug\to t)\,\mathcal{B}(t\to bW)\,
  \mathcal{B}(W\to \ell\nu)<3.0~\mathrm{pb}
\]
at 95\% CL (\texttt{PDG2025:T006:ATLAS2022:ug\_to\_t\_cross\_section}), with
the ATLAS leptonic-\(W\) sum \(\mathcal{B}(W\to\ell\nu)=0.325\)
(\texttt{PDG2025:T006:ATLAS2022:w\_leptonic\_sum}).  The same entry gives
\[
  |C^{ut}_{uG}|/\Lambda^2 < 0.057~\mathrm{TeV}^{-2},
  \qquad
  \mathcal{B}(t\to u g)<6.1\times10^{-5}.
\]
These coefficient and branching-fraction limits are recorded as
\texttt{PDG2025:T006:ATLAS2022:CuGut} and
\texttt{PDG2025:T006:ATLAS2022:t\_ug}.
The PDG block also records the CMS 7 and 8 TeV comparison result based on
\(5.0~\mathrm{fb}^{-1}\) and \(19.7~\mathrm{fb}^{-1}\)
(\texttt{CMS2017:T006:dataset}):
\(|\kappa_{tug}|/\Lambda<4.1\times10^{-3}~\mathrm{TeV}^{-1}\), corresponding
to \(\mathcal{B}(t\to u g)<2.0\times10^{-5}\)
(\texttt{CMS2017:T006:kappa\_tug}; \texttt{CMS2017:T006:t\_ug}).  For SM
context, not as a measured PDG value, Aguilar-Saavedra's charm-mode result and
CKM scaling imply
\(\mathcal{B}(t\to u g)\simeq3.6\times10^{-14}\)
(\texttt{AguilarSaavedra2004:T006:t\_ug\_SM}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This channel probes color-carrying first--third generation up-sector flavor
violation rather than the neutral-meson \(\Delta F=2\) four-quark operators
already audited in the quark scan.  In anarchic warped flavor, the heavy color
sector and the IR-localized top can generate non-universal mass-basis couplings
and loop-level chromomagnetic dipoles.  A \(t\to u g\) limit is therefore a
direct top-flavor diagnostic, complementary to \(D^0\) mixing and to
electroweak channels such as \(t\to uZ\) or \(t\to uH\).

\subsection*{Post-2008 developments}
The paper-era CFW reference point, arXiv:0804.1954, predates the LHC
single-top FCNC program and is used here only as RS-flavor context.  Since
then, CMS and ATLAS have interpreted single-top data in top-gluon FCNC
operators, with the ATLAS Run-2 dataset supplying the current PDG/pdgLive
entry.  The resulting bounds remain far above the SM prediction, so they are
new-physics limits rather than SM precision tests.

\subsection*{Constraint validity and model dependence}
The experimental upper bound is clean because the SM signal is negligible at
collider sensitivity.  Its use as an RS scan cut is model dependent: ATLAS
quotes a left-handed SMEFT \(C_{uG}^{ut}\) interpretation, while CMS uses an
older \(\kappa_{tug}\) convention.  The conversion from single-top production
to \({\cal B}(t\to u g)\) assumes one FCNC operator at a time, standard top
decays, and a specific normalization of the chromomagnetic interaction.  A
model producing both chiralities, contact terms, or correlated heavy-gluon
resonance effects needs a dedicated reinterpretation.

In down-aligned or kaon-protected RS variants, top FCNCs become leading rather
than secondary diagnostics.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required plan greps were rerun on 2026-05-16, followed by a
targeted search for \(t\to u g\), \(tug\), \(utg\), \(tqg\), \(C_{uG}\), and
\(ug\to t\) across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/}.  The only implementation-directory hits were generic FCNC
prose/comments at \texttt{quarkConstraints/PAPER\_0710\_1869.md:35} and
\texttt{tests/test\_paper\_couplings.py:258}.  The modern phenomenology surface
enumerates only \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}, and states that it is
policy-only at \texttt{quarkConstraints/modern/phenomenology.py:167}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Cataloging the external limit is straightforward, but live
integration would need a top chromomagnetic FCNC operator convention,
RS-to-SMEFT matching, decay-width and \(ug\to t\) production normalization,
PDF/collider acceptance assumptions or a validated recast, and QCD-running
choices not present in the existing \(\Delta F=2\) code.

\subsection*{Key references}
\texttt{PDG2025TopFCNCTUG}; \texttt{ATLAS2022TopFCNCTUG};
\texttt{CMS2017TopFCNCTUG}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}.
