% Flavor catalog per-process draft.
% process_id: T007
% family: top_higgs_ew
% owner_agent_id: PKA-T007
% Canonical metadata sidecar: T007.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to Hc\)}{t -> H c} FCNC Top-Higgs Decay}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(t\to Hc)\).
This entry catalogs the flavor-changing neutral-current top-Higgs decay
\(t\to Hc\) in the top/Higgs/electroweak family.  It covers direct LHC
searches for anomalous top--charm--Higgs interactions in both \(t\bar t\)
events with an FCNC top decay and associated single-top plus Higgs production.

\subsection*{PDG-or-equivalent value}
The source-of-truth numerical entries are the \texttt{pdg\_or\_equivalent}
block in \texttt{T007.yaml}.  The PDG 2026 \texttt{pdgLive} top-quark
datablock quotes the ATLAS-combination headline
\[
  \mathcal{B}(t\to Hc) < 3.4\times 10^{-4}
\]
at 95\% CL (\texttt{PDG2026:T007:tHc\_combined}), based on the ATLAS 2024
combined Higgs-decay search.  The local PDG snapshot is
\texttt{flavor\_catalog/references/T007/pdg2026\_top\_hc\_datablock.txt}.
The ATLAS primary arXiv record gives \(140~\mathrm{fb}^{-1}\) at
\(\sqrt{s}=13~\mathrm{TeV}\) (\texttt{ATLAS2024:T007:dataset}), a
multilepton-only limit \(\mathcal{B}(t\to Hc)<3.3\times10^{-4}\)
with expected \(3.8\times10^{-4}\)
(\texttt{ATLAS2024:T007:tHc\_multilepton}), and the combined limit
\(\mathcal{B}(t\to Hc)<3.4\times10^{-4}\) with expected
\(2.3\times10^{-4}\) (\texttt{ATLAS2024:T007:tHc\_combined}).  The CMS 2025
record uses \(138~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\) collected
in 2016--2018 (\texttt{CMS2025:T007:dataset}); its combined limit is
\(\mathcal{B}(t\to Hc)<0.037\%\), expected \(0.035\%\)
(\texttt{CMS2025:T007:tHc\_combined}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models and composite-Higgs variants can generate off-diagonal
scalar Yukawa couplings after rotating to the quark mass basis.  The \(t\to Hc\)
mode probes the same top-sector localization and mixing structure that also
controls the large top Yukawa, so it is complementary to light-meson
\(\Delta F=2\) constraints.  For this repo it is best treated as a direct
top-sector diagnostic, not as a replacement for the existing kaon, \(B\), and
\(D\)-mixing gates.

\subsection*{Post-2008 developments}
The requested baseline is arXiv:0804.1954
(\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}), which predates direct LHC
top-Higgs FCNC bounds.  Since then, ATLAS and CMS moved the search from
indirect model estimates to direct limits using many Higgs final states.  ATLAS
now combines \(H\to WW\), \(H\to ZZ\), \(H\to\tau\tau\),
\(H\to\gamma\gamma\), and \(H\to b\bar b\) channels in the PDG headline
(\texttt{PDG2026:T007:tHc\_combined};
\texttt{ATLAS2024:T007:tHc\_combined}).  CMS has an independent 2025
combination with \(H\to\gamma\gamma\) and \(H\to b\bar b\) inputs in addition
to the same-sign lepton analysis (\texttt{CMS2025:T007:tHc\_combined}).  The
classic top-FCNC review arXiv:hep-ph/0409342 remains useful context for why SM
top FCNC Higgs amplitudes are negligible while BSM scalar flavor can be visible
(\texttt{AguilarSaavedra2004TopFCNC}).

\subsection*{Constraint validity and model dependence}
The experimental statement is a 95\% CL upper limit on an assumed single
anomalous top-Higgs flavor coupling.  The model interpretation is
operator-convention dependent: an RS implementation must choose whether the
scan outputs scalar \(Htc\), \(Hct\), or SMEFT Wilson coefficients, and whether
associated \(tH\) production is included together with \(t\bar t\) FCNC decays.
Correlations with \(t\to Hu\) are analysis-dependent, so this entry keeps only
the charm-channel bound as the T007 catalog value.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The PKA reran the required plan greps and a
targeted search for \(t\to Hc\), \(tHc\), \(tcH\), \(Htc\), and \(tqH\) across
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The only
targeted non-doc hits were generic FCNC prose/comments in
\texttt{quarkConstraints/PAPER\_0710\_1869.md:35} and
\texttt{tests/test\_paper\_couplings.py:258}; there is no \(t\to Hc\)
observable, likelihood, or limit check.

\subsection*{Implementation difficulty}
Production integration is \textbf{HIGH}.  Recording the external upper limit is
straightforward, but using it in scans needs a new top-Higgs FCNC matching layer,
a scalar-coupling convention, and a decision about combining \(tH\) production
with \(t\bar t\) FCNC-decay interpretations.

\subsection*{Key references}
\texttt{PDG2026TopHc}; \texttt{ATLAS2024TopHcMultilepton};
\texttt{CMS2025TopHcHiggsMediated}; \texttt{AguilarSaavedra2004TopFCNC};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}.
