% Flavor catalog per-process draft.
% process_id: T008
% family: top_higgs_ew
% owner_agent_id: PKA-T008
% Canonical metadata sidecar: T008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(t\to H u\)}{t -> H u} FCNC Top-Higgs Decay}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(t\to H u)\).
This entry catalogs the flavor-changing neutral-current top-Higgs decay
\(t\to H u\), process id T008 in the top/Higgs/electroweak family.  It covers
direct LHC searches for anomalous \(Hut\) interactions in \(t\bar t\) events
with an FCNC top decay and in associated single-top plus Higgs production.

\subsection*{PDG value}
The \texttt{pdg\_or\_equivalent} block in \texttt{T008.yaml} is the numerical
source of truth.  The PDG 2026 \texttt{pdgLive} top-quark datablock quotes
\[
  \mathcal{B}(t\to H u) < 1.9\times 10^{-4}
\]
at 95\% CL (\texttt{PDG2026:T008:tHu\_headline}), based on the CMS
\(H\to\gamma\gamma\) result.  The local PDG snapshot is
\texttt{flavor\_catalog/references/T008/pdg2026\_top\_hu\_datablock.txt}.
The CMS source uses \(137~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\)
and reports the same observed limit, \(0.019\%\), with expected \(0.031\%\)
(\texttt{CMS2022:T008:tHu\_diphoton}).  PDG also lists, below its
``do not use'' separator, the ATLAS multilepton limit
\(2.8(3.0)\times10^{-4}\) observed(expected) and the ATLAS combination
\(2.6(1.8)\times10^{-4}\)
(\texttt{ATLAS2024:T008:tHu\_multilepton};
\texttt{ATLAS2024:T008:tHu\_combined}).  The CMS 2025 same-sign-lepton search
gives \(0.072\%(0.059\%)\), and its combination with CMS
\(H\to\gamma\gamma\) and \(H\to b\bar b\) searches gives
\(0.019\%(0.027\%)\)
(\texttt{CMS2025:T008:tHu\_samesign};
\texttt{CMS2025:T008:tHu\_combined}).

\subsection*{Relevance to RS / anarchic flavor}
Warped anarchic flavor and composite-Higgs variants can generate off-diagonal
scalar Yukawa couplings after rotating to the quark mass basis.  The \(t\to H u\)
channel probes up-top scalar flavor, complementary to the
charm channel in T007 and to light-meson \(\Delta F=2\) gates.  Associated
\(tH\) production is especially sensitive to an up-quark initial state, so the
experimental interpretation is not identical to simply rescaling \(t\to Hc\).

\subsection*{Post-2008 developments}
The requested baseline, arXiv:0804.1954
(\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}), predates direct LHC
top-Higgs FCNC searches.  Since then, ATLAS and CMS moved the constraint from
model estimates to direct searches in diphoton, multilepton, \(b\bar b\), and
\(\tau\tau\) Higgs final states.  The PDG headline currently comes from the
CMS diphoton search, while ATLAS and CMS now also provide multi-channel
combinations that treat \(t\bar t\) FCNC decay and associated \(tH\)
production together.

\subsection*{Constraint validity / model dependence}
The experimental statement is a direct 95\% CL upper limit under a single
anomalous \(Hut\) coupling assumption (\texttt{PDG2026:T008:tHu\_headline}).
Mapping it into this repo would require
choosing a scalar-Yukawa or SMEFT convention, deciding whether \(Hut\) and
\(Htu\) are independent, and preserving the analysis-specific combination of
\(t\bar t\) decay and associated-production topologies.  Correlations with
\(t\to Hc\) are not universal, so T008 keeps only the up-channel bound.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The required plan greps and a targeted search for
\(t\to Hu\), \(tHu\), \(tuH\), \(Hut\), \(Htu\), and \(tqH\) were rerun across
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The only
targeted hits outside the catalog were generic FCNC prose/comments in
\texttt{quarkConstraints/PAPER\_0710\_1869.md:35} and
\texttt{tests/test\_paper\_couplings.py:258}; there is no \(t\to Hu\)
observable, likelihood, matching layer, or limit check.

\subsection*{Implementation difficulty}
Production integration is \textbf{HIGH}.  Limit cataloging is straightforward,
but a live scan needs a new top-Higgs FCNC matching layer, scalar-coupling
normalization, and an analysis prescription for the \(tH\) plus \(t\bar t\)
interpretation.

\subsection*{Key references}
\texttt{PDG2026TopHu}; \texttt{CMS2022TopHuDiphoton};
\texttt{ATLAS2024TopHuMultilepton}; \texttt{CMS2025TopHuHiggsMediated};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}.
