% Flavor catalog per-process template.
% process_id: T010
% family: top_higgs_ew
% owner_agent_id: PKA-T010
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: T010.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(Z \to b\bar b\) Pole Observables}{Z to b bbar Pole Observables}}

\subsection*{Process}
This entry covers the bottom-quark Z-pole observables \(R_b^0\),
\(A_{\rm FB}^{0,b}\), and \(A_b\).  Plan v1 lists \(R_b\) as T010 and the
asymmetries as T011; this entry follows the batch assignment and treats them as
one \(Z\to b\bar b\) pole-observable package.

\subsection*{PDG-or-equivalent value}
The canonical current values are taken from the PDG Z-boson listing snapshot in
\texttt{flavor\_catalog/references/T010/pdg\_2025\_z\_boson.txt}; the same
snapshot is recorded in the \texttt{T010.yaml} \texttt{pdg\_or\_equivalent}
block.  It gives \(R_b^0=0.21629\pm0.00066\),
\(A_{\rm FB}^{0,b}=0.0992\pm0.0016\) after converting the listed
\(9.92\pm0.16\%\), and \(A_b=0.923\pm0.020\)
(\texttt{pdg\_2025\_z\_boson.txt}).  The original LEP/SLC final combination is
also snapshotted in \texttt{lepslc\_2006\_z\_resonance.txt}; it records the
same central values and identifies the \(A_{\rm FB}^{0,b}\) comparison as the
largest Z-pole pull, \(2.8\sigma\), relative to the Standard Model fit.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped models with anarchic five-dimensional Yukawas, the third-generation
left-handed doublet is typically localized closer to the IR brane to account
for the top mass.  That same localization makes the \(Z b_L\bar b_L\) coupling
sensitive to gauge-boson and fermion mixing with Kaluza-Klein states.  \(R_b\)
mostly constrains the total \(Z\to b\bar b\) partial width, while \(A_b\) and
\(A_{\rm FB}^{0,b}\) test the chiral balance of the bottom coupling.  Custodial
extensions, especially protections of \(Z b_L\bar b_L\), are therefore not a
minor detail; they determine whether this observable is a leading bound or a
diagnostic cross-check.

\subsection*{Post-2008 developments}
There has not been a new LEP/SLC-style experimental average superseding the
Z-pole combination, so the PDG value remains legacy-data dominated.  The
post-CFW theory story did change: Casagrande et al. gave a detailed RS
electroweak-precision treatment including Zbb couplings, while later SM work
completed the fermionic two-loop description of Z partial widths and branching
ratios (\texttt{freitas\_2014\_z\_widths}).  Future-collider studies now
revisit the experimental systematics of \(R_b\) and \(A_{\rm FB}^b\); the
FCC-ee projection quotes relative uncertainties of order \(0.01\%\), but it is
a prospective reference rather than a current constraint
(\texttt{fcc\_ee\_2025\_zbb\_projection.txt}).

\subsection*{Constraint validity and model dependence}
This is a precision electroweak coupling constraint, not a flavor-changing
amplitude by itself.  It is highly relevant for RS flavor because the same
fermion localizations and custodial choices that control flavor violation also
set the tree-level Z-bottom coupling shifts.  Its interpretation is therefore
model-dependent: minimal bulk RS, custodial RS, brane kinetic terms, and
different embeddings of the bottom multiplet can move the constraint
substantially.  \(A_{\rm FB}^{0,b}\) also contains the initial-state leptonic
asymmetry input, so \(A_b\) is the cleaner bottom-coupling handle.

In custodial RS, reduced \(Z b_L b_L\) pressure can make this observable
relatively less direct as a mass setter or more diagnostic of embeddings;
quote RS bounds only after specifying custodial protection, fermion embeddings,
and brane kinetic terms.

\subsection*{Code coverage in this repo}
\textbf{NO}.  The required greps found no implementation of \(R_b\), \(A_b\),
\(A_{\rm FB}^{0,b}\), or a Zbb electroweak-pole likelihood in
\texttt{quarkConstraints/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{qcd/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, or \texttt{tests/}.  The only Z-related matches were
generic \(M_Z\) support in \texttt{qcd/running.py:3},
\texttt{qcd/constants.py:11}, and \texttt{quarkConstraints/qcd\_running.py:100}.

\subsection*{Implementation difficulty}
\textbf{HIGH}.  A catalog-only record is straightforward, but a live constraint would
need a new electroweak-pole observable module, a correlated treatment of the
LEP/SLC pseudo-observables, and model-specific matching from the 5D spectrum to
\(\delta g_{Lb}\) and \(\delta g_{Rb}\).  The largest blocker is not lattice
input or QCD running; it is the RS electroweak matching and custodial-symmetry
bookkeeping.

\subsection*{Key references}
\texttt{pdg\_2025\_z\_boson}; \texttt{lepslc\_2006\_z\_resonance};
\texttt{cfw\_2008\_rs\_flavor}; \texttt{casagrande\_2008\_rs\_ewpt};
\texttt{freitas\_2014\_z\_widths}; \texttt{fcc\_ee\_2025\_zbb\_projection}.
