% Flavor catalog per-process draft.
% process_id: T018
% family: top_higgs_ew
% owner_agent_id: PKA-T018
% Canonical metadata sidecar: T018.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(h\to\mu\tau\)}{h -> mu tau} LFV Higgs Decay}

\subsection*{Process}
The observable is the lepton-flavor-violating Higgs branching fraction
\(\mathcal{B}(h\to\mu^\pm\tau^\mp)\), catalog id T018 in the
top/Higgs/electroweak family.  It covers direct ATLAS and CMS searches for a
neutral Higgs boson decaying to a muon and an oppositely charged tau lepton.

\subsection*{PDG / equivalent value(s)}
The source-of-truth entries are in the \texttt{pdg\_or\_equivalent} block of
\texttt{T018.yaml}.  The PDG 2025 Higgs review summarizes the full
\(\sqrt{s}=13~\mathrm{TeV}\) Run-2 limits:
\[
  \mathcal{B}(h\to\mu\tau) < 0.15\%
\]
from CMS, with the same \(0.15\%\) expected limit, at 95\% CL
(\texttt{CMS2021:T018:mutau\_limit}; \texttt{PDG2025:T018:cms\_run2}).  The
CMS analysis used \(137~\mathrm{fb}^{-1}\)
(\texttt{CMS2021:T018:dataset}).  The latest ATLAS Run-2 result gives
\[
  \mathcal{B}(h\to\mu\tau) < 0.18\% \quad (0.09\%\ \mathrm{expected})
\]
at 95\% CL using \(138~\mathrm{fb}^{-1}\)
(\texttt{ATLAS2023:T018:mutau\_limit};
\texttt{ATLAS2023:T018:dataset}).  The CMS observed limit is the strongest
single-experiment headline value in the local snapshots.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped or partially composite lepton sectors, fermion localization explains
charged-lepton masses, but misalignment between the mass matrix and physical
Higgs couplings can generate off-diagonal Yukawa interactions.  The
\(h\to\mu\tau\) limit directly tests the \(\mu\)-\(\tau\) charged-lepton
Yukawa entries and is complementary to dipole LFV constraints such as
\(\mu\to e\gamma\).  It is therefore relevant only to a lepton-sector extension
of the current quark scan, not to the existing \(\Delta F=2\) quark lane.

\subsection*{Post-2008 developments}
The requested baseline is arXiv:0804.1954, before the LHC Higgs LFV program.
Harnik, Kopp, and Zupan later emphasized that flavor-violating Higgs decays
could be a direct discovery channel and that \(h\to\tau\mu\) searches could
beat rare-tau bounds (\texttt{HarnikKoppZupan2012:order10}).  CMS then reported
the historical \(8~\mathrm{TeV}\) hint: a \(2.4\sigma\) excess with
\(p=0.010\), best fit
\(\mathcal{B}(H\to\mu\tau)=(0.84^{+0.39}_{-0.37})\%\), and a 95\% CL limit
of \(1.51\%\) using \(19.7~\mathrm{fb}^{-1}\)
(\texttt{CMS2015:T018:hint}; \texttt{CMS2015:T018:dataset};
\texttt{CMS2015:T018:limit}).  The full Run-2 CMS and ATLAS analyses did not
confirm a significant signal and pushed the direct limits to the
\(10^{-3}\)-branching-fraction level.

\subsection*{Constraint validity and model dependence}
Experimentally this is a direct, clean upper limit on a forbidden SM decay.
The interpretation assumes the signal production mixture and total Higgs width
used by each collaboration; a model that changes Higgs production or the total
width needs a recast rather than a literal branching-ratio cut.  Low-energy
LFV bounds constrain related Yukawa products, but the direct \(h\to\mu\tau\)
search is the least model-dependent way to constrain this specific final state.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The required greps and a targeted search for
\texttt{h->mu tau}, \texttt{H->mu tau}, \texttt{mutau}, and \texttt{Y\_mu\_tau}
across \texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no observable implementation.
The existing LFV backend is specifically \(\mu\to e\gamma\)
(\texttt{flavorConstraints/muToEGamma.py:1};
\texttt{flavorConstraints/muToEGamma.py:75}), and the scanner applies that
filter at \texttt{scanParams/scan.py:523}.  Charged-lepton Yukawa helpers are
diagonal mass-relation utilities, not an \(h\to\mu\tau\) prediction.

\subsection*{Implementation difficulty}
Production integration is \textbf{HIGH}.  The external limit is easy to store,
but a faithful RS constraint needs a new charged-lepton Higgs-Yukawa
misalignment calculation, a convention for \(\mu\tau\) versus \(\tau\mu\)
couplings, and a Higgs-rate/width interpretation before scan points can be
accepted or rejected.

\subsection*{Key references}
\texttt{PDG2025HiggsLFVReview}; \texttt{CMS2021HiggsLFVMuTau};
\texttt{ATLAS2023HiggsLFVMuTau}; \texttt{CMS2015HiggsLFVMuTauHint};
\texttt{HarnikKoppZupan2012FlavorViolatingHiggs};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor};
\texttt{PerezRandall2008WarpedLeptonFlavor}.
