% Flavor catalog per-process draft.
% process_id: T020
% family: top_higgs_ew
% owner_agent_id: PKA-T020
% Canonical metadata sidecar: T020.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(h\to e\mu\)}{h -> e mu} LFV Higgs Decay}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(h\to e^\pm\mu^\mp)\).
This entry catalogs the lepton-flavor-violating Higgs decay \(h\to e\mu\)
in the top/Higgs/electroweak family.  It covers direct ATLAS and CMS searches
for a \(125~\mathrm{GeV}\) Higgs boson decaying to an opposite-sign
electron--muon pair.

\subsection*{PDG / equivalent value(s)}
The source-of-truth values are in the \texttt{pdg\_or\_equivalent} block of
\texttt{T020.yaml}.  The PDG 2025 Higgs review summarizes the full
\(\sqrt{s}=13~\mathrm{TeV}\) Run-2 direct limits on LFV Higgs decays
(\texttt{PDG2025HiggsLFVReview}).  For \(h\to e\mu\), PDG quotes
\[
  \mathcal{B}(h\to e\mu) < 4.4\times 10^{-5}
  \quad (4.7\times 10^{-5}\ \mathrm{expected})
\]
from CMS at 95\% CL using \(138~\mathrm{fb}^{-1}\)
(\texttt{CMS2023HiggsLFVEMu}; \texttt{PDG2025:T020:cms\_run2}).  PDG also
quotes the ATLAS limit
\[
  \mathcal{B}(h\to e\mu) < 6.2\times 10^{-5}
  \quad (5.9\times 10^{-5}\ \mathrm{expected})
\]
at 95\% CL (\texttt{PDG2025:T020:atlas\_run2}).  The primary ATLAS abstract
reports the same search as \(6.1\times 10^{-5}\) observed and
\(5.8\times 10^{-5}\) expected with \(139~\mathrm{fb}^{-1}\)
(\texttt{ATLAS2020HiggsEMu}); the PDG rounding is kept as the catalog
headline.  The CMS number is the strongest direct single-experiment limit.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Warped or partially composite lepton sectors can generate off-diagonal
physical Higgs Yukawa couplings after the charged-lepton mass matrix is
diagonalized.  The \(h\to e\mu\) search directly probes the \(e\)-\(\mu\)
entries of that Higgs Yukawa matrix and is therefore complementary to the
repo's existing \(\mu\to e\gamma\) dipole filter.  It is not a constraint on
the current quark \(\Delta F=2\) scan by itself; it belongs to a future
lepton-sector extension.

\subsection*{Post-2008 developments}
The requested arXiv:0804.1954 baseline predates the LHC Higgs LFV program
(\texttt{CsakiFalkowskiWeiler2008WarpedFlavor}).  Harnik, Kopp, and Zupan
then framed flavor-violating Higgs decays as direct discovery channels and
showed that lepton-flavor-violating Higgs branching fractions could be sizable
in generic EFT settings (\texttt{HarnikKoppZupan2012FlavorViolatingHiggs}).
ATLAS produced the first full Run-2 \(h\to e\mu\) limit with
\(139~\mathrm{fb}^{-1}\) (\texttt{ATLAS2020HiggsEMu}).  CMS later used
\(138~\mathrm{fb}^{-1}\), improved the direct Higgs limit to
\(4.4\times10^{-5}\), and extended the same \(e\mu\) mass scan to
\(110\)--\(160~\mathrm{GeV}\), where a \(146~\mathrm{GeV}\) excess with
local/global significance \(3.8/2.8\sigma\) was reported but not interpreted
as evidence (\texttt{CMS2023HiggsLFVEMu}).

\subsection*{Constraint validity and model dependence}
Experimentally this is a clean direct upper limit on a Standard-Model-forbidden
Higgs decay.  A literal branching-ratio cut assumes the SM-like Higgs
production mixture and total width used by ATLAS and CMS.  Models with altered
Higgs production, exotic Higgs width, or correlated low-energy LFV signals need
a recast.  PDG notes that indirect \(\mu\to e\gamma\)-based constraints are
stronger for this channel, so this entry should be used as the direct collider
observable rather than the global \(e\)-\(\mu\) LFV bound.

\subsection*{Code coverage in this repo}
Coverage is \textbf{NO}.  The required greps and a targeted search for
\texttt{h->e mu}, \texttt{H->e mu}, \texttt{Y\_e\_mu}, and \texttt{Y\_mu\_e}
across \texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no observable implementation.
The existing lepton LFV backend is specifically \(\mu\to e\gamma\)
(\texttt{flavorConstraints/muToEGamma.py:1};
\texttt{flavorConstraints/muToEGamma.py:75}), and the scan applies that filter
at \texttt{scanParams/scan.py:523}--\texttt{scanParams/scan.py:524}.  The
charged-lepton Yukawa helper is diagonal
(\texttt{yukawa/charged\_lepton.py:1}; \texttt{yukawa/charged\_lepton.py:36}).

\subsection*{Implementation difficulty}
Production integration is \textbf{HIGH}.  The direct limit is easy to catalog,
but a scan constraint needs a new charged-lepton Higgs-Yukawa misalignment
calculation, a convention for \(Y_{e\mu}\) and \(Y_{\mu e}\), and a Higgs-rate
or total-width interpretation before accepting or rejecting points.

\subsection*{Key references}
\texttt{PDG2025HiggsLFVReview}; \texttt{CMS2023HiggsLFVEMu};
\texttt{ATLAS2020HiggsEMu}; \texttt{HarnikKoppZupan2012FlavorViolatingHiggs};
\texttt{CsakiFalkowskiWeiler2008WarpedFlavor};
\texttt{PerezRandall2008WarpedLeptonFlavor}.
