\documentclass[11pt]{article}

% ============================================================
%  B_s - Bbar_s mixing: Delta m_s and phi_s in warped models
%  A slow, pedagogical internal review.
%  Tracks (a) the physics, (b) what is in OUR code,
%  (c) the subtleties and gaps.
%  Internal working note, not for distribution.
% ============================================================

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb,amsthm}
\usepackage{mathtools}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{enumitem}
\usepackage{xcolor}
\usepackage{framed}
\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue,urlcolor=blue]{hyperref}

% lightweight "callout" box
\colorlet{shadecolor}{gray!12}
\newenvironment{callout}[1]{%
  \par\medskip\begin{shaded}\noindent\textbf{#1}\par\smallskip}{\end{shaded}\medskip}

\newcommand{\MKK}{M_{\mathrm{KK}}}
\newcommand{\LIR}{\Lambda_{\mathrm{IR}}}
\newcommand{\sw}{s_W}
\newcommand{\cw}{c_W}
\newcommand{\swsq}{s_W^2}
\newcommand{\cwsq}{c_W^2}
\newcommand{\Pibig}{\Pi}
\newcommand{\half}{\tfrac{1}{2}}
\newcommand{\vev}{v}
\newcommand{\eps}{\varepsilon}
\newcommand{\SUL}{SU(2)_L}
\newcommand{\SUR}{SU(2)_R}
\newcommand{\UX}{U(1)_X}
\newcommand{\PLR}{P_{LR}}
\newcommand{\Tparam}{\hat{T}}
\newcommand{\code}[1]{\texttt{#1}}
\newcommand{\todo}[1]{{\color{red}[#1]}}

% topic-specific shorthands
\newcommand{\Bs}{B_s}
\newcommand{\Bsbar}{\bar B_s}
\newcommand{\dms}{\Delta m_s}
\newcommand{\phis}{\phi_s}
\newcommand{\Mtwelve}{M_{12}}
\newcommand{\MtwelveNP}{M_{12}^{\mathrm{NP}}}
\newcommand{\MtwelveSM}{M_{12}^{\mathrm{SM}}}
\newcommand{\Vts}{V_{ts}}
\newcommand{\betas}{\beta_s}
\newcommand{\muhad}{\mu_{\mathrm{had}}}

\theoremstyle{definition}
\newtheorem{definition}{Definition}

\title{\bf $B_s$--$\bar B_s$ Mixing: $\Delta m_s$ and $\phi_s$ in Warped Models\\[4pt]
\large A slow, pedagogical internal review --- physics, code, and subtleties}
\author{Internal working note (5D--Neutrino--Mixing repo)}
\date{\today}

\begin{document}
\maketitle

\begin{abstract}
\noindent
This note builds the two $\Bs$--$\Bsbar$ mixing observables from nothing. The
first, $\dms$, is the oscillation frequency of the neutral $\Bs$ system: a
CP-conserving \emph{magnitude} measured to per-mille precision. The second,
$\phis$, is the CP-violating \emph{phase} of that same mixing amplitude,
measured in tree-dominated $\Bs\to J/\psi\,\phi$ decays. In our catalogue they
are processes \code{B003} and \code{B004}, and they form a magnitude--phase pair
read off the \emph{single} complex object $\MtwelveNP$. Part~\ref{part:sm}
defines both observables, the underlying $b\!\leftrightarrow\!s$ ($\Delta B=2$)
transition, and the Standard-Model (SM) numbers our code anchors to.
Part~\ref{part:rs} explains how a Randall--Sundrum (RS) warped extra dimension
generates a tree-level $\MtwelveNP$ through Kaluza--Klein (KK) gluon exchange,
why the chirally enhanced left--right operator dominates, and where the
$\MKK$ floor comes from. Part~\ref{part:cust} asks whether custodial symmetry or
flavour alignment relaxes this pair --- the short answer is that $\Delta F=2$ is
\emph{not} custodially protected and sets the strict $\sim 2$--$3$~TeV floor once
$Z\to b\bar b$ is removed. Part~\ref{part:code} documents exactly what our code
does (\code{quarkConstraints/deltaf2.py}, \code{B003.py}, \code{B004.py}),
including the in-core CKM-phase computation, the QCD running to $\muhad=2$~GeV,
and the budget$=\dms/2$ veto convention. Part~\ref{part:subtle} catalogues the
conventions and known hazards recorded in the orchestration ledgers. A common
confusions box and an annotated reading guide close the note. The shared
$\Delta F=2$ machinery (the Wilson basis, the running, the matrix elements) is
self-contained here; the companion \code{deltaF2\_framework\_review.tex} develops
that core in full generality, and \code{epsilon\_k\_review.tex} applies the same
core to the kaon system. Either can be read for additional detail.
The focus of this note is the $\Bs$ magnitude--phase pair and the phase
arithmetic.
\end{abstract}

\tableofcontents

% ====================================================================
\part*{Orientation: why this pair matters}
\addcontentsline{toc}{section}{Orientation: why this pair matters}
% ====================================================================

Of all the flavour observables in our catalogue, the $\Delta F=2$ meson-mixing
set is the one we are most confident calling \emph{rigorous}: it is computed
per-point from fitted quark couplings, run down with QCD, and contracted with
lattice hadronic matrix elements, with no closed-form proxy standing in for the
prediction. Within that set, the $\Bs$ system is special for two reasons. First,
it supplies \emph{two} measurements from \emph{one} amplitude --- a magnitude
$\dms$ and a phase $\phis$ --- so a single new-physics complex number is tested
twice, once for how big it is and once for how it is oriented in the complex
plane. Second, once the $Z\to b\bar b$ vertex constraint is switched off by
custodial protection, it is precisely this rigorous $\Delta F=2$ trio
($\epsilon_K$, $\dms$, $\phis$, i.e.\ \code{K001}/\code{B003}/\code{B004}) that
sets the residual ``strict'' Kaluza--Klein floor of the model --- about
$2$--$3$~TeV. To trust that floor we have to understand the magnitude and the
phase from the ground up. That is the purpose of this note.

A one-paragraph executive summary, unpacked over the following pages:

\begin{quote}
\small
A neutral $\Bs$ meson and its antiparticle are connected by a $\Delta B=2$
amplitude $\Mtwelve$, a single complex number. Its \emph{modulus} fixes how fast
the two states oscillate into one another, $\dms = 2|\Mtwelve|$; its
\emph{argument} fixes the CP phase $\phis$ that shows up as a time-dependent
asymmetry in $\Bs\to J/\psi\,\phi$. In the SM both are small and well predicted
($\phis\simeq -2\betas$, a tiny CKM angle). A warped extra dimension adds a
\emph{tree-level} new-physics piece $\MtwelveNP$ from KK gluon exchange across
the $b\!\leftrightarrow\!s$ transition; because the left- and right-handed quarks
are localised differently, a chirally enhanced left--right operator dominates,
and $\MtwelveNP$ is generically \emph{complex}, shifting both $\dms$ and $\phis$.
Our code computes that complex $\MtwelveNP$ once, takes its modulus for
\code{B003} and its argument (relative to the SM amplitude) for \code{B004}, and
vetoes any point whose new-physics amplitude overflows a budget set by the
SM-vs-experiment room --- of order $\dms/2$. Neither observable is protected by
custodial symmetry; together they are what pins the KK scale to a few TeV.
\end{quote}

\noindent The logical spine of the note, in one picture:
\begin{footnotesize}
\begin{verbatim}
   b <-> s  (Delta B = 2)   ==KK-gluon-tree==>   M12^NP  (ONE complex number)
                                                  |
                 +--------------------------------+--------------------------------+
                 |                                                                 |
            |M12^NP|  (modulus)                                          arg(1 + M12^NP/M12^SM)
                 |                                                                 |
          Delta m_s = 2|M12|   [B003]                          phi_s = phi_s^SM + NP phase  [B004]
                 |                                                                 |
       veto if |M12^NP| > budget                              veto if |phi_s - phi_s^exp| > sigma-budget
       budget ~ (|dm_exp - dm_SM| + sigma_comb)/2             phi_s^SM = -2 beta_s  (computed IN-CORE)
       (sigma_comb is THEORY-dominated, not residual)
                 |                                                                 |
                 +----------------- BOTH Severity.HARD, BOTH rigorous -------------+
                                                  |
            part of the rigorous Delta F=2 set {K001, B003, B004}
                          ==> strict custodial floor ~ 2-3 TeV  (once Z->bb removed)
\end{verbatim}
\end{footnotesize}
\noindent Keep this map in mind. The single most common confusion --- that
$\dms$ and $\phis$ are independent inputs --- is already defused: they are the
modulus and the argument of \emph{the same} $\MtwelveNP$, which is why our code
computes that complex number once and reads two numbers off it.

% ====================================================================
\part{The physics from scratch: what $\dms$ and $\phis$ mean}
\label{part:sm}
% ====================================================================

\section{Neutral-meson mixing: the $2\times 2$ effective Hamiltonian}
\label{sec:mixing}

A $\Bs$ meson is the bound state $(\bar b\, s)$; its antiparticle $\Bsbar$ is
$(b\,\bar s)$. They carry opposite beauty quantum number, $B=\pm 1$. The weak
interaction does not conserve $B$, so a state that starts life as a pure $\Bs$
can, a moment later, be found as a $\Bsbar$. This is \emph{flavour oscillation},
and it is governed by an effective two-state Hamiltonian
\begin{equation}
H = M - \tfrac{i}{2}\,\Gamma
= \begin{pmatrix} M_{11} & \Mtwelve \\ \Mtwelve^* & M_{22}\end{pmatrix}
 - \frac{i}{2}\begin{pmatrix} \Gamma_{11} & \Gamma_{12} \\ \Gamma_{12}^* & \Gamma_{22}\end{pmatrix},
\label{eq:Heff}
\end{equation}
where $M$ (the \emph{dispersive} part) and $\Gamma$ (the \emph{absorptive} part)
are Hermitian. CPT forces the diagonals equal. The off-diagonal $\Mtwelve$ is the
object that interests us: it is the amplitude for the transition
$\Bsbar \to \Bs$ via virtual (off-shell) intermediate states, i.e.\ the genuine
$\Delta B=2$ ``mixing'' amplitude. The companion $\Gamma_{12}$ comes from real,
on-shell decay channels common to $\Bs$ and $\Bsbar$; for the $\Bs$ system it is
small relative to $\Mtwelve$ and our code does not model it.

\begin{definition}[The mixing amplitude $\Mtwelve$]
$\Mtwelve = \langle \Bs | H_{\rm eff}^{\Delta B=2} | \Bsbar\rangle$ is the
complex matrix element connecting the two flavour states through a
beauty-changing-by-two interaction. New physics that mediates a $b\bar s \to
\bar b s$ transition adds linearly to it:
$\Mtwelve = \MtwelveSM + \MtwelveNP$.
\end{definition}

Diagonalising \eqref{eq:Heff} gives two mass eigenstates with a mass splitting
and a width splitting. To the accuracy we need ($|\Gamma_{12}|\ll|\Mtwelve|$,
which holds well for $\Bs$), the mass splitting between the heavy and light
eigenstates is simply twice the modulus of the off-diagonal element,
\begin{equation}
\boxed{\;\dms \;=\; 2\,|\Mtwelve|\;.}
\label{eq:dms}
\end{equation}
This is the first observable. It is manifestly \emph{phase-blind}: it depends
only on how large $\Mtwelve$ is, not on where it points in the complex plane.

\section{$\dms$: the oscillation frequency (observable \code{B003})}
\label{sec:dms}

Physically $\dms$ \emph{is} the oscillation frequency. A meson tagged as $\Bs$ at
$t=0$ has a probability of being found as $\Bsbar$ at time $t$ that wiggles like
$\sin^2(\dms\, t/2)$. Because $\dms$ has units of inverse time it is quoted in
$\mathrm{ps}^{-1}$ (inverse picoseconds), and the conversion to an energy
(mass) in natural units uses $\hbar$. Our code stores that conversion explicitly
as \code{\_HBAR\_GEV\_PER\_PS = 6.582119569e-13}, so that
\begin{equation}
\dms[\text{GeV}] = \dms[\text{ps}^{-1}]\times \hbar[\text{GeV}\cdot\text{ps}].
\end{equation}
The measured value is enormous on the scale of meson masses but tiny on the scale
of GeV: the HFLAV Fall-2024 recommended average, the experimental anchor in
\code{B003.yaml}, is
\begin{equation}
\dms^{\rm exp} = 17.766 \pm 0.006\ \mathrm{ps}^{-1}
\;\approx\; 1.169\times10^{-11}\ \text{GeV},
\label{eq:dmsexp}
\end{equation}
a $0.03\%$ measurement. (The exact $\hbar$ conversion gives
$1.16938\times10^{-11}$~GeV; the core stores the slightly rounded constant
\code{DELTA\_M\_BS\_EXP = 1.1688e-11}~GeV, which corresponds to
$17.757\,\mathrm{ps}^{-1}$ --- a harmless $0.05\%$ rounding of the anchor that we
flag here so the GeV and $\mathrm{ps}^{-1}$ forms are not taken as bit-identical.) The SM prediction is just as sharp; the value hardwired
in the $\Delta F=2$ core (\code{DELTA\_M\_BS\_SM}) is
\begin{equation}
\dms^{\rm SM} = 1.17\times10^{-11}\ \text{GeV}
\;\approx\; 17.77\ \mathrm{ps}^{-1},
\label{eq:dmssm}
\end{equation}
a CKMfitter-style central value. \textbf{The punchline of $\dms$ is that
experiment and SM already agree to within a fraction of a percent.} That leaves
almost no room for a new-physics amplitude: $|\MtwelveNP|$ must not push the
total $|\Mtwelve|$ outside the narrow band where SM and data overlap. The
``budget'' for new physics is therefore essentially the \emph{difference}
$|\dms^{\rm exp}-\dms^{\rm SM}|/2$ (with measurement and theory errors folded in),
and this is exactly how our \code{B003} veto is built (\S\ref{sec:codeB003}).

\section{$\phis$: the mixing CP phase (observable \code{B004})}
\label{sec:phis}

The second observable lives in the \emph{argument} of $\Mtwelve$, which $\dms$
threw away. To see it physically, consider a final state $f$ that is a \emph{CP
eigenstate} --- one that both $\Bs$ and $\Bsbar$ can decay into, such as
$J/\psi\,\phi$. The CP-eigenstate requirement is what makes the measurement
clean: because $\Bs$ and $\Bsbar$ feed the \emph{same} final state, the two decay
amplitudes can interfere, and because $f$ is CP self-conjugate the decay phase
drops out of the comparison, leaving only the phase carried by mixing. There are
then two interfering paths to $f$: decay directly, or oscillate into the
antiparticle first and then decay. Tracking the two amplitudes through the
time-evolved state, the interference between ``mix-then-decay'' and
``decay-directly'' produces a \emph{time-dependent CP asymmetry} of the
characteristic mixing-induced form
\begin{equation}
A_{\rm CP}(t) \;\equiv\;
\frac{\Gamma(\Bsbar\to f,t) - \Gamma(\Bs\to f,t)}{\Gamma(\Bsbar\to f,t)+\Gamma(\Bs\to f,t)}
\;\simeq\; \sin\phis\,\sin(\dms\, t),
\label{eq:acp}
\end{equation}
where $\dms$ sets the oscillation and the amplitude of the modulation is
$\sin\phis$. This is precisely the functional form LHCb fits to extract $\phis$:
the magnitude $\dms$ fixes \emph{how fast} the asymmetry oscillates, while the
phase $\phis$ fixes \emph{how deep} the oscillation is --- the same
modulus/argument split as before, now read out in a single time-dependent rate.
The single phase governing the modulation is the relative phase between the
mixing amplitude $\Mtwelve$ and the (real) decay amplitude. For a tree-dominated,
CP-eigenstate channel like $\Bs\to J/\psi\,\phi$, the decay phase is to excellent
approximation real, so the observable phase is essentially the phase of mixing
itself:
\begin{equation}
\phis \;\equiv\; \arg\!\big(\Mtwelve\big)\quad\text{(up to a SM decay-phase convention)}.
\label{eq:phisdef}
\end{equation}
In the SM this phase is \emph{not} zero, but it is small and CKM-predicted. The
relevant rephasing-invariant angle is $\betas$, defined exactly as our code
defines it (\S\ref{sec:incore}),
\begin{equation}
\betas = \arg\!\left(-\frac{\Vts\,V_{tb}^*}{V_{cs}\,V_{cb}^*}\right),
\qquad
\phis^{\rm SM} = -2\,\betas .
\label{eq:phissm}
\end{equation}
Numerically $\betas$ is about a degree, so the SM phase is a small negative
number. The repo-default CKM target (PDG-2024 unitary) yields, computed in-core,
\begin{equation}
\phis^{\rm SM} = -2\betas = -0.03795\ \text{rad}\ \approx\ -2.17^\circ,
\label{eq:phissmnum}
\end{equation}
consistent with the PDG window. The experimental average (HFLAV-for-PDG-2025,
the \code{B004.yaml} anchor) is
\begin{equation}
\phis^{\rm exp} = -0.041 \pm 0.016\ \text{rad},
\label{eq:phisexp}
\end{equation}
i.e.\ data and SM again sit right on top of each other, this time in the phase.
\textbf{So both members of the pair tell the same story: the SM works, and new
physics is allowed only a thin sliver.} The difference is what they probe: $\dms$
forbids a large $|\MtwelveNP|$ regardless of phase, while $\phis$ forbids a
$\MtwelveNP$ that is large \emph{and} misaligned with the SM amplitude.

\begin{callout}{Why the pair is more powerful than either alone.}
Write the new-physics amplitude as $\MtwelveNP = |\MtwelveNP|\,e^{i\theta}$.
\code{B003} bounds $|\MtwelveNP|$ directly. \code{B004} bounds the
\emph{imaginary} part relative to the SM amplitude: $\phis^{\rm NP}\simeq
\mathrm{Im}(\MtwelveNP)/|\MtwelveSM|$ when the NP piece is small. A
new-physics contribution that happens to be real and aligned with the SM is
caught only by \code{B003}; one that is mostly imaginary is caught much more
sharply by \code{B004}, because $|\MtwelveSM|$ is so small that even a modest
$\mathrm{Im}(\MtwelveNP)$ rotates the phase a lot. In an anarchic warped model
the new-physics phases are $\mathcal{O}(1)$ and uncorrelated with the CKM phase,
so the phase constraint typically bites \emph{harder} than the magnitude one ---
this is the whole reason CP observables drive the strongest $\Delta F=2$ bounds.
\end{callout}

\section{The $b\!\leftrightarrow\!s$ transition and the effective operators}
\label{sec:operators}

What microscopic interaction makes $\Mtwelve$? In the SM, $\Bs$ mixing is a
one-loop ``box'' diagram with two $W$ bosons and internal up-type quarks; the
top dominates, and the amplitude is proportional to $(\Vts\,V_{tb}^*)^2$. That
$\Vts$ factor is the fingerprint of the $b\!\to\! s$ flavour change: $\Vts$ is
the CKM element connecting the third (b) and second (s) down-type generations,
and it is what makes $\Bs$ mixing a second-third-generation transition. (In our
input bundle the $\Bs$ system is tagged with down-sector flavour indices
$(1,2)$, i.e.\ $s$ and $b$; see the \code{generations=(1, 2)} field of the
\code{b\_s} input in \S\ref{sec:codeB003}.)

Below the new-physics scale, whatever mediates $b\bar s \to \bar b s$ is
integrated out and replaced by a set of local four-quark operators. In the
compact basis our code uses there are four:
\begin{align}
Q_1^{\rm VLL} &= (\bar s_L \gamma^\mu b_L)(\bar s_L \gamma_\mu b_L), &
Q_1^{\rm VRR} &= (\bar s_R \gamma^\mu b_R)(\bar s_R \gamma_\mu b_R),
\label{eq:opsVLL}\\
Q_4^{\rm LR} &= (\bar s_L b_R)(\bar s_R b_L), &
Q_5^{\rm LR} &= (\bar s_L^\alpha b_R^\beta)(\bar s_R^\beta b_L^\alpha),
\label{eq:opsLR}
\end{align}
with $\alpha,\beta$ colour indices. The first two are ``vector'' operators with
quarks of a single chirality; the last two are ``scalar'' left--right operators
that mix the two chiralities. Each comes with a Wilson coefficient $C_i$, and the
new-physics mixing amplitude is the sum of these coefficients contracted with the
hadronic matrix elements $\langle \Bs|Q_i|\Bsbar\rangle$:
\begin{equation}
\MtwelveNP \;=\; \sum_i C_i\,\langle \Bs | Q_i | \Bsbar\rangle .
\label{eq:M12sum}
\end{equation}
This is the master formula our code evaluates. The matrix elements are
parametrised by the $\Bs$ decay constant $f_{\Bs}$, the meson mass $m_{\Bs}$, and
dimensionless ``bag'' parameters $B_1,B_4,B_5$ (lattice inputs); the Wilson
coefficients $C_i$ carry all the model dependence. The \emph{left--right}
operators \eqref{eq:opsLR} are special: their Wilson coefficients escape the
$1/6$ colour suppression of the vector operators (and are further enhanced by
QCD running), while their matrix elements pick up a mild chiral factor
$\sim (m_{\Bs}/(m_b+m_s))^2 \approx 1.6$. The coefficient effect is the decisive
one; the chiral factor is a secondary boost. Together they are why, in warped
models, the LR operator dominates $\Bs$ mixing --- a point we develop in
\S\ref{sec:lr}.

% ====================================================================
\part{How a warped extra dimension generates the effect}
\label{part:rs}
% ====================================================================

\section{KK gluon exchange: a tree-level $\Delta F=2$ amplitude}
\label{sec:kkgluon}

In the SM, meson mixing is a \emph{loop} effect, which is why it is so small. The
striking feature of warped (RS) models is that they generate the same
$\Delta F=2$ operators at \emph{tree level}, through the exchange of a heavy
Kaluza--Klein gluon. The mechanism is the same geometric localisation that
generates the fermion mass hierarchy:
\begin{enumerate}[leftmargin=1.6em]
\item Each SM fermion is the zero mode of a 5D field, localised toward the UV
brane (light quarks) or the IR brane (the top, and to a lesser extent the $b$),
according to its bulk mass parameter $c$.
\item The KK gluon, by contrast, is sharply peaked at the IR brane. Its coupling
to a given quark is therefore set by the \emph{overlap} of the quark's
wavefunction with the IR-localised gluon profile --- large for IR-localised
quarks, small for UV-localised ones.
\item These overlaps are flavour-dependent and, crucially, are \emph{not}
aligned with the SM Yukawa matrices. Rotating to the quark mass basis leaves
off-diagonal KK-gluon couplings: a tree-level $\bar s\, b$--gluon vertex.
\end{enumerate}
Two such vertices, joined by a KK-gluon propagator, give a tree-level
$b\bar s\to \bar b s$ amplitude. Integrating out the KK gluon (mass $\MKK$)
produces exactly the operators \eqref{eq:opsVLL}--\eqref{eq:opsLR} with Wilson
coefficients of the schematic size
\begin{equation}
C_i \;\sim\; \frac{g_{s*}^2}{\MKK^2}\,(\Delta_L)_{sb}\,(\Delta_R)_{sb},
\label{eq:Cscale}
\end{equation}
where $g_{s*}$ is the effective IR gluon coupling and $(\Delta_{L,R})_{sb}$ are
the left/right flavour-violating overlaps. The all-important $1/\MKK^2$ is the
universal decoupling: heavier KK modes mean smaller mixing. This is the
warped analogue of the SM box, but \emph{enhanced} by being tree level and by the
chiral structure below.

In our code this matching is brutally explicit. The function
\code{compute\_delta\_f2\_wilsons} (in \code{quarkConstraints/deltaf2.py}) takes
the mass-basis left/right couplings $g_L\equiv$\,\code{left} and
$g_R\equiv$\,\code{right} for the $sb$ pair and a prefactor
$1/\MKK^2$ and assembles, at the matching scale $\mu=\MKK$,
\begin{align}
C_1^{\rm VLL} &= \frac{g_L^2}{6\,\MKK^2}, &
C_1^{\rm VRR} &= \frac{g_R^2}{6\,\MKK^2},
\label{eq:codeVLL}\\
C_4^{\rm LR} &= -\,\frac{g_L\,g_R}{\MKK^2}, &
C_5^{\rm LR} &= \frac{g_L\,g_R}{3\,\MKK^2}.
\label{eq:codeLR}
\end{align}
Note the structure: the vector coefficients are $\propto g_L^2$ or $g_R^2$ (a
single chirality), while the LR coefficients are $\propto g_L g_R$ (one of each).
The factor of $1/6$ on the vector pieces is the SU(3) colour-Fierz factor
($\half$ from the propagator times $\tfrac13$ from $\sum_A T^A\!\otimes T^A$);
this is the convention the repo deliberately pins and which reproduces the
published Csaki--Falkowski--Weiler result to machine precision (see
\S\ref{sec:R5}). The couplings themselves are \emph{complex} in general, so
\eqref{eq:codeVLL}--\eqref{eq:codeLR} hand $\MtwelveNP$ a genuine phase --- which
is the entire origin of the $\phis$ effect.

\section{Why the left--right operator dominates the $\Bs$ system}
\label{sec:lr}

Two effects conspire to make the LR operators $Q_4,Q_5$ the leading contribution
to $\Bs$ mixing, and it is important to weight them correctly. The decisive one
is the \emph{Wilson coefficient}. Comparing \eqref{eq:codeVLL}--\eqref{eq:codeLR},
the LR coefficient $C_4 = -g_L g_R/\MKK^2$ carries no colour-Fierz suppression,
whereas the vector coefficient $C_1 = g_L^2/(6\MKK^2)$ is suppressed by the
$1/6$ colour factor. So even before any hadronic input, $|C_4|$ is a factor of
$\sim 6$ larger than $|C_1|$ for comparable couplings; QCD running
(\S\ref{sec:running}) widens the gap further by enhancing the LR coefficients
toward low scales. This Wilson-coefficient hierarchy is the bulk of the LR
dominance: at the matching scale the total LR contribution
$C_4\langle Q_4\rangle + C_5\langle Q_5\rangle$ is already several times the VLL
piece $C_1\langle Q_1\rangle$, and almost all of that ratio comes from the
coefficients, not the matrix elements.

The matrix element supplies a second, milder enhancement: a chiral factor
\[
r_\chi = \left(\frac{m_{\Bs}}{m_b+m_s}\right)^2 \approx
\left(\frac{5.37}{4.18+0.093}\right)^2 \approx 1.58,
\]
which appears in the LR matrix elements but not the VLL one. Crucially, for
$\Bs$ this makes the LR matrix elements only \emph{comparable} to the VLL one,
not dramatically larger: with the repo factors below, and folding in the FLAG
bag values $B_1=0.87,\,B_4=1.02,\,B_5=0.96$, one finds
$\langle Q_4\rangle \approx 0.52\,f^2 m$ and
$\langle Q_5\rangle \approx 0.84\,f^2 m$ against
$\langle Q_1\rangle \approx 0.58\,f^2 m$, so
the LR matrix elements range from $\sim 0.9$ to $\sim 1.4$ times the VLL one.
(With the bag parameters set to unity the prefactors are
$\tfrac23\approx0.67$, $\tfrac{r_\chi}{6}+\tfrac14\approx0.51$, and
$\tfrac{r_\chi}{2}+\tfrac1{12}\approx0.87$; the bag values shift these only
slightly and do not change the qualitative comparison.)
The chiral factor is genuine but it is not where the operator dominance lives ---
that is in the coefficient. Our code encodes the matrix elements directly in
\code{\_meson\_matrix\_elements}, where
\begin{align}
\langle Q_1^{\rm VLL}\rangle &= \tfrac23\, f_{\Bs}^2 m_{\Bs}\, B_1,
\label{eq:meVLL}\\
\langle Q_4^{\rm LR}\rangle &= \big(\tfrac{r_\chi}{6}+\tfrac14\big)\,
f_{\Bs}^2 m_{\Bs}\, B_4,\qquad
\langle Q_5^{\rm LR}\rangle = \big(\tfrac{r_\chi}{2}+\tfrac{1}{12}\big)\,
f_{\Bs}^2 m_{\Bs}\, B_5 .
\label{eq:meLR}
\end{align}
The $r_\chi$ terms in \eqref{eq:meLR} are the chiral enhancement, absent from
\eqref{eq:meVLL}. (In the kaon system the matrix-element chiral effect is much
larger because the down-type masses there are tiny; the \emph{bare} kaon
$r_\chi = (m_K/(m_s+m_d))^2 \approx 25.7$ is already an order of magnitude bigger
than the $\Bs$ value of $\approx 1.58$. Csaki--Falkowski--Weiler package the
kaon LR enhancement as the combined factor
$\tfrac34\,(m_K/(m_s+m_d))^2\,\eta_1^{-5} \approx 18$ (their Eq.~2.18): the
$\tfrac34$ operator-structure prefactor and the QCD running factor $\eta_1^{-5}$
reduce the bare $25.7$ to about $18$, so the two numbers describe the same
physics in different normalisations and neither is directly the $\Bs$ number.
For $\Bs$ the chiral effect is far milder because the $b$ mass is large.) Finally, in an anarchic warped model both $g_L$ and $g_R$ are generically
nonzero and $\mathcal{O}(1)$ in flavour space, so the product $g_L g_R$ feeding
$C_4$ is not suppressed. The combination of an unsuppressed, running-enhanced LR
Wilson coefficient with a chirally enhanced matrix element makes $Q_4$ the
dominant operator. This is the warped-model statement of a general fact:
\emph{left--right operators are the dangerous ones for meson mixing}, because
they are tiny in the SM (which is almost purely left-handed in its charged
currents) but generic in new physics with both chiralities localised
independently.

\section{QCD running: from $\MKK$ down to the hadron}
\label{sec:running}

The Wilson coefficients \eqref{eq:codeVLL}--\eqref{eq:codeLR} are defined at the
matching scale $\mu=\MKK\sim$~TeV, but the hadronic matrix elements
\eqref{eq:meVLL}--\eqref{eq:meLR} are evaluated at a low scale $\muhad=2$~GeV
where the lattice bag parameters are quoted. The coefficients must therefore be
QCD-evolved down. Our code does this with leading-log renormalisation-group
running in \code{\_evolve\_wilsons}, which delegates to
\code{evolve\_deltaf2\_wilsons} in the shared \code{qcd\_running} module. The
vector (VLL/VRR) and scalar (LR) operators run with different anomalous
dimensions; in particular the LR coefficients $C_4,C_5$ mix under running and are
\emph{enhanced} toward low scales, which further amplifies their dominance. The
running is applied automatically by the
\code{bs\_mixing\_from\_wilsons\_with\_running} path (\S\ref{part:code}) before
the matrix elements are contracted. \textbf{This is not optional bookkeeping:}
the running changes the answer by an $\mathcal{O}(1)$ factor and is part of why
our normalisation agrees with one published reference and differs from another by
a basis/running factor (\S\ref{sec:R5}).

\section{Parametric size and where the $\MKK$ floor comes from}
\label{sec:floor}

Putting the pieces together, the new-physics mixing amplitude scales as
\begin{equation}
|\MtwelveNP| \;\sim\; \frac{g_{s*}^2}{\MKK^2}\,(\Delta_L)_{sb}(\Delta_R)_{sb}\,
r_\chi\, f_{\Bs}^2 m_{\Bs}\,.
\label{eq:M12scale}
\end{equation}
A point is excluded when $|\MtwelveNP|$ exceeds the available budget, which is of
order $|\dms^{\rm exp}-\dms^{\rm SM}|/2$ for the magnitude (\code{B003}), or when
the induced phase shift exceeds the $\phis$ error (\code{B004}). Because the
budget is so small (SM and data agree to per-mille), even the $1/\MKK^2$
suppression is not enough unless $\MKK$ is large. In the fully anarchic
(no-alignment) case the literature finds that $\epsilon_K$ pushes $\MKK$ above
roughly $20$~TeV (Csaki--Falkowski--Weiler 0804.1954 quote $\gtrsim 21$~TeV;
Blanke et al.\ 0809.1073 find $\gtrsim 20$~TeV), with $\Bs$ mixing somewhat less
severe but still in the multi-TeV range. The $\Bs$ phase $\phis$ is, in models
with anarchic phases, comparably constraining because of the $1/|\MtwelveSM|$
amplification noted above. \textbf{In short: the $\MKK$ floor from $\Bs$ mixing is
the value at which the $1/\MKK^2$-suppressed, chirally enhanced, tree-level
KK-gluon amplitude finally fits inside the tiny SM-vs-data gap.}

\begin{callout}{Worked numerical example --- the budget and how a point is vetoed.}
Take the $\Bs$ inputs hardwired in the core. The experimental and SM mass
splittings are
\[
\dms^{\rm exp} = 1.1688\times10^{-11}\ \text{GeV},\qquad
\dms^{\rm SM} = 1.17\times10^{-11}\ \text{GeV}.
\]
The \emph{legacy} core budget is the more generous of half the experimental
splitting and half the residual,
\[
\text{budget}_{\rm core} = \max\!\Big(\tfrac{\dms^{\rm exp}}{2},\,
\tfrac{|\dms^{\rm exp}-\dms^{\rm SM}|}{2}\Big)
= \tfrac{1.1688\times10^{-11}}{2} \approx 5.844\times10^{-12}\ \text{GeV},
\]
which is exactly the \code{bound=5.844e-12} stored on the \code{b\_s} input. The
\emph{catalog} \code{B003} veto is tighter, and --- this is the lesson the
example is meant to teach --- it is \emph{not} set by the SM-vs-data residual at
all. It uses the residual plus the combined uncertainty,
\[
\text{budget}_{\rm B003} = \frac{|\dms^{\rm exp}-\dms^{\rm SM}| + \sigma_{\rm comb}}{2},
\qquad
\sigma_{\rm comb} = \sqrt{\sigma_{\rm exp}^2 + \sigma_{\rm theory}^2}.
\]
Plug in the stored numbers and watch where the budget comes from. The residual is
tiny: with the exact conversion $\dms^{\rm exp}=17.766\,\mathrm{ps}^{-1}\times
\hbar = 1.16938\times10^{-11}$~GeV against $\dms^{\rm SM}=1.17\times10^{-11}$~GeV,
$|\dms^{\rm exp}-\dms^{\rm SM}| \approx 6\times10^{-15}$~GeV. The experimental
error is also small, $\sigma_{\rm exp} = 0.006\,\mathrm{ps}^{-1}\times\hbar
\approx 4\times10^{-15}$~GeV. The budget is therefore dominated by the
\emph{theory} error,
\[
\sigma_{\rm theory} = 2|\dms^{\rm SM}|\times\frac{\sigma_f}{f}
= 2\,(1.17\times10^{-11})\times\frac{5.7}{256.1} \approx 5.2\times10^{-13}\ \text{GeV},
\]
which folds in the FLAG normalisation uncertainty
$f_{\Bs}\sqrt{\hat B_{\Bs}} = 256.1\pm5.7$~MeV (a $2.2\%$ relative error). Hence
$\sigma_{\rm comb}\approx\sigma_{\rm theory}$ and
\[
\text{budget}_{\rm B003}\approx
\frac{6\times10^{-15} + 5.2\times10^{-13}}{2} \approx 2.6\times10^{-13}\ \text{GeV}.
\]
This is exactly what the legacy $5.844\times10^{-12}$~GeV number hides: the actual
veto threshold is more than an order of magnitude smaller, and it is governed by
the lattice theory error, not by how well SM and data happen to agree.
A model point produces $|\MtwelveNP|$ from
\eqref{eq:M12sum}; the constraint reports
$\text{ratio} = |\MtwelveNP|/\text{budget}_{\rm B003}$ and
\textbf{vetoes the point if ratio $>1$}. Suppose a $3$~TeV anarchic point yields
$|\MtwelveNP| \approx 2.1\times10^{-12}$~GeV against this
$\sim 2.6\times10^{-13}$~GeV budget; then ratio $\approx 8$ and the point is
excluded. Pushing $\MKK$ up by $\sqrt{8}\approx 2.8$ (to $\sim 8$~TeV) drops
$|\MtwelveNP|$ by $8$ and brings ratio to $\sim 1$ --- this is the floor,
illustrated.
\end{callout}

% ====================================================================
\part{Model dependence: custodial symmetry and alignment}
\label{part:cust}
% ====================================================================

\section{Does custodial symmetry relax this bound? No.}
\label{sec:custodial}

It is worth being very precise here, because custodial symmetry is the hero of
the electroweak story and one might expect it to help the flavour story too. It
does \emph{not} help $\Delta F=2$. Custodial $\SUL\times\SUR\times\UX$ and its
discrete partner $\PLR$ protect \emph{electroweak} quantities: the $T$ parameter
(via $\SUR$) and the $Z\bar b_L b_L$ vertex (via $\PLR$). The $\Delta F=2$
operators \eqref{eq:opsVLL}--\eqref{eq:opsLR} are generated by \emph{KK-gluon}
exchange and depend only on the flavour structure of the quark localisation, not
on the electroweak gauge group. Enlarging the bulk gauge symmetry does nothing to
the $\bar s b$--gluon overlaps. Consequently:
\begin{itemize}[leftmargin=1.4em]
\item Switching on custodial protection \emph{removes} the $Z\to b\bar b$
constraint (\code{T010}/\code{T011}), which in the minimal model was the binding
floor at $\sim 25$--$30$~TeV in physical $\MKK$.
\item Once $Z\to b\bar b$ is gone, the next-strongest \emph{rigorous} constraints
are precisely the $\Delta F=2$ set $\{\epsilon_K,\dms,\phis\}$ =
$\{$\code{K001},\code{B003},\code{B004}$\}$, which are untouched by custodial
symmetry and set a strict floor of $\sim 2$--$3$~TeV.
\end{itemize}
This is the sense in which \code{B003}/\code{B004} ``set the strict custodial
floor.'' In our paired $1$M scans (baseline job \code{20128400} vs custodial
\code{20675555}, same $r\times\MKK$ grid and seeds), the custodial branch removed
$694{,}123$ minimal $Z\to b\bar b$ vetoes (to zero), and the rigorous floor
dropped onto the $\Delta F=2$ trio, running from $\sim 1$~TeV at small mixing
($r=0.05$) to $\sim 3$~TeV at $r=1.0$. \textbf{The flavour bound is the price you
keep paying after custodial symmetry has cancelled the electroweak one.}

\section{Does flavour alignment relax it? Yes --- but that is a different model.}
\label{sec:alignment}

The way to actually relax the $\Delta F=2$ bound is not symmetry but
\emph{alignment}: arrange the bulk masses so that the KK-gluon couplings are
(approximately) diagonal in the quark mass basis, killing the off-diagonal
$(\Delta_{L,R})_{sb}$ in \eqref{eq:Cscale}. This is a genuinely different
construction (e.g.\ flavour-symmetric or partially-aligned bulk masses) and is a
comparison point, not what our anarchic scan implements. Our default treatment is
\emph{anarchic}: the couplings come from the fitted mass-basis matrices with no
imposed alignment, which is the conservative, maximally-constraining choice.
\textbf{Honesty tag:} the $\Bs$ magnitude and phase are treated \emph{rigorously}
in our code (per-point complex $\MtwelveNP$, QCD-run, lattice matrix elements,
uncertainty-aware budgets), \emph{not} as proxies. The model dependence that
remains is the choice of anarchy vs.\ alignment, which is an input assumption, not
an approximation in the evaluation.

\begin{callout}{Common confusions, defused.}
\begin{itemize}[leftmargin=1.2em,nosep]
\item[\textbf{A.}] \emph{``$\dms$ and $\phis$ are two independent measurements.''}
No --- they are the modulus and the argument of the \emph{same} complex
$\MtwelveNP$. Our code computes that one number and reads two observables off it.
\item[\textbf{B.}] \emph{``Custodial symmetry protects $\Bs$ mixing like it
protects $T$.''} No --- custodial $\SUR/\PLR$ are electroweak; $\Delta F=2$ comes
from KK-gluon exchange and is untouched. \code{B003}/\code{B004} survive
custodial protection and set the strict floor.
\item[\textbf{C.}] \emph{``$\phis^{\rm SM}$ is the YAML literal $-0.0368$.''}
No --- since commit \code{c5970a7} (W4) the SM phase is computed \emph{in core}
as $-2\betas$ from the repo CKM matrix ($-0.03795$~rad); the YAML
\code{standard\_model\_reference} now supplies only the \emph{uncertainty} anchor.
\item[\textbf{D.}] \emph{``The $\times 2$ in $\dms=2|\Mtwelve|$ and the various
$/6$, $\times(2/3)$ factors are interchangeable.''} No --- the repo's
$(2/3)$-matrix-element / $/6$-Wilson convention is a fixed, self-consistent
pair that reproduces the literature (\S\ref{sec:R5}). Many textbooks instead
write $\langle Q_1\rangle = \tfrac83 f^2 m\, B_1$ with the colour-Fierz factor
\emph{absorbed into the matrix element} and a Wilson coefficient that lacks the
$/6$; the two conventions give the same $\Mtwelve$, but mixing the
$\tfrac83$-matrix-element of one with the $/6$-Wilson of the other would
double-count the colour factor and shift the answer by a factor of a few.
\item[\textbf{E.}] \emph{``budget $=\dms/2$ means half the measured value.''}
The \emph{core legacy} budget is $\max(\dms^{\rm exp}/2,\,\text{residual}/2)$; the
\emph{catalog} \code{B003} veto overrides it with the tighter, uncertainty-aware
SM-vs-experiment room. ``$\dms/2$'' is shorthand for the $M_{12}$-amplitude
normalisation ($\Mtwelve=\dms/2$), not the actual veto threshold.
\end{itemize}
\end{callout}

% ====================================================================
\part{What is in OUR code}
\label{part:code}
% ====================================================================

\emph{Reader here for the physics may skim Part~\ref{part:code} on a first pass
and jump to Part~\ref{part:subtle}; this part documents the exact code so the
note doubles as an implementation reference.}

\section{The $\Delta F=2$ core inputs for $\Bs$}
\label{sec:codeinputs}

The $\Bs$ system is one entry in the repo-owned input bundle
\code{DEFAULT\_DELTA\_F2\_INPUTS\_V1} (in \code{quarkConstraints/deltaf2.py}):
\begin{center}
\begin{tabular}{ll}
\toprule
field & value \\
\midrule
\code{key} & \code{"b\_s"} \\
\code{sector} & \code{"down"} \\
\code{generations} & \code{(1, 2)}\ \ (the $s,b$ flavour indices) \\
\code{bound} & \code{5.844e-12}\ GeV\ (legacy core $M_{12}$ budget) \\
\code{column\_name} & \code{"b\_s\_ratio"} \\
\bottomrule
\end{tabular}
\end{center}
The hadronic constants are the module-level (FLAG~2024 / PDG) values
\begin{equation}
\begin{aligned}
&f_{\Bs} = 0.2303~\text{GeV},\quad m_{\Bs}=5.36692~\text{GeV},\quad
m_b = 4.18~\text{GeV},\quad m_s = 0.0934~\text{GeV},\\
&B_1 = 0.87,\quad B_4 = 1.02,\quad B_5 = 0.96,\\
&\dms^{\rm exp} = 1.1688\times10^{-11}~\text{GeV},\quad
\dms^{\rm SM} = 1.17\times10^{-11}~\text{GeV}.
\end{aligned}
\end{equation}
(These are \code{F\_BS}, \code{M\_BS}, \code{M\_B\_QUARK},
\code{M\_S\_QUARK\_BS}, \code{B\_1\_BS}, \code{B\_4\_BS}, \code{B\_5\_BS},
\code{DELTA\_M\_BS\_EXP}, \code{DELTA\_M\_BS\_SM} respectively.) The matching
prefactor is $1/\MKK^2$ and the matching scale is $\MKK$ itself, defaulting to
\code{DEFAULT\_QUARK\_TARGET\_SCALE\_GEV = 3000.0}~GeV with
\code{DEFAULT\_QUARK\_XI\_KK = 1.0}.

\section{The complex $\MtwelveNP$, exactly}
\label{sec:codeM12}

The heart of both observables is \code{compute\_m12\_np}
(\code{deltaf2.py}, $\sim$L916), which contracts the Wilson coefficients with the
matrix elements \emph{without} taking an absolute value:
\begin{equation}
\MtwelveNP = C_1^{\rm VLL}\langle Q_1\rangle + C_1^{\rm VRR}\langle Q_1\rangle
 + C_4^{\rm LR}\langle Q_4\rangle + C_5^{\rm LR}\langle Q_5\rangle,
\label{eq:codeM12}
\end{equation}
returning a Python \code{complex}. The magnitude path
\code{evaluate\_bs\_mixing} then takes \code{abs(m12)}, while the
phase-preserving path
\code{bs\_mixing\_m12\_np\_from\_wilsons\_with\_running} (in the adapter
\code{flavor\_catalog\_constraints/physics\_adapters/deltaf2.py}) returns the
full complex number. The adapter docstring is explicit that this is
``the phase-preserving companion'' to the magnitude evaluator and ``does not
collapse the result to \code{abs(M12\_NP)}''. \textbf{This single design choice
--- compute the complex amplitude once, expose both modulus and argument --- is
what lets \code{B003} and \code{B004} share machinery.}

\section{\code{B003}: the $\dms$ magnitude veto}
\label{sec:codeB003}

\code{flavor\_catalog\_constraints/primary/beauty/B003.py} defines a
\code{Constraint} class with
\begin{equation}
\code{process\_id = "B003"},\quad
\code{severity = Severity.HARD},\quad
\code{observable = "Delta m\_s"}.
\end{equation}
Its \code{evaluate} method pulls the mass-basis couplings from the
\code{ParameterPoint} (extra key \code{quark\_mass\_basis\_couplings}; if absent
it passes trivially with a ``not evaluated'' note), builds the $\Bs$ Wilsons via
\code{bs\_mixing\_wilsons\_from\_couplings}, and calls
\code{bs\_mixing\_from\_wilsons\_with\_running} with \code{mu\_had = 2.0}~GeV and
the catalog budget. The returned \code{MesonMixingResult} carries
\code{abs\_m12\_np}, \code{budget}, \code{ratio\_to\_budget}, and \code{passes}
(true iff \code{ratio <= 1.0}). The HARD budget is \emph{not} the legacy core
value; it is the uncertainty-aware band built in \code{\_build\_budget\_band}:
\begin{equation}
\text{hard\_veto\_budget} =
\frac{|\dms^{\rm exp}-\dms^{\rm SM}| + \sigma_{\rm comb}}{2},
\qquad
\sigma_{\rm comb}=\sqrt{\sigma_{\rm exp}^2+\sigma_{\rm theory}^2},
\label{eq:B003budget}
\end{equation}
with $\sigma_{\rm theory}=2|\dms^{\rm SM}|\cdot(\sigma_f/f)$ and
$\sigma_f/f$ the FLAG $f_{\Bs}\sqrt{\hat B_{\Bs}}$ relative error
(\code{flag\_f\_bs\_sqrt\_bhat\_relative\_sigma}). The legacy
$\max(\dms^{\rm exp}/2,\,\text{residual}/2)$ value is retained in
\code{diagnostics} (\code{core\_legacy\_m12\_budget}) but does not drive the veto.
A point is vetoed when its $|\MtwelveNP|$ overflows \eqref{eq:B003budget}.

\section{\code{B004}: the $\phis$ phase veto and the in-core CKM phase}
\label{sec:codeB004}
\label{sec:incore}

\code{flavor\_catalog\_constraints/primary/beauty/B004.py} defines a
\code{Constraint} with
\begin{equation}
\code{process\_id = "B004"},\quad
\code{severity = Severity.HARD},\quad
\code{observable = "phi\_s(B\_s -> J/psi phi)"}.
\end{equation}
Its \code{evaluate} computes the complex $\MtwelveNP$ via
\code{bs\_mixing\_m12\_np\_from\_wilsons\_with\_running} (QCD-run to $2$~GeV),
takes the SM amplitude $\MtwelveSM = \dms^{\rm SM}/2$ (a positive real number, by
convention), forms the ratio, and rotates the phase:
\begin{equation}
\boxed{\;
\phis^{\rm NP} = \arg\!\Big(1 + \frac{\MtwelveNP}{\MtwelveSM}\Big),
\qquad
\phis = \phis^{\rm SM} + \phis^{\rm NP}.
\;}
\label{eq:codephis}
\end{equation}
In code this is \code{phi\_s\_np = cmath.phase(1.0 + m12\_np / m12\_sm)} followed
by \code{predicted = wrap(self.anchor.sm\_value + phi\_s\_np)}, where
\code{\_wrap\_phase\_radians} maps onto $[-\pi,\pi]$ via \code{atan2}. The
diagnostics record \code{phase\_uses\_complex\_m12\_not\_abs = True} and
\code{phase\_formula = "phi\_s\_np = arg(1 + M12\_NP / M12\_SM)"} --- the use of
the complex (not absolute) $\MtwelveNP$ is the whole point.

The SM reference phase is \emph{computed in core}, not read from the YAML. This is
the W4 work (commit \code{c5970a7}, ``$\phis$ computed in-core''). \code{B004}
calls \code{repo\_default\_ckm\_phases()} (adapter export of
\code{quarkConstraints/ckm\_extraction.py}), which builds the PDG-2024 unitary
\code{ModernDefaultCKMTarget} and evaluates, in
\code{ckm\_phases\_from\_matrix}, the rephasing-invariant
\begin{equation}
\betas = \arg\!\left(-\frac{V_{ts}V_{tb}^*}{V_{cs}V_{cb}^*}\right),
\qquad
\phis^{\rm SM} = -2\betas .
\label{eq:codebetas}
\end{equation}
The function returns a \code{CKMPhaseAngles} dataclass whose \code{phi\_s} field
is used as the SM phase. The computed values (recorded in the W4 ledger and the
commit message) are
\begin{equation}
2\beta = 45.10^\circ,\quad \sin 2\beta = 0.7083,\quad
\phis^{\rm SM} = -2\betas = -0.03795\ \text{rad},
\end{equation}
PDG-consistent. The W4 commit explicitly states the ``no CKM-phase in core''
\code{NEEDS-HUMAN} flag was \emph{removed} and the SM phase path is now
rigorous; the YAML \code{standard\_model\_reference} ($-2\betas = -0.0368$~rad
with asymmetric error $+0.0009/-0.0006$) survives only as the \emph{uncertainty}
anchor.

The veto compares the total predicted $\phis$ to the HFLAV experimental average
\eqref{eq:phisexp} within a direction-aware budget (\code{\_selected\_budget}):
the residual is wrapped to $[-\pi,\pi]$, and depending on its sign the budget is
$\sqrt{\sigma_{\rm exp}^2+\sigma^{\rm SM}_{\rm upper/lower}{}^2}$ (the asymmetric
SM uncertainty handled correctly). The point passes iff
$|\phis - \phis^{\rm exp}|/\text{budget} \le 1$.

\section{The shared machinery and how a point is vetoed}
\label{sec:codeflow}

The full evaluation chain for one parameter point, for both observables, is:
\begin{footnotesize}
\begin{verbatim}
  ParameterPoint.quark_mass_basis_couplings   (fitted, complex, mass basis)
        |  bs_mixing_wilsons_from_couplings  ->  compute_delta_f2_wilsons
        v
  DeltaF2WilsonCoefficients  (C1_VLL, C1_VRR, C4_LR, C5_LR  at mu = M_KK)
        |  _evolve_wilsons (evolve_deltaf2_wilsons, leading-log, M_KK -> 2 GeV)
        v
  evolved Wilsons at mu_had = 2 GeV
        |  compute_m12_np  (contract with f_Bs, m_Bs, B1, B4, B5)
        v
  M12^NP  (complex)
       / abs(.)                                 \ arg(1 + ./M12_SM)
  B003: |M12^NP| vs budget   (HARD)        B004: phi_s = phi_s^SM + NP phase  (HARD)
\end{verbatim}
\end{footnotesize}
Both constraints are \code{Severity.HARD}, meaning a failing point is
\emph{vetoed} (removed from the surviving parameter region), not merely flagged.
Both report \code{predicted}, \code{ratio}, \code{budget}, and \code{passes} in a
\code{ConstraintResult}, with the complex $\MtwelveNP$, the Wilson coefficients,
the matching/hadronic scales, and the full budget breakdown in
\code{diagnostics}.

% ====================================================================
\part{Subtleties and the gap to ``rigorous''}
\label{part:subtle}
% ====================================================================

\section{The normalisation cross-checks (the $\times 2$ scare)}
\label{sec:R5}

The repo's $\Delta F=2$ normalisation was audited twice and recorded as
\emph{correct} in the program ledger (the ``R5 RESOLVED'' entry, dual-confirmed
2026-06-03). Two cross-checks:
\begin{itemize}[leftmargin=1.4em]
\item Against \textbf{Csaki--Falkowski--Weiler 0804.1954} (Eqs.~3.3--3.7,
KK-gluon $t$-channel with the exact SU(3) Fierz
$\sum_A T^A\!\otimes T^A = \half(\delta\delta - \delta\delta/N_c)\to \tfrac13 Q_1$):
the repo's $2|\MtwelveNP|$ matches to machine precision (ratio $1.0000$). The
$\langle Q_1\rangle = \tfrac23 f^2 m_{\Bs} B_1$ matrix element together with the
Wilson $/6$ is the correct $\half(\text{propagator})\times\tfrac13(\text{colour-Fierz})$
convention.
\item Against \textbf{Blanke et al.\ 0809.1073} (Eq.~4.33): the ratio is
$\sim 1.69$, attributable to a \emph{basis/running difference}, \textbf{not} a
factor-of-$0.5$ failure mode. The ledger is emphatic: ``$\times 2$ would be the
WRONG fix'' --- multiplying by two to ``agree'' with one normalisation would
break the machine-precision agreement with the other.
\end{itemize}
\textbf{Documented hazard:} the $(2/3)$-matrix-element / $/6$-Wilson convention
must never be mixed with the textbook $(8/3)$-matrix-element convention. The
ledger records that no live constraint mixes them; only a test/script path
(\code{matching\_kkgluon.py}) uses the same $/6$ convention, consistently.

\section{The budget convention: ``$\dms/2$'' has three meanings}
\label{sec:budgetconv}

The phrase ``budget $=\dms/2$'' is used loosely and means three different things
that must be kept apart:
\begin{enumerate}[leftmargin=1.8em]
\item \textbf{Amplitude normalisation:} $\Mtwelve = \dms/2$ relates the
observable to the off-diagonal amplitude. This is physics, always true.
\item \textbf{Legacy core budget:} \code{\_bs\_budget} returns
$\max(\dms^{\rm exp}/2,\,|\dms^{\rm exp}-\dms^{\rm SM}|/2)$, stored as the
\code{bound=5.844e-12} on the $\Bs$ input. Generous; retained only in
diagnostics.
\item \textbf{Catalog \code{B003} veto:} the uncertainty-aware
$\big(|\dms^{\rm exp}-\dms^{\rm SM}|+\sigma_{\rm comb}\big)/2$ of
\eqref{eq:B003budget}. This is the threshold that actually vetoes.
\end{enumerate}
Quoting a $\Bs$-mixing bound without saying which of these is meant is a recipe
for a factor-of-few confusion.

\section{The $\MKK$ convention}
\label{sec:Mconvention}

As in the oblique-parameter note, ``$\MKK$'' is overloaded. The matching is done
at $\mu=\MKK$, using the point's \code{couplings.M\_KK}; the repo's
\code{DEFAULT\_QUARK\_TARGET\_SCALE\_GEV = 3000} GeV is only the default reference
scale. The
physical first KK \emph{gluon} mass and the warp scale $\LIR$ differ by a Bessel
root ($x_1\approx 2.45$ for gauge fields). When the scan quotes a ``$\sim 2$--$3$~TeV
strict floor'' it is in the $\MKK$ matching-scale convention used by the Wilson
prefactor $1/\MKK^2$; translating to a physical KK-gluon mass or to $\LIR$ needs
the same care flagged for the $Z\to b\bar b$ and oblique floors. Whatever
convention the budget and the couplings are calibrated in must match the $\MKK$
fed to \code{compute\_delta\_f2\_wilsons}.

\section{Deferred pieces and honest tags}
\label{sec:deferred}

\begin{itemize}[leftmargin=1.4em]
\item \textbf{$\Gamma_{12}$ is not modelled.} The absorptive part of the mixing
matrix (which feeds the width difference $\Delta\Gamma_s$ and a small correction
to $\phis$) is neglected; for the $\Bs$ system $|\Gamma_{12}|\ll|\Mtwelve|$, so
this is a good approximation but not exact. The YAML carries the companion
$\Delta\Gamma_s$ values for context only.
\item \textbf{SM box is an input, not recomputed.} $\dms^{\rm SM}$ and
$\MtwelveSM$ are taken as fixed CKMfitter-style numbers
(\code{DELTA\_M\_BS\_SM}); the code does not recompute the SM box per point. New
physics is added on top.
\item \textbf{The phase helpers (R3) are Opus-only reviewed.} The complex-$M_{12}$
phase-preserving helpers (ledger item R3, commit \code{e08977d}, used by
\code{B002}/\code{C002} and the $\Bs$ path) carry an ``Opus-only'' review note in
the program ledger --- dual-OK on retro audit, but worth recording.
\item \textbf{The in-core CKM phase is rigorous, with one caveat.} The W4 ledger
\code{impl\_out} notes that a true Opus review could not be run in that
environment (only a Codex subagent \code{APPROVE}); the angles were however
recomputed bit-identically from the repo CKM matrix and reproduce the SM limit,
and the change touched \emph{zero} \code{deltaf2}/$M_{12}$ files.
\end{itemize}

\section{Checklist: what a fully rigorous $\Bs$ treatment still wants}
\begin{enumerate}[leftmargin=1.8em]
\item A per-point SM box (rather than a fixed \code{DELTA\_M\_BS\_SM}), so that
$\phis^{\rm SM}$ and $\dms^{\rm SM}$ track the same CKM inputs as the NP piece.
\item $\Gamma_{12}$ / $\Delta\Gamma_s$ for the residual phase correction and the
width observable.
\item Next-to-leading-log running and a documented matrix-element scale
(the FLAG $B_4,B_5$ scale caveat flagged for the kaon system also touches the
$\Bs$ LR operators).
\item A pinned $\MKK$ convention shared across $\Delta F=2$, $Z\to b\bar b$, and
the oblique floors so the quoted ``$2$--$3$~TeV'' is unambiguous.
\end{enumerate}

% ====================================================================
\part*{Annotated reading guide}
\addcontentsline{toc}{section}{Annotated reading guide}
% ====================================================================

\begin{description}[leftmargin=0em,style=nextline]
\item[Csaki, Falkowski, Weiler, \emph{arXiv:0804.1954}.] The anarchic-RS flavour
paper our normalisation is checked against to machine precision (\S\ref{sec:R5}).
KK-gluon $t$-channel exchange, the SU(3) Fierz that gives the $\tfrac13 Q_1$
colour factor, the chirally enhanced LR operator, and the $\gtrsim 21$~TeV
$\epsilon_K$ bound. Read \S\ref{sec:kkgluon}--\S\ref{sec:lr} alongside its
Eqs.~3.3--3.7.

\item[Blanke, Buras, Duling, Gori, Weiler, \emph{arXiv:0809.1073}.] The
$\Delta F=2$ companion with custodial protection. Its Eq.~4.33 is our second
cross-check; the $\sim 1.69$ ratio is a basis/running difference, \emph{not} the
$0.5\times$ failure mode (\S\ref{sec:R5}). Also the cleanest statement that
custodial $\PLR$ suppresses the \emph{electroweak} $Z\bar d_L d_L$ couplings
while leaving $\Delta F=2$ to set the floor --- exactly our \S\ref{sec:custodial}.
Defines $\phis = \arg(\Mtwelve)$ and $\dms = 2|\Mtwelve|$.

\item[\code{deltaF2\_framework\_review.tex} (companion note).] The shared
$\Delta F=2$ machinery in full generality: the Wilson basis
\eqref{eq:opsVLL}--\eqref{eq:opsLR}, the matching \eqref{eq:codeVLL}--\eqref{eq:codeLR},
the QCD running, and the hadronic matrix elements. This $\Bs$ note is
self-contained on the framework, but the framework note is the canonical
reference for the $\Delta F=2$ core that all the meson-mixing observables share.

\item[\code{epsilon\_k\_review.tex} (companion note).] The same $\Delta F=2$ core
applied to the kaon system, where the LR chiral enhancement (bare
matrix-element factor $r_\chi\approx25.7$, or CFW's combined chiral-plus-running
$\approx 18$, \S\ref{sec:lr}) and the imaginary part of $C_4^{\rm LR}$ drive
the strongest $\gtrsim 21$~TeV anarchic floor. Read it for the cross-system view
and the $\epsilon_K$ side of the rigorous $\Delta F=2$ trio.

\item[\code{quarkConstraints/deltaf2.py}.] The $\Delta F=2$ core.
\code{compute\_m12\_np} ($\sim$L916), \code{compute\_delta\_f2\_wilsons}
($\sim$L314), \code{\_evolve\_wilsons} ($\sim$L590), the \code{b\_s} input
($\sim$L239), and the $\Bs$ constants ($\sim$L679--686). The complex amplitude is
built here; the magnitude/phase split happens downstream.

\item[\code{quarkConstraints/ckm\_extraction.py}.] The in-core CKM phase.
\code{ckm\_phases\_from\_matrix} computes $\betas$ and $\phis^{\rm SM}=-2\betas$;
\code{repo\_default\_ckm\_phases} feeds it the PDG-2024 target. This is the W4
work (commit \code{c5970a7}) that made \code{B004}'s SM phase rigorous.

\item[\code{flavor\_catalog\_constraints/primary/beauty/B003.py} and
\code{B004.py}.] The catalog constraints. \code{B003} = $\dms$ magnitude veto
with the uncertainty-aware budget \eqref{eq:B003budget}; \code{B004} = $\phis$
phase veto with the complex-$M_{12}$ phase \eqref{eq:codephis} and the in-core
$-2\betas$ SM reference. Both \code{Severity.HARD}. Their YAML sidecars
(\code{B003.yaml}, \code{B004.yaml}) hold the HFLAV/FLAG/LHCb provenance.

\item[Program ledger, \code{.orchestration/PHASE2\_PROGRAM\_LEDGER.md}.] The
``R5 RESOLVED'' normalisation audit, the R3 phase-helper note, the W4 in-core
CKM-phase entry, and the custodial $1$M scan result ($694{,}123$ minimal
$Z\to b\bar b$ vetoes $\to 0$; rigorous $\Delta F=2$ floor $\sim 2$--$3$~TeV).
The source of truth for the ``rigorous vs proxy'' tags used throughout.
\end{description}

\bigskip
\noindent\rule{\linewidth}{0.4pt}\\
\footnotesize
\emph{Internal note. Equations \eqref{eq:dms}, \eqref{eq:codeM12},
\eqref{eq:codephis}, \eqref{eq:B003budget}, \eqref{eq:codebetas} are the forms
our code uses; the numerical inputs ($f_{\Bs}=0.2303$~GeV, $\dms^{\rm exp}=17.766$
 ps$^{-1}$, $\phis^{\rm SM}=-0.03795$~rad, budget$\sim\dms/2$) are as stored in
\code{deltaf2.py}, \code{ckm\_extraction.py}, and the \code{B003}/\code{B004}
YAML sidecars. The ``rigorous'' tags for \code{B003}/\code{B004} follow the
orchestration ledgers. Cross-check before citing externally.}

\end{document}
