% Flavor catalog per-process draft.
% process_id: L003
% family: charged_lepton
% owner_agent_id: PKA-L003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: L003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L003: \texorpdfstring{\(\mu-e\)}{mu-e} Conversion in Aluminum}

\subsection*{Process}
\textbf{Standard notation:} \(R_{\mu e}^{\rm Al} =
\Gamma(\mu^-{\rm Al}\to e^-{\rm Al})/\Gamma_{\rm capture}(\mu^-{\rm Al})\).
This entry covers coherent neutrinoless muon-to-electron conversion on an
aluminum target, the design target for Mu2e and COMET.  It is a charged-LFV
nuclear process and is outside the current quark \(\Delta F=2\) scan lane.

\subsection*{PDG-or-equivalent value}
The PKA snapshots contain no published direct aluminum-target limit
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_status}).  The current
published benchmark across targets is the SINDRUM II gold result,
\[
  R_{\mu e}^{\rm Au} < 7\times10^{-13}\quad (90\%\ {\rm C.L.}),
\]
from \texttt{L003.yaml:pdg\_or\_equivalent.current\_world\_limit}; the local
snapshot is
\texttt{flavor\_catalog/references/L003/sindrumii\_2006\_gold\_juser.txt}.
This is not an aluminum measurement.  Aluminum inputs in the sidecar are
prospects: Mu2e quotes \(2.8\times10^{-17}\) single-event sensitivity and an
expected \(90\%\) C.L. upper limit \(6.7\times10^{-17}\)
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[0]}), Mu2e Run I
quotes \(R_{\mu e}<6.2\times10^{-16}\) expected sensitivity and
\(1.2\times10^{-15}\) discovery sensitivity
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[1]}), COMET
Phase-I quotes \(3.1\times10^{-15}\) single-event sensitivity and a
\(7.0\times10^{-15}\) expected upper limit
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[2]}), and COMET
Phase-II planning quotes \(2.6\times10^{-17}\) single-event sensitivity
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[3]}).

\subsection*{Relevance to RS / anarchic flavor}
In a warped lepton-flavor extension, coherent conversion probes dipole,
scalar, and vector lepton-quark operators.  KK gauge exchange, \(Z\)-like
flavor violation, Higgs-mediated scalar currents, and lepton-sector dipoles can
feed the same nuclear final state.  The observable is complementary to
\(\mu\to e\gamma\) because it can be contact-operator dominated, so it tests
lepton-extension structure not covered by the current dipole checker.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 RS-flavor baseline
(\texttt{L003.yaml:pdg\_or\_equivalent.post\_2008\_baseline}), the main change
is experimental.  Mu2e published staged aluminum sensitivity projections, and
Mu2e-II records a proposed PIP-II upgrade aiming for at least one additional
order of magnitude beyond Mu2e
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[4]}).  COMET
published Phase-I and Phase-II aluminum strategies
(\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[2]} and
\texttt{L003.yaml:pdg\_or\_equivalent.aluminum\_projections[3]}).  The process
therefore moved from SINDRUM-II context to a near-term dedicated aluminum
search program.

\subsection*{Constraint validity / model dependence}
The experimental signature is robust: a monoenergetic conversion electron from
a stopped negative muon with no neutrinos.  The mapping to RS parameters is
model-dependent.  It requires a lepton-quark operator basis, target-dependent
overlap integrals and capture rates, and a convention for combining dipole,
scalar, and vector contributions.  A gold limit cannot be treated as an
aluminum limit without a nuclear/operator translation.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no Mu2e, COMET, SINDRUM, \(R_{\mu e}\), or
\(\mu-e\)-conversion implementation.  The only adjacent LFV code is the
\(\mu\to e\gamma\) dipole checker at \texttt{flavorConstraints/muToEGamma.py}:75
and its scan call at \texttt{scanParams/scan.py}:524.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production implementation needs new lepton-quark Wilson
coefficients, target-dependent conversion formulae for aluminum, nuclear
overlap/capture inputs, and likely EFT running or matching shared with
\(\mu\to e\gamma\) and \(\mu\to3e\).  This is beyond adding a new numerical
limit to the existing dipole-only LFV path.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{SINDRUMII2006\_GoldMuE}, \texttt{Mu2e2016\_FullProjection},
\texttt{Mu2eRunI2023}, \texttt{COMETPhaseITDR2020},
\texttt{COMETStrategy2018}, \texttt{Mu2eII2022}, and \texttt{CFW2008}.
