% Flavor catalog per-process draft.
% process_id: L007
% family: charged_lepton
% owner_agent_id: PKA-L007
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: L007.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L007: \texorpdfstring{\(\tau\to\mu\gamma\)}{tau -> mu gamma} Dipole LFV}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(\tau^-\to\mu^-\gamma)\).
This entry covers the charged-lepton-flavor-violating radiative tau decay and
its use as a tau-sector dipole probe, complementary to the much tighter
\(\mu\to e\gamma\) constraint but involving the \(2\)-\(3\) lepton-flavor
transition.

\subsection*{PDG-or-equivalent value}
The current PDG/equivalent value is the sidecar
\texttt{L007.yaml:primary\_current\_limit} upper limit
\[
  \mathcal{B}(\tau^-\to\mu^-\gamma) < 4.2\times10^{-8}
  \quad (90\%\ {\rm C.L.}),
\]
from the PDGLive \(S035.31\) tau decay-mode summary, locally snapshotted at
\texttt{flavor\_catalog/references/L007/pdg2025\_tau\_mu\_gamma\_pdglive.txt}.
The primary experiment behind this value is the Belle full-data search using
\(988\,{\rm fb}^{-1}\), recorded in \texttt{L007.yaml:primary\_experiment},
which quotes
\(\mathcal{B}(\tau^\pm\to\mu^\pm\gamma)\le 4.2\times10^{-8}\) at \(90\%\)
C.L.; the local Belle snapshot is
\texttt{flavor\_catalog/references/L007/belle2021\_tau\_lgamma\_arxiv2103\_12994.txt}.

\subsection*{Relevance to RS / anarchic flavor}
In warped lepton-flavor extensions, this mode constrains the same class of
brane-localized or loop-induced charged-lepton dipoles as \(\mu\to e\gamma\),
but with the \(\tau\mu\) flavor spurion instead of the \(e\mu\) spurion.  It is
therefore not part of the quark \(\Delta F=2\) scan lane, but it is a useful
cross-check of any future lepton-sector implementation: models that suppress
\(\mu\to e\gamma\) through alignment can still leave enhanced tau-sector LFV.
The Perez--Randall warped-neutrino source records the lepton-MFV/GIM-like
assumptions under which charged-lepton flavor violation is controlled.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS flavor baseline, the experimental limit was
sharpened by the full-data \(B\)-factory searches.  BaBar's post-2008
full-data search used \((963\pm7)\times10^6\) tau decays and set
\(\mathcal{B}(\tau\to\mu\gamma)<4.4\times10^{-8}\) at \(90\%\) C.L.
(\texttt{L007.yaml:prior\_experimental\_limit}).  Belle's 2021 full-data update
improved the canonical \(\tau\to\mu\gamma\) value to \(4.2\times10^{-8}\).  The
PKA pass found no Belle II measurement superseding Belle for this channel; the
sidecar records only a Belle II Physics Book projection of
\(<5\times10^{-9}\) with \(50\,{\rm ab}^{-1}\), not a current bound.

\subsection*{Constraint validity / model dependence}
Experimentally this is a clean null search for charged-lepton flavor violation,
with negligible Standard Model rates.  Its RS interpretation is model-dependent:
the bound constrains a dipole coefficient or lepton-flavor spurion only after a
choice of lepton localization, flavor symmetry, Yukawa normalization, and KK
mass convention.  The catalog should classify it as robust experimentally but
lepton-extension-only and dipole-model-dependent for this repo.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog grep over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(\tau\to\mu\gamma\) implementation.  The adjacent
code surface is only \(\mu\to e\gamma\): \texttt{flavorConstraints/muToEGamma.py}:1
documents that process, lines 16--18 fix the \((1,2)\) element, line 75 defines
\texttt{check\_mu\_to\_e\_gamma}, and \texttt{scanParams/scan.py}:523--524 calls
that checker in scans.  Those lines are reusable design evidence, not L007
coverage.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A future implementation can reuse the existing LFV dipole
pattern, but it must generalize the flavor indices and rate normalization from
\(\mu\to e\gamma\) to tau decays, add a tau-sector branching-ratio limit, and
decide whether the same RS lepton-spurion assumptions apply.  No new hadronic
matrix elements, lattice inputs, or QCD running are needed.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2025\_TauMuGamma}, \texttt{Belle2021\_TauLGamma},
\texttt{BaBar2010\_TauLGamma}, \texttt{BelleIIPhysicsBook2019\_TauLFV},
\texttt{CFW2008\_RSWarpedFlavor}, and
\texttt{PerezRandall2008\_WarpedNeutrinos}.
