% Flavor catalog per-process draft.
% process_id: L008
% family: charged_lepton
% owner_agent_id: PKA-L008
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: L008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L008: \texorpdfstring{\(\tau\to e\gamma\)}{tau -> e gamma} Dipole LFV}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(\tau^-\to e^-\gamma)\).
This entry covers the charged-lepton-flavor-violating radiative tau decay and
its use as a tau-sector dipole probe of the tau-electron transition.  It is
the electron-channel companion to L007 \(\tau\to\mu\gamma\) and complements
the much tighter L001 \(\mu\to e\gamma\) constraint.

\subsection*{PDG-or-equivalent value}
The current PDG/equivalent value is
\texttt{L008.yaml:pdg\_or\_equivalent.primary\_current\_limit},
\[
  \mathcal{B}(\tau^-\to e^-\gamma) < 3.3\times10^{-8}
  \quad (90\%\ {\rm C.L.}),
\]
from the PDGLive \(S035.32\) tau decay-mode summary, locally snapshotted at
\texttt{flavor\_catalog/references/L008/pdg2025\_tau\_e\_gamma\_pdglive.txt}.
The primary experiment behind this value is the BaBar full-data search using
\((963\pm7)\times10^6\) tau decays
(\texttt{L008.yaml:pdg\_or\_equivalent.primary\_experiment}), which quotes
\(\mathcal{B}(\tau\to e\gamma)<3.3\times10^{-8}\) at \(90\%\) C.L.  Belle's
full-data 2021 update used \(988\,{\rm fb}^{-1}\) and obtained
\(\mathcal{B}(\tau^\pm\to e^\pm\gamma)\le5.6\times10^{-8}\)
(\texttt{L008.yaml:pdg\_or\_equivalent.recent\_belle\_cross\_check}); it is an
important cross-check but not the strongest electron-mode limit.  The Belle II
Physics Book records a \(50\,{\rm ab}^{-1}\) prospect of
\(1.2\times10^{-8}\) for this channel
(\texttt{L008.yaml:pdg\_or\_equivalent.belle\_ii\_projection}), not a current
bound.

\subsection*{Relevance to RS / anarchic flavor}
In warped lepton-flavor extensions, this mode constrains brane-localized or
loop-induced charged-lepton dipoles with a \(\tau e\) flavor spurion.  It is
not a constraint on the current quark \(\Delta F=2\) scan, but it is a useful
catalog entry for any future charged-lepton implementation because alignment
that suppresses \(\mu\to e\gamma\) need not suppress the tau-to-electron
transition in the same way.  The Perez--Randall warped-neutrino source gives
the lepton-MFV/GIM-like assumptions under which charged-lepton flavor
violation is controlled.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 RS flavor baseline, the main experimental
development is the BaBar 2010 full-data result, which remains the canonical
PDG value for \(\tau\to e\gamma\)
(\texttt{L008.yaml:pdg\_or\_equivalent.primary\_experiment};
\texttt{L008.yaml:pdg\_or\_equivalent.rs\_context}).  Belle later repeated the
search with its full \(988\,{\rm fb}^{-1}\) data set and found no significant
excess, setting the weaker electron-mode limit \(5.6\times10^{-8}\) at
\(90\%\) C.L.
(\texttt{L008.yaml:pdg\_or\_equivalent.recent\_belle\_cross\_check}).  The PKA
pass found no Belle II measurement superseding the BaBar/PDG bound; the
sidecar records only the \(50\,{\rm ab}^{-1}\),
\(1.2\times10^{-8}\) Belle II prospect
(\texttt{L008.yaml:pdg\_or\_equivalent.belle\_ii\_projection}).

\subsection*{Constraint validity / model dependence}
Experimentally this is a clean null search for charged-lepton flavor
violation, with a negligible Standard Model rate.  Its RS interpretation is
model-dependent: the bound constrains a dipole coefficient only after choosing
the lepton localization, flavor symmetry, Yukawa normalization, and KK-mass
convention.  The catalog should therefore classify it as robust
experimentally, but lepton-extension-only and dipole-model-dependent for this
repo.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog grep over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(\tau\to e\gamma\)
implementation.  The adjacent code surface is only \(\mu\to e\gamma\):
\texttt{flavorConstraints/muToEGamma.py}:1 documents that process,
\texttt{flavorConstraints/muToEGamma.py}:75 defines
\texttt{check\_mu\_to\_e\_gamma}, and \texttt{scanParams/scan.py}:523 and
\texttt{scanParams/scan.py}:524 call that checker in scans.  Those lines are
reusable design evidence, not L008 coverage.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A future implementation can reuse the existing LFV dipole
pattern, but it must generalize the flavor indices and rate normalization from
\(\mu\to e\gamma\) to tau decays, add a tau-sector branching-ratio limit, and
decide whether the same RS lepton-spurion assumptions apply.  No new hadronic
matrix elements, lattice inputs, or QCD running are needed.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2025\_TauEGamma}, \texttt{BaBar2010\_TauLGamma},
\texttt{Belle2021\_TauLGamma}, \texttt{BelleIIPhysicsBook2019\_TauLFV},
\texttt{CFW2008\_RSWarpedFlavor}, and
\texttt{PerezRandall2008\_WarpedNeutrinos}.
