% Flavor catalog process L009
% Canonical metadata sidecar: L009.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L009: \texorpdfstring{\(\tau^- \to \mu^-\mu^+\mu^-\)}{tau -> 3 mu} LFV}

\subsection*{Process}
The process is the charged-lepton-flavor-violating four-lepton decay
\(\tau^- \to \mu^-\mu^+\mu^-\), including the charge-conjugate tau-plus mode
where experiments quote combined limits.  This entry belongs to the
\texttt{charged\_lepton} family and is the contact-operator counterpart to
the tau dipole searches.

\subsection*{PDG / equivalent value(s)}
The current PDG tau listing gives
\[
  \mathcal{B}(\tau^- \to \mu^-\mu^+\mu^-) < 1.9\times 10^{-8}
  \quad (90\%~{\rm CL}),
\]
with the PDG-selected entry attributed to the Belle II ADACHI 24R result
using \(424~{\rm fb}^{-1}\) of \(e^+e^-\) data.  The local PDG extract is
\texttt{flavor\_catalog/references/L009/pdg\_2025\_tau\_listing.txt}.
The Belle II primary paper reports the same \(1.9\times 10^{-8}\) 90\% CL
limit.  A newer LHCb Run 2 preprint, not yet part of that PDG listing, also
sets \(1.9\,(2.3)\times 10^{-8}\) at 90\% (95\%) CL with \(5.4~{\rm fb}^{-1}\)
of \(13~{\rm TeV}\) \(pp\) data.  Older benchmark limits are Belle 2010
\(<2.1\times 10^{-8}\), BaBar 2010 \(<3.3\times 10^{-8}\), and LHCb 2015
\(<4.6\times 10^{-8}\), all at 90\% CL.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This mode tests lepton-sector flavor violation that need not be dipole
dominated.  In warped or composite-flavor extensions, flavor-nonuniversal
lepton profiles, KK gauge exchange, flavor-changing \(Z\) couplings, or
scalar exchange can generate effective \(\tau\mu\mu\mu\) operators.  The
observable is therefore complementary to \(\tau\to\mu\gamma\) and
\(\mu\to e\gamma\): dipoles can feed the three-muon final state through an
off-shell photon, but the four-lepton final state is also directly sensitive
to contact LFV.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 RS-flavor baseline, the experimental
frontier moved from B-factory-era \(10^{-7}\)-scale expectations into stable
\(10^{-8}\)-scale limits.  Belle and BaBar published full three-lepton tau
searches in 2010, Belle reaching \(2.1\times 10^{-8}\) for this channel and
BaBar reaching \(3.3\times 10^{-8}\).  LHCb then demonstrated a hadron-collider
tau-to-three-muons program, setting \(4.6\times 10^{-8}\) with Run 1 data and,
in 2026, \(1.9\times 10^{-8}\) with Run 2.  Belle II now supplies the PDG
benchmark, \(1.9\times 10^{-8}\), with an analysis explicitly optimized for
inclusive tau reconstruction and multivariate background rejection.

\subsection*{Constraint validity and model dependence}
Experimentally this is a clean upper limit on a forbidden charged-LFV decay.
As a constraint on the current quark-scan code it is lepton-extension-only:
the present quark Delta F=2 pipeline has no direct tau-lepton matching.  As a
future RS constraint, the translation is model dependent because a dipole-only
assumption, a contact-operator assumption, and a full lepton-sector EFT can
give different correlations with \(\tau\to\mu\gamma\), \(\mu\to e\gamma\), and
\(\mu\to 3e\).

\subsection*{Code coverage in this repo}
Code coverage is \textbf{NO}.  Targeted greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no implementation of
\(\tau\to3\mu\), tau four-lepton LFV, or contact LFV.  The adjacent LFV code is
only \(\mu\to e\gamma\): \texttt{flavorConstraints/muToEGamma.py:1},
\texttt{flavorConstraints/muToEGamma.py:75}, and \texttt{scanParams/scan.py:524}.
The modern phenomenology surface is neutral-meson mixing only, see
\texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{MEDIUM}.  A first implementation needs a new four-lepton LFV observable
and a convention for lepton-flavor Wilson coefficients or RS matching.  It
does not require lattice inputs or hadronic long-distance treatment, but a
production-grade implementation should decide whether to include dipole/contact
interference and correlations with the existing \(\mu\to e\gamma\) lane.

\subsection*{Key references}
Process-local raw keys: \texttt{PDG2025\_Tau3Mu},
\texttt{BelleII2024\_Tau3Mu}, \texttt{LHCb2026\_Tau3Mu},
\texttt{LHCb2015\_Tau3Mu}, \texttt{Belle2010\_Tau3Leptons},
\texttt{BaBar2010\_Tau3Leptons}, and \texttt{CFW2008\_RSWarpedFlavor}.
