% Flavor catalog process L010
% Canonical metadata sidecar: L010.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L010: \texorpdfstring{\(\tau^- \to e^-e^+e^-\)}{tau -> 3e} LFV}

\subsection*{Process}
\textbf{Standard notation:}
\(\mathcal{B}(\tau^- \to e^-e^+e^-)\).
This entry covers the charged-lepton-flavor-violating four-lepton decay
\(\tau^- \to e^-e^+e^-\), including charge-conjugate modes when experiments
quote combined limits.  It is the electron-flavor counterpart of L009
\(\tau\to3\mu\) in the \texttt{charged\_lepton} family.

\subsection*{PDG-or-equivalent value}
The current PDG live tau datablock S035R58 gives
\[
  \mathcal{B}(\tau^- \to e^-e^+e^-) < 2.7\times 10^{-8}
  \quad (90\%~{\rm CL}).
\]
PDG attributes the selected limit to the Belle 2010 analysis by Hayasaka
et al., based on \(782~{\rm fb}^{-1}\) of \(e^+e^-\) data at
\(\sqrt{s}=10.6~{\rm GeV}\)
(\texttt{L010.yaml:pdg\_or\_equivalent.primary\_current\_limit}).  The local
PDG snapshot is
\texttt{flavor\_catalog/references/L010/pdg2025\_tau3e\_pdglive\_s035r58.txt}.
The Belle primary paper reports the same \(2.7\times10^{-8}\) limit
(\texttt{L010.yaml:pdg\_or\_equivalent.primary\_experiment}).  The BaBar 2010
analysis provides the principal independent cross-check,
\(\mathcal{B}<2.9\times10^{-8}\) at \(90\%\) CL with \(468~{\rm fb}^{-1}\)
(\texttt{L010.yaml:pdg\_or\_equivalent.supporting\_experiment}).

\subsection*{Relevance to RS / anarchic flavor}
This mode tests lepton-sector flavor violation that is not forced to be
dipole dominated.  Warped lepton extensions can generate
\(\tau eee\) through flavor-nonuniversal lepton profiles, KK neutral-gauge
exchange, flavor-changing \(Z\) couplings, or scalar exchange.  It is therefore
complementary to \(\tau\to e\gamma\) and \(\mu\to e\gamma\): an off-shell
photon can contribute, but contact four-lepton operators can be the leading
effect in models with tree-level lepton-current misalignment.

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954 RS-flavor baseline, the direct experimental
bound became a B-factory \(10^{-8}\)-level constraint in 2010
(\texttt{L010.yaml:pdg\_or\_equivalent.rs\_context};
\texttt{L010.yaml:pdg\_or\_equivalent.primary\_experiment}).  Belle set the
current PDG-selected limit \(2.7\times10^{-8}\), and BaBar reached the
comparable \(2.9\times10^{-8}\) limit
(\texttt{L010.yaml:pdg\_or\_equivalent.primary\_current\_limit};
\texttt{L010.yaml:pdg\_or\_equivalent.supporting\_experiment}).  No newer LHCb
electron-mode value is used here: the snapshotted LHCb source is for the
all-muon companion mode only
(\texttt{L010.yaml:pdg\_or\_equivalent.lhcb\_context}).  For prospects, the
Belle II Physics Book quotes \(50~{\rm ab}^{-1}\) sensitivity at the
\(\mathcal{O}(10^{-9})\)--\(\mathcal{O}(10^{-10})\) level for favorable
low-background tau LFV modes
(\texttt{L010.yaml:pdg\_or\_equivalent.prospects}).

\subsection*{Constraint validity / model dependence}
Experimentally this is a clean upper limit on a forbidden charged-LFV decay.
Its interpretation in the present quark-scan repository is lepton-extension
only: there is no tau-sector matching or four-lepton LFV observable in the
current scan.  As a future RS constraint it is model dependent because
dipole-only, contact-operator, and full lepton-EFT assumptions give different
correlations with \(\tau\to e\gamma\), \(\tau\to 3\mu\), \(\mu\to e\gamma\),
and \(\mu\to 3e\).

\subsection*{Code coverage in this repo}
\textbf{NO.}  Targeted greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no implementation of
\(\tau\to3e\), tau four-lepton LFV, or charged-lepton contact LFV.  The
adjacent implemented LFV surface is only \(\mu\to e\gamma\):
\texttt{flavorConstraints/muToEGamma.py:75} and
\texttt{scanParams/scan.py:524}.  The modern phenomenology registry is limited
to neutral-meson systems at \texttt{quarkConstraints/modern/phenomenology.py:23}.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A first implementation needs a new four-lepton LFV observable
and a convention for lepton-flavor Wilson coefficients or RS matching.  It
does not require lattice inputs or hadronic long-distance calculations, but a
production implementation should specify dipole/contact interference and
correlations with the existing \(\mu\to e\gamma\) lane.

\subsection*{Key references}
Process-local raw keys: \texttt{PDG2025\_Tau3E},
\texttt{Belle2010\_Tau3Leptons}, \texttt{BaBar2010\_Tau3Leptons},
\texttt{BelleIIPhysicsBook2019\_TauLFV},
\texttt{LHCb2026\_Tau3MuContext},
\texttt{AgasheBlechmanPetriello2006\_RSLFV}, and
\texttt{CFW2008\_RSWarpedFlavor}.
