% Flavor catalog per-process draft.
% process_id: L023
% family: charged_lepton
% owner_agent_id: PKA-L023
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: L023.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{L023: Neutrino Trident Production}

\subsection*{Process}
\textbf{Standard notation:} \(\nu_\mu N\to\nu_\mu N\mu^+\mu^-\).
This charged-lepton-sector entry covers muon-neutrino trident production on a
nuclear target.  It is flavor-sensitive but not charged-lepton-flavor
violation: the useful handle is the muon-neutrino/muon current, usually phrased
as a contact interaction or a gauged \(L_\mu-L_\tau\) mediator.

\subsection*{PDG / equivalent value(s)}
There is no HFLAV-style average.  The current measured inputs are the historical
experiment ratios to the Standard Model prediction recorded in
\texttt{L023.yaml:pdg\_or\_equivalent.measured\_observables}:
\[
  \sigma_{\rm CHARM-II}/\sigma_{\rm SM}=1.58\pm0.64,\qquad
  \sigma_{\rm CCFR}/\sigma_{\rm SM}=0.82\pm0.28,\qquad
  \sigma_{\rm NuTeV}/\sigma_{\rm SM}=0.72^{+1.73}_{-0.72}.
\]
The CCFR value is the strongest practical bound; the local CCFR snapshot also
records the primary event-count basis, \(37.0\pm12.4\) corrected trident events
against \(45.3\pm2.3\) Standard Model events.  CHARM-II is the CERN-SPS
observation input, and NuTeV remains a preliminary/weak observation input.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Trident production constrains second-generation lepton currents rather than the
quark \(\Delta F=2\) system.  In an RS lepton extension, KK electroweak bosons,
brane kinetic mixing, or a light \(L_\mu-L_\tau\)-like gauge state can shift the
effective \((\bar\nu_\mu\gamma^\alpha P_L\nu_\mu)(\bar\mu\gamma_\alpha\mu)\)
and axial analogues.  The constraint is therefore a distinct muon contact/gauge
constraint, complementary to dipole LFV such as \(\mu\to e\gamma\).

\subsection*{Post-2008 developments}
Relative to the arXiv:0804.1954-era RS flavor baseline, the important updates
are reinterpretations and future-experiment studies.  Altmannshofer--Gori--
Pospelov--Yavin (2014) made the CCFR measurement a standard \(L_\mu-L_\tau\)
constraint, including the \(0.82\pm0.28\) ratio and the familiar 95\% CL
exclusion contours.  Belle-II studies then connected the same gauge-current
parameter space to \(e^+e^-\to\gamma+\) missing energy at
\(\sqrt{s}=10.58\) GeV and an intended \(50\,{\rm ab}^{-1}\) data set, but this
is auxiliary collider reach rather than a trident measurement.  The DUNE study
quotes the historical CHARM-II/CCFR/NuTeV ratios and projects a DUNE near
detector trident measurement: its abstract gives about 25\% accuracy after
roughly three years in each beam mode, while the body uses a 40\% baseline and
a 25\% improved contour.

\subsection*{Constraint validity and model dependence}
The experimental observable is cleanly electroweak, but the bound is not a
single universal number: it depends on the target material, neutrino spectrum,
selection cuts, nuclear form factors, and the assumed mediator mass relative to
the momentum transfer.  CCFR is robust as a measured rate ratio; translating it
to a new RS mediator requires a dedicated trident cross-section calculation and
cannot be borrowed from the meson-mixing or dipole backends.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no trident, CCFR, NuTeV, CHARM-II, DUNE, or
\(L_\mu-L_\tau\) implementation.  The only ``CHARM'' hits are QCD charm-mass
threshold constants, not this process.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint would need a new lepton-current
operator convention, mediator matching, nuclear/target treatment, neutrino-flux
integration, and an experiment-specific rate or likelihood.  This is a new mode
calculation, not a parameter update to the existing \(\Delta F=2\) or
\(\mu\to e\gamma\) paths.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{CCFR1991TridentsWZ}, \texttt{CHARMII1990FirstObservation},
\texttt{NuTeV1998Trident}, \texttt{Altmannshofer2014TridentProbe},
\texttt{Altmannshofer2019DUNETridents},
\texttt{KanetaShimomura2017BelleIITrident}, and
\texttt{CsakiFalkowskiWeiler2008Flavor}.
