\documentclass[11pt]{article}
\usepackage[margin=0.75in]{geometry}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{parskip}

\hypersetup{colorlinks=true, linkcolor=blue!60!black, urlcolor=blue!60!black}

\setlength{\parskip}{2.5pt plus 0.5pt}
\setlength{\parindent}{0pt}
\pagestyle{empty}

\begin{document}

{\centering\Large\bfseries A Verification Pipeline for the 5D Flavor
Constraint Catalog\par}
{\centering\small 5D-Neutrino-Mixing catalog \texttt{v0.4} (2026-05-17)\par}
\vspace{4pt}

\textbf{What the catalog is.}
A structured inventory of \textbf{102 flavor-physics constraints} on warped
extra-dimensional (RS) parameter space: 80 low-energy entries (kaon, charm,
beauty, top/Higgs/EW, charged-lepton LFV, EDM/neutrino), 14 direct-collider
RS resonance entries (KK-gluon, KK gauge, KK-graviton, custodial top
partners, VLQ, EW-precision tail), and 8 deferred-scope re-promotions.
Each entry records the measured experimental value or limit with year,
uncertainty, source URL, access date, and \texttt{sha256} of a tracked
local text snapshot. Tags \verb|v0|, \verb|v0.1|, \verb|v0.2|, \verb|v0.3|,
\verb|v0.4| pin reproducible states.

\textbf{How processes were found.}
Five independent mechanisms, layered.
(i)~An overcomplete 128-entry seed list assembled from PDG, HFLAV/FLAG, and
the core RS-flavor literature (Agashe--Contino--Pomarol,
Csaki--Falkowski--Weiler, Perez--Randall).
(ii)~10 PI-seed processes (Wave-1, physics judgment).
(iii)~Four non-overlapping Discovery Agent rounds (DA-1..DA-4), each
surveying a distinct slice of the literature against the running inventory.
(iv)~An \emph{independent external reconciliation}: GPT Deep Research was
handed the v0.1 catalog and the broader literature and surfaced 5 entries
DA-4 had ambiguously closed (Wave-7: T003, T004, T008, T012, B012).
(v)~Scope extensions: Wave-8 promoted 8 SECONDARY entries from the
DA-deferred tail; Wave-9 opened a new \texttt{collider\_rs} family of 14
PRIMARY entries under explicit PI directive.
The convergence rule (two consecutive DA rounds finding $\le 1$ entry each)
was met; 43 remaining plan rows carry \texttt{DEFERRED-SCOPE} tags with
named promotion triggers---no silent drops.

\textbf{How each entry is verified.}
Every numerical claim survives a five-stage chain before approval.
\textbf{(1)~Process Knowledge Agent} retrieves the canonical PDG / HFLAV /
collaboration value and writes a local text snapshot with \texttt{sha256}.
\textbf{(2)~Writer Agent} polishes prose and structured metadata.
\textbf{(3)~Checker Agent}---in an \emph{independent} session, never the WA
on the same batch---runs an 8-item checklist: every numerical claim traces
to a structured \texttt{pdg\_or\_equivalent} block with year, uncertainty,
URL, access date, \texttt{sha256}; every reference key resolves to a
manifest entry; \texttt{status\_history} transitions legal; in-code coverage
claims \texttt{grep}-match cited evidence; \LaTeX{} hygiene clean.
\textbf{(4)~Fact-Check Agent}, also independent and equipped with WebFetch,
\emph{re-fetches every cited URL}, verifies authors/title/year against the
manifest, and verifies the specific numerical value appears in both the
fetched page and the local snapshot.
\textbf{(5)~Opus sign-off} reviews the chain and emits APPROVE /
RETURN-TO-WA / ESCALATE-TO-PI, with a per-round verdict index committed to
git. Writer/checker separation is non-negotiable; in the companion quark-scan
paper, two BLOCKER-class physics errors were caught only because the CA was
genuinely independent.

\textbf{Two concrete catches.}
\emph{T020 ($h\to e\mu$).} The catalog recorded
$\mathcal{B}(h\to e\mu) < 6.1\times 10^{-5}$. The fact-check WebFetch hit
the live \href{https://arxiv.org/abs/1909.10235}{ATLAS source} and saw
$<6.2\times 10^{-5}$ observed ($<5.9\times 10^{-5}$ expected). A
one-digit slip, fixed and re-fact-checked. It is the \textbf{only}
numerical mismatch caught across all 102 entries---exactly the class of
error single-agent self-review cannot find.
\emph{K020 ($K^+\to\pi^+ e^\pm\mu^\mp$).} The Checker Agent flagged that a
measured upper limit ($<2.1\times 10^{-11}$ at 90\% CL, Sher / BNL E865)
appeared in prose but was missing from the structured
\texttt{pdg\_or\_equivalent.values} block. The Writer promoted it; the
Checker re-verified on cycle-2. Without the writer/checker split, the
number would have been citable but not structured-provenanced.

\textbf{What you get.}
\textbf{102 entries}: 94 PRIMARY (80 flavor + 14 collider RS) + 8
SECONDARY. \textbf{5 Opus sign-off rounds, 102/102 APPROVE,
0 RETURN-TO-WA, 0 ESCALATE-TO-PI.} \textbf{Fact-check: 100 VERIFIED /
2 PARTIAL (both metadata-only, documented) / 0 MISMATCH / 0 FAILED.}
Three arbitrations (L001; B001+B003; B021+B023) codified a CHK-1
carve-out separating measured observables from theory-normalization
scales and dataset descriptors; downstream batches applied it uniformly
without re-litigation. Every source snapshot is tracked in git with
\texttt{sha256}; \verb|git checkout <tag>| rebuilds the catalog from
scratch with full provenance.

{\sloppy\textbf{Pointers.} Playbook
\texttt{flavor\_catalog/AGENTIC\_WORKFLOW.md};
catalog PDF (v0.4, 179 pp.) \texttt{flavor\_catalog/catalog\_master.pdf};
per-round verdicts \texttt{signoff/round\_NNN\_index.md};
fact-check tables \texttt{audits/factcheck\_*.md}.\par}

\end{document}
