% Flavor catalog per-process draft.
% process_id: B001
% family: beauty
% owner_agent_id: PKA-B001
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B001.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B001: \(\Delta m_d\) in \(B_d\) mixing}

\subsection*{Process}
\textbf{Standard notation:} \(\Delta m_d\).
This entry covers the mass splitting of the neutral \(B_d\) eigenstates,
equivalently the oscillation frequency in \(B^0_d-\bar B^0_d\) mixing.  It is
the beauty-sector down-type \(\Delta F=2\) magnitude constraint already used by
the quark-scan code.

\subsection*{PDG or equivalent value}
The canonical measured value is the HFLAV/PDG 2025 average recorded in
\texttt{B001.yaml} under \texttt{pdg\_or\_equivalent}, source key
\texttt{hflav\_pdg2025\_bd\_mixing}.  HFLAV gives
\[
  \Delta m_d = 0.5069 \pm 0.0019\ {\rm ps}^{-1},
\]
using time-dependent measurements from ALEPH, DELPHI, L3, OPAL, CDF, D0,
BABAR, Belle, and LHCb.  With the HFLAV assumptions of no CP violation in
mixing and no \(B^0\) width difference, the same snapshot records the companion
world averages \(x_d=0.7697\pm0.0035\) and \(\chi_d=0.1860\pm0.0011\).  The
local source snapshot is
\texttt{flavor\_catalog/references/B001/hflav\_pdg2025\_bd\_mixing.txt},
accessed on 2026-05-16.

\subsection*{Relevance to RS / anarchic flavor}
Anarchic warped models generate tree-level flavor-changing neutral currents
from KK gluon and electroweak exchange after rotating to the quark-mass basis.
\(B_d\) mixing probes the \(b\leftrightarrow d\) down-sector alignment and is a
direct test of the same Wilson-coefficient pipeline used for kaon and \(B_s\)
mixing.  Compared with \(\varepsilon_K\), it is less chirally enhanced but
constrains a different row-column structure of the anarchic profiles.

\subsection*{Post-2008 developments}
The arXiv:0804.1954 RS-flavor baseline, source key
\texttt{cfw\_2008\_rs\_flavor}, highlighted KK-gluon flavor bounds near
\(21\,{\rm TeV}\) in standard RS scenarios and \(33\,{\rm TeV}\) in the
pseudo-Goldstone setup, with boundary kinetic terms and flavor assumptions as
caveats.  Since then, \(\Delta m_d\) has become a precision-average observable.
Belle II has repeated the benchmark measurement with early SuperKEKB data,
reporting
\[
  \Delta m_d = 0.516 \pm 0.008_{\rm stat}\pm0.005_{\rm syst}\ {\rm ps}^{-1}
\]
from \(190\,{\rm fb}^{-1}\), with both numbers recorded under source key
\texttt{belleii\_2023\_bd\_mixing}.  On the theory side, source key
\texttt{flag2024\_b\_mixing} documents the FLAG Review 2024 heavy-quark inputs
relevant for \(B\)-mixing matrix elements and global unitarity-triangle fits;
those inputs are theory normalization data, not the measured observable.

\subsection*{Constraint validity / model dependence}
This is a robust neutral-meson-mixing magnitude constraint.  The experimental
average is precise, but turning it into a new-physics exclusion requires a
policy for the SM contribution and CKM inputs.  The current code uses an
allowed NP budget rather than a full correlated CKM fit, so catalog users
should treat it as a conservative magnitude screen, not as a global-fit
replacement.

\subsection*{Code coverage in this repo}
\textbf{YES-D2-BD.}  The legacy \(\Delta F=2\) backend defines the \(B_d\)
input at \texttt{quarkConstraints/deltaf2.py:225} and notes the hadronic
matrix-element treatment at \texttt{quarkConstraints/deltaf2.py:236}.
The in-code \(B_d\) hadronic and experimental constants are at
\texttt{quarkConstraints/deltaf2.py:631}--\texttt{638}.  The scan dispatches
\texttt{b\_d} through \texttt{evaluate\_bd\_mixing} at
\texttt{quarkConstraints/deltaf2.py:383}--\texttt{391}; the evaluator itself is
\texttt{quarkConstraints/deltaf2.py:903}--\texttt{915}, with the running wrapper
at \texttt{quarkConstraints/deltaf2.py:960}--\texttt{966}.  The modern metadata
layer also carries \(B_d\) as a policy system at
\texttt{quarkConstraints/modern/phenomenology.py:23} and mirrors the input at
\texttt{quarkConstraints/modern/inputs.py:967}--\texttt{976}.

\subsection*{Implementation difficulty}
\textbf{LOW.}  The existing \(\Delta F=2\) SLL/SLR/VLL/VRR/LR machinery and
BMU-style running cover the \(B_d\) mixing magnitude observable.  A future
production refresh would mainly improve provenance, unit conversion, and
likelihood policy rather than adding new operators or RG evolution.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
\texttt{hflav\_pdg2025\_bd\_mixing},
\texttt{belleii\_2023\_bd\_mixing},
\texttt{flag2024\_b\_mixing}, and
\texttt{cfw\_2008\_rs\_flavor}.
