% Flavor catalog per-process draft.
% process_id: B002
% family: beauty
% owner_agent_id: PKA-B002
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B002.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B002: \(S_{\psi K_S}\) and \(\sin 2\beta\)}

\subsection*{Process}
\textbf{Standard notation:} \(S_{\psi K_S}\), equivalently
\(\sin 2\beta\) or \(\sin 2\phi_1\).
This entry covers the mixing-induced CP asymmetry in
\(B_d^0\to J/\psi K_S^0\), conventionally reported as
\(S_{\psi K_S}\simeq \sin 2\beta\).  It is the beauty-sector benchmark CP
phase of the unitarity triangle and is dominated by interference between
\(B_d-\bar B_d\) mixing and the \(b\to c\bar c s\) tree amplitude.

\subsection*{PDG or equivalent value}
The canonical values are the \texttt{pdg\_or\_equivalent} entries in
\texttt{B002.yaml}.  HFLAV Summer 2025
(\texttt{hflav\_triangle\_summer2025\_sin2beta}) gives
the current all-charmonium average
\[
  \sin(2\beta)=\sin(2\phi_1)=0.710\pm0.011,
\]
with a stat-only uncertainty of \(0.010\) and fit CL \(0.34\), accessed on
2026-05-16 in
\texttt{references/B002/hflav\_triangle\_summer2025\_sin2beta.txt}.  The
same HFLAV block gives the direct \(J/\psi K_S\) mode average
\[
  S_{\psi K_S}=0.712\pm0.011.
\]
The corresponding physical CKM-angle solution is
\(\beta=(22.63^{+0.45}_{-0.44})^\circ\), with the trigonometric alternate
solution also stored in the sidecar.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic warped models, tree-level KK-gluon and electroweak exchange can
generate a new complex contribution to \(M_{12}^d\).  \(S_{\psi K_S}\) is
therefore the phase counterpart of the existing \(B_d\) mass-difference
constraint: a scan point can satisfy \(\Delta m_d\) while still shifting
\(\arg(M_{12}^d)\).  This observable is especially useful because the decay
amplitude is CKM-favored and theoretically clean compared with many hadronic
beauty modes.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS-flavor baseline, the central experimental story
is precision rather than discovery.  Belle and BaBar final samples established
the B-factory anchor, and the post-2023 update added two important inputs:
LHCb measured
\[
  S_{\psi K_S}=0.717\pm0.013_{\rm stat}\pm0.008_{\rm syst}
\]
using \(6\,{\rm fb}^{-1}\)
(\texttt{lhcb\_2024\_spsiks}), and Belle II measured
\[
  S=0.724\pm0.035_{\rm stat}\pm0.009_{\rm syst}
\]
with \(362\,{\rm fb}^{-1}\)
(\texttt{belleii\_2024\_sin2phi1}).  These inputs moved the HFLAV average to
the percent-level regime.  On the theory side, the main development is sharper
accounting of doubly Cabibbo-suppressed penguin pollution; the
\texttt{frings\_nierste\_wiebusch\_2015} snapshot quotes
\(|\Delta\phi_d|\le 0.68^\circ\).

\subsection*{Constraint validity and model dependence}
This is a robust neutral-meson-mixing phase constraint, but a catalog number
is not a standalone exclusion without a CKM convention.  A live implementation
must decide whether the SM \(\beta\) input is fixed from a global fit or fitted
simultaneously, and how to budget the small penguin phase.  New physics in the
decay amplitude would make the usual \(S_{\psi K_S}\simeq \sin 2\beta\)
identification model-dependent, but for RS quark-flavor scans the dominant
target is the new phase in \(B_d\) mixing.

\subsection*{Code coverage in this repo}
\textbf{PARTIAL.}  No implementation named \texttt{S\_psi}, \texttt{J/psi K\_S},
\texttt{sin2beta}, or equivalent was found in the required greps.  However,
\texttt{quarkConstraints/deltaf2.py:225} defines the existing \(B_d\) mixing
input, \texttt{quarkConstraints/deltaf2.py:631} and
\texttt{quarkConstraints/deltaf2.py:638} define its hadronic and
\(\Delta m_d\) inputs, and
\texttt{quarkConstraints/deltaf2.py:903} evaluates \(M_{12}^{d,\rm NP}\).
That evaluator reduces the result to \(\lvert M_{12}^{d,\rm NP}\rvert\) at
\texttt{quarkConstraints/deltaf2.py:910}, so the phase needed for
\(S_{\psi K_S}\) is not exposed.  The shared \(\Delta F=2\) running basis is
documented at \texttt{quarkConstraints/qcd\_running.py:7}.

\subsection*{Implementation difficulty}
\textbf{LOW.}  The existing \(\Delta F=2\) Wilson and hadronic machinery covers the
needed operator basis.  The missing work is to retain the complex \(B_d\)
mixing amplitude, define the SM phase convention and allowed penguin
uncertainty, and add an observable policy for the measured \(S_{\psi K_S}\).

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{hflav\_triangle\_summer2025\_sin2beta},
\texttt{lhcb\_2024\_spsiks},
\texttt{belleii\_2024\_sin2phi1},
\texttt{frings\_nierste\_wiebusch\_2015},
\texttt{faller\_fleischer\_jung\_mannel\_2008}, and
\texttt{csaki\_falkowski\_weiler\_2008}.
