% Flavor catalog per-process draft.
% process_id: B003
% family: beauty
% owner_agent_id: PKA-B003
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B003: \(\Delta m_s\) / \(B_s\) Mixing}

\subsection*{Process}
\textbf{Standard notation:} \(\Delta m_s\).  This entry covers the
\(B_s^0-\bar B_s^0\) mass splitting, equivalently the oscillation frequency
measured in time-dependent flavor-tagged \(B_s\) decays.  It is the magnitude
observable in the \(\Delta B=2\), \(b\leftrightarrow s\) neutral-meson mixing
system.

\subsection*{PDG / equivalent value(s)}
The current canonical equivalent value is the HFLAV recommended
lifetime-and-oscillation average snapshotted as
\texttt{references/B003/hflav\_2024\_dms.txt}:
\[
  \Delta m_s = 17.766\pm0.006~{\rm ps}^{-1}
\]
from CDF, LHCb, and CMS.  The same HFLAV page gives the derived companion
quantities \(x_s=26.94\pm0.10\) and
\(\chi_s=0.499314\pm0.000005\), using
\(1/\Gamma_s=1.516\pm0.006~{\rm ps}\),
\(\Delta\Gamma_s=+0.0781\pm0.0035~{\rm ps}^{-1}\), and no CP violation in
mixing.  The published-only HFLAV/PDG 2025 preparation page, snapshotted as
\texttt{references/B003/hflav\_pdg2025\_dms.txt}, gives the nearly identical
\(\Delta m_s=17.765\pm0.006~{\rm ps}^{-1}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic Randall--Sundrum flavor, tree-level KK-gluon and electroweak
exchange generate \(\Delta B=2\) four-quark operators.  \(B_s\) mixing is the
down-sector \(s-b\) analogue of \(B_d\) mixing and complements the stronger
kaon constraints by testing a different localization and CKM structure.  The
existing code treats \(\Delta m_s\) as a direct bound on the new-physics
contribution to \(M_{12}^s\), with separate weights for current-current and
left-right operators.

\subsection*{Post-2008 developments}
The 2008 RS-flavor baseline in \texttt{cfw\_2008\_rs\_flavor} predates the
precision LHCb \(B_s\) oscillation program.  The key post-2008 experimental
step for this catalog is the LHCb measurement in
\texttt{lhcb\_2021\_deltams\_arxiv}: using \(6~{\rm fb}^{-1}\) of Run-2
\(B_s\to D_s\pi\) data, LHCb finds
\[
  \Delta m_s=17.7683\pm0.0051_{\rm stat}\pm0.0032_{\rm syst}~{\rm ps}^{-1},
\]
and a LHCb-only combination
\[
  \Delta m_s=17.7656\pm0.0057~{\rm ps}^{-1}.
\]
On the theory side, \texttt{flag\_2024\_bmixing} records the FLAG Review 2024
\(N_f=2+1+1\) auxiliary inputs
\[
  f_{B_s}\sqrt{\hat B_{B_s}}=256.1\pm5.7~{\rm MeV},\qquad
  \xi=1.216\pm0.016,
\]
with a warning that correlated decay-constant and mixing inputs should not be
reconstructed from separate averages.

\subsection*{Constraint validity and model dependence}
The experimental oscillation frequency is very clean.  The model-dependent step
is translating it into a new-physics allowance: a conservative catalog can bound
\(|M_{12}^{s,{\rm NP}}|\) directly from the measured splitting, while a sharper
SM-subtracted interpretation depends on CKM inputs and FLAG lattice matrix
elements.  The constraint is therefore a robust \(\Delta F=2\) magnitude test,
but cancellations between SM and new physics or correlated CKM-fit choices
should be made explicit in any live likelihood.

\subsection*{Code coverage in this repo}
\textbf{YES.}  The v1 Delta F=2 input bundle defines the \(B_s\) system at
\texttt{quarkConstraints/deltaf2.py:238} with key \texttt{b\_s} at
\texttt{quarkConstraints/deltaf2.py:239} and down-sector generations
\texttt{(1, 2)} at \texttt{quarkConstraints/deltaf2.py:244}.  The hadronic
constants include the \(B_s\) decay constant at
\texttt{quarkConstraints/deltaf2.py:645} and \(\Delta m_s\) input at
\texttt{quarkConstraints/deltaf2.py:651}.  The budget helper is at
\texttt{quarkConstraints/deltaf2.py:893}; the evaluator is
\texttt{evaluate\_bs\_mixing} at \texttt{quarkConstraints/deltaf2.py:922},
with the QCD-running wrapper at \texttt{quarkConstraints/deltaf2.py:969}.
The modern policy also carries \(B_s\) in
\texttt{quarkConstraints/modern/phenomenology.py:23}, defines the policy entry
at \texttt{quarkConstraints/modern/phenomenology.py:135}, and routes it through
the bridge evaluator at \texttt{quarkConstraints/modern/phenomenology.py:657}
and \texttt{quarkConstraints/modern/phenomenology.py:1346}.  The shared
\(\Delta F=2\) operator basis is documented at
\texttt{quarkConstraints/qcd\_running.py:7}.

\subsection*{Implementation difficulty}
\textbf{LOW.}  The existing \(\Delta F=2\) basis and RG path already cover the
needed VLL, VRR, scalar, and left-right structures for \(B_s\) mixing.  Future
production work is mostly input hygiene: decide the HFLAV/PDG value policy,
refresh FLAG normalization constants, and document whether the live constraint
uses a conservative absolute \(M_{12}^{\rm NP}\) budget or an SM-subtracted one.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
\texttt{hflav\_2024\_dms}, \texttt{hflav\_pdg2025\_dms},
\texttt{lhcb\_2021\_deltams\_arxiv}, \texttt{flag\_2024\_bmixing}, and
\texttt{cfw\_2008\_rs\_flavor}.
