% Flavor catalog per-process draft.
% process_id: B004
% family: beauty
% owner_agent_id: PKA-B004
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B004.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B004: \(\phi_s\) in \(B_s^0\to J/\psi\phi\)}

\subsection*{Process}
\textbf{Standard notation:} \(\phi_s^{c\bar c s}\), often shortened to
\(\phi_s\).  This entry covers the mixing-induced CP phase measured in
time-dependent angular analyses of \(B_s^0\to J/\psi K^+K^-\) near the
\(\phi(1020)\) resonance, conventionally reported as \(B_s^0\to J/\psi\phi\).
Because the final state is vector--vector, the experimental extraction also
separates CP-even and CP-odd angular components.

\subsection*{PDG or equivalent value}
The canonical source is the HFLAV PDG 2025 \(\phi_s\) input table, snapshotted
as \texttt{references/B004/hflav\_pdg2025\_phis\_inputs.txt}.  HFLAV gives the
all-combined average
\[
  \phi_s^{c\bar c s}=-0.041\pm0.016~{\rm rad},
  \qquad
  \Delta\Gamma_s=+0.079\pm0.006~{\rm ps}^{-1}.
\]
For the strict \(B_s^0\to J/\psi K^+K^-\) channel combination, HFLAV gives
\[
  \phi_s^{c\bar c s}=-0.050\pm0.017~{\rm rad},
  \qquad
  \Delta\Gamma_s=+0.077\pm0.006~{\rm ps}^{-1}.
\]
The dominant recent LHCb Run-2 input, snapshotted as
\texttt{references/B004/lhcb\_2024\_jpsikk\_phis\_arxiv.txt}, reports
\[
  \phi_s=-0.039\pm0.022_{\rm stat}\pm0.006_{\rm syst}~{\rm rad}
\]
from \(6~{\rm fb}^{-1}\) and approximately \(349000\) signal decays.  The same
paper quotes the CKM-fit Standard Model expectation
\(-2\beta_s=-0.0368^{+0.0009}_{-0.0006}~{\rm rad}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic warped models, tree-level KK-gluon and electroweak exchange can
generate a complex new contribution to \(B_s-\bar B_s\) mixing.  \(\phi_s\) is
therefore the phase complement to the \(\Delta m_s\) magnitude constraint: a
point can satisfy the mass splitting while still shifting \(\arg M_{12}^s\).
The process is especially clean for RS quark scans because the dominant decay
amplitude is the CKM-favored \(b\to c\bar c s\) transition, while new physics
mainly enters through \(\Delta B=2\) mixing.

\subsection*{Post-2008 developments}
The arXiv:0804.1954 baseline predates the LHCb era and used RS flavor as a
generic \(\Delta F=2\) stress test rather than a precision \(\phi_s\) input.
Since then, Tevatron, ATLAS, CMS, and especially LHCb measurements have turned
\(\phi_s\) from an exploratory new-physics search into a percent-level phase
test.  The 2024 LHCb Run-2 analysis superseded the earlier Run-2 result in the
same channel, added improved flavor tagging and decay-time calibration, and
found no evidence for polarization dependence.  HFLAV's PDG 2025 combination
now reaches \(0.016~{\rm rad}\) precision and is consistent with the small SM
phase.

\subsection*{Constraint validity and model dependence}
This is a robust neutral-meson-mixing phase constraint, but it is not identical
to a pure \(\arg M_{12}^s\) observable without assumptions.  The interpretation
uses a CKM phase convention, assumes no large new physics in the tree-dominated
decay amplitude, and must budget subleading penguin effects.  The vector--vector
final state also requires an angular analysis and experimental correlations
with \(\Delta\Gamma_s\).  For the present catalog, it should be classified as a
robust \(\Delta F=2\) phase observable with small decay-amplitude systematics.

\subsection*{Code coverage in this repo}
\textbf{PARTIAL.}  A focused grep for \texttt{phi\_s}, \texttt{phis},
\texttt{J/psi}, \texttt{Jpsi}, \texttt{psi.*phi}, \texttt{B\_s.*phi}, and
\texttt{beta\_s} found no direct observable implementation in the required
implementation and test directories.  The underlying \(B_s\) mixing lane exists:
\texttt{quarkConstraints/deltaf2.py:239} defines the \texttt{b\_s} input,
\texttt{quarkConstraints/deltaf2.py:651} stores \(\Delta m_s\),
and \texttt{quarkConstraints/deltaf2.py:922} evaluates the \(B_s\) mixing
contribution.  However, \texttt{quarkConstraints/deltaf2.py:929} reduces the
computed complex amplitude to \(\lvert M_{12}^{s,\rm NP}\rvert\), so the phase
needed for \(\phi_s\) is not exposed.  The modern bridge also evaluates only
the magnitude-style \(B_s\) mixing contribution at
\texttt{quarkConstraints/modern/phenomenology.py:657}; the shared
\(\Delta F=2\) operator basis is documented at
\texttt{quarkConstraints/qcd\_running.py:7}.

\subsection*{Implementation difficulty}
\textbf{LOW.}  No new operator basis is required: the existing
SLL/SLR/VLL/VRR/LR \(\Delta F=2\) machinery covers the \(B_s\) mixing
amplitude.  The missing work is to retain the complex \(M_{12}^s\), combine it
with the SM \(-2\beta_s\) convention, and add a likelihood or tolerance policy
including the HFLAV uncertainty and small penguin-systematic allowance.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
\texttt{hflav\_pdg2025\_phis\_inputs},
\texttt{lhcb\_2024\_jpsikk\_phis\_arxiv}, and
\texttt{cfw\_2008\_rs\_flavor}.
