% Flavor catalog per-process template.
% process_id: B005
% family: beauty
% owner_agent_id: PKA-B005
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B005.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B005: \(B_s^0\to\mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B_s^0\to\mu^+\mu^-)\).
This entry covers the time-integrated rare leptonic decay \(B_s^0\to\mu^+\mu^-\),
a helicity-suppressed \(b\to s\ell^+\ell^-\) flavor-changing neutral-current
channel.  It is distinct from the inclusive and exclusive semileptonic
\(b\to s\ell^+\ell^-\) entries because the final state is purely leptonic and
the leading hadronic input is the \(B_s\) decay constant.

\subsection*{PDG / equivalent value(s)}
The current PDG live/API value, accessed on 2026-05-16, is
\[
  \mathcal{B}(B_s^0\to\mu^+\mu^-)_{\rm exp}
  = (3.34\pm0.27)\times10^{-9}.
\]
The local snapshot is
\texttt{flavor\_catalog/references/B005/pdg\_2026\_bsmumu.txt}.  The same
value is quoted in the 2024 Czaja--Misiak SM-status review as the present
weighted experimental average.  That review gives the Standard Model prediction
\[
  \mathcal{B}(B_s^0\to\mu^+\mu^-)_{\rm SM}
  = (3.64\pm0.12)\times10^{-9}.
\]
For input-tracing, the sidecar also records the HFLAV rare-decay page
average \((3.45\pm0.29)\times10^{-9}\), CMS
\((3.83^{+0.38}_{-0.36}\,{}^{+0.19}_{-0.16}\,{}^{+0.14}_{-0.13})\times10^{-9}\),
LHCb \((3.09^{+0.46+0.15}_{-0.43-0.11})\times10^{-9}\), and ATLAS
\((2.8^{+0.8}_{-0.7})\times10^{-9}\) snapshots.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This mode probes the short-distance \(b\to s\mu^+\mu^-\) Hamiltonian in a clean
single-number observable.  In anarchic RS scenarios, flavor-changing neutral
gauge couplings, KK electroweak exchange, Higgs/radion scalar exchange, or
leptoquark-like completions can shift axial-vector, scalar, and pseudoscalar
Wilson coefficients.  The scalar and pseudoscalar terms are especially
important because they can remove the Standard Model helicity suppression and
are prominent in large-\(\tan\beta\) supersymmetric or extended-Higgs
interpretations.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS-flavor baseline, this channel changed from an
upper-limit target into a precision observable.  LHCb and CMS first established
the decay, and the present average combines modern LHCb, CMS, and ATLAS inputs.
CMS now reports the most precise single-experiment branching-fraction
measurement, while LHCb provides a simultaneous branching-fraction and
effective-lifetime analysis.  Theory has also improved: modern SM predictions
include precise lattice \(f_{B_s}\), CKM inputs, electroweak and QCD
corrections, and the time-integration correction associated with the
\(B_s\) width difference.

\subsection*{Constraint validity and model dependence}
This is a robust short-distance rare-decay constraint, but it is not covered by
the repo's neutral-meson-mixing machinery.  The SM comparison is clean relative
to angular \(b\to s\ell\ell\) observables, yet it still depends on the
definition of the time-integrated branching fraction, \(f_{B_s}\), CKM inputs,
and the treatment of scalar and pseudoscalar operators.  It is directly useful
for models that predict \(C_{10}^{(\prime)}\), \(C_S^{(\prime)}\), or
\(C_P^{(\prime)}\), including scalar leptoquarks, \(Z'\) models, and
tan-beta-enhanced Higgs sectors.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps and a focused search for
\texttt{B\_s.*mu}, \texttt{mumu}, \texttt{C10}, scalar/pseudoscalar rare-decay
terms, and \(b\to s\mu\mu\) found no live \(B_s^0\to\mu^+\mu^-\) implementation
in \texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, or \texttt{tests/}.  The nearest
related code is \(B_s\) mixing, e.g. \texttt{quarkConstraints/deltaf2.py:239}
and \texttt{quarkConstraints/deltaf2.py:922}, which is a \(\Delta F=2\)
observable rather than this \(\Delta B=1\) decay.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A catalog-to-code implementation needs a new \(\Delta B=1\)
leptonic rare-decay observable, Wilson conventions for
\(C_{10}^{(\prime)}, C_S^{(\prime)}, C_P^{(\prime)}\), and a branching-ratio
formula with the \(B_s\) lifetime and width-difference convention.  It does not
need an angular likelihood or exclusive form factors, but a production-grade
RS matching path would need carefully documented scalar and electroweak
operator normalization.

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{PDG2026:BsMuMu}, \texttt{HFLAV2023:BsMuMu},
\texttt{CMS2023:BsMuMu}, \texttt{LHCb2022:BsMuMu},
\texttt{ATLAS2019:BsMuMu}, \texttt{CzajaMisiak2024:BsMuMuSM}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
