% Flavor catalog per-process template.
% process_id: B006
% family: beauty
% owner_agent_id: PKA-B006
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B006.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B006: \(B^0\to\mu^+\mu^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B^0\to\mu^+\mu^-)\).
This entry covers the rare leptonic \(b\to d\mu^+\mu^-\) flavor-changing
neutral-current decay of the neutral \(B_d\) meson.  It is the \(b\to d\)
analogue of \(B_s^0\to\mu^+\mu^-\), but is CKM-suppressed and currently enters
the catalog as an upper limit rather than an observed branching fraction.

\subsection*{PDG / equivalent value(s)}
The current PDG live/API listing \texttt{S042.7}, accessed on 2026-05-16, gives
\[
  \mathcal{B}(B^0\to\mu^+\mu^-) < 1.5\times10^{-10}\quad(90\%\ {\rm CL}).
\]
The PDG input used for this limit is the CMS Run 2 result, which also reports
\(<1.9\times10^{-10}\) at \(95\%\) CL.  The local canonical snapshot is
\texttt{flavor\_catalog/references/B006/pdg\_2026\_bdmumu.txt}, with source key
\texttt{PDG2026:BdMuMu}.  As an equivalent HFLAV rare-decay ratio constraint,
the April 2023 table gives
\[
  \mathcal{B}(B^0\to\mu^+\mu^-)/\mathcal{B}(B_s^0\to\mu^+\mu^-) < 8.1\times10^{-2}
  \quad(90\%\ {\rm CL}),
\]
using the LHCb input.  For scale, the reduced-uncertainty Standard Model
prediction recorded in \texttt{BobethEtAl2013:BdMuMuSM} is
\[
  \mathcal{B}(B_d\to\mu^+\mu^-)_{\rm SM}=(1.06\pm0.09)\times10^{-10}.
\]

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This mode is a clean \(\Delta B=1\) leptonic rare decay.  In warped/anarchic
flavor models, flavor-changing \(Z\), KK electroweak gauge, Higgs, radion, or
other scalar exchanges can contribute to axial-vector, scalar, and pseudoscalar
\(b\to d\mu\mu\) Wilson coefficients.  Scalar and pseudoscalar terms are
especially diagnostic because they can compete with the helicity-suppressed
Standard Model amplitude.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS-flavor baseline, this channel moved from
pre-LHC upper limits to a mature LHC rare-decay search.  ATLAS combined Run 1
and 2015--2016 data to set \(2.1\times10^{-10}\) at \(95\%\) CL.  LHCb later
set \(2.6\times10^{-10}\) at \(95\%\) CL and constrained the \(B^0/B_s^0\)
dimuon branching-ratio ratio.  CMS Run 2, with \(140\,{\rm fb}^{-1}\) at
\(\sqrt{s}=13\) TeV, now supplies the PDG canonical \(90\%\)-CL limit.  On the
theory side, \(B_{s,d}\to\ell^+\ell^-\) Standard Model predictions now include
reduced perturbative electroweak and QCD uncertainties.

\subsection*{Constraint validity and model dependence}
The experimental object is robust as an upper limit on a short-distance
branching fraction, but the catalog interpretation is model-dependent.  A live
constraint needs a consistent \(\Delta B=1\) Hamiltonian, CKM convention,
normalization to \(f_{B_d}\), and treatment of scalar/pseudoscalar operators.
Unlike angular \(b\to d\ell\ell\) modes it does not require a multi-bin
form-factor likelihood.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(B^0\to\mu^+\mu^-\) or
\(b\to d\mu\mu\) observable implementation.  Nearby hits such as
\texttt{quarkConstraints/deltaf2.py:225} and
\texttt{quarkConstraints/deltaf2.py:903} are \(B_d\) \(\Delta F=2\) mixing
entries, not this rare leptonic \(\Delta B=1\) decay.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  This requires a new \(\Delta B=1\) leptonic rare-decay
observable and Wilson normalization for \(C_{10}^{(\prime)}\),
\(C_S^{(\prime)}\), and \(C_P^{(\prime)}\).  It should not need new lattice
matrix-element machinery beyond decay-constant inputs, RG for a full angular
analysis, or exclusive semileptonic form factors.

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{PDG2026:BdMuMu}, \texttt{HFLAV2023:BdOverBsMuMu},
\texttt{CMS2023:BdMuMu}, \texttt{LHCb2022:BdMuMu},
\texttt{ATLAS2019:BdMuMu}, \texttt{BobethEtAl2013:BdMuMuSM}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
