% Flavor catalog per-process draft.
% process_id: B009
% family: beauty
% owner_agent_id: PKA-B009
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B009.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B009: \(B^+\to\tau^+\nu_\tau\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B^+\to\tau^+\nu_\tau)\).
This entry covers the purely leptonic charged-\(B\) branching fraction, including
the Belle, Belle II, BaBar, PDG, and HFLAV averages collected in the sidecar.
It is a beauty-family charged-current observable rather than a neutral-meson
mixing constraint.

\subsection*{PDG / equivalent value(s)}
The canonical sidecar value is the HFLAV End-of-December-2025 average
\[
  \mathcal{B}(B^+\to\tau^+\nu_\tau) = (1.12 \pm 0.19)\times 10^{-4},
\]
from the local snapshot
\texttt{flavor\_catalog/references/B009/hflav\_dec2025\_btaunu.txt}.
The PDG 2025 REST entry gives the compatible average
\((1.09^{+0.25}_{-0.24})\times 10^{-4}\), with the PDG uncertainty scaled by
the factor recorded in \texttt{pdg2025\_btaunu\_api.txt}.  HFLAV lists the
post-2008 inputs as Belle hadronic tag \((0.72^{+0.27}_{-0.25}\pm0.11)\times
10^{-4}\), Belle semileptonic tag \((1.25\pm0.28\pm0.27)\times10^{-4}\),
Belle II hadronic tag \((1.24\pm0.41\pm0.19)\times10^{-4}\), BaBar hadronic
tag \((1.83^{+0.53}_{-0.49}\pm0.24)\times10^{-4}\), and BaBar semileptonic
tag \((1.70\pm0.80\pm0.20)\times10^{-4}\).  For comparison to the
\(|V_{ub}| f_B\) Standard Model prediction, the sidecar records the UTfit
Summer 2024 SM prediction \((0.865\pm0.041)\times10^{-4}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This channel probes \(b\to u\tau\nu\) charged currents.  In the SM it is fixed
by \(f_B |V_{ub}|\), the charged-\(B\) lifetime, and the tau mass; therefore it
is a clean place where a new charged current can interfere with the SM
amplitude.  It is directly relevant to charged-Higgs, \(W'\), and leptoquark
benchmarks.  For warped or anarchic-flavor extensions, it is not part of the
current quark \(\Delta F=2\) lane, but it would test KK charged-gauge-boson or
non-minimal charged-scalar effects in the \(b\)-to-\(u\) current and in the
tau-neutrino current.

\subsection*{Post-2008 developments}
Relative to the Csaki--Falkowski--Weiler 2008 flavor baseline
(\texttt{cfw2008\_arxiv0804\_1954.txt}), the measurement landscape changed
substantially.  BaBar published semileptonic-tag and hadronic-tag results in
2010 and 2013.  Belle superseded earlier evidence with the full-data hadronic
tag result in 2013 and a semileptonic-tag full-sample result in 2015.  Belle II
added a hadronic-FEI measurement in 2025, which HFLAV includes in its latest
average while noting that the red Belle II input is not part of the PDG
average.  On the theory/global-fit side, UTfit now quotes a sub-5-percent SM
prediction for the branching fraction in its Summer 2024 fit table, making the
dominant comparison issue the \(|V_{ub}|\) and global-fit convention rather
than a missing hadronic matrix element.

\subsection*{Constraint validity and model dependence}
The experimental average is straightforward, but the constraint is
model-dependent.  It is robust as a charged-current amplitude test; it is not a
generic RS bound unless the model supplies a calculable \(b\to u\tau\nu\)
matching contribution.  A charged scalar, \(W'\), or leptoquark can interfere
constructively or destructively with the SM, so a one-number exclusion requires
the operator normalization and neutrino-flavor assumptions.  The SM comparison
is global-fit dependent through \(|V_{ub}|\), even though the leptonic decay
constant input itself is now standard.

\subsection*{Code coverage in this repo}
\textbf{NO.}  I reran the required coverage greps over
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The broad plan
greps find the existing neutral \(\Delta F=2\) and \(\mu\to e\gamma\) surfaces,
but no charged-current leptonic-\(B\) observable.  Targeted searches for
\texttt{B\string^+ -> tau}, \texttt{B+ --> tau}, \texttt{tau.*nu},
\texttt{b.*->.*u}, \texttt{charged Higgs}, \texttt{leptoquark}, and \(W'\)
returned no code hits.  Docs-only catalog-planning rows were not counted as
implementation evidence.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  The catalog-level formula is simple and uses standard
experimental and lattice/CKM inputs, but production use would require a new
charged-current observable and model-specific matching for \(W'\),
charged-scalar, or leptoquark amplitudes.  It should not extend the legacy
\texttt{deltaf2.py} path; if promoted, it belongs in the modern constraint
surface.

\subsection*{Key references}
Process-local snapshots before bibliography consolidation:
\texttt{hflav\_dec2025\_btaunu.txt},
\texttt{pdg2025\_btaunu\_api.txt},
\texttt{utfit\_summer2024\_btaunu.txt},
\texttt{belle2013\_arxiv1208\_4678.txt},
\texttt{belle2015\_arxiv1503\_05613.txt},
\texttt{belleii2025\_arxiv2502\_04885.txt},
\texttt{babar2013\_arxiv1207\_0698.txt},
\texttt{babar2010\_arxiv0912\_2453.txt}, and
\texttt{cfw2008\_arxiv0804\_1954.txt}.
