% Flavor catalog per-process draft.
% process_id: B011
% family: beauty
% owner_agent_id: PKA-B011
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B011.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B011: Inclusive \(B\to X_s\gamma\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(\bar B\to X_s\gamma)\).
This entry covers the CP- and isospin-averaged inclusive radiative decay
\(\bar B\to X_s\gamma\), equivalently the partonic FCNC transition
\(b\to s\gamma\), at the canonical photon-energy threshold
\(E_\gamma>1.6\,\mathrm{GeV}\).  It is separated from the exclusive
\(B\to K^*\gamma\) and \(B_s\to\phi\gamma\) modes.

\subsection*{PDG / equivalent value(s)}
The canonical sidecar value is the HFLAV inclusive average
\[
  {\cal B}(\bar B\to X_s\gamma)_{\rm exp}
  = (3.49\pm0.19)\times 10^{-4},
  \qquad E_\gamma>1.6\,\mathrm{GeV},
\]
accessed on 2026-05-16, with local snapshots
\texttt{references/B011/hflav\_results\_2026-05-16.txt} and
\texttt{references/B011/hflav\_rare\_decays\_dec2024\_table67.txt}.  The
HFLAV table reports the same average as \(349\pm19\) in units of \(10^{-6}\)
after extrapolating the Belle, Belle II, BaBar, and CLEO inputs to the common
threshold.  For theory comparison, the sidecar records the
Misiak--Rehman--Steinhauser NNLO SM prediction
\[
  {\cal B}(\bar B\to X_s\gamma)_{\rm SM}
  = (3.40\pm0.17)\times 10^{-4},
  \qquad E_\gamma>1.6\,\mathrm{GeV},
\]
from \texttt{references/B011/misiak\_rehman\_steinhauser\_2020\_arxiv.txt}
(arXiv:2002.01548).  It also records the PDG-reviewed Misiak et al. number
\((3.36\pm0.23)\times10^{-4}\) from
\texttt{references/B011/misiak\_et\_al\_2015\_arxiv.txt}
(arXiv:1503.01789).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This observable tests the electromagnetic and chromomagnetic dipole sector,
usually parameterized by \(C_7\) and \(C_8\).  In anarchic RS models,
KK fermion, gauge, Higgs, or charged-scalar loops can generate flavor-changing
dipoles even when the tree-level neutral-meson mixing constraints are passed.
The inclusive rate is therefore a sharp complement to the existing
\(\Delta F=2\) lane: it probes loop-level chirality-flipping flavor structure
rather than the four-quark operators currently audited in the quark scan.

\subsection*{Post-2008 developments}
The main post-CFW updates are experimental averaging and NNLO theory.  Belle
published a full-data inclusive \(B\to X_{s+d}\gamma\) photon-spectrum
analysis, Belle II added a hadronic-tag photon-spectrum measurement, and HFLAV
now averages Belle, Belle II, BaBar, and CLEO inputs at the common
\(E_\gamma>1.6\,\mathrm{GeV}\) threshold.  On the SM side, Misiak et al.
updated the NNLO prediction after the original paper-era calculations, and
Misiak, Rehman, and Steinhauser subsequently incorporated improved treatment
of nonperturbative effects and progress toward removing the charm-mass
interpolation.

\subsection*{Constraint validity and model dependence}
This is a robust loop/dipole constraint but not a plug-in likelihood without
model work.  The inclusive observable is cleaner than exclusive radiative
modes, yet its comparison still depends on the photon-energy cut,
extrapolation to the common threshold, perturbative matching, resolved-photon
and other nonperturbative uncertainties, and the convention used for
\(C_7,C_8\).  A catalog-level entry is unambiguous; using it as a hard RS
constraint requires a dedicated \(b\to s\gamma\) Wilson-coefficient pipeline.

Inclusive \(B\to X_s\gamma\) constrains \(|C_7,C_8|\) dipoles; the RS
right-handed-dipole signature requires exclusive polarization and
time-dependent CP observables sensitive to \(C_7'\) (see B012 once available).

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required catalog greps were rerun.  A focused implementation grep for
\texttt{X\_s}, \texttt{b->s gamma}, \texttt{C7}, and \texttt{C8} across
\texttt{quarkConstraints/}, \texttt{flavorConstraints/}, \texttt{scanParams/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{qcd/}, \texttt{warpConfig/},
\texttt{solvers/}, and \texttt{tests/} returned no hits.  The modern quark
surface enumerates only \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\)
at \texttt{quarkConstraints/modern/phenomenology.py:23}, and says it is
policy-only at \texttt{quarkConstraints/modern/phenomenology.py:165}.  The
only dipole implementation found is the lepton-sector
\(\mu\to e\gamma\) module at \texttt{flavorConstraints/muToEGamma.py:1}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use would need a new \(b\to s\gamma\) observable module,
matching onto \(C_7\) and \(C_8\), QCD running in the dipole basis,
normalization to the inclusive rate, and a documented treatment of the SM
prediction and experimental photon-energy threshold.  None of that machinery
is present in the audited \(\Delta F=2\) code.

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{hflav\_rare\_decays\_dec2024},
\texttt{hflav\_results\_2026},
\texttt{pdg2024\_b\_meson\_prod\_decay},
\texttt{misiak\_rehman\_steinhauser\_2020},
\texttt{misiak\_et\_al\_2015},
\texttt{belleii\_2022}, and \texttt{belle\_2016}.
