% Flavor catalog per-process draft.
% process_id: B012
% family: beauty
% owner_agent_id: PKA-B012
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B012.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B012: Exclusive \(B\to K^*\gamma\)}

\subsection*{Process}
\textbf{Standard notation:} \(B\to K^*(892)\gamma\).
This entry covers the exclusive radiative \(b\to s\gamma\) channels
\(B^0\to K^{*0}\gamma\) and \(B^+\to K^{*+}\gamma\), with emphasis on the
time-dependent \(S_{K^*\gamma}\) photon-helicity observable.

\subsection*{PDG value}
The HFLAV Dec.~2024 averages give
\[
{\cal B}(B^0\to K^{*0}\gamma)=(41.63\pm0.92)\times10^{-6},
\qquad
{\cal B}(B^+\to K^{*+}\gamma)=(39.5\pm1.0)\times10^{-6},
\]
from \texttt{references/B012/hflav\_rare\_decays\_dec2024\_btokstargamma.txt}
(\texttt{hflav\_rare\_decays\_dec2024\_btokstargamma}).  The same HFLAV
snapshot gives
\(\Delta_{0+}(B\to K^*\gamma)=0.059\pm0.014\) and
\(A_{CP}(B\to K^*\gamma)=-0.004\pm0.011\)
(\texttt{hflav\_rare\_decays\_dec2024\_btokstargamma}); the HFLAV note marks
the isospin averages as naive and to be treated with caution.  The PDG 2025
pdgLive time-dependent average is
\[
S_{K^{*0}\gamma}(B^0\to K^{*0}\gamma)=-0.08\pm0.17,
\qquad
C_{K^{*0}\gamma}=0.03\pm0.10,
\]
from \texttt{references/B012/pdglive\_2025\_kstargamma\_cp.txt}
(\texttt{pdglive\_2025\_kstargamma\_cp}).

\subsection*{Relevance to RS / anarchic flavor}
This is the exclusive radiative complement to the inclusive \(B\to X_s\gamma\)
entry.  The inclusive rate mostly constrains the size of the electromagnetic
dipole combination, while \(S_{K^*\gamma}\) is a chirality test: a large
right-handed dipole coefficient \(C_7'\) can enhance the mixing-induced
asymmetry even when the total rate remains near the SM value.  Anarchic RS
models can generate chirality-flipped dipoles through KK-fermion, KK-gauge,
or Higgs-sector loops, so this process directly probes a direction not covered
by the present \(\Delta F=2\) scan.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 flavor-baseline era
(\texttt{cfw\_2008\_rs\_flavor}), BaBar produced a high-statistics
branching-fraction, direct-CP, and isospin-asymmetry measurement in 2009
(\texttt{babar\_2009\_btokstargamma}); Belle reported evidence for isospin
violation in 2017 (\texttt{belle\_2017\_isospin\_cp}); LHCb observed photon
polarization in \(b\to s\gamma\) using
\(B^\pm\to K^\pm\pi^\mp\pi^\pm\gamma\)
(\texttt{lhcb\_2014\_photon\_polarization}); and Belle II added
\(B\to K^*\gamma\) measurements now entering HFLAV
(\texttt{belleii\_2024\_btokstargamma}).  PDG 2025 also includes a new
Belle/Belle II input in the \(S_{K^*\gamma}\) average
(\texttt{pdglive\_2025\_kstargamma\_cp}).

\subsection*{Constraint validity / model dependence}
The branching fractions are measured cleanly but are less theory-clean than the
inclusive rate because exclusive form factors and spectator effects enter the
SM comparison.  The time-dependent asymmetry is a sharper null-test of photon
helicity, but its present uncertainty is still statistics-limited.  Translating
the entry into an RS bound requires a convention-matched \(C_7,C_7'\) and
\(C_8,C_8'\) pipeline plus exclusive-amplitude inputs; the measured averages
alone should not be treated as a standalone likelihood.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(B\to K^*\gamma\), \(C_7'\), photon-polarization, or
right-handed \(b\to s\gamma\) implementation.  The modern quark surface is
limited to neutral-meson mixing systems at
\texttt{quarkConstraints/modern/phenomenology.py:23}; the only dipole code
found is the unrelated lepton-sector \(\mu\to e\gamma\) check at
\texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use needs new dipole matching, RG evolution for
\(C_7,C_7'\) and \(C_8,C_8'\), exclusive \(B\to K^*\) form-factor handling,
and a time-dependent CP/helicity observable.  None of that is supplied by the
current \(\Delta F=2\) operator basis.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{hflav\_rare\_decays\_dec2024\_btokstargamma},
\texttt{pdglive\_2025\_kstargamma\_cp},
\texttt{belleii\_2024\_btokstargamma},
\texttt{belle\_2017\_isospin\_cp},
\texttt{babar\_2009\_btokstargamma},
\texttt{lhcb\_2014\_photon\_polarization}, and
\texttt{cfw\_2008\_rs\_flavor}.
