% Flavor catalog per-process template.
% process_id: B015
% family: beauty
% owner_agent_id: PKA-B015
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B015.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B015: Inclusive \(B\to X_s\ell^+\ell^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B\to X_s\ell^+\ell^-)\).
This entry covers the inclusive rare electroweak-penguin process
\(B\to X_s\ell^+\ell^-\), equivalently inclusive \(b\to s\ell^+\ell^-\),
with \(\ell=e,\mu\).  It excludes the exclusive modes \(B\to K\ell\ell\) and
\(B\to K^*\ell\ell\), and the LFU ratios \(R_K\) and \(R_{K^*}\), which are
separate catalog entries B016--B019.

\subsection*{PDG / equivalent value(s)}
The canonical sidecar value is the HFLAV December 2024 inclusive average,
\[
  \mathcal B(B\to X_s\ell^+\ell^-)=(5.84\pm0.69)\times10^{-6},
\]
with the same table listing the PDG value
\((5.84^{+1.31}_{-1.23})\times10^{-6}\).  HFLAV combines the BaBar input
\((6.73^{+0.70}_{-0.64}{}^{+0.60}_{-0.56})\times10^{-6}\) and the Belle input
\((4.11\pm0.83^{+0.85}_{-0.81})\times10^{-6}\); the source notes different
low-dilepton-mass thresholds and different charmonium treatments in
\texttt{references/B015/hflav\_dec2024\_B\_to\_Xsll.txt}.  For the standard
perturbative bins, Huber--Hurth--Lunghi quote weighted experimental averages
of \((1.58\pm0.37)\times10^{-6}\) for \(1<q^2<6\,\mathrm{GeV}^2\) and
\((0.48\pm0.10)\times10^{-6}\) at high \(q^2\), as recorded in
\texttt{references/B015/huber\_hurth\_lunghi\_1503\_04849\_arxiv.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is a \(\Delta B=1\) semileptonic FCNC channel.  It probes flavor-changing
\(Z\) couplings, electroweak-penguin matching, and dipole correlations with
\(b\to s\gamma\), rather than the \(\Delta F=2\) four-quark operators already
used by the repo's neutral-meson constraints.  In RS/anarchic flavor it is most
useful as a diagnostic of semileptonic Wilson coefficients such as \(C_7\),
\(C_9\), \(C_{10}\) and their chirality-flipped partners.

\subsection*{Post-2008 developments}
Since the CFW 2008 RS-flavor baseline, the inclusive channel has gained a
BaBar measurement and a modern HFLAV average, but it remains statistics-limited
and experimentally based on sum-of-exclusive reconstruction.  Theory has also
matured: the 2015 Huber--Hurth--Lunghi analysis includes NNLO QCD, NLO QED,
power corrections, collinear-photon effects, and Belle II projections with
\(50\,\mathrm{ab}^{-1}\).  Current inclusive branching fractions are
compatible with the SM within uncertainties; the sharper exclusive and LFU
anomaly discussions belong in B016--B019.

\subsection*{Constraint validity and model dependence}
The inclusive perturbative windows are cleaner than exclusive form-factor
observables, but a catalog single number is not a plug-in hard bound.  The
interpretation depends on \(q^2\) binning, charm-resonance vetoes, photon
treatment, and the mapping from RS flavor parameters to the \(\Delta B=1\)
weak Hamiltonian.  It is best classified as a theory-controlled but
mode-calculation-limited rare-decay constraint.

In custodial RS, reduced \(Z b_L b_L\) pressure can make this observable
relatively more discriminating; quote RS bounds only after specifying
custodial protection, fermion embeddings, and brane kinetic terms.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The modern phenomenology policy enumerates only
\(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}, and states that this is
policy-only rather than a numeric backend at
\texttt{quarkConstraints/modern/phenomenology.py:166}.  The only live lepton
flavor routine found is \(\mu\to e\gamma\) at
\texttt{flavorConstraints/muToEGamma.py:75}.  Required greps over
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(b\to s\ell\ell\),
\(X_s\ell\ell\), \(C_9\), or \(C_{10}\) implementation.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use would require a new \(\Delta B=1\) semileptonic
operator basis, matching and running for \(C_7,C_9,C_{10}\) plus primed
operators, bin-aware SM predictions, charm/QED treatment, and an experimental
likelihood or covariance model.

\subsection*{Key references}
Process-local snapshots: HFLAV2024Dec:BtoXsll, BaBar2014:BtoXsll,
Belle2005:BtoXsll, HuberHurthLunghi2015:BtoXsll, and
CsakiFalkowskiWeiler2008:CompositeFlavor.
