% Flavor catalog per-process template.
% process_id: B018
% family: beauty
% owner_agent_id: PKA-B018
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B018.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B018: \(R_K\) in \(B^+\to K^+\ell^+\ell^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(R_K\equiv
\mathcal B(B^+\to K^+\mu^+\mu^-)/\mathcal B(B^+\to K^+e^+e^-)\).
This beauty-sector entry covers the charged \(B\to K\ell\ell\) lepton-flavor
universality ratio, not the exclusive \(K^*\) counterpart \(R_{K^*}\) or the
absolute \(B\to K\ell\ell\) branching fractions.

\subsection*{PDG or equivalent value}
The current HFLAV-equivalent source is the Dec. 2025 rare-decay table.  For
the low-\(q^2\) bin \(0.1<q^2<1.1\,{\rm GeV}^2/c^4\), HFLAV lists
\[
  R_K = 0.994\pm0.090,
\]
under \texttt{HFLAV2025Dec:RKBplusKLowQ2}, from LHCb's
\(0.994^{+0.090}_{-0.082}{}^{+0.029}_{-0.027}\) measurement.  For the central
bin \(1.1<q^2<6.0\,{\rm GeV}^2/c^4\), HFLAV quotes
\[
  R_K = 0.947\pm0.047,
\]
under \texttt{HFLAV2025Dec:RKBplusKCentralQ2}, combining LHCb
\(0.949^{+0.042}_{-0.041}\pm0.022\) with CMS
\(0.78^{+0.46}_{-0.23}{}^{+0.09}_{-0.05}\).  HFLAV also records a Belle-only
full-\(q^2\) ratio \(1.08\pm0.16\) under
\texttt{HFLAV2025Dec:RKBplusKFullQ2Belle}.  Local snapshots are
\texttt{references/B018/hflav\_dec2025\_rk\_lowq2.txt},
\texttt{references/B018/hflav\_dec2025\_rk\_centralq2.txt}, and
\texttt{references/B018/hflav\_dec2025\_rk\_fullq2\_belle.txt}, accessed
2026-05-16.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
\(R_K\) is a clean \(\Delta B=1\) semileptonic FCNC ratio.  In an RS or
anarchic-flavor interpretation it probes nonuniversal contributions to the
\(b\to s\ell^+\ell^-\) weak Hamiltonian, especially flavor-changing \(Z\) or
KK-gauge effects and semileptonic Wilson coefficients \(C_9^{\ell}\) and
\(C_{10}^{\ell}\).  It is therefore complementary to the repo's neutral-meson
\(\Delta F=2\) constraints.

\subsection*{Post-2008 developments}
The CFW 2008 baseline predates the modern \(R_K\) anomaly program.  The key
post-2008 developments are experimental: LHCb's 2021 update measured
\(R_K=0.846^{+0.042}_{-0.039}{}^{+0.013}_{-0.012}\) in the central bin and
reported a \(3.1\sigma\) tension with the SM
(\texttt{LHCb2021:UpdatedRK}).  The later LHCb simultaneous
\(R_K\)/\(R_{K^*}\) analysis using \(9\,{\rm fb}^{-1}\) superseded that result
and found the four LFU measurements compatible with the SM
(\texttt{LHCb2023:RKRKstarDetailed}).  HFLAV Dec. 2025 therefore treats the
charged \(R_K\) bins as SM-consistent averages.  On the theory side,
Bordone--Isidori--Pattori established the ratio as a clean probe once
radiative corrections and experimental cuts are handled consistently.

\subsection*{Constraint validity and model dependence}
This is a robust LFU null test, but not a standalone bound on the current
quark-scan model.  It requires a \(\Delta B=1\) semileptonic matching
calculation, bin definitions, QED/radiative treatment, and experimental
correlations.  A universal shift in electron and muon coefficients cancels
strongly in the ratio, while lepton-nonuniversal new physics can be visible.

In custodial RS, reduced \(Z b_L b_L\) pressure can make \(R_K\) relatively
more discriminating as an LFU cross-check; quote RS bounds only after
specifying custodial protection, fermion embeddings, and brane kinetic terms.
Use \(R_K/R_{K^*}\) as precision LFU null tests; do not impose the pre-2023
anomaly narrative as a prior.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(R_K\), \(b\to s\ell\ell\), \(C_9\), \(C_{10}\), or
LFU implementation.  The implemented flavor surface is neutral-meson mixing:
\texttt{quarkConstraints/modern/phenomenology.py:23} enumerates only
\(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\), and
\texttt{quarkConstraints/deltaf2.py:209} defines the legacy \(\Delta F=2\)
inputs.  The only live lepton-flavor routine found is
\texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use would require a new \(\Delta B=1\) semileptonic
operator basis, matching and running for lepton-flavor-dependent \(C_9\),
\(C_{10}\), and primed coefficients, SM bin predictions including radiative
corrections, and likelihood handling for HFLAV/LHCb/CMS inputs.

\subsection*{Key references}
Process-local snapshots: HFLAV2025Dec:RKBplusKLowQ2,
HFLAV2025Dec:RKBplusKCentralQ2, HFLAV2025Dec:RKBplusKFullQ2Belle,
LHCb2023:RKRKstarDetailed, LHCb2021:UpdatedRK,
BordoneIsidoriPattori2016:RKRKstarSM, and
CsakiFalkowskiWeiler2008:CompositeFlavor.
