% Flavor catalog per-process template.
% process_id: B021
% family: beauty
% owner_agent_id: PKA-B021
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B021.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B021: \(\Lambda_b^0\to\Lambda\ell^+\ell^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(\Lambda_b^0\to\Lambda\ell^+\ell^-\).
This is the baryonic exclusive \(b\to s\ell^+\ell^-\) channel.  The current
canonical measured mode is \(\Lambda_b^0\to\Lambda\mu^+\mu^-\); no comparable
PDG electron-mode average was found in this PKA pass.

\subsection*{PDG or equivalent value}
The sidecar is the numerical source of truth.  PDG Live's 2025
\(\Lambda_b^0\) listing gives
\[
  \mathcal B(\Lambda_b^0\to\Lambda\mu^+\mu^-)
  =(1.08\pm0.28)\times10^{-6},
\]
from the decay-mode table under source key
\texttt{PDG2025:LambdaBToLambdaMuMu}.  The LHCb angular analysis under
\texttt{LHCb2015:LambdaBToLambdaMuMu} reports, for
\(15<q^2<20\,{\rm GeV}^2/c^4\),
\[
  \frac{d\mathcal B}{dq^2}
  =(1.18^{+0.09}_{-0.08}\pm0.03\pm0.27)\times10^{-7}
  ({\rm GeV}^2/c^4)^{-1},
\]
and \(A_{\rm FB}^{\ell}=-0.05\pm0.09\pm0.03\),
\(A_{\rm FB}^{h}=-0.29\pm0.07\pm0.03\).
Local snapshots are in \texttt{flavor\_catalog/references/B021/}.

\subsection*{Relevance to RS / anarchic flavor}
This mode probes \(\Delta B=1\) semileptonic FCNC operators rather than the
\(\Delta F=2\) four-quark basis implemented for neutral meson mixing.  Warped
flavor models can generate flavor-changing \(Z\) couplings, KK electroweak
exchange, and loop-induced dipoles feeding \(C_7\), \(C_9\), \(C_{10}\), and
primed semileptonic coefficients.  The baryon final state adds spin and
polarization information unavailable in \(B\to K^{(*)}\ell^+\ell^-\), so it is
a complementary diagnostic of chirality and hadronic systematics.

\subsection*{Post-2008 developments}
The arXiv:0804.1954 RS-flavor baseline predates this channel as an observed
rare decay (\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}).  CDF reported
the first observation in 2011 with 24 signal events, 5.8 standard-deviation
significance, and
\(\mathcal B=(1.73\pm0.42\pm0.55)\times10^{-6}\)
(\texttt{CDF2011:LambdaBToLambdaMuMu}).  LHCb later used
\(3.0\,{\rm fb}^{-1}\) to publish the \(q^2\)-binned branching-fraction and
angular analysis quoted above
(\texttt{LHCb2015:LambdaBToLambdaMuMu}).  Lattice-QCD work by Detmold, Lin,
Meinel, and Wingate supplied post-2008 \(\Lambda_b\to\Lambda\) form factors,
so this baryonic mode should not be folded into the mesonic
\(B\to K^{(*)}\ell\ell\) treatment
(\texttt{DetmoldLinMeinelWingate2013:LambdaBToLambdaFormFactors}).

\subsection*{Constraint validity / model dependence}
This is a useful catalog constraint but not a single-number hard bound.  The
interpretation depends on \(q^2\) binning, charmonium vetoes, normalization to
\(\Lambda_b^0\to J/\psi\Lambda\), baryonic form factors, and nonlocal charm
effects.  Its most robust role is as a \(\Delta B=1\) semileptonic cross-check
with different hadronic systematics from mesonic rare \(B\) decays.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The modern phenomenology surface lists only
\(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}.  The only live
lepton-flavor module is the \(\mu\to e\gamma\) dipole check at
\texttt{flavorConstraints/muToEGamma.py:75}.  Required plan greps and targeted
searches for \(\Lambda_b\), \(b\to s\), \(C_9\), \(C_{10}\), and semileptonic
rare decays found no B021 implementation.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint would need a new \(\Delta B=1\)
semileptonic Hamiltonian, RS matching onto \(C_7,C_9,C_{10}\) and primed
operators, baryonic form factors, \(q^2\)-bin predictions, angular likelihoods,
and experimental covariance/normalization treatment.

\subsection*{Key references}
\texttt{PDG2025:LambdaBToLambdaMuMu},
\texttt{LHCb2015:LambdaBToLambdaMuMu},
\texttt{CDF2011:LambdaBToLambdaMuMu},
\texttt{DetmoldLinMeinelWingate2013:LambdaBToLambdaFormFactors}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
