% Flavor catalog per-process template.
% process_id: B022
% family: beauty
% owner_agent_id: PKA-B022
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B022.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B022: \(B^+\to K^+\nu\bar{\nu}\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B^+\to K^+\nu\bar{\nu})\).
This beauty-sector entry covers the leading exclusive invisible
\(b\to s\nu\bar{\nu}\) mode, with emphasis on the charged channel now measured
by Belle II.  The related vector mode \(B\to K^*\nu\bar{\nu}\) is B023.

\subsection*{PDG or equivalent value}
The current HFLAV-equivalent Dec. 2025 table gives
\[
  \mathcal{B}(B^+\to K^+\nu\bar{\nu})=(1.38\pm0.35)\times10^{-5},
\]
with local snapshot
\texttt{flavor\_catalog/references/B022/hflav\_dec2025\_bplus\_kplus\_nunu.txt}
accessed 2026-05-16 (\texttt{HFLAV2025Dec:BplusKplusNuNu}).  The same HFLAV
table displays the PDG value
\((2.30^{+0.71}_{-0.64})\times10^{-5}\), and the PDG live/API listing records
the Belle II evidence input
\((2.3\pm0.5_{\rm stat}{}^{+0.5}_{-0.4}{}_{\rm syst})\times10^{-5}\)
(\texttt{PDG2026:BplusKplusNuNu}, \texttt{BelleII2024:BplusKplusNuNu}).
Belle II used \(362~{\rm fb}^{-1}\) at the \(\Upsilon(4S)\), reported
\(3.5\sigma\) evidence for the decay, and found the combined result
\(2.7\sigma\) above the Standard Model expectation
(\texttt{BelleII2024:BplusKplusNuNu}).  For theory orientation, the HPQCD 2023
SM prediction is
\((5.58\pm0.37)\times10^{-6}\), summed over neutrino flavours and including the
charged-mode long-distance term (\texttt{HPQCD2023:BtoKNuNuSM}).

\subsection*{Relevance to RS / anarchic flavor}
This mode probes a \(\Delta B=1\) neutral-current transition with missing
energy.  In RS/anarchic-flavor models it can receive contributions from
flavor-changing \(b\)-\(s\) currents coupled to \(Z\), KK electroweak gauge
bosons, or other neutral invisible states.  It is complementary to
\(\Delta F=2\) \(B_s\) mixing because it tests a semileptonic/invisible
operator, not a neutral-meson mixing amplitude.

\subsection*{Post-2008 developments}
The CFW 2008 RS-flavor baseline predates the modern \(B\to K\nu\bar{\nu}\)
program (\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}).  BaBar later set
hadronic-tag limits, including
\(\mathcal{B}(B^+\to K^+\nu\bar{\nu})<3.7\times10^{-5}\) at 90\% CL
(\texttt{BaBar2013:BKstarNuNu}).  Belle II changed the status of the mode with
the 2024 evidence measurement quoted above
(\texttt{BelleII2024:BplusKplusNuNu}).  On the theory side, modern lattice form
factors support the SM prediction quoted above
(\texttt{HPQCD2023:BtoKNuNuSM}), and Belle II has released a 2025
model-agnostic likelihood package to reinterpret the measurement under non-SM
invisible kinematics or WET coefficient choices
(\texttt{BelleII2025:BKnnLikelihood}).

\subsection*{Constraint validity / model dependence}
The SM prediction is comparatively clean: there are no charmonium veto regions
as in \(b\to s\ell^+\ell^-\), and the dominant hadronic input is the
\(B\to K\) vector form factor.  The experimental extraction is less universal:
Belle II's headline branching fraction assumes SM kinematics, while invisible
new particles can change the \(q^2\) spectrum and selection efficiency.  A live
constraint should therefore use either the published likelihood or a validated
reweighting prescription rather than only a one-bin branching-fraction pull.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(B\to K\nu\bar{\nu}\), \(b\to s\nu\bar{\nu}\), or
rare invisible decay implementation.  The modern phenomenology surface lists
only \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}; its note says this is
policy-only at \texttt{quarkConstraints/modern/phenomenology.py:166}.  The
legacy \(\Delta F=2\) inputs are at \texttt{quarkConstraints/deltaf2.py:209},
with \(B_d\) and \(B_s\) mixing evaluators at
\texttt{quarkConstraints/deltaf2.py:903} and
\texttt{quarkConstraints/deltaf2.py:922}.  The only live lepton-flavor routine
seen is \(\mu\to e\gamma\) at \texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  This would require a new \(\Delta B=1\) \(b\to s\nu\bar{\nu}\)
Hamiltonian, exclusive \(B\to K\) form-factor integration, invisible-final-state
acceptance treatment, and Belle II likelihood or kinematic-reweighting support.
The existing neutral-meson \(\Delta F=2\) SLL/SLR/VLL/VRR/LR machinery does not
cover this observable.

\subsection*{Key references}
\texttt{HFLAV2025Dec:BplusKplusNuNu}, \texttt{PDG2026:BplusKplusNuNu},
\texttt{BelleII2024:BplusKplusNuNu}, \texttt{BelleII2025:BKnnLikelihood},
\texttt{BaBar2013:BKstarNuNu}, \texttt{HPQCD2023:BtoKNuNuSM}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
