% Flavor catalog per-process template.
% process_id: B023
% family: beauty
% owner_agent_id: PKA-B023
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B023.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B023: \(B\to K^*\nu\bar{\nu}\)}

\subsection*{Process}
\textbf{Standard notation:} \(\mathcal{B}(B\to K^*\nu\bar{\nu})\).
This beauty-sector entry covers the invisible vector-kaon modes
\(B^0\to K^{*0}(892)\nu\bar{\nu}\) and
\(B^+\to K^{*+}(892)\nu\bar{\nu}\).  The pseudoscalar companion
\(B\to K\nu\bar{\nu}\) is B022.

\subsection*{PDG / equivalent value(s)}
The canonical current PDG/HFLAV values are upper limits.  HFLAV Dec. 2025,
cross-linked to PDG Live 2025, lists
\[
  \mathcal{B}(B^0\to K^{*0}(892)\nu\bar{\nu}) < 1.8\times 10^{-5},
  \qquad 90\%~{\rm CL},
\]
and
\[
  \mathcal{B}(B^+\to K^{*+}(892)\nu\bar{\nu}) < 4.0\times 10^{-5},
  \qquad 90\%~{\rm CL}.
\]
The neutral limit is from Belle's semileptonic-tag search
(\texttt{Belle2017:BHnunuSemileptonic}); the charged limit is from Belle's
full-sample hadronic-tag search (\texttt{Belle2013:BHnunuHadronic}).  BaBar's
2013 hadronic-tag limits, \(<9.3\times10^{-5}\) for \(B^0\to K^{*0}\nu\bar\nu\)
and \(<11.6\times10^{-5}\) for \(B^+\to K^{*+}\nu\bar\nu\), are superseded but
remain part of the HFLAV input history.  Local snapshots are under
\texttt{references/B023/}, accessed 2026-05-16.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
These modes probe the \(\Delta B=1\) FCNC transition \(b\to s\nu\bar{\nu}\).
In RS/anarchic-flavor models they are sensitive to flavor-changing \(Z\),
heavy electroweak-gauge, or other neutral-current couplings generated after
fermion localization and mass-basis rotation.  They are complementary to
\(B_s\) mixing because the final state tests a semileptonic neutral current,
not a \(\Delta F=2\) four-quark amplitude, and the \(K^*\) final state can also
separate left- and right-handed short-distance structures through polarization.

\subsection*{Post-2008 developments}
The CFW 2008 baseline predates all current \(B\to K^*\nu\bar{\nu}\) limits.
Belle's 2013 full-\(\Upsilon(4S)\) hadronic-tag analysis set
\(B^+\to K^{*+}\nu\bar\nu <4.0\times10^{-5}\) and
\(B^0\to K^{*0}\nu\bar\nu <5.5\times10^{-5}\).  BaBar's 2013 analysis found no
significant excess and reported a combined
\(\mathcal{B}(B\to K^*\nu\bar\nu)<7.9\times10^{-5}\).  Belle's 2017
semileptonic-tag search improved the neutral mode to
\(<1.8\times10^{-5}\) and obtained a combined vector limit of
\(<2.7\times10^{-5}\).  Buras--Girrbach-Noe--Niehoff--Straub 2015 updated the
SM treatment using form factors and electroweak corrections, quoting
\(\mathcal{B}(B^0\to K^{*0}\nu\bar\nu)=(9.2\pm1.0)\times10^{-6}\), and framed
the right-handed-current observables used in later new-physics studies.

\subsection*{Constraint validity and model dependence}
Experimentally this is a clean missing-energy upper limit, but it is not a
drop-in bound for the present quark scan.  A production constraint needs the
\(b\to s\nu\bar\nu\) weak Hamiltonian, \(B\to K^*\) form factors, treatment of
right-handed currents and polarization, and either an experimental likelihood
or a conservative reinterpretation of the published upper limits.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Targeted greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(B\to K^*\nu\bar\nu\), \(b\to s\nu\bar\nu\), or
invisible-\(B\) implementation.  The modern phenomenology surface is limited
to \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}.  The legacy default
inputs are \(\Delta F=2\) at \texttt{quarkConstraints/deltaf2.py:209}, with
\(B_d\) and \(B_s\) mixing evaluators at
\texttt{quarkConstraints/deltaf2.py:903} and
\texttt{quarkConstraints/deltaf2.py:922}.  The only live lepton-flavor routine
found is \(\mu\to e\gamma\) at \texttt{flavorConstraints/muToEGamma.py:75}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Implementing B023 requires a new \(\Delta B=1\)
\(b\to s\nu\bar\nu\) operator basis, RS matching for neutral-current
left- and right-handed coefficients, \(B\to K^*\) form-factor and polarization
treatment, and an upper-limit likelihood or validated CL reinterpretation.

\subsection*{Key references}
Process-local reference keys before bibliography consolidation:
\texttt{PDG2025:B0KstarNunu},
\texttt{PDG2025:BpKstarNunu},
\texttt{HFLAV2025Dec:B0KstarNunu},
\texttt{HFLAV2025Dec:BpKstarNunu},
\texttt{Belle2017:BHnunuSemileptonic},
\texttt{Belle2013:BHnunuHadronic},
\texttt{BaBar2013:BKstarNunu},
\texttt{BurasGirrbachNoeNiehoffStraub2015:BKstarNunu}, and
\texttt{CsakiFalkowskiWeiler2008:CompositeFlavor}.
