% Flavor catalog per-process draft.
% process_id: B025
% family: beauty
% owner_agent_id: PKA-B025
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B025.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B025: \(R_D\) in \(B\to D\tau\nu\)}

\subsection*{Process}
\textbf{Standard notation:} \(R_D\equiv
\mathcal{B}(B\to D\tau\nu_\tau)/\mathcal{B}(B\to D\ell\nu_\ell)\), with
\(\ell=e,\mu\).  This beauty-family entry covers the tau-versus-light-lepton
charged-current LFU ratio in exclusive \(b\to c\ell\nu\) semileptonic decays.

\subsection*{PDG / equivalent value(s)}
The canonical current equivalent value is the HFLAV CKM 2025 joint average,
updated on 2025-09-28 and snapshotted in
\texttt{flavor\_catalog/references/B025/hflav\_ckm2025\_rdrds.txt}:
\[
  R_D = 0.358 \pm 0.024 .
\]
The same fit gives \(R_{D^*}=0.281\pm0.011\), correlation
\(\rho(R_D,R_{D^*})=-0.374\), and \(\chi^2/\mathrm{dof}=16.683/14\)
with confidence level \(0.27\).  For comparison, HFLAV quotes an arithmetic
SM reference \(R_D=0.296\pm0.004\), \(R_{D^*}=0.254\pm0.005\).  Against that
reference the combined \(R_D\)-\(R_{D^*}\) discrepancy is quoted as about
\(3.8\sigma\), with \(p=1.48\times10^{-4}\).  The sidecar records the
individual \(R_D\) inputs from BaBar, Belle, LHCb, and Belle II.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
\(R_D\) probes \(b\to c\tau\nu\) charged currents rather than neutral
\(\Delta F=2\) mixing.  It is therefore not a direct constraint on the current
quark-scan lane, but it is important for any warped/anarchic extension with
non-universal charged currents, third-generation enhanced lepton couplings,
charged scalar exchange, \(W'\)-like vectors, or leptoquark-motivated matching.
The ratio cancels many normalization inputs, so a persistent excess is a clean
diagnostic of LFU violation once the model supplies the relevant semileptonic
Wilson coefficients and neutrino-flavor assumptions.

\subsection*{Post-2008 developments}
The Csaki--Falkowski--Weiler 2008 baseline predates the \(R_D^{(*)}\) anomaly
program.  The key post-2008 shift was BaBar's 2012 and 2013 evidence for an
excess in \(B\to D^{(*)}\tau\nu\), followed by Belle hadronic-tag and
semileptonic-tag measurements, LHCb measurements with muonic tau decays, and
Belle II semileptonic-tag and CKM-2025 hadronic-tag inputs.  HFLAV now uses a
joint correlated average rather than a single-experiment comparison.  On the
SM side, lattice and form-factor work matured substantially: HFLAV references
FNAL/MILC, HPQCD, JLQCD, FLAG 2024, and later phenomenological combinations,
so the tension is now limited by correlated experimental averaging and form
factor conventions rather than by the absence of a basic SM prediction.

\subsection*{Constraint validity and model dependence}
The experimental ratio is robust, but interpreting it as an RS bound is
model-dependent.  A live constraint needs the operator basis for
\((\bar c\,\Gamma b)(\bar\tau\,\Gamma\nu)\), the assumed neutrino species, and
the integrated \(B\to D\) form-factor response to vector, scalar, and tensor
operators.  Because HFLAV fits \(R_D\) together with \(R_{D^*}\), a serious
implementation should use the two-dimensional likelihood or covariance rather
than a standalone Gaussian for \(R_D\).

\subsection*{Code coverage in this repo}
\textbf{NO.}  I reran the required coverage greps over
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/}.  The broad plan
greps recover the existing neutral-meson \(\Delta F=2\) and
\(\mu\to e\gamma\) surfaces, but no \(R_D\), \(B\to D\tau\nu\), \(b\to c\)
charged-current, charged-Higgs, or leptoquark observable implementation.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Promotion to a live constraint requires a new semileptonic
charged-current observable, form-factor/mode integration for at least the
\(B\to D\) final state, and a correlated treatment with \(R_{D^*}\).  This
belongs in the modern constraint surface if it is later implemented.

\subsection*{Key references}
Process-local snapshots before bibliography consolidation:
\texttt{hflav\_ckm2025\_rdrds.txt},
\texttt{hflav\_ckm2025\_logfile.txt},
\texttt{babar2012\_arxiv1205\_5442.txt},
\texttt{babar2013\_arxiv1303\_0571.txt},
\texttt{belle2015\_arxiv1507\_03233.txt},
\texttt{belle2019\_arxiv1910\_05864.txt},
\texttt{lhcb2023\_arxiv2302\_02886.txt},
\texttt{lhcb2025\_arxiv2406\_03387.txt},
\texttt{belleii2025\_arxiv2504\_11220.txt},
\texttt{flag2024\_arxiv2411\_04268.txt}, and
\texttt{cfw2008\_arxiv0804\_1954.txt}.
