% Flavor catalog per-process draft.
% process_id: B032
% family: beauty
% owner_agent_id: PKA-B032
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B032.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B032: \(\bar B\to \pi\bar K\)}

\subsection*{Process}
\textbf{Standard notation:} \(\bar B\to \pi\bar K\), equivalently the four
two-body charmless \(B\to K\pi\) modes with charge conjugates implied.  This
entry covers branching fractions, direct CP asymmetries, and the
time-dependent \(C_{K^0\pi^0}\) and \(S_{K^0\pi^0}\) coefficients.

\subsection*{PDG or equivalent value}
The canonical branching-fraction source is the HFLAV End-of-December 2025
rare/charmless update, locally snapshot in
\texttt{references/B032/hflav\_dec2025\_btopik\_values.txt} under source key
\texttt{hflav\_dec2025\_btopik}.  In HFLAV units of \(10^{-5}\),
\[
\begin{array}{c|c}
{\rm mode} & {\cal B} \\
\hline
B^+\to K^0\pi^+ & 2.392\pm0.062 \\
B^+\to K^+\pi^0 & 1.322\pm0.043 \\
B^0\to K^+\pi^- & 2.007\pm0.040 \\
B^0\to K^0\pi^0 & 1.012\pm0.043
\end{array}
\]
The same HFLAV snapshot gives direct asymmetries in \%:
\[
A_{CP}(K^0_S\pi^+)=(-2.67\pm0.87)\%,\quad
A_{CP}(K^+\pi^0)=(+2.7\pm1.2)\%,
\]
\[
A_{CP}(K^+\pi^-)=(-8.31\pm0.31)\%,\quad
A_{CP}(K^0\pi^0)=(-1\pm13)\% .
\]
For the neutral time-dependent mode, the PDG 2025 API snapshot
\texttt{references/B032/pdg2025\_k0pi0\_time\_dependent\_cp\_api.txt} gives
\[
  C_{K^0\pi^0}=0.00\pm0.08,\qquad S_{K^0\pi^0}=0.64\pm0.13 .
\]
The sign convention should be checked before combining with Belle-style
\(A=-C\) inputs.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
\(\bar B\to\pi\bar K\) is a \(b\to s\) charmless penguin system with tree,
QCD-penguin, and electroweak-penguin amplitudes.  Anarchic RS models can
induce nonstandard \(b\to s\) flavor-changing \(Z\), dipole, or four-quark
operators after KK matching.  This process is therefore a diagnostic of
penguin flavor structure that is complementary to the existing neutral-meson
\(\Delta F=2\) constraints, but it is not a clean tree-level bound by itself.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS-flavor benchmark era, the main changes are
experimental.  Belle and BaBar final samples were folded into HFLAV, LHCb
measured \(A_{CP}(B^+\to K^+\pi^0)=0.025\pm0.015\pm0.006\pm0.003\) and
explicitly sharpened the charged--neutral \(K\pi\) direct-asymmetry puzzle,
under source key \texttt{lhcb2021\_bplus\_kplus\_pi0\_acp}, and Belle II
added 2024 measurements of all four \(K\pi\) branching fractions and direct
asymmetries under \texttt{belleii2024\_btokpi}.  Belle II also measured
\(B^0\to K_S^0\pi^0\)
time-dependent CP in 2023, providing the largest modern input to the
PDG/HFLAV \(S_{K^0\pi^0}\) average.  The Belle II \(K\pi\) sum-rule test,
\(-0.03\pm0.13\pm0.04\), is currently consistent with the SM expectation
(\texttt{belleii2024\_btokpi}).

\subsection*{Constraint validity and model dependence}
This is an experimentally mature but SM-theory-limited nonleptonic constraint.
Branching fractions and CP asymmetries are easy to catalog, while interpreting
them as RS exclusions requires a hadronic amplitude framework, electroweak
penguin conventions, strong phases, and correlated treatment of the four
isospin-related modes.  It should be treated as a model-dependent penguin
diagnostic until a dedicated likelihood or conservative amplitude scan exists.

\subsection*{Code coverage in this repo}
\textbf{NO.}  A focused grep for \(B\to K\pi\), charmless, nonleptonic, and
electroweak-penguin strings across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no implementation.  The modern policy surface lists only
\(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) at
\texttt{quarkConstraints/modern/phenomenology.py:23}; its notes say this is a
policy-only fence with no numeric EFT backend at
\texttt{quarkConstraints/modern/phenomenology.py:165}.  The implemented
default inputs in \texttt{quarkConstraints/deltaf2.py:209} are neutral-meson
\(\Delta F=2\) systems only, and the dipole code found at
\texttt{flavorConstraints/muToEGamma.py:75} is the lepton \(\mu\to e\gamma\)
constraint.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A production constraint would need a new nonleptonic
\(b\to s\bar q q\) operator/amplitude layer, electroweak-penguin matching,
hadronic strong-phase treatment, and a correlated four-mode likelihood or
conservative theory envelope.  The existing \(\Delta F=2\) SLL/SLR/VLL/VRR
basis does not cover this calculation.

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{hflav\_dec2025\_btopik},
\texttt{pdg2025\_k0pi0\_time\_dependent\_cp\_api},
\texttt{belleii2024\_btokpi},
\texttt{lhcb2021\_bplus\_kplus\_pi0\_acp},
\texttt{belleii2023\_b0\_ks\_pi0\_cp}, and
\texttt{cfw2008\_rs\_flavor}.
