% Flavor catalog per-process draft.
% process_id: B033
% family: beauty
% owner_agent_id: PKA-B033
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B033.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B033: \(B^0\to\phi K_S^0\) Penguin CP Asymmetry}

\subsection*{Process}
The process is the time-dependent CP asymmetry in the penguin-dominated
beauty decay \(B^0\to\phi K_S^0\), usually reported through
\(\sin(2\beta_{\rm eff})\) and \(C_{\phi K^0}\).  It probes the
\(b\to s\bar s s\) loop amplitude and is interpreted by comparing its weak
phase with the reference \(b\to c\bar c s\) value from
\(B^0\to J/\psi K_S^0\).

\subsection*{PDG / equivalent value(s)}
The source-of-truth numerical block is \texttt{pdg\_or\_equivalent} in
\texttt{B033.yaml}.  HFLAV Summer 2025 gives, for the \(\phi K^0\) average,
\[
  \sin(2\beta_{\rm eff})_{\phi K^0}=0.74\pm0.12,\qquad
  C_{\phi K^0}=-0.09\pm0.12.
\]
HFLAV uses \(S=-\eta_{CP}\sin(2\beta_{\rm eff})\) and quotes
\(\eta_{CP}=-1\) for \(\phi K_S\), so this \(\sin(2\beta_{\rm eff})\) is the
usual \(S_{\phi K_S}\) coefficient in this convention.  The comparison
benchmark on the same HFLAV page is the all-charmonium
\[
  \sin(2\beta)=0.710\pm0.011,
\]
with the strict \(J/\psi K_S\) mode average \(0.712\pm0.011\).  The local
snapshot is \texttt{references/B033/hflav\_triangle\_summer2025\_phiK0.txt},
accessed on 2026-05-16.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In anarchic warped models, KK gluons, electroweak KK modes, or flavor-changing
\(Z/H\)-like effects can add new weak phases to \(b\to s\bar s s\)
\(\Delta B=1\) amplitudes.  \(B^0\to\phi K_S^0\) is therefore a diagnostic of
new penguin phases that would not be captured by a pure \(\Delta m_{B_s}\) or
\(\Delta m_{B_d}\) magnitude constraint.  A large departure of
\(S_{\phi K_S}\) from \(S_{\psi K_S}\) would point to decay-amplitude new
physics rather than just the CKM phase measured in the golden charmonium mode.

\subsection*{Post-2008 developments}
Since the arXiv:0804.1954 RS-flavor baseline, the old B-factory tension in
penguin CP phases has been replaced by a stable world average compatible with
\(S_{\psi K_S}\).  HFLAV Summer 2025 combines BaBar's 2012 Dalitz analysis,
Belle's 2010 time-dependent Dalitz analysis, and Belle II's 2023
time-dependent \(B^0\to\phi K_S^0\) measurement.  Belle II is the important
new post-B-factory input: it measures \(S=0.54\pm0.26^{+0.06}_{-0.08}\) and,
with HFLAV's \(C=-A\) convention, \(C=-0.31\pm0.20\pm0.05\).  The present
HFLAV average differs from the charmonium benchmark by only \(0.03\), far below
the current \(\phi K^0\) uncertainty.

\subsection*{Constraint validity and model dependence}
This is a useful but theory-limited nonleptonic penguin observable.  It is
cleaner as a null test than as a standalone hard bound: the SM prediction is
close to \(\sin(2\beta)\), but subleading amplitudes and hadronic strong
phases are mode dependent.  A production implementation would need a
\(\Delta B=1\) operator basis, RG evolution, and a hadronic amplitude or
phenomenological likelihood.  Treat it as charmless-penguin contextual input
unless the PI chooses a specific hadronic framework.

\subsection*{Code coverage in this repo}
NO.  Focused greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no implementation of \(B\to\phi K\),
\(b\to s\bar s s\) penguin CP asymmetries, \(\sin(2\beta_{\rm eff})\), or
time-dependent charmless \(B\) CP observables.  The nearest adjacent code is
neutral-meson mixing: \texttt{quarkConstraints/deltaf2.py:209} defines the
\(\Delta F=2\) input registry, \texttt{quarkConstraints/deltaf2.py:903}
evaluates \(B_d\) mixing, and \texttt{quarkConstraints/deltaf2.py:922}
evaluates \(B_s\) mixing.  Those do not compute \(\Delta B=1\) penguin decay
amplitudes.

\subsection*{Implementation difficulty}
HIGH.  The existing \(\Delta F=2\) SLL/SLR/VLL/VRR/LR1/LR2 machinery is not
enough.  A live constraint would require \(\Delta B=1\) four-quark penguin
operators, matching from RS sources, QCD running to the \(b\) scale, and a
hadronic treatment of the \(B\to\phi K\) amplitude and strong phases.

\subsection*{Key references}
Process-local raw reference keys before bibliography consolidation:
\texttt{hflav\_triangle\_summer2025\_phiK0},
\texttt{babar\_2012\_b0\_kkks},
\texttt{belle\_2010\_b0\_kkks},
\texttt{belleii\_2023\_phik0}, and
\texttt{csaki\_falkowski\_weiler\_2008}.
