% Flavor catalog per-process draft.
% process_id: B034
% family: beauty
% owner_agent_id: PKA-B034
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B034.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B034: \(B_s^0\to\phi\phi\) Penguin CP Phase}

\subsection*{Process}
\textbf{Standard notation:} \(\phi_s^{s\bar{s}s}\) and \(|\lambda|\) in
\(B_s^0\to\phi(1020)\phi(1020)\).  This entry covers the flavour-tagged,
time-dependent angular CP analysis of the charmless penguin decay
\(B_s^0\to\phi\phi\), a \(b\to s\bar{s}s\) transition.  The process is a
counterpart to the cleaner \(b\to c\bar c s\) phase measurements, but with the
weak phase attached to a loop-induced decay amplitude.

\subsection*{PDG or equivalent value}
The current source-of-truth numerical block is \texttt{B034.yaml}.  The PDG
\(B_s^0\) listing records the \(b\to s\bar{s}s\) convention
\[
  \beta_s=(3.7\pm3.5)\times 10^{-2}\ {\rm rad},
\]
and its AAIJ 23AT note gives the LHCb combined phase and direct-CP parameter
\[
  \phi_s^{s\bar{s}s}=-0.074\pm0.069\ {\rm rad},\qquad
  |\lambda|=1.009\pm0.030 .
\]
The PDG convention is recorded under \texttt{pdg2025\_bs\_phiphi\_cp}; the
same combined LHCb values appear in \texttt{lhcb2023\_bs\_phiphi\_cp\_cds}.
As contextual rate information for the channel, HFLAV May 2024 quotes
\[
  \mathcal B(B_s^0\to\phi\phi)=(1.85\pm0.14)\times 10^{-5}.
\]
This rate is tracked under \texttt{hflav2024\_bs\_phiphi\_branching}.  Local
snapshots are in \texttt{flavor\_catalog/references/B034/}, accessed on
2026-05-16.

\subsection*{Relevance to RS / anarchic flavor}
In warped anarchic flavour models, flavour-changing KK gluon, electroweak-KK,
or misaligned \(Z/H\)-like effects can induce new \(\Delta B=1\) penguin
operators with phases not fixed by the Standard Model CKM fit.  \(B_s^0\to
\phi\phi\) is therefore a useful null test for new weak phases in
\(b\to s\bar{s}s\) amplitudes.  It is complementary to the existing repo's
\(B_s\)-mixing magnitude lane: a new phase could appear in the decay amplitude
or in mixing-decay interference even when a simple \(\Delta m_s\) bound is
satisfied.

\subsection*{Post-2008 developments}
The process matured after the arXiv:0804.1954 era.  LHCb's 2014 analysis used
\(3.0\,{\rm fb}^{-1}\), about 4000 signal decays, and found
\(\phi_s=-0.17\pm0.15\pm0.03\ {\rm rad}\)
(\texttt{lhcb2014\_bs\_phiphi\_cp\_arxiv}).  The 2019 update used
\(5.0\,{\rm fb}^{-1}\), about 9000 signal decays, and reported
\(\phi_s^{s\bar{s}s}=-0.073\pm0.115\pm0.027\ {\rm rad}\) with
\(|\lambda|=0.99\pm0.05\pm0.01\)
(\texttt{lhcb2019\_bs\_phiphi\_cp\_cds}).  The 2023 precision measurement used
\(6\,{\rm fb}^{-1}\) at \(13\,{\rm TeV}\), giving
\(\phi_s^{s\bar{s}s}=-0.042\pm0.075\pm0.009\ {\rm rad}\) and
\(|\lambda|=1.004\pm0.030\pm0.009\) before combination
(\texttt{lhcb2023\_bs\_phiphi\_cp\_cds}).  The combined LHCb result remains
consistent with CP conservation and Standard Model expectations.

\subsection*{Constraint validity / model dependence}
This is a strong experimental null test but a model-dependent contextual observable.
The Standard Model expectation for the penguin phase is close to zero, while
\(|\lambda|=1\) corresponds to no direct CP violation, but a production bound
requires a \(\Delta B=1\) operator normalization, QCD running, polarization
treatment, hadronic amplitudes, and strong-phase assumptions.  It should be
cataloged as a high-value contextual penguin-phase observable until a specific
nonleptonic framework is chosen.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \(B_s^0\to\phi\phi\), \(b\to s\bar{s}s\) penguin,
time-dependent charmless CP, or angular-likelihood implementation.  Adjacent
code only covers neutral \(B_s\) mixing: \texttt{quarkConstraints/deltaf2.py:239}
defines the \(B_s\) input, \texttt{quarkConstraints/deltaf2.py:922} evaluates
\(B_s\) mixing, and \texttt{quarkConstraints/modern/phenomenology.py:657}
bridges the modern \(B_s\)-mixing evaluator.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  The existing \(\Delta F=2\) basis does not compute
\(\Delta B=1\) penguin amplitudes.  A live constraint needs new nonleptonic
operators, matching, running, angular/polarization likelihood handling, and a
hadronic-amplitude prescription.

\subsection*{Key references}
\texttt{pdg2025\_bs\_phiphi\_cp},
\texttt{lhcb2023\_bs\_phiphi\_cp\_cds},
\texttt{lhcb2019\_bs\_phiphi\_cp\_cds},
\texttt{lhcb2014\_bs\_phiphi\_cp\_arxiv},
\texttt{hflav2024\_bs\_phiphi\_branching}, and
\texttt{cfw2008\_arxiv0804\_1954}.
