% Flavor catalog per-process entry.
% process_id: B007
% family: beauty
% owner_agent_id: PKA-B007
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B007.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B007: \(B_s^0\to e^+e^-\), \(B^0\to e^+e^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(B_s^0\to e^+e^-\) and \(B^0\to e^+e^-\).
This entry covers rare electronic leptonic neutral-\(B\) decays,
respectively the \(b\to s e^+e^-\) and \(b\to d e^+e^-\) flavor-changing
neutral-current tails.  It is the electron-mode companion to the muonic
entries \(B005\) and \(B006\), but is cataloged separately because scalar and
pseudoscalar electron operators can remove the Standard Model helicity
suppression in ways not captured by a direct muon-mode rescaling.

\subsection*{PDG / equivalent value(s)}
The current PDG live/API listings (2026 edition, accessed 2026-05-17)
quote only upper limits:
\[
  {\cal B}(B_s^0\to e^+e^-) < 9.4\times 10^{-9}
  \quad(90\%\ {\rm CL}),
\]
assuming no contribution from \(B^0\to e^+e^-\), and
\[
  {\cal B}(B^0\to e^+e^-) < 2.5\times 10^{-9}
  \quad(90\%\ {\rm CL}),
\]
assuming no contribution from \(B_s^0\to e^+e^-\).  The source key is
\texttt{PDG2026\_BsBdEe}, with local snapshot
\texttt{flavor\_catalog/references/B007/pdg\_2026\_bsee\_bdee.txt}.  PDG uses
the LHCb 2020 PRL result as the active input.  The LHCb paper also reports the
corresponding \(95\%\)-CL limits \(11.2\times10^{-9}\) and \(3.0\times10^{-9}\),
respectively, recorded under \texttt{LHCb2020\_BsBdEe}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
\textbf{SECONDARY tier.}  Per \texttt{flavor\_catalog/PRIORITY\_TIERS.md},
this process is a deferred Wave-8 promotion: it is less urgent than the
Wave-1--7 PRIMARY set, but it probes an electron-specific direction absent
from \(B005/B006\).  In anarchic RS models, non-universal fermion localization
generates flavor-changing \(Z\), KK electroweak-gauge, Higgs, radion, or other
scalar exchanges after rotating to the mass basis.  Axial-vector contributions
remain helicity suppressed in the Standard Model pattern, while scalar and
pseudoscalar operators can be chirality enhanced relative to the electronic SM
amplitude.  The mode is therefore a useful handle on electron-sector
misalignment and on any 5D-Yukawa or brane-Higgs structure that feeds
\(C_S^{(\prime)}\) or \(C_P^{(\prime)}\) differently from \(C_{10}^{(\prime)}\).

\subsection*{Post-2008 developments}
The CFW RS-flavor baseline is arXiv:0804.1954
(\texttt{CsakiFalkowskiWeiler2008\_RSFlavor}); its quoted KK reference scales
are theory anchors and are kept out of \texttt{pdg\_or\_equivalent}.  The
experimental landscape then moved through CDF's arXiv:0901.3803 search, which
set the previous \(B_s^0\) and \(B^0\) electronic limits later superseded by
LHCb.  BaBar's arXiv:0712.1516 and Belle's older \(B^0\to e^+e^-\) bound remain
historical \(B_d\)-mode context in the PDG table.  Bobeth et al.,
arXiv:1311.0903, supplied the reduced-uncertainty SM \(B_{s,d}\to\ell^+\ell^-\)
predictions and made explicit that the electron modes are suppressed by the
lepton mass in the SM.  Fleischer, Jaarsma, and Tetlalmatzi-Xolocotzi,
arXiv:1703.10160, emphasized that new physics in the \(B_{s,d}\to e^+e^-\)
channels can be much less suppressed than the SM electron amplitude in
scalar/pseudoscalar scenarios.  LHCb's arXiv:2003.03999 search is the decisive
post-2008 experimental update and supersedes the previous CDF limits.

\subsection*{Constraint validity and model dependence}
The canonical observables are robust experimental upper limits, but their model
interpretation is not a direct neutral-meson-mixing constraint.  The LHCb limits
are quoted one channel at a time, assuming no contribution from the other
neutral-\(B\) electronic mode, and the \(B_s^0\) result assumes the mean
\(B_s^0\) lifetime; the paper reports a \(2.4\%\) shift for SM-like CP-odd or
CP-even alternatives.  A production RS implementation needs a consistent
\(\Delta B=1\) Hamiltonian, the \(B_q\) decay constants and CKM inputs as
theory inputs, a convention for electron bremsstrahlung/QED effects, and
separate scalar and pseudoscalar Wilson coefficients.  The limits are strongest
as exclusions on large electron-specific scalar/pseudoscalar amplitudes rather
than as precision tests of the tiny SM prediction.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(B_s^0\to e^+e^-\),
\(B^0\to e^+e^-\), \(b\to s e e\), or \(b\to d e e\) rare-decay
implementation.  The exact nearby hits are neutral \(B_d/B_s\) mixing inputs at
\texttt{quarkConstraints/deltaf2.py:225} and
\texttt{quarkConstraints/deltaf2.py:239}, and the corresponding mixing
evaluators at \texttt{quarkConstraints/deltaf2.py:903} and
\texttt{quarkConstraints/deltaf2.py:922}; they are \(\Delta F=2\), not this
\(\Delta B=1\) electronic leptonic observable.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  The first useful implementation can share the pure-leptonic
\(\Delta B=1\) machinery needed for \(B005/B006\): \(C_{10}^{(\prime)}\),
\(C_S^{(\prime)}\), \(C_P^{(\prime)}\), \(f_{B_q}\), lifetimes, CKM inputs, and
a branching-ratio formula.  The electron channel adds care around QED tails and
the LHCb assumptions, but it does not require angular observables or exclusive
form-factor likelihoods.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026\_BsBdEe}, \texttt{LHCb2020\_BsBdEe},
\texttt{BobethEtAl2013\_BqllSM},
\texttt{CDF2009\_BsBdEe},
\texttt{FleischerJaarsmaTetlalmatziXolocotzi2017\_BqllNP},
\texttt{BaBar2008\_BdEe}, and
\texttt{CsakiFalkowskiWeiler2008\_RSFlavor}.
