% Flavor catalog per-process entry.
% process_id: B008
% family: beauty
% owner_agent_id: PKA-B008
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B008: \(B_s^0\to\tau^+\tau^-\), \(B^0\to\tau^+\tau^-\)}

\subsection*{Process}
\textbf{Standard notation:} \(B_s^0 \to \tau^+\tau^-\) and
\(B^0 \to \tau^+\tau^-\).  This entry covers the rare tauonic leptonic
neutral-\(B\) decays, i.e. the \(b\to s\tau^+\tau^-\) and
\(b\to d\tau^+\tau^-\) purely leptonic tails.  Experimentally these modes are
hard because both taus decay with missing neutrinos; the current direct limits
come from tau reconstruction in the \(3\pi\nu_\tau\) channel.

\subsection*{PDG / equivalent value(s)}
The canonical PDG live/API values, accessed 2026-05-17, are upper limits:
\[
  {\cal B}(B_s^0\to\tau^+\tau^-) < 6.8\times10^{-3}\quad(95\%\ {\rm CL}),
\]
assuming no contribution from \(B^0\to\tau^+\tau^-\), and
\[
  {\cal B}(B^0\to\tau^+\tau^-) < 2.1\times10^{-3}\quad(95\%\ {\rm CL}),
\]
assuming no contribution from \(B_s^0\to\tau^+\tau^-\).  Both entries trace to
the LHCb 2017 PRL search, using \(pp\) data at 7 and 8 TeV.  The sidecar stores
these upper limits in \texttt{pdg\_or\_equivalent}; dataset metadata and
theory predictions are intentionally kept in auxiliary fields following the
CHK-1 carve-out precedent.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This Wave-8 entry is tagged \textbf{SECONDARY}; see
\texttt{flavor\_catalog/PRIORITY\_TIERS.md} for the tier policy.  The mode is
secondary because the direct limits are still far above the Standard Model
expectation and are experimentally difficult, but it is a useful tau-specific
handle on scalar and pseudoscalar structures.  In warped/anarchic-flavor
models, fermion localization and Yukawa misalignment can induce flavor-changing
\(Z\), Higgs, or heavy-electroweak/Kaluza--Klein exchange contributions to the
\(\Delta B=1\) Wilson coefficients \(C_{10}\), \(C_S\), and \(C_P\).  The tau
mass weakens the helicity suppression relative to electron and muon final
states, and scalar/pseudoscalar operators can produce especially large effects.
KK-gluon exchange is more directly constrained by \(B_{s,d}\) mixing, but the
same flavor rotations and localization choices feed the rare leptonic channel.
Dipole operators are not the leading pure-leptonic contribution, yet they are
part of the same RS flavor-misalignment diagnostic suite.

\subsection*{Post-2008 developments}
Relative to the Csaki--Falkowski--Weiler/Perez--Randall-era flavor literature,
the decisive experimental update is the LHCb search
arXiv:1703.02508, published as PRL 118, 251802.  It used \(3\,{\rm fb}^{-1}\)
of 2011--2012 data and tau reconstruction through
\(\tau^-\to\pi^-\pi^+\pi^-\nu_\tau\), setting the first direct
\(B_s^0\to\tau^+\tau^-\) limit and the strongest \(B^0\to\tau^+\tau^-\)
limit at publication.  The older BABAR direct \(B^0\) result,
arXiv:hep-ex/0511015, remains useful history but is superseded in PDG by LHCb.
The BABAR arXiv:1605.09637 result is a related \(B^+\to K^+\tau^+\tau^-\)
semileptonic input, not the B008 neutral-leptonic observable.

On the theory side, Bobeth et al. arXiv:1311.0903 supplied the
reduced-uncertainty SM normalization for \(B_{s,d}\to\ell^+\ell^-\) modes.
Capdevila et al. arXiv:1712.01919 showed why \(b\to s\tau^+\tau^-\) can remain
a high-leverage new-physics probe in lepton-flavor-nonuniversal scenarios.
Bordone and Fernandez Navarro arXiv:2307.07013 connected \(b\to s\tau\tau\)
new physics to \(\tau_{B_s}/\tau_{B_d}\) and \(\Delta\Gamma_s\), emphasizing
that scalar operators make \(B_s\to\tau^+\tau^-\) particularly sensitive
through chiral enhancement.

\subsection*{Constraint validity and model dependence}
Class: upper-limit and model-dependent for new-physics interpretation.  The
experimental limits are robust as one-mode-at-a-time upper limits, but they are
not measurements of a branching fraction and should not be treated as Gaussian
averages.  A simultaneous RS scan with both \(B_s^0\) and \(B^0\) tauonic
decays would ideally use a two-dimensional likelihood or reproduce the LHCb
assumptions, because each quoted limit assumes the other neutral mode is absent.
Theory translation requires a consistent normalization for time-integrated
branching fractions, tau-mass phase space, and \(C_{10}\), \(C_S\), and
\(C_P\) Wilson coefficients.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required coverage greps across
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, and \texttt{tests/} found no B008
rare-leptonic implementation.  Existing hits cover \(B_d\) and \(B_s\)
\(\Delta F=2\) mixing
(\texttt{quarkConstraints/deltaf2.py:903} and
\texttt{quarkConstraints/deltaf2.py:922}), bridge wrappers for the same mixing
observables (\texttt{quarkConstraints/modern/phenomenology.py:646} and
\texttt{quarkConstraints/modern/phenomenology.py:657}), an unrelated
\(\mu\to e\gamma\) routine (\texttt{flavorConstraints/muToEGamma.py:75}), and
a scan-parameter example involving \(y_\tau\) (\texttt{scanParams/README.md:161}).
They do not implement a \(B_{s,d}\to\tau^+\tau^-\) branching ratio, a
\(b\to s,d\,\tau^+\tau^-\) likelihood, or a tauonic \(C_{10}\), \(C_S\), or
\(C_P\) rare-decay evaluator.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  A catalog-level constraint can be built from the standard
pure-leptonic \(B_q\to\ell^+\ell^-\) formula with tau-mass phase space,
time-integration conventions, and scalar/pseudoscalar Wilson coefficients.
This is more work than wiring a published average, but it avoids the exclusive
form-factor and angular-analysis machinery needed for semileptonic
\(b\to s\tau^+\tau^-\) modes.  A faithful reproduction of the experimental
two-mode likelihood would raise the difficulty.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2026\_BsTauTau}, \texttt{PDG2026\_BdTauTau},
\texttt{AaijEtAl2017\_BqTauTau}, \texttt{AubertEtAl2006\_BdTauTau},
\texttt{LeesEtAl2017\_BKTauTauRelated}, \texttt{BobethEtAl2014\_BqTauTauSM},
\texttt{CapdevilaEtAl2018\_BSTauTauNP},
\texttt{BordoneNavarro2023\_BSTauTauNP}, and
\texttt{CsakiFalkowskiWeiler2008\_RSFlavor}.
