% Flavor catalog per-process draft.
% process_id: B013
% family: beauty
% owner_agent_id: PKA-B013
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B013.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B013: \(B_s \to \phi\gamma\)}

\subsection*{Process}
\textbf{Standard notation:} \(B_s^0\to\phi(1020)\gamma\).
This entry covers the exclusive radiative \(b\to s\gamma\) decay of the
neutral \(B_s\) meson, including the branching fraction and the
time-dependent photon-helicity observables \(S_{\phi\gamma}\),
\(C_{\phi\gamma}\), and \(A^\Delta_{\phi\gamma}\).

\subsection*{PDG / equivalent value(s)}
The PDG 2025 \(B_s^0\) listing gives
\[
  {\cal B}(B_s^0\to\phi\gamma)=(3.4\pm0.4)\times10^{-5},
\]
with local snapshot
\texttt{flavor\_catalog/references/B013/pdg2025\_bs\_phi\_gamma.txt}.
The HFLAV end-of-year 2024 rare-decay table gives the compatible average
\[
  {\cal B}(B_s^0\to\phi\gamma)=(34.0\pm3.2)\times10^{-6},
\]
from the LHCb and Belle inputs, with local snapshot
\texttt{flavor\_catalog/references/B013/hflav\_rare\_decays\_dec2024\_bs\_phi\_gamma.txt}.
The current time-dependent \(B_s^0\to\phi\gamma\) observables are from the
LHCb 2019 flavor-tagged analysis,
\[
  S_{\phi\gamma}=0.43\pm0.30\pm0.11,\qquad
  C_{\phi\gamma}=0.11\pm0.29\pm0.11,
\]
\[
  A^\Delta_{\phi\gamma}=-0.67^{+0.37}_{-0.41}\pm0.17,
\]
where the first uncertainty is statistical and the second is systematic; see
\texttt{flavor\_catalog/references/B013/lhcb\_2019\_bsphigamma\_cp\_arxiv.txt}
and the PDG snapshot.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Wave-8 policy tags this entry as \textbf{SECONDARY}; see
\texttt{flavor\_catalog/PRIORITY\_TIERS.md} for the intended priority-tier
contract.  The physics motivation is direct: \(B_s^0\to\phi\gamma\) probes the
electromagnetic dipole transition \(b\to s\gamma\), but with a helicity handle
that the inclusive \(B\to X_s\gamma\) rate does not provide.  In anarchic RS
or composite-Higgs variants, KK fermions, KK gauge bosons, and the Higgs
sector can generate chirality-flipped dipole coefficients \(C_7'\) and
\(C_8'\).  Those contributions may leave the inclusive rate close to the SM
while shifting \(A^\Delta_{\phi\gamma}\) or \(S_{\phi\gamma}\), so this mode is
a useful companion to B011 and B012.

\subsection*{Post-2008 developments}
The pre-LHC formalism source is Muheim--Xie--Zwicky, arXiv:0802.0876, which
identified the \(B_s\) width difference as a way to measure the
\(\sinh(\Delta\Gamma_s t/2)\) coefficient in \(B_s\to\phi\gamma\) and thereby
probe right-handed photon amplitudes.  Belle measured
\(B_s^0\to\phi\gamma\) at the \(\Upsilon(5S)\) in arXiv:1411.7771; this is one
of the inputs to the modern PDG/HFLAV branching-fraction average.  LHCb's
arXiv:1905.06284 measurement is the current time-dependent CP reference,
giving the first \(S_{\phi\gamma}\) and \(C_{\phi\gamma}\) measurements in a
radiative \(B_s\) decay and updating the earlier untagged
\(A^\Delta_{\phi\gamma}\) result.  LHCb arXiv:2406.00235 added a Run-1/Run-2
amplitude analysis of \(B_s^0\to K^+K^-\gamma\), clarifying resonant
composition around the \(\phi(1020)\).  LHCb arXiv:2411.10219 uses the
very-low-\(q^2\) \(B_s^0\to\phi e^+e^-\) angular distribution as a virtual
photon-polarization cross-check.

\subsection*{Constraint validity and model dependence}
The branching fraction is experimentally established, but an exclusive
constraint needs form-factor and spectator-amplitude conventions rather than
only the inclusive \(C_7\) rate machinery.  The time-dependent observables are
cleaner chirality probes, yet their use in a scan still requires a consistent
mapping from RS dipole coefficients to \(C_7,C_7'\) and \(C_8,C_8'\), the
\(B_s\)-mixing phase and width-difference conventions, and an exclusive
\(B_s\to\phi\) amplitude model.  A catalog entry is therefore robust, while a
hard likelihood is model-dependent until the dipole and exclusive-amplitude
pipeline exists.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required greps over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no implementation of
\(B_s^0\to\phi\gamma\), \(S_{\phi\gamma}\), \(A^\Delta_{\phi\gamma}\), or a
quark-sector \(b\to s\gamma\) dipole likelihood.  The existing modern quark
surface enumerates only \(\epsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\)
neutral-meson mixing at \texttt{quarkConstraints/modern/phenomenology.py:23}.
The dipole hit at \texttt{flavorConstraints/muToEGamma.py:75} is the unrelated
charged-lepton \(\mu\to e\gamma\) check.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Production use needs new \(b\to s\gamma\) dipole matching,
QCD running for \(C_7,C_7'\) and \(C_8,C_8'\), exclusive \(B_s\to\phi\)
form-factor and resonance inputs, and a time-dependent \(B_s\) likelihood.
The current \(\Delta F=2\) code does not supply that operator basis or
observable layer.

\subsection*{Key references}
Process-local keys before bibliography consolidation:
\texttt{PDG2025\_Bs\_phi\_gamma},
\texttt{HFLAV2024\_rare\_decays\_Bs\_phi\_gamma},
\texttt{LHCb2019\_Bs\_phi\_gamma\_CP},
\texttt{Belle2014\_Bs\_phi\_gamma},
\texttt{LHCb2024\_Bs\_KK\_gamma},
\texttt{LHCb2024\_Bs\_phi\_ee\_photon\_polarisation},
\texttt{MuheimXieZwicky2008\_Bs\_phi\_gamma}, and
\texttt{CFW2008\_RS\_flavor}.
