% Flavor catalog per-process entry.
% process_id: B014
% family: beauty
% priority_tier: SECONDARY
% owner_agent_id: PKA-B014
% writer_agent_id: WA
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: B014.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{B014: \(B\to\rho\gamma\) and \(B\to\omega\gamma\)}

\subsection*{Process}
\textbf{Standard notation:} \(B\to\rho\gamma\), \(B\to\omega\gamma\).
This entry covers the exclusive radiative \(b\to d\gamma\) channels
\(B^+\to\rho^+\gamma\), \(B^0\to\rho^0\gamma\), and
\(B^0\to\omega\gamma\), plus their common HFLAV \(B\to\rho\gamma\) and
\(B\to\rho/\omega\gamma\) averages where useful.  The process is CKM
suppressed relative to the \(b\to s\gamma\) entries B011/B012 and probes the
down-sector electromagnetic dipole with different flavor insertions.

\subsection*{PDG / equivalent value(s)}
The PDG 2025 listings give the exclusive component averages
\[
  {\cal B}(B^+\to\rho^+\gamma)=(9.8\pm2.5)\times10^{-7},
\]
\[
  {\cal B}(B^0\to\rho^0\gamma)=(8.6\pm1.5)\times10^{-7},
\qquad
  {\cal B}(B^0\to\omega\gamma)=
    \left(4.4^{+1.8}_{-1.6}\right)\times10^{-7}.
\]
The HFLAV end-of-year 2024 rare-decay table gives, in units of \(10^{-6}\),
\[
  {\cal B}(B\to\rho\gamma)=1.40\pm0.22,\qquad
  {\cal B}(B\to\rho/\omega\gamma)=1.30\pm0.18,
\]
and quotes the naive isospin average
\[
  \frac{\Gamma(B^+\to\rho^+\gamma)}
       {2\Gamma(B^0\to\rho^0\gamma)}-1=-0.46\pm0.17.
\]
HFLAV explicitly cautions that the isospin averages in that table are computed
naively.  The sidecar also records the HFLAV semi-inclusive
\(B\to X_d\gamma\) average, \((9.2\pm3.0)\times10^{-6}\), as a related
normalization and CKM-ratio input, not as the exclusive B014 headline value.
All values are backed by local snapshots under
\texttt{flavor\_catalog/references/B014/}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This Wave-8 entry is \textbf{SECONDARY} under
\texttt{flavor\_catalog/PRIORITY\_TIERS.md}.  In an RS/anarchic-flavor
treatment the relevant short-distance objects are the \(b\to d\)
electromagnetic and chromomagnetic dipole coefficients \(C_7^{(d)}\),
\(C_7^{\prime(d)}\), \(C_8^{(d)}\), and \(C_8^{\prime(d)}\).  KK gauge bosons,
KK fermions, and Higgs-sector loops can induce chirality-flipped dipoles whose
amplitudes depend on 5D fermion localization and anarchic Yukawa insertions.
Compared with B011/B012, this entry tests the same dipole machinery in the
\(b\to d\) flavor direction, where the exclusive isospin and CP observables can
be sensitive to right-handed photons, spectator effects, and weak-annihilation
contamination.

\subsection*{Post-2008 developments}
BaBar arXiv:1005.4087 extended the 2008 Belle/BaBar exclusive picture by
studying semi-inclusive \(B\to X_{s,d}\gamma\) and extracting
\(|V_{td}/V_{ts}|\).  Hurth and Nakao arXiv:1005.1224 is the compact
post-2008 review of how inclusive and exclusive \(b\to d\gamma\) data are
compared with \(b\to s\gamma\).

Belle/Belle II arXiv:2407.08984 provides a newer joint \(B\to\rho\gamma\)
measurement with CP and isospin asymmetries, while LHCb arXiv:2507.14401
reports a high-precision \(B^0\to\rho(770)^0\gamma\) branching fraction
normalized to \(B^0\to K^{*0}\gamma\).  These are important for a future
likelihood update even though the canonical PDG/HFLAV snapshot values above
remain the conservative catalog anchors.

Descotes-Genon et al. arXiv:1104.3342 gives the standard \(C_7\)-\(C_7'\)
language for radiative \(B\) constraints, and Bharucha--Straub--Zwicky
arXiv:1503.05534 supplies updated \(B\to\rho\) and \(B\to\omega\) form-factor
inputs from light-cone sum rules.  These sources matter because an exclusive
\(B\to\rho/\omega\gamma\) constraint is only as clean as its dipole matching,
RG evolution, and form-factor/annihilation prescription.

\subsection*{Constraint validity and model dependence}
Class: useful but model-dependent.  The inclusive \(b\to d\gamma\) rate and
the exclusive \(B\to\rho/\omega\gamma\) averages constrain \(|C_7^{(d)}|^2\)
and \(|C_7^{\prime(d)}|^2\) combinations only after choosing CKM inputs,
exclusive form factors, weak-annihilation treatment, and a convention for SM
long-distance pieces.  The isospin asymmetry should be treated as diagnostic
unless the implementation includes spectator and annihilation effects.  The
LHCb 2025 measurement also carries an explicit saturation assumption for the
selected \(\rho(770)^0\) and \(K^{*}(892)^0\) dihadron spectra.  A hard RS
exclusion should therefore come from a dedicated Wilson-coefficient likelihood,
not from a direct comparison of raw branching fractions alone.

\subsection*{Code coverage in this repo}
\textbf{NO.}  A focused search across \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} for \(B\to\rho\gamma\),
\(B\to\omega\gamma\), \(b\to d\gamma\), \(X_d\gamma\), and B014 returned no
matches.  Broader dipole searches find only lepton-sector coverage, for
example \texttt{flavorConstraints/muToEGamma.py:75} and
\texttt{flavorConstraints/README.md:3}.  The modern quark policy surface at
\texttt{quarkConstraints/modern/phenomenology.py:23} enumerates only
\(\varepsilon_K\), \(K\), \(B_d\), \(B_s\), and \(D^0\) mixing systems; the
\(\Delta F=2\) beauty routines at
\texttt{quarkConstraints/deltaf2.py:903},
\texttt{quarkConstraints/deltaf2.py:922}, and
\texttt{quarkConstraints/deltaf2.py:941} do not implement radiative
\(b\to d\gamma\) decays.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  The repo would need new \(b\to d\gamma\) dipole matching,
running and mixing for \(C_7^{(d)}\), \(C_7^{\prime(d)}\), \(C_8^{(d)}\), and
\(C_8^{\prime(d)}\), a bridge from RS overlap/Yukawa data into those
coefficients, and an exclusive \(B\to\rho/\omega\gamma\) likelihood with
form-factor, isospin, CP, and CKM-ratio uncertainties.  Existing
\(\Delta F=2\) and \(\mu\to e\gamma\) code cannot be reused as a finished
constraint.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{hflav\_rare\_decays\_dec2024\_bd\_gamma},
\texttt{pdg2025\_bplus\_rhop\_gamma},
\texttt{pdg2025\_bzero\_rho\_omega\_gamma},
\texttt{babar\_2008\_rho\_omega\_gamma},
\texttt{belle\_2008\_bd\_gamma},
\texttt{babar\_2010\_xdgamma},
\texttt{hurth\_nakao\_2010\_penguins},
\texttt{descotes\_genon\_2011\_c7\_c7prime},
\texttt{bharucha\_straub\_zwicky\_2016\_lcsr},
\texttt{belle\_belleii\_2024\_rhogamma},
\texttt{lhcb\_2025\_b0rho0gamma}, and
\texttt{cfw\_2008\_rs\_flavor}.
