% Flavor catalog per-process draft.
% process_id: T014
% family: top_higgs_ew
% owner_agent_id: PKA-T014
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: T014.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(Z\to bs,\,bd,\,sd\)}{Z -> bs, bd, sd} Down-Sector FCNC Decays}

\subsection*{Process}
\textbf{Standard notation:} \(Z\to b\bar s+\bar b s\),
\(Z\to b\bar d+\bar b d\), and \(Z\to s\bar d+\bar s d\).
This entry covers on-shell flavor-changing neutral-current \(Z\)-boson decays
to unequal down-type quark flavors.  It is a Wave-8 \textbf{SECONDARY} entry
under the policy described in \texttt{flavor\_catalog/PRIORITY\_TIERS.md}:
it is useful as the catalog's standalone FCNC-\(Z\) row, but it is lower
priority than the Wave 1--7 PRIMARY constraints.

\subsection*{PDG / equivalent value(s)}
The PDG 2025 \(Z\)-boson listing does not provide a dedicated row for
\(Z\to bs\), \(Z\to bd\), or \(Z\to sd\).  The current experiment-equivalent
direct bound used by recent FCNC-\(Z\) summaries is instead the inclusive
non-standard hadronic-width constraint,
\[
  {\cal B}(Z\to q_i\bar q_j+\bar q_i q_j) < 2.9\times10^{-3}
  \qquad (95\%~{\rm CL},\ i\ne j),
\]
from the agreement of the measured \(Z\) hadronic width with the SM
prediction.  For this entry the sidecar records the same direct bound for
\(bs\), \(bd\), and \(sd\), with the \(bs\) and \(bd\) provenance anchored in
the ECFA 2025 and Kamenik et al. 2024 extracts and the explicit \(sd\)
application anchored in Abu-Ajamieh et al. 2026.  The supporting PDG snapshot
records the underlying hadronic \(Z\) branching fraction
\({\cal B}(Z\to{\rm hadrons})=(69.911\pm0.056)\%\), but that inclusive
branching fraction is not itself the FCNC observable.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
Anarchic warped models naturally generate flavor-nonuniversal neutral-gauge
couplings after rotating the localized fermion zero modes to the mass basis.
For down-type quarks this creates off-diagonal \(Z d_i d_j\) vertices through
zero-mode coupling nonuniversality, mixing with KK gauge bosons, and mixing
with KK fermions.  The custodial construction that protects \(Zb_L\bar b_L\)
also matters for off-diagonal left-handed \(Z d_L^i\bar d_L^j\) couplings;
in custodial RS, rare \(K\) and \(B\) amplitudes can instead be dominated by
right-handed tree-level \(Z\) exchange.  The direct on-shell \(Z\to q_iq_j\)
bound is therefore a weak but conceptually clean collider diagnostic for the
same effective vertices that enter \(K\), \(B_d\), and \(B_s\) rare decays and
mixing.

\subsection*{Post-2008 developments}
Blanke, Buras, Duling, Gemmler, and Gori 2009 is the key RS-specific update
relative to the CFW era: it studies rare \(K\) and \(B\) decays in a custodial
warped model and shows how tree-level \(Z\) exchange with flavor-changing
down-quark couplings can dominate selected \(\Delta F=1\) amplitudes.  Kamenik
et al. 2024 updated the SM predictions and future-collider reach, quoting
\({\cal B}(Z\to bs)=(4.2\pm0.7)\times10^{-8}\) and
\({\cal B}(Z\to bd)=(1.8\pm0.3)\times10^{-9}\), plus the common
\(2.9\times10^{-3}\) current direct bound.  The ECFA 2025 report folds these
results into the Higgs/electroweak/top factory program and gives FCC-ee
projection benchmarks such as \(7.33\times10^{-6}\) for \(Z\to bs\) with
0.1\% systematics.  Abu-Ajamieh et al. 2026 gives a dedicated quark-sector
survey of flavor-violating \(Z\) couplings: direct searches are only at the
\(\sqrt{|g_L|^2+|g_R|^2}\sim5\times10^{-2}\) level, while meson oscillations
push the effective \(bd\), \(bs\), and \(sd\) coupling bounds many orders of
magnitude lower.

\subsection*{Constraint validity and model dependence}
The direct \(2.9\times10^{-3}\) limit is flavor-inclusive and not a dedicated
\(bs\), \(bd\), or \(sd\) analysis; it should not be treated as a powerful
standalone RS exclusion.  Low-energy constraints from \(K\), \(B_d\), and
\(B_s\) mixing or rare decays are much stronger, but they test model-dependent
linear combinations of left- and right-handed \(Z\) couplings and can be
affected by correlations or cancellations with KK-gauge and other
\(\Delta F=1,2\) contributions.  A live implementation therefore needs an
explicit convention for off-diagonal \(Z d_i d_j\) couplings and a decision on
whether to impose only the weak direct width bound or the stronger
low-energy-derived coupling bounds.

\subsection*{Code coverage in this repo}
\textbf{NO.}  A targeted grep for \(Z\to bs\), \(Z\to bd\), \(Z\to sd\),
\texttt{Zbs}/\texttt{Zbd}/\texttt{Zsd}, and flavor-violating \(Z\)-coupling
strings across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} returned no hits.  Broader searches find only existing
\(\Delta F=2\) neutral-meson machinery
(\texttt{quarkConstraints/modern/phenomenology.py:23}) and generic
\(M_Z\)/\(\alpha_s(M_Z)\) support such as
\texttt{qcd/constants.py:11} and \texttt{quarkConstraints/qcd\_running.py:100}.
There is no on-shell FCNC-\(Z\) branching-ratio likelihood or \(Z d_i d_j\)
operator interface.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  Recording the external direct limit is straightforward, but a
production RS constraint requires new electroweak \(\Delta F=1\) matching for
off-diagonal \(Z\) couplings, custodial-embedding bookkeeping, and a policy for
correlating direct \(Z\)-width information with already-implemented
\(\Delta F=2\) and future rare-decay constraints.  The current code only
covers neutral-meson mixing and unrelated charged-lepton dipoles.

\subsection*{Key references}
\texttt{PDG2025\_Z\_hadronic\_width};
\texttt{ECFA2025\_FV\_Z\_decays};
\texttt{Kamenik2024\_FV\_Higgs\_Z\_FCCee};
\texttt{AbuAjamieh2026\_FV\_Z\_quark\_bounds};
\texttt{Eilam2002\_Rare\_Z\_decays};
\texttt{CsakiFalkowskiWeiler2008\_WarpedFlavor};
\texttt{BlankeBurasDulingGemmlerGori2009\_RareKBWarped}.
