% Flavor catalog per-process entry.
% process_id: CR004
% family: collider_rs
% owner_agent_id: PKA-CR004
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR004.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{CR004: \(pp \to B\bar B \to tW/bZ/bH + X\)}

\subsection*{Process}
\textbf{Standard notation:} \(pp \to B\bar B \to tW/bZ/bH + X\).
This entry covers LHC direct searches for pair production of a charge
\(-1/3\) vector-like bottom partner \(B\), a custodial fermion partner
that can decay through \(B\to tW\), \(B\to bZ\), and \(B\to bH\).
The production mode is QCD pair production; the interpretation depends on
the assumed branching-fraction point in the \(tW\), \(bZ\), \(bH\) simplex.

\subsection*{Current best limit(s)}
The canonical PDG 2025 \(b'(-1/3)\) listing gives three directly relevant
pair-production lower mass limits at \(95\%~\mathrm{CL}\):
\[
  m_B > 1.57~\mathrm{TeV}\quad [\mathcal{B}(B\to Hb)=1],
\]
\[
  m_B > 1.54~\mathrm{TeV}\quad [\mathcal{B}(B\to Zb)=1],
  \qquad
  m_B > 1.56~\mathrm{TeV}\quad [\mathcal{B}(B\to Wt)=1].
\]
The \(Hb\) and \(Zb\) values are the CMS Run-2 bottom-type VLQ search
\texttt{arXiv:2402.13808}; the \(Wt\)-saturated value is the CMS Run-2
leptonic VLQ search \texttt{arXiv:2209.07327}.  See
\texttt{flavor\_catalog/references/CR004/pdg2025\_bprime\_listing.txt},
\texttt{arxiv\_2402\_13808.txt}, \texttt{arxiv\_2209\_07327.txt}, and the
HEPData record \texttt{hepdata\_2024\_bvlq\_record.txt}.  PDG also lists
single-production bounds under additional coupling assumptions; those are
not promoted here because CR004 is the pair-production process.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In custodial RS and composite-Higgs language, the \(B\) state is a physical
fermion resonance, not the KK gluon itself.  A direct \(B\bar B\) search
therefore constrains \(m_B\) under a specified custodial multiplet and decay
pattern; it becomes a constraint on \(M_{\mathrm{KK}}\) only after choosing
the model relation between the light bottom partner and the gauge/fermion
KK scale.  Pair production is comparatively robust because it is QCD driven,
but the mass exclusion still depends on the signal width, the allowed
decays, and the branching fractions into \(tW\), \(bZ\), and \(bH\).

For the anarchic-flavor pipeline in this repo, CR004 is a cross-check rather
than the leading bound.  The rc1.1 quark-scan methodology note reports
\(M_{\mathrm{KK}}^{\min}(p50,g_\ast=3)=47.26~\mathrm{TeV}\) from the
low-energy flavor scan, with \(127.13~\mathrm{TeV}\) at \(95\%\) acceptance.
That scale is far above the present direct \(B\)-partner reach near
\(1.5~\mathrm{TeV}\).  The collider entry is still useful for non-anarchic
RS variants, custodial spectra where fermion partners sit well below the
gauge KK scale, or benchmark points tuned to evade the low-energy flavor
envelope.

\subsection*{Post-2010 developments}
The pre-LHC RS-motivated baseline is Contino--Servant
\texttt{arXiv:0801.1679}, which emphasized same-sign dileptons from
\(B,T_{5/3}\to Wt\) in custodial top-partner spectra.  Post-2010 LHC work
turned that benchmark strategy into broad branching-fraction searches:
\texttt{arXiv:1808.02343} combined ATLAS \(13~\mathrm{TeV}\) searches across
the \(T\) and \(B\) decay simplex; \texttt{arXiv:2008.09835} made CMS
fully hadronic \(bH/bZ\) final states competitive with leptonic channels;
\texttt{arXiv:2209.07327} used CMS single-lepton, same-sign dilepton, and
multilepton categories and drives the PDG \(B\to Wt\) corner; and
\texttt{arXiv:2210.15413} plus \texttt{arXiv:2212.05263} are the full
Run-2 ATLAS \(Z+\)third-generation and high-\(E_T^{\rm miss}\) cross-checks.
The current CMS \texttt{arXiv:2402.13808} result added a \(0\ell/2\ell\)
combination with HEPData exclusion contours over the \(bH\), \(bZ\), and
\(tW\) branching simplex.  The CMS \texttt{arXiv:2405.17605} review is used
as a synthesis of the Run-2 VLQ program, not as a new measured limit.

\subsection*{Constraint validity and model dependence}
The quoted limits are valid as direct LHC mass-exclusion statements for
prompt, narrow enough, pair-produced \(B\) quarks with the stated branching
assumptions.  They are not inclusive limits on every custodial-RS bottom
partner.  A broad resonance, nonstandard cascade decays, additional nearly
degenerate partners, altered \(B\)-tag/Higgs/Z acceptances, or branching
fractions spread across several modes can move the bound.  A single
production bound can reach higher masses, but it is controlled by
electroweak mixing/coupling choices and is therefore not the canonical CR004
pair-production observable.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required code-coverage grep over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no direct collider
constraint, VLQ object, branching-simplex filter, or ATLAS/CMS/HEPData
limit ingestion.  The collider/VLQ query returned only
\texttt{tests/test\_alpha\_s.py:88--89}, a \(\alpha_s\) CMS/RunDec example,
not an LHC search.  Nearby evidence is flavor-only:
\texttt{scanParams/scan.py:399--429} computes \(M_{\mathrm{KK}}\) for a
scan row and \texttt{scanParams/scan.py:523--535} applies the
\(\mu\to e\gamma\) check, while
\texttt{quarkConstraints/scan.py:359--380} maps \(\Lambda_{\rm IR}\) to
\(M_{\mathrm{KK}}\) and evaluates \(\Delta F=2\) constraints.

Exact queries recorded in the worklog include:
\texttt{rg -n -i "vector[-\_]?...|CMS" ...},
\texttt{rg -n "collider|LHC|ATLAS|CMS|HEPData|mass.?limit|..." ...}, and
\texttt{rg -n "M\_KK|MKK|KK|Mmin|M\_min|Mkk|mKK" ...}.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A faithful implementation needs external LHC likelihoods or
a reinterpretation chain such as CheckMATE, MadAnalysis5, or SModelS, plus
signal generation for the custodial spectrum, widths, branching fractions,
detector acceptances, and correlations across final states.  A simple
hard-coded mass veto would be easy but would be misleading for RS scans
because \(m_B/M_{\mathrm{KK}}\), widths, and \(B\to tW,bZ,bH\) fractions are
model dependent.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2025\_BPrimeListing},
\texttt{ContinoServant2008\_TopPartners},
\texttt{ATLAS2018\_VLQCombination},
\texttt{CMS2020\_BVLQFullyHadronic},
\texttt{CMS2023\_VLQLeptonic},
\texttt{ATLAS2023\_ZThirdGen},
\texttt{ATLAS2023\_METPartners},
\texttt{CMS2024\_BVLQDilepHad},
\texttt{HEPData2024\_BVLQContours}, and
\texttt{CMS2025\_VLQReview}.
