% Flavor catalog per-process entry.
% process_id: CR002
% family: collider_rs
% owner_agent_id: PKA-CR002
% writer_agent_id: WA
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR002.yaml

\section{\texorpdfstring{\(T_{5/3}\bar T_{5/3}\) Pair Production}{T5/3 Tbar5/3 Pair Production}}

\subsection*{Process}
Collider RS resonance / partner search framing: CR002 is the direct LHC
search for the exotic-charge custodial top partner that decays through
\(T_{5/3}\to W^+t\).  The process is
\[
  pp \to T_{5/3}\bar T_{5/3}
  \to W^+ t\, W^- \bar t ,
\]
equivalently \(pp\to X_{5/3}\bar X_{5/3}\) in CMS notation.  The distinctive
experimental handle is the same-sign dilepton or one-lepton plus jets topology
from the four \(W\) bosons in the \(t\bar tWW\) final state.

\subsection*{Current best limit(s)}
The canonical PDG-equivalent entry is the current PDG encoder q009 mass limit,
\[
  m_{t'(5/3)} > 1460~\mathrm{GeV}\qquad(95\%~\mathrm{CL}),
\]
from the ATLAS full-Run-2 search in \(139~\mathrm{fb}^{-1}\) of
\(\sqrt{s}=13~\mathrm{TeV}\) data, for the exclusive \(B/X\to Wt\)
interpretation.  The same ATLAS paper quotes a stronger
\(1.59~\mathrm{TeV}\) lower limit for a mass-degenerate vector-like doublet,
which is a different branching-ratio and spectrum benchmark.

The strongest CMS pair-production limits in the PDG table are
\(m_{X_{5/3}}>1.33~\mathrm{TeV}\) for the right-handed coupling benchmark and
\(m_{X_{5/3}}>1.30~\mathrm{TeV}\) for the left-handed benchmark, using
\(35.9~\mathrm{fb}^{-1}\) at \(\sqrt{s}=13~\mathrm{TeV}\).  Earlier ATLAS
same-charge-lepton data gave \(m_{T_{5/3}}>1.19~\mathrm{TeV}\) for
pair production alone, and a coupling-dependent pair-plus-single-production
interpretation reached \(m_{T_{5/3}}>1.6~\mathrm{TeV}\).

\subsection*{Relevance to RS}
CR002 is a direct LHC constraint on the custodial top-partner spectrum, not a
low-energy \(\Delta F=1\) or \(\Delta F=2\) observable.  It is therefore most
useful as a cross-check on non-anarchic or compressed custodial-RS spectra in
which the lightest fermion partners can be much lighter than the KK gauge
scale.  In an anarchic-flavor RS scan, the repo-local rc1.1 quark methodology
already reports
\[
  M_{KK}^{\min,p50}(\,g_\ast=3\,)=47.26~\mathrm{TeV},
\]
so a \(T_{5/3}\) direct-search reach near the \(1.5~\mathrm{TeV}\) scale is
not the leading constraint on the default anarchic-flavor ensemble.

The collider number constrains a physical custodial-partner mass under
specific LHC simplified-model assumptions.  Mapping it onto \(M_{KK}\) needs a
model-dependent relation between the fermion-partner spectrum, top
compositeness, and the gauge KK scale; it should not be treated as a direct
cut on the same \(M_{KK}\) variable used by the quark-flavor scan.

\subsection*{Post-2010 developments}
The LHC program closely follows the Contino--Servant and Mrazek--Wulzer
same-sign-dilepton motivation:
\begin{itemize}
  \item CMS arXiv:1312.2391 established the first LHC same-sign-dilepton
  charge-\(5/3\) limit, excluding masses below \(800~\mathrm{GeV}\) at
  \(\sqrt{s}=8~\mathrm{TeV}\) for exclusive \(tW\) decay.
  \item CMS arXiv:1705.10967 moved the search to \(\sqrt{s}=13~\mathrm{TeV}\)
  and combined same-sign dilepton with single-lepton final states, reaching
  \(1.02~\mathrm{TeV}\) and \(0.99~\mathrm{TeV}\) for the right- and
  left-handed coupling benchmarks.
  \item ATLAS arXiv:1807.11883 used same-charge leptons and \(b\)-jets to set
  the \(1.19~\mathrm{TeV}\) pair-production limit and to demonstrate the
  stronger but coupling-dependent single-production interpretation.
  \item CMS arXiv:1810.03188 increased the dataset to \(35.9~\mathrm{fb}^{-1}\)
  and produced the \(1.33~\mathrm{TeV}\) / \(1.30~\mathrm{TeV}\) CMS Run-2
  limits.
  \item ATLAS arXiv:2212.05263 used the full Run-2 one-lepton plus
  missing-transverse-momentum search to provide the current PDG-leading
  \(1.46~\mathrm{TeV}\) exclusive \(B/X\to Wt\) limit.
\end{itemize}

\subsection*{Validity / model dependence}
The pair-production cross section is QCD dominated, so the production rate is
less sensitive to the \(T_{5/3}Wt\) electroweak coupling than single
production.  The acceptance and the quoted mass limit are nevertheless tied to
the assumed prompt decay pattern, top-partner width, branching fractions, and
event topology.  If the \(T_{5/3}\) has sizable non-\(tW\) decays, cascade
decays into other custodial states, a broad width, or a compressed spectrum,
the simple PDG mass bound is not automatically applicable.  The stronger
single-production reinterpretation is explicitly coupling dependent and should
be catalogued separately from the pair-production CR002 entry if it is ever
implemented.

\subsection*{Code coverage}
\textbf{NO.}  A collider-specific grep over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no \(T_{5/3}\),
\(X_{5/3}\), VLQ, top-partner, collider, or LHC direct-search implementation.
The adjacent code is low-energy RS machinery: \texttt{quarkConstraints/modern/scan.py:1230}
maps \(\Lambda_{\mathrm{IR}}\) to \(M_{KK}\), \texttt{quarkConstraints/modern/scan.py:1254}
stores that scan-point \(M_{KK}\), \texttt{quarkConstraints/couplings.py:103}
defines mass-basis KK-gluon couplings, \texttt{quarkConstraints/couplings.py:116}
describes the enhanced 5D KK-gluon coupling, and
\texttt{quarkConstraints/deltaf2.py:1} identifies the implemented exclusion
slice as a tree-level KK-gluon-inspired \(\Delta F=2\) benchmark.  The
matching layer itself notes at \texttt{quarkConstraints/modern/matching.py:240}
that it is not a full operator-complete EFT/RG package.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A faithful implementation would need at least a recast pipeline:
event generation for \(T_{5/3}\bar T_{5/3}\), decay and branching-ratio
control, detector-level efficiencies or public likelihoods, and validation
against ATLAS/CMS exclusion tables.  External reinterpretation tools such as
CheckMATE, MadAnalysis5, or SModelS would be more realistic than a
hand-written scan cut.

\subsection*{Key references}
\texttt{PDGEncoderQ009\_TPrime5Over3};
\texttt{ATLAS2023\_VLQ\_MET};
\texttt{CMS2019\_X53\_Run2};
\texttt{ATLAS2018\_SameCharge\_BJets};
\texttt{CMS2017\_X53\_13TeV};
\texttt{CMS2014\_X53\_8TeV};
\texttt{ContinoServant2008\_TopPartners};
\texttt{MrazekWulzer2009\_TopPartners}.
