% Flavor catalog per-process template.
% process_id: CR008
% family: collider_rs
% owner_agent_id: PKA-CR008
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR008.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(pp\to T\bar T\) Singlet VLQ \(T\to bW,tZ,tH\)}{pp to T Tbar singlet VLQ T to bW, tZ, tH}}

\subsection*{Process}
This entry covers direct LHC searches for QCD pair production of a charge
\(+2/3\) vector-like top partner \(T\), treated as an electroweak singlet,
\[
  pp\to T\bar T,\qquad T\to bW,\ tZ,\ tH .
\]
It is the non-custodial singlet counterpart of heavier-partner searches in the
custodial-RS collider family.  The experimentally standard singlet benchmark
uses \({\cal B}(T\to Wb:Ht:Zt)=1/2:1/4:1/4\) at high mass.

\subsection*{Current best limit(s)}
The process-specific PDG/ATLAS benchmark limit is
\[
  m_T > 1.36~{\rm TeV}\quad (95\%~{\rm CL})
\]
for pair-produced isospin-singlet \(T\) quarks with
\({\cal B}(T\to Wb:Ht:Zt)=1/2:1/4:1/4\).  The source is the ATLAS Run-2
lepton+jets search using 140 fb\(^{-1}\) at \(\sqrt{s}=13\) TeV, recorded
locally in \texttt{atlas\_2024\_arxiv2401\_17165.txt} and summarized in the
PDG 2025 \(t'\) searches listing
\texttt{pdg2025\_tprime\_vlq\_limits.txt}.

The strongest broad-envelope Run-2 statement is the CMS leptonic-channel
combination: \(T\bar T\) production is excluded for \(T\) masses up to
1.54 TeV depending on branching fractions, and masses below 1.48 TeV are
excluded for all decays to third-generation quarks.  This is not a single
singlet branching-ratio point, but it is useful as a model-independent
cross-check over the \(bW/tZ/tH\) branching triangle
(\texttt{cms\_2023\_arxiv2209\_07327.txt}).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
In warped models, a charge-\(2/3\) top partner is a direct handle on the
fermionic top-sector resonance spectrum.  A singlet \(T\) search constrains a
specific light-partner limit: QCD pair production is essentially set by
\(m_T\), while the search interpretation depends on the assumed standard
decays \(T\to bW,tZ,tH\) and on whether exotic or cascade decays are absent.
For a non-custodial singlet top partner, the ATLAS benchmark maps to
\(m_T>1.36\) TeV at 95\% CL under the standard singlet branching ratios.

This is not competitive with the anarchic-flavor mass reach already implied by
the low-energy catalog.  The quark-scan methodology note quotes the rc1.1
headline crossing \(M_{KK}^{\mathrm{min},p50}=47.26\) TeV at \(g_*=3\).  A direct
singlet-top-partner bound near 1.4--1.5 TeV therefore works mainly as a
collider cross-check, as leverage for non-anarchic or alignment-tuned RS
variants, or as a constraint on scenarios where the lightest fermion partner
is parametrically lighter than the gauge KK scale.

\subsection*{Post-2010 developments}
The post-2010 history is driven by the LHC moving from Run-1 branching-fraction
triangles to full Run-2 multichannel combinations.  The ATLAS 8 TeV
lepton+jets search set \(T\)-mass lower limits over the \(bW/tZ/tH\) plane in
the 715--950 GeV range.  CMS then used the first 13 TeV data with boosted
jet-substructure techniques and obtained a singlet \(T\) limit of 860 GeV.
With 35.9 fb\(^{-1}\), CMS combined single-lepton, same-sign dilepton, and
multilepton channels and pushed \(T\) limits to 1.14--1.30 TeV depending on
branching fractions.  ATLAS full Run-2 searches added complementary
lepton+jets and large-\(E_T^{\rm miss}\) selections; the current singlet
\(bW/tH/tZ=1/2:1/4:1/4\) point is 1.36 TeV from the 2024 lepton+jets search,
while the CMS full Run-2 leptonic search gives the stronger 1.48 TeV
all-branching-envelope statement.

\subsection*{Constraint validity and model dependence}
The mass limits are collider exclusions, not generic RS bounds.  They assume
prompt pair-produced narrow vector-like quarks, standard decays to
third-generation quarks plus \(W/Z/H\), and no sizable exotic modes such as
cascade decays through additional composite-sector states.  Pair production is
less coupling-dependent than single production, but the final-state acceptance
is still branching-ratio dependent.  A model with displaced decays, large
widths, light neutral states, non-third-generation couplings, or a compressed
spectrum would need a dedicated reinterpretation.

\subsection*{Code coverage in this repo}
\textbf{NO}.  Required greps over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no VLQ, top-partner, ATLAS/CMS direct-search, or recast
implementation.  Adjacent evidence confirms the existing pipeline computes
\(M_{KK}\) and low-energy filters only: \texttt{scanParams/scan.py:399}
constructs \(M_{KK}=\xi_{KK}\Lambda_{\rm IR}\),
\texttt{scanParams/scan.py:523}--\texttt{scanParams/scan.py:535} applies the
\(\mu\to e\gamma\) filter, and \texttt{quarkConstraints/scan.py:377}--
\texttt{quarkConstraints/scan.py:380} evaluates the quark \(\Delta F=2\)
constraints.  There is no collider likelihood, cross-section limit, or
branching-fraction-triangle filter.

\subsection*{Implementation difficulty}
\textbf{HIGH}.  A live constraint would require an external collider-recast
layer: signal generation or tabulated cross sections, branching-ratio
bookkeeping, acceptance and efficiency maps or full likelihoods, and validation
against ATLAS/CMS exclusions.  Practical implementation would likely use or
interface to CheckMATE, MadAnalysis5, SModelS, Rivet/Contur, or collaboration
HEPData likelihood material rather than a lightweight in-repo formula.

\subsection*{Key references}
\texttt{PDG2025\_TprimeVLQ}; \texttt{ATLAS2024\_TsingletPair};
\texttt{CMS2023\_VLQPairLeptonic}; \texttt{ATLAS2015\_VLQPair8TeV};
\texttt{CMS2017\_VLQPairSingleLepton}; \texttt{CMS2018\_VLQPairLeptonic};
\texttt{ATLAS2023\_VLQPairMET}; \texttt{AguilarSaavedra2009\_TopPartners};
\texttt{AguilarSaavedraEtAl2013\_VLQHandbook};
\texttt{LariEtAl2008\_ColliderFlavourHighQ}.
