% Flavor catalog per-process template.
% process_id: CR001
% family: collider_rs
% owner_agent_id: PKA-CR001
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR001.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(pp \to g^{(1)}_{\rm KK}\to t\bar t\)}{pp to KK gluon to ttbar}}

\subsection*{Process}
This entry covers direct LHC resonance searches for the first color-octet
Kaluza--Klein gluon in warped extra dimensions, in the standard topology
\(pp\to g^{(1)}_{\rm KK}\to t\bar t\).  It is a high-mass tail search for a
spin-1 KK gauge resonance, not a low-energy flavor observable and not a
separate vector-like-partner search.

\subsection*{Current best limit(s)}
The current best direct \(t\bar t\) benchmark bound is the CMS Run-2
all-topology search CMS-B2G-25-009, \texttt{arXiv:2603.23454}.  Using
\(138\,{\rm fb}^{-1}\) of \(13\) TeV data and the 0-, 1-, and 2-lepton
\(t\bar t\) final states, CMS finds no significant excess and excludes the
Randall--Sundrum KK-gluon benchmark over \(0.5<m_{g_{\rm KK}}<5.5\) TeV at
95\% CL.  The sidecar records this as the canonical current lower edge,
\(m_{g_{\rm KK}}>5.5\) TeV for this benchmark, with the interval wording kept
explicit in \texttt{pdg\_or\_equivalent.values}.

PDG Live entry \texttt{S071KKG} is still useful as a review-table snapshot but
is not the latest LHC result for this topology.  It lists the older
ATLAS lepton-plus-jets benchmark value \(m_{g_{\rm KK}}>3.8\) TeV at 95\% CL
for a \(\Gamma/m=15.3\%\) warped-extra-dimension benchmark.  CMS
\texttt{arXiv:1810.05905} superseded that scale in a 2016-data combination
with \(0.50<m_{g_{\rm KK}}<4.55\) TeV excluded, and CMS-B2G-25-009 is the
current best result.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
The search constrains the physical first KK-gluon resonance mass in a specified
RS collider benchmark: production through the color-octet vector state,
template assumptions for its width and couplings, and a large branching
fraction to \(t\bar t\).  This is the canonical collider signature of bulk RS
because the IR-localized top quark couples strongly to the KK gluon.

For the anarchic-flavor scan in this repository, the direct reach is not the
leading mass constraint.  The methodology note's RUNA reference scan gives
\(\MKKmin(p50,\gsstar=3)=47.26\) TeV and
\(\MKKmin(p95,\gsstar=3)=127.13\) TeV from low-energy \(\Delta F=2\) flavor
constraints.  A \(5.5\) TeV direct \(g_{\rm KK}\to t\bar t\) exclusion is
therefore mainly a cross-check for the anarchic pipeline and a useful handle on
non-anarchic, aligned, or otherwise collider-visible RS variants where the
flavor bound is weakened.

\subsection*{Post-2010 developments}
The collider history starts from the Lillie--Randall--Wang boosted-top
proposal, \texttt{hep-ph/0701166}, which identified \(g_{\rm KK}\to t\bar t\)
as the characteristic bulk-RS LHC signal.  Post-2010 searches improved by
raising the collision energy, adding luminosity, and extending top-tagging
across boosted decay topologies.

ATLAS \texttt{arXiv:1207.2409} used \(2.05\,{\rm fb}^{-1}\) at 7 TeV and
excluded \(m_{g_{\rm KK}}<1.5\) TeV, establishing the boosted lepton-plus-jets
strategy.  ATLAS \texttt{arXiv:1305.2756} used the full 2011
\(4.7\,{\rm fb}^{-1}\) 7 TeV sample and pushed the broad RS KK-gluon exclusion
to \(m_{g_{\rm KK}}<2.07\) TeV.  Early 13 TeV CMS work,
\texttt{arXiv:1704.03366}, combined boosted lepton-plus-jets and fully
hadronic channels and improved sensitivity above 2 TeV.

ATLAS \texttt{arXiv:1804.10823} used \(36.1\,{\rm fb}^{-1}\) at 13 TeV in the
lepton-plus-jets channel; this is the ATLAS result behind the PDG Live
\(3.8\) TeV benchmark row.  CMS \texttt{arXiv:1810.05905} then combined the
dilepton, single-lepton, and all-hadronic \(t\bar t\) topologies in
\(35.9\,{\rm fb}^{-1}\), excluding \(0.50<m_{g_{\rm KK}}<4.55\) TeV.  ATLAS
\texttt{arXiv:2005.05138} brought the all-hadronic channel to the
\(139\,{\rm fb}^{-1}\) Run-2 scale, while ATLAS \texttt{arXiv:2512.17856}
updated one- and two-lepton final states with \(140\,{\rm fb}^{-1}\) and
explicit KK-gluon templates over a \(0.4\)--\(5.0\) TeV search range.  CMS
\texttt{arXiv:2603.23454} is the current full-Run-2 all-topology update and
sets the \(5.5\) TeV limit used here.

\subsection*{Constraint validity and model dependence}
The limit is not a model-independent lower bound on every RS \(M_{\rm KK}\).
It assumes the signal model used by the experimental template: the KK-gluon
production rate, width, chiral couplings, and \(t\bar t\) branching fraction.
If the KK gluon has sizable decays to vector-like quarks, other BSM states, or
light-flavor channels, the \(t\bar t\) branching fraction and line shape change.
Very broad resonances, interference with SM \(t\bar t\), or altered light-quark
couplings also require reinterpretation rather than direct use of the quoted
mass edge.

For custodial RS, this entry constrains the KK gauge resonance sector.  It does
not by itself constrain custodial fermion partners such as \(T_{5/3}\); those
require separate heavy-partner searches and branching assumptions.

\subsection*{Code coverage in this repo}
\textbf{NO} for a direct-collider \(g_{\rm KK}\to t\bar t\) constraint.  The
direct-search grep over \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no \texttt{ttbar}, top-pair-resonance, LHC, CheckMATE,
MadAnalysis5, or SModelS implementation.

There is adjacent low-energy KK-gluon infrastructure only:
\texttt{quarkConstraints/couplings.py:1} defines mass-basis KK-gluon couplings,
\texttt{quarkConstraints/deltaf2.py:1} describes a tree-level KK-gluon-inspired
\(\Delta F=2\) matching layer, and \texttt{quarkConstraints/scan.py:359-380}
computes \(M_{\rm KK}\) and evaluates flavor diagnostics.  The modern matching
wrapper also states that it is not a full operator-complete EFT/RG package
(\texttt{quarkConstraints/modern/matching.py:241-243}).  None of these files
implements a collider likelihood or filters scan points on direct LHC
resonance exclusions.

\subsection*{Implementation difficulty}
\textbf{HIGH}.  A live constraint would need either the experimental likelihood
or an external reinterpretation chain such as CheckMATE, MadAnalysis5, SModelS,
or a dedicated recast using generated \(pp\to g_{\rm KK}\to t\bar t\) samples,
top-tagging efficiencies, mass-resolution effects, and width/interference
systematics.  A simple mass cut would be acceptable only as a documented
benchmark overlay, not as a robust constraint on the general RS parameter
space.

\subsection*{Key references}
\texttt{CMS2026\_TTbarResonance}; \texttt{HEPData2026\_CMSB2G25009};
\texttt{PDGLive2026\_S071KKG}; \texttt{CMS2019\_TTbarResonance};
\texttt{ATLAS2025\_TTbarResonance}; \texttt{ATLAS2020\_HadronicTTbar};
\texttt{ATLAS2018\_LeptonJetsTTbar}; \texttt{ATLAS2013\_LeptonJetsTTbar};
\texttt{ATLAS2012\_BoostedTTbar}; \texttt{CMS2017\_BoostedTTbar};
\texttt{LillieRandallWang2007\_BulkRSKKGluon};
\texttt{QuarkScanMethodology2026\_MKK}.
