% Flavor catalog per-process entry.
% process_id: CR003
% family: collider_rs
% owner_agent_id: PKA-CR003
% writer_agent_id: WA
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR003.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(T\bar T\) Pair Production}{T Tbar Pair Production}}

\subsection*{Process}
Collider RS resonance / partner search framing: CR003 is the direct LHC
search for a custodial charge-\(2/3\) top partner produced in pairs.  The
standard topology is
\[
  pp\to T\bar T\to tZ/tH/bW+X .
\]
This entry covers searches for pair production of a charge-\(2/3\)
vector-like top partner \(T\), often denoted \(t'\) in PDG listings, with
decays to third-generation quarks and electroweak or Higgs bosons.

\subsection*{Current best limit(s)}
The current PDG Live \(Q009TPP\) listing records the relevant pair-production
mass exclusions.  The canonical 95\% CL entries for CR003 are:
\[
\begin{array}{lll}
\hline
\hbox{Assumption} & \hbox{Observed lower limit} & \hbox{Primary source} \\
\hline
{\cal B}(T\to Wb)=1 & m_T>1.70~\mathrm{TeV} &
\hbox{ATLAS 2024, PDG AAD 24N} \\
{\cal B}(T\to Wb:Ht:Zt)=1/2:1/4:1/4 & m_T>1.36~\mathrm{TeV} &
\hbox{ATLAS 2024, PDG AAD 24N} \\
{\cal B}(T\to Zt)=1 & m_T>1.60~\mathrm{TeV} &
\hbox{ATLAS 2023, PDG AAD 23AV} \\
{\cal B}(T\to Ht)=1 & m_T>1.50~\mathrm{TeV} &
\hbox{CMS 2023, PDG TUMASYAN 23V} \\
\hbox{all third-generation decay mixtures} & m_T>1.48~\mathrm{TeV} &
\hbox{CMS 2023} \\
\hline
\end{array}
\]
The strict metadata for these mass-exclusion values is in
\texttt{CR003.yaml} under \texttt{pdg\_or\_equivalent}; luminosity,
\(\sqrt{s}\), and channel details are kept as supporting inputs rather than
promoted observables.

\subsection*{Relevance to RS}
CR003 constrains the physical mass of a charge-\(2/3\) custodial fermion
partner, not the KK-gluon mass or the flavor-anarchy matching scale by itself.
For QCD pair production the production rate is comparatively model-independent,
but the acceptance and mass limit depend on the assumed branching fractions
among \(Wb\), \(Zt\), and \(Ht\).  A custodial-RS model can map the lightest
top-partner mass and branching ratios to the 5D fermion representation, IR
localization, and electroweak embedding; absent that map, the LHC number is a
direct-search cross-check rather than a universal RS-flavor bound.

The current low-energy quark-flavor scan already quotes
\(M_{KK}^{\min}(p50,g_\ast=3)=47.26~\mathrm{TeV}\) in
\texttt{docs/quark\_scan\_methodology\_note.tex}.  The \(T\)-partner direct
limits above sit in the \(1.36\)--\(1.70~\mathrm{TeV}\) range, so they do not
compete with the anarchic-flavor \(M_{KK}\) envelope.  Their value is instead
to test non-anarchic corners, spectra with light custodial fermions, or models
where collider partners are not tied tightly to the flavor-setting KK scale.

\subsection*{Post-2010 developments}
The Contino--Servant top-partner paper set the custodial-partner collider
motivation before LHC data.  The LHC search history then moved from early
same-sign and lepton+jets top-partner searches to full-Run-2
branching-fraction scans.  ATLAS arXiv:1707.03347 established a 13 TeV
lepton+jets \(Wb\)-targeted search with boosted \(W\) reconstruction.  ATLAS
arXiv:1803.09678 and arXiv:1808.01771 broadened the coverage to \(Ht\),
\(Zt\), multi-\(b\), and all-hadronic final states.  ATLAS arXiv:2210.15413
used the full Run-2 \(Z\)-lepton channel and gives the strongest pure-\(Zt\)
row in the PDG table.  CMS arXiv:2209.07327 combined single-lepton,
same-sign dilepton, and multilepton channels and gives the robust
all-decay-mixture exclusion.  ATLAS arXiv:2401.17165 is the current
PDG-leading pure-\(Wb\) and singlet \(Wb:Ht:Zt\) source.

\subsection*{Validity / model dependence}
These limits assume prompt pair production of narrow vector-like quarks and
specific decay-mode hypotheses.  The common simplified-model assumption is
that \({\cal B}(T\to Wb)+{\cal B}(T\to Zt)+{\cal B}(T\to Ht)=1\).  Exotic
decays, sizable widths, altered electroweak couplings, long-lived partners, or
compressed spectra can invalidate a direct reading of the quoted mass limits.
Single-production searches can reach higher masses for chosen couplings, but
they are not the CR003 observable because the assigned process is pair
production.

\subsection*{Code coverage}
\textbf{NO.}  Targeted greps across \texttt{quarkConstraints/}, \texttt{qcd/},
\texttt{flavorConstraints/}, \texttt{neutrinos/}, \texttt{yukawa/},
\texttt{warpConfig/}, \texttt{solvers/}, \texttt{scanParams/}, and
\texttt{tests/} found no implementation of VLQ \(T\)-pair collider limits,
ATLAS/CMS direct-search likelihoods, HEPData exclusion contours, or a
top-partner mass filter.  Adjacent evidence is limited to KK-scale and
flavor-filter plumbing: \texttt{quarkConstraints/modern/scan.py:1230}
constructs \texttt{M\_KK} for scan points, \texttt{quarkConstraints/modern/scan.py:1492}
builds failing-system lists from flavor ratios, \texttt{quarkConstraints/modern/scan.py:1503}
restricts those systems to \(\epsilon_K,K,B_d,B_s,D^0\), and
\texttt{quarkConstraints/modern/evaluation.py:643} starts the \(M_{KK}\)
resolution used for KK-gluon matching.  The current quark scope is summarized
as MFV fitting at \texttt{quarkConstraints/README.md:34}, KK-scale conventions
at \texttt{quarkConstraints/README.md:36}, and a \(\Delta F=2\) exclusion
slice at \texttt{quarkConstraints/README.md:38}; none of those lines is a
collider top-partner filter.

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A faithful live constraint needs either a simplified
acceptance map over \({\cal B}(Wb),{\cal B}(Zt),{\cal B}(Ht)\) or an external
reinterpretation workflow such as CheckMATE, MadAnalysis5, SModelS, or a
collaboration likelihood/HEPData grid.  It also needs an RS spectrum model
that predicts the lightest custodial \(T\) mass, width, and branching
fractions.  The current code has neither collider-event machinery nor a
top-partner spectrum/decay module.

\subsection*{Key references}
\texttt{PDGLive2026\_Q009TPP\_TprimePair};
\texttt{ATLAS2024\_VLQPairWb\_Run2};
\texttt{ATLAS2023\_VLQPairZt\_Run2};
\texttt{CMS2023\_VLQPairLeptonic\_Run2};
\texttt{ATLAS2017\_VLQPairWb\_13TeV};
\texttt{ATLAS2018\_VLQPairMultiB};
\texttt{ATLAS2018\_VLQPairHadronic};
\texttt{ContinoServant2008\_TopPartners};
\texttt{QuarkScanMethodology2026\_MKKEnvelope}.
