% Flavor catalog per-process template.
% process_id: CR014
% family: collider_rs
% owner_agent_id: PKA-CR014
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: CR014.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{\texorpdfstring{\(pp \to t\bar t t\bar t\) Four-Top Production}{pp to t tbar t tbar Four-Top Production}}

\subsection*{Process}
This entry covers Standard-Model and beyond-the-Standard-Model production of
four top quarks at the LHC, \(pp\to t\bar t t\bar t\).  In the
\texttt{collider\_rs} scope it is a direct-collider handle on top-philic
resonances, heavy top-partner sectors that feed multi-top final states, and
four-top contact operators.  It is not a single inclusive \(M_{\rm KK}\)
observable: a collider interpretation must specify the resonance spin, width,
couplings, production mechanism, and branching fractions.

\subsection*{Current best limit(s)}
The PDG 2025 top-quark review records the Run-2 observation measurements as the
canonical inclusive \(t\bar t t\bar t\) cross-section inputs.  ATLAS measures
\(\sigma(pp\to t\bar t t\bar t)=22.5^{+6.6}_{-5.5}\,\mathrm{fb}\) in the
multilepton observation analysis, while CMS measures
\(\sigma(pp\to t\bar t t\bar t)=17.7^{+4.4}_{-4.0}\,\mathrm{fb}\) in the
corresponding PDG summary.  The CMS paper gives the same central value with
separate statistical and systematic uncertainties.  These measurements are
higher than the Standard-Model reference rate but compatible within current
uncertainties, so the inclusive four-top result is currently a
measurement and reinterpretation input rather than a standalone RS mass
exclusion.

For a direct four-top resonance interpretation, the most recent official CMS
public result found in this pass is CMS-B2G-25-005, also summarized in
arXiv:2604.14058.  It searches for resonances in four-top events with two
leptons using \(13\) and \(13.6\) TeV data.  CMS sets upper limits over
resonance masses from \(500\,\mathrm{GeV}\) to \(4\,\mathrm{TeV}\) and relative
widths from \(4\%\) to \(50\%\); for a top-philic vector mediator with
\(\Gamma/m=50\%\), masses are excluded at \(95\%\) CL up to
\(850\,\mathrm{GeV}\) observed.  ATLAS provides a complementary top-philic
\(Z'\) search in the single-lepton channel with observed \(95\%\) CL
cross-section upper limits ranging from \(21\) to \(119\,\mathrm{fb}\) across
its simplified-model parameter choices.

\subsection*{Relevance to RS / anarchic-flavor pipeline}
Four-top production is relevant to custodial or composite RS because the top
quark is typically the most IR-localized Standard-Model fermion.  A KK gluon,
composite vector, or heavy top partner can couple preferentially to tops and
produce \(t\bar t t\bar t\) through associated production
\(pp\to t\bar t X\), \(X\to t\bar t\), through off-shell exchange, or through
the low-energy four-top contact operators used in EFT reinterpretations.  The
observable therefore probes the same top-compositeness sector that direct
\(t\bar t\) resonance and vector-like-quark searches probe, but it does so in a
more model-dependent topology.

The anarchic-flavor pipeline is already dominated by low-energy quark flavor.
The methodology note reports the corrected RS-anarchy median bound
\(M_{\rm KK}^{\min}(p50,g_s^\star=3)=47.26\,\mathrm{TeV}\).  That scale is far
above the present four-top resonance reach, which is sub-TeV for the broad
top-philic vector benchmark in CMS-B2G-25-005 and at the few-TeV level only as a
model-dependent cross-section search.  Consequently CR014 is a PRIMARY
collider-RS cross-check and a useful handle on aligned, custodial, or
non-anarchic spectra, but it is not the leading bound for the anarchic
low-energy flavor scan.

\subsection*{Post-2010 developments}
CMS opened the published LHC search history with the 8 TeV lepton-plus-jets
analysis in arXiv:1409.7339.  The importance of that result is historical: it
established the multivariate strategy for a final state with a very small SM
rate and large \(t\bar t+\)jets backgrounds.

The first 13 TeV CMS searches, arXiv:1702.06164 and arXiv:1710.10614, moved the
program into Run 2 and separated the lepton-plus-jets/opposite-sign dilepton
and same-sign/multilepton handles.  The multilepton analysis also began using
four-top data to constrain the top-Higgs Yukawa coupling, making the connection
to top compositeness explicit.

ATLAS arXiv:1811.02305 added a 13 TeV single-lepton and opposite-sign dilepton
search and combined it with earlier ATLAS multilepton inputs; CMS
arXiv:1908.06463 then used the full 2016--2018 multilepton data set and added
BSM scalar, pseudoscalar, and EFT interpretations.

The Run-2 evidence and observation stage came from ATLAS arXiv:2106.11683,
CMS arXiv:2303.03864, ATLAS arXiv:2303.15061, and CMS arXiv:2305.13439.
The key changes were full Run-2 luminosity, improved heavy-flavor and lepton
object identification, more powerful multivariate or graph-neural-network
classifiers, and combinations across complementary final states.

The direct resonance branch is now represented by ATLAS arXiv:2304.01678 and
CMS-B2G-25-005/arXiv:2604.14058.  These move beyond an inclusive signal-strength
measurement into explicit top-philic resonance searches, but the exclusions are
still benchmark dependent.

\subsection*{Constraint validity / model dependence}
The inclusive \(t\bar t t\bar t\) cross section is a robust experimental
observable, but it becomes an RS constraint only after specifying a BSM
interpretation.  A broad vector mediator, a scalar or pseudoscalar, a KK gluon,
and a fermionic top partner can produce similar event counts but different
kinematics, interference patterns, and acceptances.  EFT translations are valid
only when the mediator is sufficiently heavier than the resolved event scale;
for lighter or broad resonances a simplified-model or full-model simulation is
needed.

The current top-philic resonance limits assume exclusive or dominant couplings
to top quarks, specified widths, and specific production modes.  A custodial-RS
spectrum with several nearby resonances, non-saturated branching ratio
\(\mathrm{BR}(X\to t\bar t)\), additional decays to top partners, or altered
top-tagging acceptance cannot be read off from the quoted mass number without a
dedicated reinterpretation.

\subsection*{Code coverage in this repo}
\textbf{NO}.  The required CR014 grep found no implementation of four-top,
top-philic-resonance, or direct collider-search constraints in
\texttt{quarkConstraints/}, \texttt{qcd/}, \texttt{flavorConstraints/},
\texttt{neutrinos/}, \texttt{yukawa/}, \texttt{warpConfig/},
\texttt{solvers/}, \texttt{scanParams/}, or \texttt{tests/}.  The exact query
\texttt{rg -n "CR014|four.?top|4.?top|tttt|top.?philic" ...} returned no
matches.  A separate collider-term query found only an unrelated
\texttt{CMS/RunDec} alpha-s test comment in \texttt{tests/test\_alpha\_s.py:89}.

Adjacent evidence confirms that the scan computes low-energy KK-gluon flavor
constraints, not collider limits.  \texttt{quarkConstraints/couplings.py:96}
defines \texttt{compute\_quark\_kk\_gluon\_couplings};
\texttt{quarkConstraints/deltaf2.py:449} defines
\texttt{evaluate\_delta\_f2\_constraints}; and
\texttt{quarkConstraints/scan.py:377} through \texttt{quarkConstraints/scan.py:441}
threads those \(\Delta F=2\) ratios into the quark-scan pass/fail row.  No
analogous module consumes LHC cross sections, resonance mass limits, or
experimental likelihoods.

\subsection*{Implementation difficulty}
\textbf{HIGH}.  A faithful live constraint would require a model-to-collider
chain: RS spectrum generation, production and decay simulation, detector-level
acceptance, and a likelihood or recast for the ATLAS/CMS analyses.  A simple
``\(M_{\rm KK}>850\,\mathrm{GeV}\)'' filter would be misleading because the CMS
number is a broad top-philic vector benchmark, not a generic KK-gluon or
custodial-partner exclusion.  Practical implementation should use an external
reinterpretation tool such as CheckMATE, MadAnalysis5, SModelS where applicable,
or a preserved HEPData/analysis likelihood.

\subsection*{Key references}
\texttt{PDG2025\_TopFourTop};
\texttt{ATLAS2023\_FourTopObservation};
\texttt{CMS2023\_FourTopObservation};
\texttt{CMSB2G25005\_PublicResult};
\texttt{CMS2026\_FourTopResonance};
\texttt{ATLASTopPhilic2024};
\texttt{CaoChenLiu2016};
\texttt{DeBlasEberhardtKrause2018};
\texttt{BanelliEtAl2021\_FourTopOperators};
\texttt{DarmeFuksMaltoni2021\_TopPhilic};
\texttt{QuarkScanMethodology2026}.
