% Flavor catalog per-process entry.
% process_id: K019
% family: kaon
% owner_agent_id: PKA-K019
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K019.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K019: \(K_L \to e^{\pm}\mu^{\mp}\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_L \to e^{\pm}\mu^{\mp}\).  This entry covers
the charged-lepton-flavor-violating two-body decay of the long-lived neutral
kaon, summed over the two charge assignments.  It is a null-search channel:
the Standard Model with only neutrino mixing gives no observable charged-LFV
kaon rate, so any signal would point to new flavor structure.

\subsection*{PDG / equivalent value(s)}
The canonical sidecar value is the PDG 2025 \(K_L^0\) listing limit
\[
  {\cal B}(K_L\to e^{\pm}\mu^{\mp}) < 4.7\times 10^{-12}
  \quad (90\%~{\rm CL}).
\]
The value is listed by PDG as \(\Gamma(e^{\pm}\mu^{\mp})/\Gamma_{\rm total}\)
and is the BNL E871 final result of Ambrose et al.; see
\texttt{flavor\_catalog/references/K019/pdg2025\_kl\_emu.txt} and
\texttt{flavor\_catalog/references/K019/ambrose\_1998\_arxiv\_hepex9811038.txt}.

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is a \textbf{SECONDARY} Wave-8 entry; see
\texttt{flavor\_catalog/PRIORITY\_TIERS.md} for the tier policy.  The process
was deferred because the quark-only RS flavor pipeline does not naturally
produce an \(s\to d e\mu\) amplitude.  It becomes relevant once bulk leptons,
lepton-flavor-nonuniversal gauge couplings, Pati--Salam leptoquark gauge
bosons, or other lepton-sector flavor spurions are included.

In such extensions, \(K_L\to e\mu\) constrains products of \(s\)-\(d\) and
\(e\)-\(\mu\) flavor-violating couplings.  Neutral KK gauge exchange or a
flavor-changing \(Z\) can generate vector/axial semileptonic operators, while
scalar or Higgs-mediated structures probe chirality-enhanced pseudoscalar
matrix elements proportional to the kaon decay constant and quark masses.
Dipole effects are less direct for this two-body mode but become part of the
same lepton-bulk RS flavor story when the charged-lepton misalignment is not
minimal-flavor-violating.

\subsection*{Post-2008 developments}
No newer direct \(K_L\to e\mu\) branching-fraction limit appears in the
PDG 2025 \(K_L^0\) listing; the BNL E871 result remains the canonical bound.
Post-2008 work matters mainly through model interpretation.  Buras et al.
(\texttt{arXiv:1006.5356}) included \(K_L\to\mu e\) and
\(K_L\to\pi^0\mu e\) in a broad charged-LFV pattern study, providing a useful
template for comparing kaon LFV with charged-lepton and \(B\)-meson LFV
channels.  Beneke, Moch, and Rohrwild (\texttt{arXiv:1508.01705}) updated the
RS charged-lepton LFV calculation in a full 5D framework, emphasizing dipoles,
\(\mu\to 3e\), and muon conversion rather than kaon modes, but fixing the
lepton-bulk flavor ingredients needed before K019 can be predicted.

D'Ambrosio and Iyer (\texttt{arXiv:1712.08122}) studied warped custodial
models with partially composite leptons, rare \(K\) decays, and lepton-sector
flavor violation.  Blanke and Crivellin (\texttt{arXiv:1801.07256}) are the
most explicit RS-adjacent post-2008 handle for this entry: their
Pati--Salam-in-RS setup notes that conventional vector-leptoquark scenarios
are stringently constrained by \(K_L\to\mu e\) and \(K\to\pi\mu e\).  The LHCb
strange-hadron prospects report (\texttt{arXiv:1808.03477}) is included only
as experimental/prospective context, not as a replacement for the \(K_L\)
limit.

\subsection*{Constraint validity and model dependence}
The experimental limit is robust and clean as a bound on the physical
branching fraction.  Its use as an RS constraint is model-dependent.  A
minimal quark-only RS implementation should not impose this as a primary
constraint, because the \(e\)-\(\mu\) flavor transition is absent.  A
lepton-bulk or leptoquark-extended implementation can use it as a strong
constraint after specifying the charged-lepton flavor basis, the relevant
semileptonic Wilson coefficients, and whether vector, axial, scalar,
pseudoscalar, or Higgs-mediated operators dominate.

\subsection*{Code coverage in this repo}
\textbf{NO.}  Exact K019 searches over \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no
\(K_L\to e^{\pm}\mu^{\mp}\), \(s\to d e\mu\), or kaon semileptonic LFV
implementation.  The nearby code surfaces are different observables:
\texttt{flavorConstraints/muToEGamma.py:1} and
\texttt{flavorConstraints/muToEGamma.py:15--21} document a
\(\mu\to e\gamma\) dipole constraint,
\texttt{scanParams/scan.py:523--535} consumes only that LFV check, and
\texttt{quarkConstraints/deltaf2.py:610--624} defines neutral-kaon
\(\Delta F=2\) inputs rather than a charged-LFV kaon decay.

\subsection*{Implementation difficulty}
\textbf{MEDIUM.}  The observable itself is experimentally clean, but the repo
would need a new \(\Delta S=1\) charged-LFV semileptonic operator interface,
matching from the chosen lepton-bulk or leptoquark RS extension, and a kaon
decay-rate evaluator with vector/axial and scalar/pseudoscalar matrix
elements.  No new long-distance SM subtraction is the main simplifying
feature, but the necessary operator basis is not currently present.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2025\_KL\_emu}, \texttt{Ambrose1998\_KL\_emu},
\texttt{PDG2025\_ConservationLaws\_CLFV},
\texttt{CsakiFalkowskiWeiler2008\_RsFlavor},
\texttt{PerezRandall2008\_WarpedNeutrino},
\texttt{BurasDulingEtAl2010\_LFVFourthGeneration},
\texttt{BenekeMochRohrwild2015\_RsLeptonLFV},
\texttt{DAmbrosioIyer2018\_WarpedRareK},
\texttt{BlankeCrivellin2018\_PatiSalamRS}, and
\texttt{LHCbStrange2018\_Prospects}.
