% Flavor catalog per-process entry.
% process_id: K021
% family: kaon
% owner_agent_id: PKA-K021
% writer_agent_id: null
% checker_agent_id: null
% opus_signoff_id: null
% Canonical metadata sidecar: K021.yaml
% Status is controlled by the YAML sidecar status_history, not this comment.

\section{K021: \(K_L \to \pi^0 e^{\pm}\mu^{\mp}\)}

\subsection*{Process}
\textbf{Standard notation:} \(K_L \to \pi^0 e^{\pm}\mu^{\mp}\).  This
entry covers the lepton-family-number-violating neutral-kaon semileptonic
decay, equivalently the summed charge-state mode
\(\Gamma(\pi^0\mu^\pm e^\mp)/\Gamma_{\rm total}\) in the PDG \(K_L^0\)
listing.

\subsection*{PDG / equivalent value(s)}
The canonical current limit is
\[
  {\cal B}(K_L\to\pi^0 e^{\pm}\mu^{\mp}) < 7.6\times10^{-11}
  \qquad (90\%~{\rm CL}),
\]
from the PDG \(K_L^0\) listing, 2025 update, accessed 2026-05-17; see
\texttt{flavor\_catalog/references/K021/pdg2025\_kl\_pi0emu.txt}.  PDG labels
the entry \(LF\), gives the value for the sum of the indicated charge states,
and lists the underlying input as the KTeV Abouzaid 2008 result.  The KTeV
abstract reports the exact experiment limit
\({\cal B}(K_L\to\pi^0\mu e)<7.56\times10^{-11}\) at \(90\%\) CL with no
events in the signal region; PDG rounds this to \(7.6\times10^{-11}\).

\subsection*{Relevance to the RS / anarchic-flavor pipeline}
This is a \textbf{SECONDARY} Wave-8 entry; see
\texttt{flavor\_catalog/PRIORITY\_TIERS.md} for the tier policy.  It is a
\(\Delta S=1\), neutral-current LFV channel.  In an RS/anarchic
flavor pipeline it is sensitive to products of flavor off-diagonal quark and
lepton couplings, for example tree-level exchange of KK gauge bosons or
flavor-violating \(Z\)-like states generating
\((\bar s\gamma_\alpha d)(\bar e\gamma^\alpha\mu)\)-type operators.  The same
fermion-localization profiles that set quark FCNCs also set the charged-lepton
overlaps; in lepton-bulk variants the Perez--Randall seesaw/neutrino-Yukawa
spurions control charged-LFV misalignment.  Dipole constraints such as
\(\mu\to e\gamma\) probe a different operator class but constrain the same
leptonic flavor sector, while scalar or Higgs-flavor contributions would need
separate chirality and hadronic form-factor treatment.

\subsection*{Post-2008 developments}
The direct neutral-mode experimental situation has not moved beyond KTeV in
the PDG 2025 listing: the K021 limit remains the 2008 KTeV result.  The main
post-2008 experimental development is adjacent rather than superseding: NA62
reported 2017--2018 searches for \(K^+\to\pi^+\mu^-e^+\),
\(K^+\to\pi^-\mu^+e^+\), and \(\pi^0\to\mu^-e^+\), setting
\(90\%\)-CL limits at the \(10^{-11}\)--\(10^{-10}\) level and improving the
charged-kaon and pion LFV reach by about one order of magnitude.

The theory context changed more substantially.  Crivellin, D'Ambrosio,
Hoferichter, and Tunstall (arXiv:1601.00970) formulated rare kaon LFV/LFU
tests in terms of four-fermion operators for \(K\to\pi\ell\ell'\) and
\(K\to\ell\ell'\).  Angelescu, Faroughy, and Sumensari (arXiv:2002.05684)
gave numerical low-energy formulae for semileptonic LFV meson decays and
showed how LHC dilepton tails complement flavor limits.  Roy and Valencia
(arXiv:2410.05859) and Delzanno et al. (arXiv:2411.13497) updated the SMEFT
perspective by matching rare-kaon/CLFV operators to high-\(p_T\), electroweak,
and low-energy probes with RG running and operator correlations.

\subsection*{Constraint validity and model dependence}
The experimental upper limit is cleanly usable as a branching-ratio cap, but
the RS interpretation is model-dependent.  A catalog implementation must choose
an effective-operator basis, charge-state convention, \(K\to\pi\) vector and
scalar form factors, and the mapping from 5D fermion localization to
off-diagonal quark and lepton couplings.  There is no Standard Model
long-distance amplitude to subtract at an observable level for LFV, but there
is also no current repo machinery for the required \(\Delta S=1\) semileptonic
LFV matching.  Correlations with \(K_L\to e^\pm\mu^\mp\),
\(K^+\to\pi^+e^\pm\mu^\mp\), \(\mu\to e\gamma\), and \(\mu\to e\) conversion
should be kept explicit.

\subsection*{Code coverage in this repo}
\textbf{NO.}  The required grep sweep across \texttt{quarkConstraints/},
\texttt{qcd/}, \texttt{flavorConstraints/}, \texttt{neutrinos/},
\texttt{yukawa/}, \texttt{warpConfig/}, \texttt{solvers/},
\texttt{scanParams/}, and \texttt{tests/} found no K021 implementation and no
generic \(s\to d e\mu\) semileptonic LFV surface.  Existing nearby code covers
kaon \(\Delta F=2\) mixing, for example
\texttt{quarkConstraints/deltaf2.py:1} and
\texttt{quarkConstraints/deltaf2.py:615}, plus a separate \(\mu\to e\gamma\)
NDA dipole check in \texttt{flavorConstraints/muToEGamma.py:1}; neither
computes \(K_L\to\pi^0 e^\pm\mu^\mp\).

\subsection*{Implementation difficulty}
\textbf{HIGH.}  A pure EFT rate is standard once semileptonic LFV Wilson
coefficients are supplied, but this repository does not yet have the needed
\(\Delta S=1\) semileptonic operator basis, \(K\to\pi\) form-factor interface,
or RS matching for simultaneous quark and lepton flavor violation.  Integrating
K021 consistently with the existing RS scan would therefore require new
cross-sector matching rather than only adding a numerical limit.

\subsection*{Key references}
Process-local source keys before bibliography consolidation:
\texttt{PDG2025\_KL\_pi0emu},
\texttt{KTeV2008\_KL\_pi0emu},
\texttt{CFW2008\_composite\_pgh\_flavor},
\texttt{PerezRandall2008\_warped\_neutrinos},
\texttt{CrivellinDAmbrosioHoferichterTunstall2016\_rare\_kaon\_lfv},
\texttt{NA622021\_Kplus\_pi\_mu\_e},
\texttt{AngelescuFaroughySumensari2020\_lfv\_dilepton\_tails},
\texttt{RoyValencia2024\_highpt\_rare\_kaon\_smeft}, and
\texttt{DelzannoFuyutoGonzalezSolisMereghetti2024\_mue\_smeft}.
