% quark_scan_assumptions.tex
% Converted from quark_scan_assumptions.md — preserves every formula, table,
% assumption, numerical value, and footnote from the original document.
\documentclass[11pt]{article}

\usepackage[margin=1in]{geometry}
\usepackage{amsmath,amssymb}
\usepackage{booktabs}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{enumitem}
\usepackage{array}
\usepackage{longtable}

\hypersetup{
  colorlinks=true,
  linkcolor=blue,
  citecolor=blue,
  urlcolor=blue
}

\newcommand{\bra}[1]{\langle #1 |}
\newcommand{\ket}[1]{| #1 \rangle}
\newcommand{\Mkk}{M_{\mathrm{KK}}}
\newcommand{\LamIR}{\Lambda_{\mathrm{IR}}}
\newcommand{\Mpl}{M_{\mathrm{Pl}}}
\newcommand{\vev}{v}
\newcommand{\gs}{g_s^*}

\title{Quark-Sector Scan: Complete Assumptions and Pipeline}
\author{}
\date{}

\begin{document}
\maketitle

This document traces every assumption, formula, and convention that goes into
producing the publication figures \texttt{fig1\_exclusion\_boundaries} and
\texttt{fig2\_mkk\_bound\_2007\_vs\_modern}. It follows the computation in the
order it actually executes, from geometry definition through to the final pixel.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 0: Define the Warped Geometry}
\label{sec:step0}

The spacetime is a slice of $\mathrm{AdS}_5$ (Randall--Sundrum~I) compactified
on an $S^1/\mathbb{Z}_2$ orbifold, bounded by two 3-branes:

\begin{itemize}
  \item \textbf{UV brane} at the orbifold fixed point $y = 0$ (Planck-scale
    physics)
  \item \textbf{IR brane} at $y = \pi r_c$ (TeV-scale physics)
\end{itemize}

The 5D metric in conformal coordinates (mostly-plus signature) is:
\begin{equation}
  ds^2 = (kz)^{-2}\bigl(\eta_{\mu\nu}\,dx^\mu\,dx^\nu + dz^2\bigr)
\end{equation}
where $\eta = \mathrm{diag}(-1,+1,+1,+1)$ and $z$ runs from $z_h = 1/k$
(UV brane) to $z_v = 1/\LamIR$ (IR brane).  In proper-distance coordinates:
\begin{equation}
  ds^2 = e^{-2k|y|}\,\eta_{\mu\nu}\,dx^\mu\,dx^\nu + dy^2
\end{equation}

Two parameters fix the entire geometry:

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Parameter & Symbol & Default & Meaning \\
\midrule
AdS curvature & $k$ & $1.2209\times10^{19}$~GeV $(= \Mpl)$ & Sets the UV scale \\
IR scale & $\LamIR$ & scanned (500--20\,000~GeV) & Sets the TeV-scale brane \\
\bottomrule
\end{tabular}
\end{table}

From these, everything else is derived:

\begin{itemize}
  \item \textbf{Warp factor}: $\varepsilon = \LamIR / k$ (typically
    $\sim 10^{-15}$ for $\LamIR \sim$ few~TeV)
  \item \textbf{Orbifold radius}: $r_c = \ln(k/\LamIR)/(\pi k)$.  The warp
    factor and radius are related by $\varepsilon = e^{-\pi k r_c}$.
  \item \textbf{UV brane position} (conformal):
    $z_h = 1/k \sim 10^{-19}\;\mathrm{GeV}^{-1}$
  \item \textbf{IR brane position} (conformal):
    $z_v = 1/\LamIR \sim 10^{-4}\;\mathrm{GeV}^{-1}$
\end{itemize}

\textbf{Fixed external parameter}:
\begin{itemize}
  \item \textbf{Electroweak VEV}: $v = 174$~GeV.  This is the Higgs VEV, not
    the reduced VEV $v/\sqrt{2} = 246/\sqrt{2}$.  The code uses 174~GeV
    throughout.
\end{itemize}

\textbf{Assumption~0a}: The Higgs is localized on (or very near) the IR brane.
This is why the Yukawa interaction is proportional to the fermion zero-mode
value at the IR brane, and why TeV-scale new physics is connected to the IR
scale.

\textbf{Assumption~0b}: $k$ is fixed at $\Mpl = 1.2209\times10^{19}$~GeV.  The
scan does not vary~$k$.  This means the warp factor $\varepsilon$ and the
hierarchy are controlled entirely by $\LamIR$.

\textbf{Assumption~0c}: Backreaction of bulk fields on the geometry is
neglected.  The metric is taken to be the pure $\mathrm{AdS}_5$ slice
throughout.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 1: Zero-Mode Profiles ($f$-factors)}
\label{sec:step1}

Each 5D fermion field has a bulk Dirac mass $M_5$.  The dimensionless bulk mass
parameter is $c = M_5/k$.  The zero-mode wavefunction in the extra dimension is
determined by~$c$: it satisfies the 5D Dirac equation with the AdS background,
and the boundary conditions select a single normalizable zero mode per
chirality.

The physical quantity that enters all 4D couplings is the value of this
normalized zero-mode wavefunction at the IR brane.  For left-handed zero modes
(the ones relevant for Higgs overlap), this ``$f$-factor'' is:
\begin{align}
  f_{\mathrm{IR}}^2(c,\varepsilon) &= \frac{\tfrac{1}{2}-c}
    {1 - \varepsilon^{1-2c}}\,, \\
  f_{\mathrm{IR}}(c,\varepsilon) &= \sqrt{\max\!\bigl(f_{\mathrm{IR}}^2,\;0\bigr)}\,.
\end{align}

The formula arises from integrating the square of the zero-mode profile
$z^{2-c}$ over the extra dimension to normalize it, then evaluating at
$z = z_v$.  The $\max(\ldots,0)$ is a numerical safeguard against round-off.

\textbf{Physical behavior}:
\begin{itemize}
  \item $c > 1/2$: The exponent $(1-2c)$ is negative, so
    $\varepsilon^{1-2c}$ is huge (recall $\varepsilon\sim10^{-15}$).  The
    denominator is dominated by $-\varepsilon^{1-2c}$, and
    $f_{\mathrm{IR}}^2 \sim (c-\tfrac{1}{2})\,\varepsilon^{2c-1}$, which is
    exponentially small.
    \emph{These fermions are UV-localized and have tiny overlap with the
    IR-brane Higgs.}

  \item $c < 1/2$: The exponent $(1-2c)$ is positive, so
    $\varepsilon^{1-2c}\sim 0$.  Then $f_{\mathrm{IR}}^2 \sim (1/2-c)$,
    which is $O(1)$.
    \emph{These fermions are IR-localized and have large Yukawa overlap.}

  \item $c = 1/2$: The formula is $0/0$.  The limit is
    $f_{\mathrm{IR}}^2 = 1/(-2\ln\varepsilon)$.
    For $\varepsilon\sim10^{-15}$, this gives
    $f_{\mathrm{IR}}^2 \sim 1/69 \sim 0.014$.
\end{itemize}

\textbf{Numerical examples} (at $\varepsilon = 3000/1.2209\times10^{19}
\approx 2.46\times10^{-16}$):
\begin{itemize}
  \item $c = 0.72$ (light quark): $f_{\mathrm{IR}} \sim 4.4\times10^{-8}$
  \item $c = 0.51$ (near flat): $f_{\mathrm{IR}} \sim 0.11$
  \item $c = 0.30$ (heavy quark): $f_{\mathrm{IR}} \sim 0.45$
\end{itemize}

This enormous dynamic range --- 10 orders of magnitude between $c = 0.72$ and
$c = 0.30$ --- is the core of the RS flavor mechanism.  Mass hierarchies come
from geometry, not from hierarchical Yukawa couplings.

\textbf{Convention}: $c = M_5/k$, so positive $c$ means the bulk mass and the
AdS curvature have the same sign.  This is the standard convention in the RS
flavor literature (Agashe, Contino, Perez 2005; Csaki et al.\ 2009).

There is also a UV-brane overlap $f_{\mathrm{UV}}$, used for neutrino Majorana
masses in the lepton sector, but it does not enter the quark scan.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 2: Choose the Scan Grid}
\label{sec:step2}

The dense scan (the one used for the publication figures) sweeps a 3D grid:

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
Parameter & Grid & Range & Points \\
\midrule
$r$ & log-uniform & 0.02--2.0 & 100 \\
\texttt{overall\_scale} & linear & 1.5--6.0 & 20 \\
$\LamIR$ & log-uniform & 500--20\,000~GeV & 50 \\
\bottomrule
\end{tabular}
\end{table}

Total: $100 \times 20 \times 50 = 100{,}000$ scan points.

Each point is fitted independently from the same deterministic seed (no
warm-starting between points).  Points are fit in parallel; the result is
independent of execution order.

\textbf{Fixed parameters at scan time}:
\begin{itemize}
  \item $\xi_{\mathrm{KK}} = 1.0$.  This means $\Mkk = \LamIR$ in the scan's
    bookkeeping convention.  The Wilson coefficients use $\Mkk = \LamIR$ as the
    propagator mass.  (See \hyperref[sec:step16b]{Step~16b} for the post-hoc
    conversion to a physical KK-gluon mass.)

    \textcolor{red}{\textbf{To do:} Future scans should set
    $\xi_{\mathrm{KK}} = 2.4487$ (the physical first KK-gluon mass from the
    gauge-sector Bessel root) so that $\Mkk = m_g^{(1)}$ from the start.  The
    current post-hoc correction (\hyperref[sec:step16b]{Step~16b}) rescales
    the $1/\Mkk^2$ propagator factor but does not account for the fact that
    the QCD running of Wilson coefficients (Step~13) also starts at the wrong
    matching scale.  Using the physical $\xi_{\mathrm{KK}}$ would eliminate
    both issues.}
  \item $\gs = 3.0$.  The enhanced KK-gluon coupling, not the perturbative
    $g_s$.  This value is the one-loop estimate from Gedalia, Grossman, Nir,
    Perez (2009).  It is passed directly into the coupling computation at scan
    time, so all stored Wilson coefficients and ratios already include this
    enhancement.

    \textcolor{red}{\textbf{To do:} Confirm the correct value of $\gs$ with
    Lisa.  The tree-level estimate is $\gs \sim 6$ (Csaki, Falkowski, Weiler
    2008); the one-loop value is $\gs \sim 3$ (Gedalia et al.\ 2009).  Since
    $\gs$ enters as $\gs^2$, the difference between these two choices is a
    factor of~4 in all Wilson coefficients and constraint ratios.}
  \item $k = 1.2209\times10^{19}$~GeV $(= \Mpl)$.
  \item $v = 174$~GeV (electroweak VEV).
\end{itemize}

\textbf{The initial fit seed} uses $O(1)$ singular values and small CKM-like
left-rotation angles, chosen by hand to be in the right ballpark for SM-like
quark masses.  Right rotations in the seed are set to identity during
canonicalization before the fit begins
(\hyperref[sec:step10]{Step~10}).

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 3: Construct the Yukawa Spurions}
\label{sec:step3}

$Y_u$ and $Y_d$ are complex $3\times3$ matrices.  They are the 5D Yukawa
coupling matrices that appear in the action on the IR brane as
$\mathcal{L} = Y_{ij}\,Q_i\,H\,u_j$ (schematic).
In the scan, they are parametrized via a singular value decomposition:
\begin{align}
  Y_u &= \texttt{overall\_scale} \times U_{\mathrm{left}}^u
    \cdot \operatorname{diag}(\sigma_u)
    \cdot \bigl(U_{\mathrm{right}}^u\bigr)^\dagger\,, \\
  Y_d &= \texttt{overall\_scale} \times U_{\mathrm{left}}^d
    \cdot \operatorname{diag}(\sigma_d)
    \cdot \bigl(U_{\mathrm{right}}^d\bigr)^\dagger\,,
\end{align}
where:
\begin{itemize}
  \item $\sigma_u = (\sigma_{u1},\,\sigma_{u2},\,\sigma_{u3})$ are 3 positive
    singular values, ordered light-to-heavy.  These control the ``hierarchy''
    within each Yukawa.
  \item $\sigma_d = (\sigma_{d1},\,\sigma_{d2},\,\sigma_{d3})$ similarly for
    the down sector.
  \item $U_{\mathrm{left}}^{u,d}$ are CKM-like $3\times3$ unitary matrices,
    each with 4 real parameters: three Euler angles
    $(\theta_{12},\,\theta_{13},\,\theta_{23})$ and one CP-violating phase
    $(\delta)$.  These control the ``orientation'' of the Yukawa in flavor
    space.
  \item $U_{\mathrm{right}}^{u,d}$ are fixed to the $3\times3$ identity matrix
    (not fitted).  This is a restriction on the parameter space --- see below.
  \item \texttt{overall\_scale} is a common real positive prefactor multiplying
    both $Y_u$ and $Y_d$.  It controls the overall magnitude of the Yukawa
    entries.
\end{itemize}

The unitary matrices use the standard CKM (PDG) parametrization:
\begin{equation}
  U = \begin{pmatrix}
    c_{12}\,c_{13}
      & s_{12}\,c_{13}
      & s_{13}\,e^{-i\delta} \\
    -s_{12}\,c_{23} - c_{12}\,s_{23}\,s_{13}\,e^{i\delta}
      & c_{12}\,c_{23} - s_{12}\,s_{23}\,s_{13}\,e^{i\delta}
      & s_{23}\,c_{13} \\
    s_{12}\,s_{23} - c_{12}\,c_{23}\,s_{13}\,e^{i\delta}
      & -c_{12}\,s_{23} - s_{12}\,c_{23}\,s_{13}\,e^{i\delta}
      & c_{23}\,c_{13}
  \end{pmatrix}
\end{equation}
where $c_{ij} = \cos\theta_{ij}$, $s_{ij} = \sin\theta_{ij}$.  All angles are
wrapped into $[-\pi,\pi)$.

\textbf{Canonicalization}: Before the fit begins, \texttt{overall\_scale} is
absorbed into the singular values and set to~$1.0$; right rotations are set to
identity.  After canonicalization:
\begin{align}
  Y_u &= U_{\mathrm{left}}^u \cdot
    \operatorname{diag}(\sigma_u)\,, \qquad
  Y_d = U_{\mathrm{left}}^d \cdot
    \operatorname{diag}(\sigma_d)\,.
\end{align}

\textbf{Consequence of $U_{\mathrm{right}} = I$}: Since the right rotations are
identity:
\begin{align}
  Y_u^\dagger Y_u &= \operatorname{diag}(\sigma_u)^2 \quad\text{(diagonal)}\,, \\
  Y_d^\dagger Y_d &= \operatorname{diag}(\sigma_d)^2 \quad\text{(diagonal)}\,, \\
  Y_u Y_u^\dagger &= U_{\mathrm{left}}^u \cdot \operatorname{diag}(\sigma_u)^2
    \cdot \bigl(U_{\mathrm{left}}^u\bigr)^\dagger
    \quad\text{(generally dense)}\,, \\
  Y_d Y_d^\dagger &= U_{\mathrm{left}}^d \cdot \operatorname{diag}(\sigma_d)^2
    \cdot \bigl(U_{\mathrm{left}}^d\bigr)^\dagger
    \quad\text{(generally dense)}\,.
\end{align}

So $C_u$ and $C_d$ (defined next) are automatically diagonal, while $C_Q$ is
generally dense.  This means all off-diagonal flavor structure in the
left-handed quark sector --- and therefore all tree-level FCNCs --- come from
the combination of the two left rotations $U_{\mathrm{left}}^u$ and
$U_{\mathrm{left}}^d$ through~$C_Q$.

\textbf{Assumption~3a}: Right rotations are frozen to identity.  This restricts
the Yukawa space: 15 free parameters instead of 37 for two general complex
$3\times 3$ matrices.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 4: Build the Bulk Mass Matrices}
\label{sec:step4}

From the Yukawa spurions, three Hermitian matrices are constructed:
\begin{align}
  C_u &= Y_u^\dagger \cdot Y_u
    &&\text{[controls RH up-type quark localization]}\,, \\
  C_d &= Y_d^\dagger \cdot Y_d
    &&\text{[controls RH down-type quark localization]}\,, \\
  C_Q &= r \cdot (Y_u\,Y_u^\dagger) + (Y_d\,Y_d^\dagger)
    &&\text{[controls LH doublet localization]}\,.
\end{align}

\textbf{Physical motivation for $C_Q$}: In the RS NMFV framework, the 5D bulk
mass matrix for the left-handed quark doublets is assumed to be a function of
the Yukawa spurions (since the Yukawas are the only sources of flavor
breaking).  At leading order in the spurion expansion:
\begin{equation}
  C_Q = \alpha_Q\,\mathbf{I} + \beta_Q\,Y_d Y_d^\dagger
    + \gamma_Q\,Y_u Y_u^\dagger + \cdots
\end{equation}

The parameter $r = \gamma_Q/\beta_Q$ measures the relative weight of the
up-type vs down-type Yukawa contribution.  The code uses the simplified form
with $\beta_Q = 1$ (normalized out) and no flavor-universal $\alpha_Q$ term:
\begin{equation}
  C_Q = r\cdot(Y_u\,Y_u^\dagger) + (Y_d\,Y_d^\dagger)
\end{equation}

$C_Q$ is Hermitian and positive semi-definite (it is a sum of positive
semi-definite matrices with non-negative coefficients).

\textbf{The role of $r$}: When $r = 0$, $C_Q = Y_d\,Y_d^\dagger$.  If we work
in the basis where $Y_d$ is diagonal (which we can always choose), then $C_Q$
is also diagonal.  In that basis, the left-handed overlap matrix $F_Q$ is
diagonal, and there are no tree-level FCNCs in the down sector.  This is the
``alignment'' limit.

When $r > 0$, the $Y_u\,Y_u^\dagger$ term introduces off-diagonal entries
(since $Y_u$ contains CKM-like rotations relative to $Y_d$).  These
off-diagonal entries in $C_Q$ misalign the left-handed quark basis from the
down-Yukawa eigenbasis, generating tree-level FCNCs.

\textbf{Key difference from the standard NMFV parametrization}: The literature
(Csaki et al.\ 0907.0474) writes
$C_Q = \alpha_Q\,\mathbf{I} + \beta_Q\,Y_d Y_d^\dagger +
\gamma_Q\,Y_u Y_u^\dagger$.
The $\alpha_Q\,\mathbf{I}$ term provides a flavor-universal baseline bulk mass
(typically $\alpha_Q \sim 0.5$--$0.7$ to localize quarks near the UV brane).
This scan omits $\alpha_Q\,\mathbf{I}$.  Its role is instead played by the
BulkMassMap (\hyperref[sec:step5]{Step~5}), which maps the eigenvalues of $C_Q$
onto a bounded physical range $[0.30,\,0.72]$.  The BulkMassMap gives
$c_Q = 0.72$ when the eigenvalue is zero (equivalent to $\alpha_Q = 0.72$),
but for nonzero eigenvalues the relationship is nonlinear (sigmoid), not linear
as it would be with explicit $\alpha_Q$.

\textcolor{red}{\textbf{To do:} The note from Jackie prescribes the explicit
$(\alpha_Q,\,\beta_Q,\,\gamma_Q)$ parametrization with $C_Q =
\alpha_Q\,\mathbf{I} + \beta_Q\,Y_d Y_d^\dagger + \gamma_Q\,Y_u Y_u^\dagger$,
where all three coefficients are free $O(1)$ parameters.  The current scan uses
a different structure (no $\alpha_Q$, nonlinear BulkMassMap).  A future scan
following the note should implement the explicit parametrization directly.}

\textbf{Note on $C_u$ and $C_d$}: Because $U_{\mathrm{right}} = I$
(\hyperref[sec:step3]{Step~3}), both $C_u$ and $C_d$ are diagonal:
$C_u = \operatorname{diag}(\sigma_u^2)$,
$C_d = \operatorname{diag}(\sigma_d^2)$.  Only $C_Q$ carries off-diagonal
structure.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 5: Diagonalize and Map to Physical Bulk Masses}
\label{sec:step5}

\subsection{5a: Hermitian eigendecomposition}
\label{sec:step5a}

Each of $C_Q$, $C_u$, $C_d$ is diagonalized (Hermitian eigendecomposition):
\begin{equation}
  C_X = \text{rotation}_X \cdot \operatorname{diag}(\lambda_X)
    \cdot \text{rotation}_X^\dagger
\end{equation}
with eigenvalues sorted ascending (lightest generation first).  Since $C_u$ and
$C_d$ are already diagonal, their rotations are trivially the identity.  For
$C_Q$ the rotation is nontrivial and defines the basis transformation from the
spurion basis to the bulk-mass eigenbasis.

\subsection{5b: Nonlinear map from eigenvalues to bulk masses}
\label{sec:step5b}

The eigenvalues $\lambda_X$ (non-negative reals) are mapped to physical bulk
mass parameters $c_X$ through a bounded monotone sigmoid:
\begin{equation}
  c_X = c_{\mathrm{uv}} - (c_{\mathrm{uv}} - c_{\mathrm{ir}})
    \cdot \frac{\lambda}{\lambda + \text{eigen\_scale}}
\end{equation}

With the defaults $c_{\mathrm{uv}} = 0.72$, $c_{\mathrm{ir}} = 0.30$,
$\text{eigen\_scale} = 1.0$, this becomes:
\begin{equation}
  c_X = 0.72 - 0.42\;\frac{\lambda}{\lambda + 1}
\end{equation}

This is a monotone map bounded in $[0.30,\,0.72]$:
$\lambda = 0 \Rightarrow c = 0.72$ (UV-localized),
$\lambda = 1 \Rightarrow c = 0.51$,
$\lambda \to \infty \Rightarrow c \to 0.30$ (IR-localized).
The map enforces that all bulk masses stay in a physically sensible range
($c < 0$ gives imaginary $f$-factors; $c > 0.8$ gives essentially zero overlap).

\textbf{Assumption~5a}: The window $[0.30,\,0.72]$ is a design choice.
$c_{\mathrm{uv}} = 0.72$ means that a fermion with zero spurion eigenvalue
(i.e., decoupled from the Yukawa structure) sits at $c = 0.72$, which is
UV-localized and very light ($f_{\mathrm{IR}} \sim 4\times10^{-8}$).
$c_{\mathrm{ir}} = 0.30$ means that the most IR-localized fermion has
$c = 0.30$ ($f_{\mathrm{IR}} \sim 0.45$).  The top quark, which needs
$f_{\mathrm{IR}} \sim O(1)$, would need $c \sim 0.3$ or below; the BulkMassMap
cannot produce $c < 0.30$.  This forces the top Yukawa singular value to be
$\sim 2.4$ to reproduce $m_t = 172$~GeV (see \hyperref[sec:step8]{Step~8}),
which is perturbative but larger than the ``anarchic $O(1)$'' expectation.

\textbf{Assumption~5b}: The sigmoid shape ($\lambda/(\lambda+1)$) is a
convenience choice.  In the standard parametrization with explicit
$(\alpha_Q,\beta_Q)$, the map would be linear:
$c_{Q,i} = \alpha_Q + \beta_Q\cdot\lambda_i$.  The sigmoid compresses large
eigenvalues, preventing any $c$ from falling below $c_{\mathrm{ir}}$.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 6: Compute Zero-Mode Overlaps}
\label{sec:step6}

With the physical bulk masses $c_Q$, $c_u$, $c_d$ (each a length-3 vector, one
per generation), the zero-mode IR-brane overlaps are computed element-wise using
the formula from \hyperref[sec:step1]{Step~1}:
\begin{align}
  F_Q[i] &= f_{\mathrm{IR}}(c_Q[i],\,\varepsilon)
    \qquad\text{for } i = 1,2,3 \text{ (generations)}\,, \\
  F_u[i] &= f_{\mathrm{IR}}(c_u[i],\,\varepsilon)\,, \\
  F_d[i] &= f_{\mathrm{IR}}(c_d[i],\,\varepsilon)\,.
\end{align}

These are real, positive numbers stored as 1D arrays of length~3.  They will be
used as diagonal matrices in the mass formula.

Because of the BulkMassMap range $[0.30,\,0.72]$, all $c$ values are $> 1/2$
except possibly the third generation.  In practice:
\begin{itemize}
  \item First-generation quarks ($c \sim 0.7$):
    $F \sim 10^{-7}$~to~$10^{-8}$
  \item Second-generation quarks ($c \sim 0.55$--$0.65$):
    $F \sim 10^{-3}$~to~$10^{-5}$
  \item Third-generation quarks ($c \sim 0.30$--$0.45$):
    $F \sim 0.1$~to~$0.45$
\end{itemize}

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 7: Rotate Yukawas to the Bulk-Mass Basis}
\label{sec:step7}

The diagonalization of $C_Q$, $C_u$, $C_d$ in \hyperref[sec:step5]{Step~5}
defines three new bases.  The Yukawas must be rotated into the bulk-mass
eigenbasis before the mass matrices can be built, because the overlap matrices
$F_Q$, $F_u$, $F_d$ are diagonal only in that basis.

The rotation is:
\begin{align}
  Y_u^{\mathrm{bulk}} &= \text{rotation}_Q^\dagger \cdot Y_u
    \cdot \text{rotation}_u\,, \\
  Y_d^{\mathrm{bulk}} &= \text{rotation}_Q^\dagger \cdot Y_d
    \cdot \text{rotation}_d\,,
\end{align}
where $\text{rotation}_Q$, $\text{rotation}_u$, $\text{rotation}_d$ are the
unitary eigenvector matrices from \hyperref[sec:step5]{Step~5}.

\textbf{Important}: This rotation does \textbf{not} diagonalize the Yukawas.
It diagonalizes the bulk mass matrices.  The rotated Yukawas
$Y_u^{\mathrm{bulk}}$ and $Y_d^{\mathrm{bulk}}$ are generally dense $3\times3$
complex matrices.  Off-diagonal entries in these rotated Yukawas, combined with
the non-degenerate diagonal overlap factors, are what ultimately produce
off-diagonal entries in the mass matrices and drive the CKM mixing.

(Since $C_u$ and $C_d$ are already diagonal, $\text{rotation}_u$ and
$\text{rotation}_d$ reduce to the identity in practice.)

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 8: Build 4D Mass Matrices}
\label{sec:step8}

The effective 4D quark mass matrices in the bulk-mass eigenbasis are:
\begin{align}
  M_u &= 2v \cdot \operatorname{diag}(F_Q) \cdot Y_u^{\mathrm{bulk}}
    \cdot \operatorname{diag}(F_u)\,, \\
  M_d &= 2v \cdot \operatorname{diag}(F_Q) \cdot Y_d^{\mathrm{bulk}}
    \cdot \operatorname{diag}(F_d)\,,
\end{align}
where $v = 174$~GeV is the electroweak VEV.

\textbf{Origin of the factor $2v$}: With $v = 174$~GeV, the prefactor
$2v = 348$~GeV.  Note that $2\times174 = 348 \sim \sqrt{2}\times246$, where
246~GeV is the standard electroweak VEV
($v_{\mathrm{SM}} = 246$~GeV, with the Higgs field normalization
$\langle H \rangle = v_{\mathrm{SM}}/\sqrt{2} = 174$~GeV).  So the mass
formula is equivalently:
\begin{equation}
  M = \sqrt{2}\;v_{\mathrm{SM}} \cdot \operatorname{diag}(F_Q)
    \cdot Y^{\mathrm{bulk}} \cdot \operatorname{diag}(F)
\end{equation}

The factor of $\sqrt{2}$ arises from the normalization of the Higgs doublet VEV
relative to the mass term in the Lagrangian.  The 5D Yukawa couplings $Y$ in
this code are dimensionless (they absorb the factor of $k$ that appears in the
lepton-sector formula $m_E = 2vk\,f_L\,Y_E\,f_E$ used elsewhere in this
repo).  What matters is that the target quark masses
(\hyperref[sec:step10]{Step~10}) are defined consistently with this convention.

\textbf{Structure of $M_u$ and $M_d$}: The left overlap $\operatorname{diag}(F_Q)$
is the same for both sectors (since $Q$ is the $SU(2)$ doublet containing both
$u_L$ and $d_L$).  The right overlaps $\operatorname{diag}(F_u)$ and
$\operatorname{diag}(F_d)$ differ.  The Yukawas $Y_u^{\mathrm{bulk}}$ and
$Y_d^{\mathrm{bulk}}$ are generally dense.

The physical quark mass for generation $i$ is roughly:
\begin{equation}
  m_i \sim 2v \cdot F_Q[i] \cdot Y^{\mathrm{bulk}}_{ii}
    \cdot F_{u\,\text{or}\,d}[i]
\end{equation}
for the approximately diagonal case.  The exponential hierarchy in the
$F$-factors produces the quark mass hierarchy without requiring hierarchical
Yukawa entries.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 9: Extract Physical Masses and CKM}
\label{sec:step9}

Each mass matrix is decomposed via SVD (biunitary diagonalization) using the
convention:
\begin{equation}
  M = U_L \cdot \operatorname{diag}(\text{singular values})
    \cdot U_R^\dagger
\end{equation}
so that $U_L^\dagger \cdot M \cdot U_R =
\operatorname{diag}(m_1,\,m_2,\,m_3)$ with $m_i \ge 0$, sorted ascending
($m_1 < m_2 < m_3$ corresponds to $u < c < t$ or $d < s < b$).

The CKM matrix is constructed from the left-handed rotation matrices:
\begin{equation}
  V_{\mathrm{CKM}} = (U_L^u)^\dagger \cdot U_L^d
\end{equation}

This is the standard definition: $V_{\mathrm{CKM}}$ rotates from the down mass
eigenbasis to the up mass eigenbasis for left-handed quarks.

\textbf{CKM observables extracted} (4 real numbers):
\begin{enumerate}
  \item $|V_{us}| = |V_{\mathrm{CKM}}[0,1]|$ (Cabibbo angle)
  \item $|V_{cb}| = |V_{\mathrm{CKM}}[1,2]|$
  \item $|V_{ub}| = |V_{\mathrm{CKM}}[0,2]|$
  \item $J = \mathrm{Im}\!\bigl(V_{\mathrm{CKM}}[0,1] \cdot
    V_{\mathrm{CKM}}[1,2] \cdot V_{\mathrm{CKM}}[0,2]^* \cdot
    V_{\mathrm{CKM}}[1,1]^*\bigr)$
    --- the Jarlskog invariant, a rephasing-invariant measure of CP violation
\end{enumerate}

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 10: The Fit (Optimization Loop)}
\label{sec:step10}

Steps~3 through~9 are wrapped inside a Trust Region Reflective (TRF) optimizer
(\texttt{scipy.optimize.least\_squares}).  The fit adjusts the Yukawa
parameters until the predicted quark masses and CKM match the observed values.

\subsection{10a: Free parameters (14 total)}
\label{sec:step10a}

The optimizer works in a ``canonical chart'' with 14 real coordinates:

\begin{enumerate}
  \item[1--3.] $\ln(\text{physical\_}\sigma_u[1])$,
    $\ln(\text{physical\_}\sigma_u[2])$,
    $\ln(\text{physical\_}\sigma_u[3])$
    --- log of the up-sector singular values (the log ensures positivity)
  \item[4--6.] $\ln(\text{physical\_}\sigma_d[1])$,
    $\ln(\text{physical\_}\sigma_d[2])$,
    $\ln(\text{physical\_}\sigma_d[3])$
    --- log of the down-sector singular values
  \item[7--10.] $\theta_{12}^u$, $\theta_{13}^u$, $\theta_{23}^u$, $\delta^u$
    --- four parameters of the up-sector left rotation
  \item[11--14.] $\theta_{12}^d$, $\theta_{13}^d$, $\theta_{23}^d$, $\delta^d$
    --- four parameters of the down-sector left rotation
\end{enumerate}

All angles are in $[-\pi,\pi)$ after canonicalization.

\textbf{Fixed during fit}: $r$, \texttt{overall\_scale} (absorbed into singular
values as~$1.0$), $\LamIR$, $k$, $v$, BulkMassMap parameters, right rotations
$(= I)$.

\subsection{10b: Target observables (10 total)}
\label{sec:step10b}

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Observable & Target value & Source \\
\midrule
$m_u$ & 0.0013~GeV & Repo-owned target set \\
$m_c$ & 0.62~GeV & Repo-owned target set \\
$m_t$ & 172.0~GeV & Repo-owned target set \\
$m_d$ & 0.0028~GeV & Repo-owned target set \\
$m_s$ & 0.057~GeV & Repo-owned target set \\
$m_b$ & 2.86~GeV & Repo-owned target set \\
$|V_{us}|$ & 0.225 & CKM parametrization \\
$|V_{cb}|$ & 0.0415 & CKM parametrization \\
$|V_{ub}|$ & 0.00361 & CKM parametrization \\
$J$ & $\sim 3.08\times10^{-5}$ &
  From $(\theta_{12}{=}0.2274,\;\theta_{13}{=}0.00368,$\\
  && $\theta_{23}{=}0.0415,\;\delta{=}1.196)$ \\
\bottomrule
\end{tabular}
\end{table}

The target CKM is built from a CKM-like unitary with angles
$(\theta_{12}=0.2274,\;\theta_{13}=0.00368,\;\theta_{23}=0.0415,\;
\delta=1.196)$.  The four CKM observables $(|V_{us}|,\;|V_{cb}|,\;|V_{ub}|,\;
J)$ are extracted from this matrix.

\textbf{Note on mass targets}: These are repo-owned ``effective'' quark masses,
not $\overline{\mathrm{MS}}$ masses at any single consistent renormalization
scale.  Some values ($m_u = 1.3$~MeV, $m_d = 2.8$~MeV) are close to
$\overline{\mathrm{MS}}$ at $\mu = 2$~GeV; others ($m_c = 0.62$~GeV) are
closer to $\overline{\mathrm{MS}}$ at $\mu \sim 3$~TeV; $m_b = 2.86$~GeV is
close to $\overline{\mathrm{MS}}$ at $\mu = m_b$.  The values were chosen for
scan stability and to give physically reasonable bulk mass parameters, not for
precise consistency with a single renormalization scheme.  Since the fit
determines the bulk masses (and thus the $f$-factors and FCNC couplings) from
these targets, any systematic shift in the targets would propagate into the
constraint ratios.  This is a source of unquantified systematic uncertainty.

\textcolor{red}{\textbf{To do:} Replace these with properly defined PDG
$\overline{\mathrm{MS}}$ quark masses at a consistent renormalization scale
(e.g., all at $\mu = 2$~GeV, or all at $\mu = \Mkk$).  The current
inconsistency between the scales at which the target masses are defined is
an uncontrolled systematic.}

\subsection{10c: Residual vector (10 components)}
\label{sec:step10c}

The optimizer minimizes a vector of 10 residuals:
\begin{equation}
\text{residuals} = \begin{pmatrix}
  \ln(m_u^{\mathrm{pred}}/0.0013) \\[2pt]
  \ln(m_c^{\mathrm{pred}}/0.62) \\[2pt]
  \ln(m_t^{\mathrm{pred}}/172.0) \\[2pt]
  \ln(m_d^{\mathrm{pred}}/0.0028) \\[2pt]
  \ln(m_s^{\mathrm{pred}}/0.057) \\[2pt]
  \ln(m_b^{\mathrm{pred}}/2.86) \\[2pt]
  (|V_{us}|^{\mathrm{pred}} - 0.225) / 0.225 \\[2pt]
  (|V_{cb}|^{\mathrm{pred}} - 0.0415) / 0.0415 \\[2pt]
  (|V_{ub}|^{\mathrm{pred}} - 0.00361) / 0.00361 \\[2pt]
  (J^{\mathrm{pred}} - J^{\mathrm{target}}) / |J^{\mathrm{target}}|
\end{pmatrix}
\end{equation}

Mass residuals are in log-space (dimensionless), CKM residuals are fractional
deviations normalized by the target value.

\textbf{Fit score} $= \sqrt{\mathrm{mean}(\text{residuals}^2)}$.  This is the
RMS of all 10 residuals.  A score of~$0.1$ means $\sim 10\%$ average deviation
across all observables.

\subsection{10d: Optimizer settings}
\label{sec:step10d}

\begin{itemize}
  \item \textbf{Method}: Trust Region Reflective (TRF) via
    \texttt{scipy.optimize.least\_squares}.
  \item \textbf{Max evaluations}: 120 (each evaluation runs Steps~3--9 once).
\end{itemize}

Points with $\text{fit\_score} > 0.1$ after the optimizer finishes are flagged
as poorly converged and discarded at plotting time
(\hyperref[sec:step16a]{Step~16a}).

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 11: Mass-Basis KK-Gluon Couplings}
\label{sec:step11}

After the fit converges, we have: (1)~the diagonal overlap profiles $F_Q$,
$F_u$, $F_d$, and (2)~the unitary rotation matrices $U_L^u$, $U_R^u$,
$U_L^d$, $U_R^d$ from the SVD of the mass matrices.  These are combined to
build the KK-gluon coupling matrices in the physical quark mass basis.

The first KK-gluon excitation couples to zero-mode quarks proportionally to
their IR-brane wavefunction values squared.  In the bulk-mass eigenbasis, this
coupling is diagonal: $\gs\cdot\operatorname{diag}(F^2)$.  To get the coupling
in the mass basis, we rotate:
\begin{equation}
  (\text{overlap})_{ij}^{\text{mass basis}} = \bigl(U^\dagger \cdot
    \operatorname{diag}(F^2) \cdot U\bigr)_{ij}
\end{equation}
where $U$ is the appropriate left or right rotation matrix from the SVD.

Four coupling matrices are built:
\begin{align}
  g_L^{\mathrm{down}}[i,j] &= \gs \cdot \bigl(U_L^d\bigr)^\dagger
    \cdot \operatorname{diag}(F_Q^2) \cdot U_L^d \Big|_{ij}\,, \\
  g_R^{\mathrm{down}}[i,j] &= \gs \cdot \bigl(U_R^d\bigr)^\dagger
    \cdot \operatorname{diag}(F_d^2) \cdot U_R^d \Big|_{ij}\,, \\
  g_L^{\mathrm{up}}[i,j] &= \gs \cdot \bigl(U_L^u\bigr)^\dagger
    \cdot \operatorname{diag}(F_Q^2) \cdot U_L^u \Big|_{ij}\,, \\
  g_R^{\mathrm{up}}[i,j] &= \gs \cdot \bigl(U_R^u\bigr)^\dagger
    \cdot \operatorname{diag}(F_u^2) \cdot U_R^u \Big|_{ij}\,.
\end{align}

Each is a Hermitian $3\times3$ matrix.  The diagonal entries are the
flavor-conserving couplings; the off-diagonal entries drive FCNCs.

Note: $F_Q$ appears in both the LH-down and LH-up couplings because both
$u_L$ and $d_L$ live in the same $SU(2)$ doublet $Q$, which has the same bulk
mass and therefore the same overlap profile.  The difference between
$g_L^{\mathrm{down}}$ and $g_L^{\mathrm{up}}$ comes entirely from the
different rotation matrices $U_L^d$ vs $U_L^u$.

\textbf{On $\gs$}: The code uses $\gs = 3.0$ (passed at scan time).  This
replaces the perturbative QCD coupling
$g_s = \sqrt{4\pi\alpha_s(\Mkk)}$.  In RS, the first KK-gluon has a
wavefunction peaked near the IR brane, enhancing its coupling to IR-localized
fermions by a factor $\sqrt{2\,k\,\pi\,r_c} \sim 6$--$8$ at tree level.  The
one-loop corrected value is $\gs \sim 3$ (Gedalia et al.\ 2009).

Since $\gs$ enters the Wilson coefficients as $\gs^2$, the difference between
$\gs = 1$ (perturbative) and $\gs = 3$ is a factor of~$9$ in all constraint
ratios.  This is a major assumption.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 12: Tree-Level Wilson Coefficients}
\label{sec:step12}

The KK-gluon is integrated out at the matching scale $\mu = \Mkk$, producing
four $\Delta F = 2$ four-quark operators in the BMU basis (Buras, Misiak,
Urban, hep-ph/0005183).  For a meson system involving quark flavors $i$ and
$j$:
\begin{align}
  \text{prefactor} &= \frac{1}{\Mkk^2}\,, \\[6pt]
  C_1^{\mathrm{VLL}} &= \bigl(g_L[i,j]\bigr)^2 \cdot
    \frac{\text{prefactor}}{6}\,, \\
  C_1^{\mathrm{VRR}} &= \bigl(g_R[i,j]\bigr)^2 \cdot
    \frac{\text{prefactor}}{6}\,, \\
  C_4^{\mathrm{LR}} &= -\bigl(g_L[i,j]\cdot g_R[i,j]\bigr) \cdot
    \text{prefactor}\,, \\
  C_5^{\mathrm{LR}} &= \bigl(g_L[i,j]\cdot g_R[i,j]\bigr) \cdot
    \frac{\text{prefactor}}{3}\,,
\end{align}
where $g_L[i,j]$ and $g_R[i,j]$ are the (complex) off-diagonal entries of the
coupling matrices from \hyperref[sec:step11]{Step~11}.

\textbf{The Wilson coefficients are complex}: Since $g_L[i,j]$ and $g_R[i,j]$
are off-diagonal entries of Hermitian matrices, they are generally complex (not
real).  The products $g_L^2$, $g_R^2$, and $g_L\cdot g_R$ are complex numbers.
The imaginary parts carry CP-violating information and are essential for the
$\epsilon_K$ constraint.

\textbf{Color factor origin}: These come from the color algebra of tree-level
single-KK-gluon exchange in the $t$-channel.  Each vertex carries a color
generator $T^a$, giving the product:
\begin{equation}
  (T^a)_{\alpha\beta}\,(T^a)_{\gamma\delta} = \tfrac{1}{2}\,
    \delta_{\alpha\delta}\,\delta_{\gamma\beta}
    - \tfrac{1}{2N_c}\,\delta_{\alpha\beta}\,\delta_{\gamma\delta}
\end{equation}
After Fierz rearrangement into the BMU basis:
\begin{itemize}
  \item The VLL/VRR operators pick up $1/(2N_c) = 1/6$ for $N_c = 3$.
  \item The LR operators arise from Fierz-rearranging the
    $(V{-}A)\times(V{+}A)$ structure into scalar/pseudoscalar operator pairs.
    The specific coefficients $-1$ and $+1/3$ for $C_4^{\mathrm{LR}}$ and
    $C_5^{\mathrm{LR}}$ follow from the Fierz identity for the LR color
    contractions (see e.g., Buras, Weak Hamiltonian review, Eq.~6.6).
\end{itemize}

\textbf{Why only 4 operators}: Tree-level single vector boson exchange produces
only vector current structures at the vertices ($\gamma^\mu P_L$ or $P_R$).
This gives VLL, VRR, and LR operators but \textbf{not} scalar LL/RR operators
(SLL, SRR), which would require scalar current insertions.  The full BMU basis
has 8 operators, but SLL/SRR are absent at tree level.  They could appear at
one loop but are not included in this analysis.

\textbf{Flavor indices for each meson system}:

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
System & Sector & $(i,j)$ & Coupling matrices used \\
\midrule
$\epsilon_K$ & down & $(0,1) = d,s$ &
  $g_L^{\mathrm{down}},\; g_R^{\mathrm{down}}$ \\
$\Delta M_K$ & down & $(0,1) = d,s$ &
  $g_L^{\mathrm{down}},\; g_R^{\mathrm{down}}$ \\
$\Delta M_{B_d}$ & down & $(0,2) = d,b$ &
  $g_L^{\mathrm{down}},\; g_R^{\mathrm{down}}$ \\
$\Delta M_{B_s}$ & down & $(1,2) = s,b$ &
  $g_L^{\mathrm{down}},\; g_R^{\mathrm{down}}$ \\
$\Delta M_{D^0}$ & up & $(0,1) = u,c$ &
  $g_L^{\mathrm{up}},\; g_R^{\mathrm{up}}$ \\
\bottomrule
\end{tabular}
\end{table}

$\epsilon_K$ and $\Delta M_K$ use the same Wilson coefficients (same quark
pair); they differ only in which observable is computed from $M_{12}$
(\hyperref[sec:step15]{Step~15}).

\textbf{Assumption~12a}: Tree-level matching only.  No one-loop corrections at
the matching scale (no threshold corrections, no scheme conversion beyond tree
level).  This is the standard approximation in the RS FCNC literature.

\textbf{Assumption~12b}: Only the first KK-gluon contributes.  Higher KK modes
are not summed.  For the leading exclusion bound this is typically a
$\sim 10$--$20\%$ correction.

\textbf{Assumption~12c}: $\Mkk = \LamIR$ is used as both the propagator mass
and the matching scale.  The physical first KK-gluon mass is
$m_g^{(1)} = 2.45\times\LamIR$ (\hyperref[sec:step16b]{Step~16b} corrects for
this at plotting time).

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 13: QCD Running to the Hadronic Scale}
\label{sec:step13}

The Wilson coefficients are evaluated at the matching scale $\Mkk$ (multi-TeV).
The hadronic matrix elements (\hyperref[sec:step14]{Step~14}) are evaluated at
$\mu_{\mathrm{had}} = 2$~GeV.  The Wilson coefficients must be evolved from
$\Mkk$ down to $\mu_{\mathrm{had}}$ using the QCD renormalization group.

\subsection{13a: VLL and VRR operators (multiplicative running)}
\label{sec:step13a}

The VLL and VRR operators do not mix with any other operators under QCD.  Their
anomalous dimension is
$\gamma_{\mathrm{VLL}} = 6(N_c-1)/N_c = 4$ for $N_c = 3$.

For a single segment with $n_f$ active flavors between scales $\mu_{\mathrm{high}}$
and $\mu_{\mathrm{low}}$:
\begin{equation}
  C_{\mathrm{VLL}}(\mu_{\mathrm{low}}) =
    C_{\mathrm{VLL}}(\mu_{\mathrm{high}}) \cdot
    \left[\frac{\alpha_s(\mu_{\mathrm{low}})}
               {\alpha_s(\mu_{\mathrm{high}})}\right]^{\gamma_{\mathrm{VLL}}/(2\beta_0)}
\end{equation}
where $\beta_0 = (33 - 2n_f)/3$ is the one-loop beta function coefficient.

Since $\gamma_{\mathrm{VLL}} > 0$ and
$\alpha_s(\mu_{\mathrm{low}}) > \alpha_s(\mu_{\mathrm{high}})$, the ratio
$> 1$ and the VLL coefficient is \textbf{enhanced} at lower scales.

\subsection{13b: LR operators ($2\times2$ matrix mixing)}
\label{sec:step13b}

The $C_4^{\mathrm{LR}}$ and $C_5^{\mathrm{LR}}$ operators mix under QCD
running.  The anomalous dimension matrix is:
\begin{equation}
  \gamma_{\mathrm{LR}} = \begin{pmatrix} 8 & -4 \\ -16/3 & -28/3 \end{pmatrix}
\end{equation}

For each $n_f$ segment, the evolution matrix is:
\begin{equation}
  U_{\mathrm{LR}} = M \cdot \operatorname{diag}\!\left(
    \left[\frac{\alpha_s^{\mathrm{low}}}{\alpha_s^{\mathrm{high}}}\right]
    ^{d_i/(2\beta_0)}\right) \cdot M^{-1}
\end{equation}
where $d_i$ are the eigenvalues of $\gamma_{\mathrm{LR}}$ and $M$ is the
eigenvector matrix.  The dominant eigenvalue of $\gamma_{\mathrm{LR}}$ is large
and positive, giving a significant enhancement (${\sim}\,3$--$5\times$) of the
LR operators at low scales.  This is the main reason why $\epsilon_K$ is such a
powerful constraint in RS models: the LR operators, which receive the
chirality-enhanced hadronic matrix elements (proportional to
$(m_K/(m_s + m_d))^2 \sim 25$), are further amplified by QCD running.

\subsection{13c: Multi-segment evolution with flavor thresholds}
\label{sec:step13c}

The running from $\Mkk$ to $\mu_{\mathrm{had}} = 2$~GeV crosses one quark
threshold ($m_b = 4.18$~GeV; $m_c = 1.27$~GeV is below $\mu_{\mathrm{had}}$):
\begin{align*}
  \Mkk &\longrightarrow m_b = 4.18\;\text{GeV} \quad (n_f = 5) \\
  m_b  &\longrightarrow 2.0\;\text{GeV} \quad (n_f = 4)
\end{align*}

At each threshold, the Wilson coefficients are matched continuously (no finite
matching corrections at leading order).

The $\alpha_s$ running within each segment uses a one-loop formula:
\begin{equation}
  \alpha_s(\mu) = \frac{\alpha_s(\mu_{\mathrm{ref}})}
    {1 + \dfrac{\beta_0\,\alpha_s(\mu_{\mathrm{ref}})}{2\pi}\,
    \ln\!\left(\dfrac{\mu}{\mu_{\mathrm{ref}}}\right)}
\end{equation}
with $\alpha_s(M_Z = 91.19\;\text{GeV}) = 0.1179$ as the reference value, and
threshold matching at $m_b$ and $m_c$.

The cumulative evolution factors for VLL/VRR are multiplied across segments;
the $2\times2$ LR matrices are multiplied in order.

\textbf{Assumption~13a}: Leading-log anomalous dimensions only.  The operator
mixing is LO (one-loop $\gamma$).  This is adequate for the current precision.

\textbf{Assumption~13b}: The $\alpha_s$ running for the operator evolution uses
a one-loop formula ($\alpha_s(M_Z) = 0.1179$), while the coupling computation
(\hyperref[sec:step11]{Step~11}) uses 4-loop running ($\alpha_s(M_Z) = 0.1180$).
This $O(\text{few-\%})$ inconsistency is subdominant compared to the $\gs$
uncertainty.

\textbf{Assumption~13c}: Continuous threshold matching (no finite corrections
at $m_b$ or $m_c$).  This is the standard LO prescription.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 14: Hadronic Matrix Elements}
\label{sec:step14}

The RG-evolved Wilson coefficients at $\mu_{\mathrm{had}} = 2$~GeV are
contracted with hadronic matrix elements to obtain $M_{12}^{\mathrm{NP}}$, the
new-physics contribution to the meson mixing amplitude.

The general formula for a pseudoscalar meson $P$ with valence quarks $q_1$,
$q_2$ is:
\begin{equation}
  M_{12}^{\mathrm{NP}} = C_1^{\mathrm{VLL}} \cdot \mathrm{ME}_{\mathrm{VLL}}
    + C_1^{\mathrm{VRR}} \cdot \mathrm{ME}_{\mathrm{VLL}}
    + C_4^{\mathrm{LR}} \cdot \mathrm{ME}_{\mathrm{LR4}}
    + C_5^{\mathrm{LR}} \cdot \mathrm{ME}_{\mathrm{LR5}}
\end{equation}

Note: VRR has the same matrix element as VLL by parity symmetry of QCD.  This
means
$\langle\bar{P}|\mathcal{O}_{\mathrm{VRR}}|P\rangle =
\langle\bar{P}|\mathcal{O}_{\mathrm{VLL}}|P\rangle$.

The matrix elements are:
\begin{align}
  \mathrm{ME}_{\mathrm{VLL}} &= \tfrac{2}{3}\,f_P^2\,m_P\,B_1\,, \\[4pt]
  r_{\chi} &= \left(\frac{m_P}{m_{q_1} + m_{q_2}}\right)^2\,, \\[4pt]
  \mathrm{ME}_{\mathrm{LR4}} &= \bigl(\tfrac{r_{\chi}}{6}
    + \tfrac{1}{4}\bigr)\,f_P^2\,m_P\,B_4\,, \\[4pt]
  \mathrm{ME}_{\mathrm{LR5}} &= \bigl(\tfrac{r_{\chi}}{2}
    + \tfrac{1}{12}\bigr)\,f_P^2\,m_P\,B_5\,.
\end{align}

The factor $r_{\chi}$ is the chiral enhancement factor.  For kaons:
$r_{\chi} = (0.49761/(0.0934 + 0.00467))^2 \approx 25.2$.
This is why the LR operators dominate $\epsilon_K$: their matrix elements are
enhanced by ${\sim}\,25$ relative to the VLL matrix element.

\subsection{Hadronic inputs by meson system}

\textbf{Kaon ($K^0$)} --- valence quarks $d$, $s$:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Input & Value & Source \\
\midrule
$f_K$ & 155.7~MeV & PDG 2024 \\
$m_K$ & 497.61~MeV & PDG 2024 \\
$m_s(2\;\text{GeV})$ & 93.4~MeV & FLAG 2024 \\
$m_d(2\;\text{GeV})$ & 4.67~MeV & FLAG 2024 \\
$B_1^K$ & 0.717 & FLAG/lattice average \\
$B_4^K$ & 0.78 & ETM 2013 \\
$B_5^K$ & 0.57 & ETM 2013 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{$B_d$} --- valence quarks $d$, $b$:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Input & Value & Source \\
\midrule
$f_{B_d}$ & 190.0~MeV & FLAG 2024 \\
$m_{B_d}$ & 5279.72~MeV & PDG 2024 \\
$m_b(m_b)$ & 4.18~GeV & PDG ($\overline{\mathrm{MS}}$) \\
$m_d(2\;\text{GeV})$ & 4.67~MeV & FLAG 2024 \\
$B_1^{B_d}$ & 0.87 & FLAG 2024 \\
$B_4^{B_d}$ & 1.02 & FLAG 2024 \\
$B_5^{B_d}$ & 0.96 & FLAG 2024 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{$B_s$} --- valence quarks $s$, $b$:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Input & Value & Source \\
\midrule
$f_{B_s}$ & 230.3~MeV & FLAG 2024 \\
$m_{B_s}$ & 5366.92~MeV & PDG 2024 \\
$m_s(2\;\text{GeV})$ & 93.4~MeV & FLAG 2024 \\
$B_1^{B_s}$ & 0.87 & FLAG 2024 \\
$B_4^{B_s}$ & 1.02 & FLAG 2024 \\
$B_5^{B_s}$ & 0.96 & FLAG 2024 \\
\bottomrule
\end{tabular}
\end{table}

\textbf{$D^0$} --- valence quarks $u$, $c$:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
Input & Value & Source \\
\midrule
$f_D$ & 212.0~MeV & FLAG 2024 \\
$m_{D^0}$ & 1864.84~MeV & PDG 2024 \\
$m_c(m_c)$ & 1.27~GeV & PDG ($\overline{\mathrm{MS}}$) \\
$m_u(2\;\text{GeV})$ & 2.16~MeV & FLAG 2024 \\
$B_1^D$ & 0.75 & Lattice (less precise) \\
$B_4^D$ & 1.0 & Estimated \\
$B_5^D$ & 1.0 & Estimated \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Assumption~14a}: Bag parameters $B_4^D$ and $B_5^D$ for $D^0$ mixing
are set to~$1.0$.  No reliable lattice determination exists.  This introduces
$O(1)$ uncertainty in the $D^0$ constraint.

\textbf{Assumption~14b}: The quark masses entering the chiral enhancement
factor $r_{\chi}$ are $\overline{\mathrm{MS}}$ masses at their respective
self-scales, \textbf{not} all at $\mu = 2$~GeV.  For $B$~mesons,
$m_b(m_b) = 4.18$~GeV is used rather than $m_b(2\;\text{GeV}) \sim 5.4$~GeV;
for $D^0$, $m_c(m_c) = 1.27$~GeV.  This is inconsistent with evaluating the
matrix elements at $\mu_{\mathrm{had}} = 2$~GeV.  Using $m_b(2\;\text{GeV})$
instead would change $r_{\chi}$ for $B_d$ from ${\sim}\,1.6$ to ${\sim}\,1.0$,
an $O(40\%)$ shift in the LR matrix element.  For the $B$ and $D$ systems the
LR contribution is subdominant ($r_{\chi} \sim 1$--$2$, vs ${\sim}\,25$ for
kaons), so this inconsistency has limited impact on the final bounds, but it is
a known systematic.

\textbf{Assumption~14c}: The matrix element formulae above are the ``vacuum
insertion approximation'' corrected by the bag parameters $B_i$.  The $B_i$
encode deviations from the naive factorization
$\langle P|\mathcal{O}|P\rangle =
\langle P|\bar{q}q|0\rangle\langle 0|\bar{q}q|P\rangle$.
Lattice QCD determines the $B_i$.

\textbf{Normalization convention}: $M_{12}^{\mathrm{NP}}$ as computed here is
the \textbf{full} off-diagonal Hamiltonian matrix element
$\langle\bar{P}|\mathcal{H}_{\mathrm{eff}}|P\rangle$, with dimensions of GeV.
It does \textbf{not} include a $1/(2m_P)$ normalization that some references
fold into the definition of~$M_{12}$.  Consistently, the mass difference is
$\Delta m = 2|M_{12}|$, so the constraint
$|M_{12}^{\mathrm{NP}}| \le \Delta m/2$ is equivalent to
$|M_{12}^{\mathrm{NP}}| \le |M_{12}^{\mathrm{exp}}|$.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 15: Observable Evaluation and Acceptance}
\label{sec:step15}

\subsection{15a: $\epsilon_K$ (CP violation in kaon mixing)}
\label{sec:step15a}

The NP contribution to $\epsilon_K$ is:
\begin{equation}
  \epsilon_K^{\mathrm{NP}} = \frac{|\kappa_\epsilon|}
    {\sqrt{2}\,\Delta m_K} \cdot |\mathrm{Im}(M_{12}^{\mathrm{NP}})|
\end{equation}
with:
\begin{itemize}
  \item $\kappa_\epsilon = 0.94$ (accounts for long-distance and higher-order
    corrections, Buras et al.)
  \item $\Delta m_K = 3.484\times10^{-15}$~GeV ($K_L$--$K_S$ mass difference,
    PDG)
\end{itemize}

The NP budget is the gap between the experimental value and the SM prediction:
\begin{equation}
  \text{budget} = |\epsilon_K^{\mathrm{exp}} - \epsilon_K^{\mathrm{SM}}|
    = |2.228\times10^{-3} - 1.81\times10^{-3}| = 4.18\times10^{-4}
\end{equation}

Ratio to bound: $\epsilon_K^{\mathrm{NP}} / \text{budget}$.
\textbf{Passes if ratio $\le 1.0$.}

\textbf{Assumption~15a-i}: The SM prediction
$\epsilon_K^{\mathrm{SM}} = 1.81\times10^{-3}$ is taken from the CKMfitter
central value.  The experimental value is $2.228\times10^{-3}$ (PDG).  The
difference of $4.18\times10^{-4}$ is the allowed ``room'' for NP.  This is a
generous budget --- some analyses use a tighter SM prediction.

\textbf{Assumption~15a-ii}: The formula takes $|\mathrm{Im}(M_{12}^{\mathrm{NP}})|$,
discarding the sign of the NP CP-violating phase.  This means we do not account
for constructive vs destructive interference between NP and SM.  If the NP
phase happens to partially cancel the SM contribution, the actual constraint
would be weaker; if it enhances it, stronger.  Using the absolute value is a
standard simplification for model-independent bounds.

\subsection{15b: $\Delta M_K$ (kaon mass splitting)}
\label{sec:step15b}

The NP contribution to the kaon mass difference is:
\begin{equation}
  \frac{|M_{12}^{\mathrm{NP}}|_K}{\Delta m_K / 2} = \text{ratio}
\end{equation}

Budget $= \Delta m_K/2 = 1.742\times10^{-15}$~GeV.

The constraint is that $|M_{12}^{\mathrm{NP}}|$ should not exceed
$|M_{12}^{\mathrm{exp}}| = \Delta m_K/2$.  This is conservative because the SM
contribution to $\Delta M_K$ is dominated by poorly-known long-distance effects,
so the entire experimental value is treated as a budget for NP (rather than
requiring $|M_{12}^{\mathrm{NP}}| < |M_{12}^{\mathrm{exp}} -
M_{12}^{\mathrm{SM}}|$, which would need a reliable SM prediction).
\textbf{Passes if ratio $\le 1.0$.}

\subsection{15c: $B_d$, $B_s$, $D^0$ mixing (mass differences)}
\label{sec:step15c}

For each system, $M_{12}^{\mathrm{NP}}$ is computed using the system-specific
hadronic parameters.  The budget definitions are:

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
System & Budget formula & Numerical value \\
\midrule
$B_d$ & $\max(\Delta m^{\mathrm{exp}}/2,\;
  |\Delta m^{\mathrm{exp}} - \Delta m^{\mathrm{SM}}|/2)$
  & $\max(1.667\times10^{-13},\;1.33\times10^{-14})$ \\
  & & $= \mathbf{1.667\times10^{-13}}$~GeV \\[4pt]
$B_s$ & $\max(\Delta m^{\mathrm{exp}}/2,\;
  |\Delta m^{\mathrm{exp}} - \Delta m^{\mathrm{SM}}|/2)$
  & $\max(5.844\times10^{-12},\;6.0\times10^{-15})$ \\
  & & $= \mathbf{5.844\times10^{-12}}$~GeV \\[4pt]
$D^0$ & $\Delta m^{\mathrm{exp}}/2$ (SM long-distance dominated)
  & $\mathbf{3.125\times10^{-15}}$~GeV \\
\bottomrule
\end{tabular}
\end{table}

The $\max(\ldots)$ formula is conservative: it uses whichever is larger ---
half the experimental value, or half the experiment--SM difference.  For $B_d$
and $B_s$, the experimental value dominates (the SM predictions are close to
experiment).

Ratio to bound: $|M_{12}^{\mathrm{NP}}| / \text{budget}$.
\textbf{Passes if ratio $\le 1.0$.}

\subsection{15d: Experimental inputs for budgets}
\label{sec:step15d}

\begin{table}[h]
\centering
\begin{tabular}{@{}lll@{}}
\toprule
System & $\Delta m^{\mathrm{exp}}$ & $\Delta m^{\mathrm{SM}}$ \\
\midrule
$K$ & $3.484\times10^{-15}$~GeV & (enters only via $\epsilon_K$) \\
$B_d$ & $3.334\times10^{-13}$~GeV & $3.6\times10^{-13}$~GeV (CKMfitter) \\
$B_s$ & $1.1688\times10^{-11}$~GeV & $1.17\times10^{-11}$~GeV (CKMfitter) \\
$D^0$ & $6.25\times10^{-15}$~GeV & Long-distance dominated (HFLAV) \\
\bottomrule
\end{tabular}
\end{table}

\subsection{15e: Overall acceptance}
\label{sec:step15e}

A scan point is \textbf{accepted} if the ratio to bound is $\le 1.0$ for
\textbf{all five} systems simultaneously: $\epsilon_K$, $\Delta M_K$,
$\Delta M_{B_d}$, $\Delta M_{B_s}$, $\Delta M_{D^0}$.

Additionally, the fit must have converged with $\text{fit\_score} \le 0.1$
(meaning the quark masses and CKM are reproduced well enough that the Wilson
coefficients are meaningful).

$\Delta M_K$ was added as a 5th constraint system in the scan pipeline used for
the publication figures; earlier versions used only the other four.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 16: Post-Processing for Figures}
\label{sec:step16}

The raw scan stores results in JSONL format (one JSON object per scan point).
Before plotting, several transformations are applied.

\subsection{16a: Quality filter}
\label{sec:step16a}

Points where the fit did not converge or where $\text{fit\_score} > 0.1$ are
discarded.  A poor fit means the quark masses and CKM were not reproduced, so
the Wilson coefficients are unreliable.

\subsection{16b: Mass-axis convention ($\LamIR \to m_g^{(1)}$)}
\label{sec:step16b}

The scan uses $\Mkk = \LamIR$ ($\xi_{\mathrm{KK}} = 1$) as the propagator mass
in all Wilson coefficient formulas (\hyperref[sec:step12]{Step~12}).  The
physical first KK-gluon mass is larger:
\begin{equation}
  m_g^{(1)} = \xi_{\mathrm{kk}} \cdot \LamIR
\end{equation}
where $\xi_{\mathrm{kk}} = 2.448687$ is the first root of the gauge-sector KK
mass eigenvalue equation with Neumann--Neumann boundary conditions on a warped
interval.

To correctly relabel the axis, we must account for the fact that the scan used
$\LamIR$ (not $m_g^{(1)}$) in the $1/\Mkk^2$ propagator.  Since the Wilson
coefficients scale as $1/\Mkk^2$, a point at $\LamIR$ with ratio~$R$ should
have ratio $R/\xi_{\mathrm{kk}}^2$ when interpreted as being at
$m_g^{(1)} = \xi_{\mathrm{kk}}\cdot\LamIR$:
\begin{align}
  \text{axis\_scale} &= \xi_{\mathrm{kk}} / \xi_{\mathrm{scan}}
    = 2.448687 / 1.0 = 2.448687\,, \\
  \Mkk^{\mathrm{plot}} &= \LamIR \cdot \text{axis\_scale}\,, \\
  \text{ratio}^{\mathrm{plot}} &= \text{ratio}^{\mathrm{stored}} /
    \text{axis\_scale}^2\,.
\end{align}

The net effect: a point that was marginal (ratio $= 1$) in the raw scan becomes
well within bounds (ratio $= 1/\xi_{\mathrm{kk}}^2 \sim 1/6$) after the
correction, because the physical propagator mass is $2.45\times$ larger than
what the scan used.  The exclusion boundary shifts to a lower $\LamIR$ (where
the raw ratio was ${\sim}\,\xi_{\mathrm{kk}}^2 \sim 6$).  In terms of
$m_g^{(1)}$, this lower $\LamIR$ multiplied by $\xi_{\mathrm{kk}}$ partially
compensates, so the boundary $m_g^{(1)}$ is similar to (but not exactly equal
to) the raw-scan $\LamIR$ boundary.

\subsection{16c: Grid aggregation (common best point)}
\label{sec:step16c}

At each unique $(r,\,\Mkk)$ grid point, there are up to 20 different
\texttt{overall\_scale} values (from the scan grid).  The plotter selects the
single \texttt{overall\_scale} that minimizes:
\begin{equation}
  \max\!\bigl(\text{ratio}_{\epsilon_K},\;\text{ratio}_K,\;
    \text{ratio}_{B_d},\;\text{ratio}_{B_s},\;\text{ratio}_{D^0}\bigr)
\end{equation}
across all five systems simultaneously.  All five system ratios are then read
from that same point.

\textbf{Why this matters}: All five contour lines come from one consistent MFV
point at each grid location.  Sweeping \texttt{overall\_scale} at fixed
$(r,\,\LamIR)$ explores different tradeoffs between reproducing the diagonal
quark masses and minimizing off-diagonal FCNCs; picking the best one finds the
most favorable tradeoff.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 17: Figure 1 --- System-by-System Exclusion Boundaries}
\label{sec:step17}

\textbf{What it shows}: Contour lines in the $(r,\,m_g^{(1)})$ plane where
each meson system's $\text{ratio\_to\_bound} = 1$, with green/red shading for
the combined allowed/excluded regions.

\textbf{Construction}: The aggregated data from
\hyperref[sec:step16c]{Step~16c} is interpolated onto a regular grid in
$(\log_{10} r,\;\log_{10} \Mkk)$ space.  For each system, a contour is drawn
at $\text{ratio} = 1$.  The region above all contours is shaded green
(allowed); below is red (excluded).

\textbf{Interpretation}: At a given $r$, any $m_g^{(1)}$ above all contour
lines is allowed by all five meson constraints.  The contour that sits highest
at each $r$ is the binding constraint.  Typically $\epsilon_K$ dominates for
$r \sim 0.1$--$0.5$, and $\Delta M_K$ takes over at large~$r$.

\textbf{Important caveat}: This is a best-case envelope.  At each grid point,
the fitter found the single most favorable Yukawa structure, and the plotter
picked the most favorable \texttt{overall\_scale}.  The contour shows the
lowest $\Mkk$ at which any fitted point survives --- it is an existence bound,
not a statement about typical NMFV behavior.

\textcolor{red}{\textbf{To do:} These figures answer ``can NMFV ever allow
$\Mkk$ this low?''\ via optimization.  The analysis Jackie's note asks for is
different: generate an ensemble of random $O(1)$ NMFV Yukawas in the explicit
$(\alpha_Q,\,\beta_Q,\,\gamma_Q)$ parametrization, keep only points that
reproduce observed quark masses, and histogram the $\Mkk$ values at which
$\mathrm{Im}(C_4^K)$ meets its bound.  That would answer ``what does NMFV
\emph{typically} require?''\ --- both analyses are needed.}

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Step 18: Figure 2 --- $\Mkk$ Lower Bound: 2007 vs Modern}
\label{sec:step18}

\textbf{What it shows}: For each $r$ value, the minimum $m_g^{(1)}$ among all
accepted points, comparing modern (2024+) constraints to rescaled 2007-era
constraints.

\textbf{Construction}:
\begin{enumerate}
  \item For each unique $r$ value in the scan grid, collect all
    $(\Mkk,\;\text{ratios})$ pairs across all $\LamIR$ and
    \texttt{overall\_scale} values.
  \item For the \textbf{modern} bound: check each pair's
    $\max(\text{all 5 ratios}) \le 1$.  Record the smallest $\Mkk$ among
    passing points.  If no point passes at any $\Mkk$, mark this $r$ as fully
    excluded.
  \item For the \textbf{2007} bound: multiply each system's ratio by the
    corresponding \texttt{BOUND\_RATIO} factor (which makes the constraint
    looser, since modern bounds are tighter).  Then apply the same acceptance
    check and find the minimum passing $\Mkk$.
  \item Plot both curves as a function of~$r$.
  \item Shade the region between the two curves to visualize the improvement
    since 2007.
\end{enumerate}

\textbf{Note on consistency with Figure~1}: Figure~2 checks
$\max(\text{all 5 ratios}) \le 1$ per scan row, so it does not mix different
\texttt{overall\_scale} values across systems.  The difference from Figure~1 is
that Figure~2 does not first collapse each $(r,\,\Mkk)$ to a single best-scale
representative; it considers every stored row individually.

\textbf{2007 rescaling factors} (\texttt{BOUND\_RATIOS}):

These factors represent the ratio of the modern experimental bound to the
2007-era bound.  Multiplying the modern ratio by this factor gives the
2007-equivalent ratio:

\begin{table}[h]
\centering
\begin{tabular}{@{}llll@{}}
\toprule
System & Factor & Origin & Interpretation \\
\midrule
$\epsilon_K$ & 0.70 & Tighter lattice + CKM inputs & Modern 30\% tighter \\
$\Delta M_K$ & 0.70 & Same improvement as $\epsilon_K$ & Modern 30\% tighter \\
$\Delta M_{B_d}$ & 0.67 & Better lattice + exp & Modern 33\% tighter \\
$\Delta M_{B_s}$ & 0.37 & Huge improvement in $B_s$ measurements &
  Modern 63\% tighter \\
$\Delta M_{D^0}$ & 0.106 & $D^0$ mixing barely measured in 2007 &
  Modern ${\sim}\,90\%$ tighter \\
\bottomrule
\end{tabular}
\end{table}

Example: if a point has modern $B_s$ ratio $= 0.9$ (barely passing), its 2007
equivalent is $0.9\times0.37 = 0.33$ (easily passing).  So the modern
constraint is much more stringent for $B_s$ mixing.

\textbf{Interpretation}: The purple shaded band between the two curves shows
how much constraints have tightened since 2007.  At small $r$ (where
$\epsilon_K$ dominates), the improvement is modest (${\sim}\,30\%$).  At
large~$r$ (where $B_s$ and $D^0$ dominate), the improvement is dramatic.

\bigskip
\hrule
\bigskip

%% ====================================================================
\section{Summary of Key Assumptions}
\label{sec:summary}

\begin{enumerate}
  \item \textbf{Geometry}: Slice of $\mathrm{AdS}_5$ with
    $k = \Mpl = 1.2209\times10^{19}$~GeV, Higgs on the IR brane, no
    backreaction.

  \item \textbf{Yukawa parametrization}: SVD with right rotations fixed to
    identity.  This forces $C_u$, $C_d$ to be diagonal.  Only $C_Q$ has
    off-diagonal structure.  The full Yukawa space is not explored.

  \item \textbf{Bulk mass construction}:
    $C_Q = r\,Y_u Y_u^\dagger + Y_d Y_d^\dagger$ with no explicit
    $\alpha_Q$ identity term.  The BulkMassMap (sigmoid mapping eigenvalues
    to $c \in [0.30,\,0.72]$) substitutes for $\alpha_Q$ nonlinearly.

  \item \textbf{Fit procedure}: 14-parameter Trust Region Reflective (TRF) optimization
    with max 120 evaluations.  Finds the best Yukawa structure at each scan
    point, not a representative sample.  Each point starts from the same
    deterministic seed.

  \item \textbf{KK-gluon coupling}: $\gs = 3.0$ (one-loop enhanced, Gedalia
    et al.\ 2009).  Enters as $\gs^2$ in all Wilson coefficients.  The
    tree-level estimate is $\gs \sim 6$; the perturbative QCD value is
    $g_s \sim 1$.  This single parameter changes all bounds by a factor of up
    to~36.

  \item \textbf{Matching}: Tree-level only, at scale $\Mkk = \LamIR$.  Only
    the first KK-gluon mode.  No loop corrections.

  \item \textbf{QCD running}: LO anomalous dimensions for $\Delta F{=}2$
    operator mixing, one-loop $\alpha_s$ running with threshold matching at
    $m_b$ and $m_c$.  Hadronic evaluation scale
    $\mu_{\mathrm{had}} = 2$~GeV.

  \item \textbf{Hadronic inputs}: FLAG 2024 / PDG 2024 for bag parameters and
    decay constants.  $D^0$ bag parameters $B_4$, $B_5$ estimated at~$1.0$.
    Kaon $B_4$, $B_5$ from ETM 2013.

  \item \textbf{Acceptance budgets}: $\epsilon_K$ uses the exp--SM gap
    $(4.18\times10^{-4})$.  $\Delta M_K$ uses half the experimental value.
    $B_d$, $B_s$ use $\max(\text{exp}/2,\;|\text{exp}-\text{SM}|/2)$.
    $D^0$ uses $\text{exp}/2$.

  \item \textbf{Axis convention}: Publication figures use
    $m_g^{(1)} = 2.4487\,\LamIR$ (first gauge KK eigenvalue with NN BCs,
    from Bessel root) with a corresponding $1/\xi_{\mathrm{kk}}^2$ ratio
    correction.

  \item \textbf{Best-case envelope}: Both figures show the most favorable
    point at each $(r,\,\Mkk)$.  This is an existence bound (``NMFV can allow
    $\Mkk$ this low''), not a characterization of typical NMFV behavior.
    A sampling/histogram analysis is needed for the latter.

  \item \textbf{Target quark masses}: The fit targets
    ($m_u = 1.3$~MeV, $m_c = 620$~MeV, $m_t = 172$~GeV, $m_d = 2.8$~MeV,
    $m_s = 57$~MeV, $m_b = 2.86$~GeV) are repo-owned values, not standard
    PDG pole or $\overline{\mathrm{MS}}$ masses at a canonical scale.  They
    are chosen for scan stability.
\end{enumerate}

\end{document}
